### 2015-04-23 paper.tex
Adding paper and figures

\documentclass[10pt]{article}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{fancyhdr}
\usepackage{amssymb,amsmath}
\usepackage{nicefrac}
\usepackage[usenames,dvipsnames]{color}
\usepackage[colorlinks,citecolor=RedViolet,urlcolor=blue]{hyperref}
\usepackage{doi}
\usepackage{setspace}
\usepackage[paperwidth=8.5in, paperheight=11in,top=2in, bottom=1.5in, left=1.2in, right=1.2in]{geometry}

\usepackage[authoryear,square]{natbib}
\pagestyle{fancy}
\fancyhead[R]{Veibell \thepage}
\fancyhead[L]{}

\begin{document}
\title{Geomagnetic Storm Precursors}
\author{Victoir Veibell\footnote{vveibell@gmu.edu}}
\maketitle
\hrule
\setlength{\parskip}{3ex}
\renewcommand{\labelitemi}{$-$}

\section{Prior work}
\citep{Takahashi} state that spikes in the Disturbance Storm Time (DST) index coincide with with significant changes in equatorial mass density. They look at five specific storms over a 20 day period with evidence that two had density spikes after the DST drop, two had density spikes before the drop, and one showed no effect.

\section{Our work}
Our work takes the datasets from \citep{Denton} and \citep{Reconstruction}, uses a mean interpolation to take the mass density parameter from a highly non-uniform 15 minute grid of the former to the contiguous one hour grid of the latter, and looks for storms based on the definition of storm periods provided by \citep{Takahashi}, namely when $DST<-50nT$. The former has a time coverage of 1980-1991, but covered by different satellites in different years (sometimes with overlap), and the latter data set covers 1972-2013. By then looking at an hourly average of variables from 24 hours before storm onset to 48 hours after, trends in storms can be discerned.

\bibliographystyle{vplainnat}

\bibliography{reportbib}

\end{document}

### 2015-04-23 Density.m

@@ -143,12 +143,22 @@ OverlayDBz=((250-150).*(DBz-min(DBz)))./(max(DBz)-min(DBz)) + 150;
 OverlayDBS=((250-150).*(DBS-min(DBS)))./(max(DBS)-min(DBS)) + 150;
 
 %MassDensitySpline=interp1(DentonTime,MassDensity,OMNITime,'linear');
-MassDensitySpline=interptest(DentonTime,MassDensity,OMNITime,(OMNITime(2)-OMNITime(1))/2);
-MassDensitySpline=MassDensitySpline';
+if(exist('InterpedVals.mat','file'))
+    load('InterpedVals')
+else
+    MassDensitySpline=interptest(DentonTime,MassDensity,OMNITime,(OMNITime(2)-OMNITime(1))/2);
+    F107Spline=interptest(DentonTime,F107,OMNITime,(OMNITime(2)-OMNITime(1))/2);
+    MassDensitySpline=MassDensitySpline';
+    F107Spline=F107Spline';
+    save('InterpedVals','MassDensitySpline','F107Spline');
+end
+
+FILLED=[FILLED F107Spline];
+headers{end+1}='F107';
 
  
 %Find storm with enough data to analyze
-%storms=diff([0 (FILLED(:,15)<-30)' 0]);
+storms=diff([0 (FILLED(:,15)<-50)' 0]);
 MassDensityNanSpline=interp1(OMNITime(~isnan(MassDensitySpline)),MassDensitySpline(~isnan(MassDensitySpline)),OMNITime,'linear');
 storms=diff([0 (MassDensityNanSpline>40)' 0]);
 starti=find(storms>0);
@@ -157,8 +167,13 @@ duration=endi-starti+1;
 stormi=1;
 AVMat=[];
 AVMDMat=[];
-
-starti(1)=[]; endi(1)=[]; starti(end)=[]; endi(end)=[];
+maxwidth=48;
+while(starti(1)-maxwidth<1)
+    starti(1)=[]; endi(1)=[]; 
+end
+while(endi(end)+maxwidth>length(MassDensitySpline))
+    starti(end)=[]; endi(end)=[];
+end
 for i=1:length(starti)
 
    datanum=sum(~isnan(MassDensitySpline(starti(i):endi(i))));
@@ -174,10 +189,10 @@ end
 AVs=nanmean(AVMat,1);
 AVMDs=nanmean(AVMDMat);
 AVnnans=sum(~isnan(AVMDMat));
-for i=1:length(AVs)
[…]

### 2015-05-27 paper.tex
Edits to paper.tex

@@
-\documentclass[10pt]{article}
+\documentclass[10pt,twocolumn]{article}
 \usepackage{graphicx}
@@
 \usepackage{setspace}
-\usepackage[paperwidth=8.5in, paperheight=11in,top=2in, bottom=1.5in, left=1.2in, right=1.2in]{geometry}
+\usepackage[paperwidth=8.5in, paperheight=11in,top=1in, bottom=1in, left=1in, right=1in]{geometry}
+\usepackage[compact]{titlesec}
 
@@
 \begin{document}
-\title{Geomagnetic Storm Precursors}
+\title{Relationship solar wind, $D_{st}$, and plasmasphere mass density on on-hour time scales}
 \author{Victoir Veibell\footnote{vveibell@gmu.edu}}
+\author{R.S. Weigel\footnote{rweigel@gmu.edu}}
+
+\setlength{\parskip}{3ex}
+\renewcommand{\labelitemi}{$-$}
+\titlespacing{\section}{0pc}{0.2pc}{-1pc}
+\titlespacing{\subsection}{0pc}{0.1pc}{-1pc}
+\titleformat*{\section}{\normalsize\bfseries}
+\titleformat*{\subsection}{\small\bfseries}
+
+\twocolumn[
+  \begin{@twocolumnfalse}
 \maketitle
 \hrule
-\setlength{\parskip}{3ex}
-\renewcommand{\labelitemi}{$-$}
+\begin{abstract}
+We consider solar wind conditions surrounding time intervals of large negative excursions of the $D_{st}$ index and large positive excursions of plasmaspheric mass density.
+Consistent with previous results, that a sudden decrease in $D_{st}$ is associated with an increase in equatorial mass density.
+We find ...
+\vspace{2em}
+\end{abstract}
+ \end{@twocolumnfalse}
+  ]
 
-\section{Prior work}
-\citep{Takahashi} state that spikes in the Disturbance Storm Time (DST) index coincide with with significant changes in equatorial mass density.
-They look at five specific storms over a 20 day period with evidence that two had density spikes after the DST drop, two had density spikes before the drop, and one showed no effect.
+% while adding a level of depth and specification to the applicability of their results.
+It compares data at 1-hour averages to data at 1-day averages, and briefly to data at 27-day averages to examine if the trend holds at varying time scales and finds that it does, so long as the data is pre-processed to linearly remove a large time scale $F_{10.7}$ dependence.
 
-\section{Our work}
-Our work takes the datasets from \citep{Denton} and \citep{Reconstruction}, uses a mean interpolation to take the mass density parameter from a highly non-uniform 15 minute grid of the former to the contiguous one hour grid of the latter, and looks for storms based on the definition of storm periods provided by \citep{Takahashi}, namely when $DST<-50nT$.
+\section{Introduction}
+% try is colloqual.  
+% hope is colloqual.
+% intends is colloqual.
+
+%This paper intends to investigate solar wind and magnetospheric conditions immediately before geomagnetic storm onset to determine trends and useful correlations, specifically looking at the effects on equatorial mass density ($\rho_{eq}$).
+
+In this paper we test the relationship of short timescale effects on mass density from $D_{ST}$, $F_{10.7}$, and $B_Z$, in comparison to the long time scales presented in \cite{Takahashi2010,Takahashi2006}, as well as looking at other preconditioning factors by analysis of hourly data within a day surrounding storm onsets.
+
+%Keep the following for now.  Not sure where we will put it.
+%We also hope that by looking at all possible storms under less stringent qualifications, instead of hand selected storms with specific selection criteria, our results will be more generalizable and less prone to bias.
+
+%I think this opening is cliche by now. (Although I am guilty of using it.)
+%Storms consisting of high energy particles in the magnetosphere have the capacity to damage satellites and ground-based electrical systems.
+Learning how they behave and what sort of preconditioning goes into making stronger storms helps to forecast storms and mitigate damage caused.
+
+% does't -> does not.  Contractions are colloq.
+\cite{Takahashi2006} considered the relaptionship between geomagnetic activity and average ion mass ($M$).
+A scatter plot of log$_{10}(M)$ versus $-D_{st}$ showed an increasing trend.
+The scatter plot of log$_{10}(M)$ versus $K_p$ had near zero correlation, but a positive trend was found when log$_{10}(M)$ versus 1.5-day averaged $K_p$ was considered, and this trend persisted when 3-day averages were used.
+
+% I use ``state'' when I mean ``said, but I don't necessarily agree with some aspect of the analysis''.
+The sentence containing the word ``state'' is usually followed by a sentence starting with ``However''.
+\cite{Takahashi2010} found that spikes in the Disturbance Storm Time ($D_{ST}$) index coincide with with significant changes in $\rho_{eq}$ at an L-shell of 6.8$R_E$.
+For five storms over a 20 day period two had $\rho_{eq}$ spikes after the $D_{ST}$ drop, two had $\rho_{eq}$ spikes before the drop, and one showed little change in $\rho_{eq}$.
+They then show an epoch analysis where $\rho_{eq}$ is seen to spike the day of a $D_{ST}$ drop, using a daily average of 30 minute $\rho_{eq}$ and one hour $D_{ST}$ measurements.
+
+\cite{Lavraud2006} show that storms preceded by a northward interplanetary magnetic field (IMF) tend to have higher plasma density than those preceded by a southward IMF, and suggest an increased geoeffectiveness from a northward IMF and dense plasma sheet.
+
+\cite{Tsurutani1997} show how the density of a corotating interaction region (CIR) shows strong preconditioning for a drop in $D_{ST}$ and spike in magnetic field intensity.
+Assuming a reasonable amount of coupling between that region's density and the plasmaspheric density, this result could be relatable to others focusing on the plasmasphere.
+
+\cite{Denton2006} show how $D_{ST}$ affects the distribution of plasma density along different magnetic latitudes, and specifically along the same field lines as looked at in later papers (6-8$R_E$).
+Though this shows that the trends for density may differ between field lines, it's mentioned mostly as a point for future research as the data used in this paper is already adjusted for one field line, as described by \cite{Takahashi2010}.
+
+\section{Previous Results}
+We will briefly compare our results to other published results to verify our methods and handling of data.
+
+Our work takes the datasets from \cite{Denton} and \cite{Reconstruction}, uses a mean interpolation to take the mass density parameter from a highly non-uniform 15 minute grid of the former to the contiguous one hour grid of the latter, and looks for storms based on the definition of storm periods provided by \cite{Takahashi2010}, namely when $D_{ST}<-50nT$.
 The former has a time coverage of 1980-1991, but covered by different satellites in different years (sometimes with overlap), and the latter data set covers 1972-2013.
-By then looking at an hourly average of variables from 24 hours before storm onset to 48 hours after, trends in storms can be discerned.
+By then looking at an hourly average of variables from 24 hours before storm onset to 48 hours after, short timescale trends can be discerned.
 
+\section{Results}
+
+\subsection{DST Storm}
+Two storm indicators are looked at in this study.
+The first is looking for a drop in DST below the threshhold of $-50nT$ specified in \cite{Takahashi2010}, dubbed the "onset", and then considering the timeframe a storm until $D_{ST}$ passes back above the $-50nT$ threshold.
+This method finds 669 such periods between May 1983 and August 1991 with an average duration of 9 hours and a median duration of 3 hours.
+A subset of longer duration storms will be looked at later.
+Figure \ref{DSTstorm} shows the average values of $B_Z$, $V_{SW}$, $D_{ST}$, $F_{10.7}$, and Mass Density for a period of 24 hours before and 48 hours after a storm onset, as well as a plot of mass density with the found storm times highlighted.
+
+\begin{figure}[htp]
+\centering
+\includegraphics[scale=0.35]{paperfigures/alldata.png}
+\includegraphics[scale=0.35]{paperfigures/massdensitystorms.png}
+\caption{All used data (left) and selected storm times highlighted (right). $\rho_{eq}$ interpolated to 1-hour averages}
+\label{DSTstorm}
+\end{figure}
+
+This figure shows a definite spike in the $Z$ component of the magnetic field, as well as the defined drop in $DST$, but no obvious change in mass density at an hourly timescale.
+This points to an issue with only looking at long-timescale trends between density and $D_{ST}$, and allows for the possibility that other factors are influencing the long term correlation since there's no obvious connection on a short timescale.
+One possibility is that, as suggested in \cite{Takahashi2010}, $F_{10.7}$ plays a significant role in driving long term density values which biases the long term correlation of density and $D_{ST}$.
+
+\subsection{Mass Density Storm}
+Figure \ref{MassStorm} shows this same algorithm, but looking for a rise in mass density over a value of 40$g/cm^3$.
+This results in 130 storms with a mean duration of 32 hours and a median duration of 17 hours, marked in red on the left figure.
+
+\begin{figure}[htp!]
+\centering
+\includegraphics[scale=0.35]{paperfigures/stormavs-dst.png}
+\includegraphics[scale=0.35]{paperfigures/stormavs-mass.png}
+\caption{$D_{ST}<-40nT$ onset, Mass Density $>40 amu/cm^3$}
+\label{MassStorm}
+\end{figure}
+
+This shows that when using all data for mass density derived storms, almost no significant changes can be seen around storm onset.
+
+\section{More specific storms}
+It's hypothesized that progressively picking more specific storm criteria will allow for the possibility of more significant results, at the expense of more bias in the selection process and potentially less overall usefulness of the results.
+That said, the predictability of extreme storms is of definite interest, so an attempt has been made to find some reproducible method of prediction.
+Looking at storms that last longer than 12 hours and storms with an onset threshhold greater than $70g/cm^3$ results in the left and right sides of Figure \ref{Mspec} respectively.
+
+\begin{figure}[htp!]
+\centering
+\includegraphics[scale=0.35]{paperfigures/stormavs-md12.png}
+\includegraphics[scale=0.35]{paperfigures/stormavs-m70.png}
+\caption{Duration $>$ 12 hours, Mass Density $>70 amu/cm^3$}
+\label{Mspec}
+\end{figure}
+
+Neither of these seem to indicate anything too significant, so looking at $D_{ST}$ storms instead to look for something that causes a significant change in Mass Density results in Figure \ref{Dspec}.
+This shows that by either looking only at $D_{ST}$ storms that last longer than an hour (left) or at storms where the onset condition is $D_{ST}<-80nT$, a spike in mass density is seen, but also a definite lack of data availability to the point where that spike may be coming from less than five of the total 143 storms.
+
+\begin{figure}[htp!]
+\centering
+\includegraphics[scale=0.35]{paperfigures/stormavs-dd12.png}
+\includegraphics[scale=0.35]{paperfigures/stormavs-d80.png}
+\caption{$D_{ST}$ Storms $>$ 12 hours, $D_{ST}<-80nT$}
+\label{Dspec}
+\end{figure}
+
+Unforunately there are no storms in this time frame that are longer than 12 hours with $D_{ST}$ minima lower than $-80nT$ that have existing mass density data around onset, so an analysis of this particular relationship can't be made.
+
+\section{F10.7 dependence}
+In an effort to analyze the dependence of mass density on $F_{10.7}$, a few tests were performed.
+\cite{Takahashi2010} mention a strong correlation between the two.
+The long term correlation could be a bias for $D_{ST}$'s effects, so a linear model was created, recreating mass density purely from $F_{10.7}$ in the form of $\rho_{eq}(t)=A*F_{10.7}(t)$.
+This re-created density shows around a 45\% correlation with the actual density, suggesting a strong influence, while doing the same procedure with $DST$ shows only a 20-25\% correlation.
+
+Taking this re-created data set and subtracting it from the original should remove the $F_{10.7}$ dependence from the data, and allow for a less biased analysis of the relationship between $D_{ST}$ and mass density.
+Figure \ref{nof107} shows the stack plot for the reduced $F_{10.7}$, where a more distinct peak after storm onset can be seen.
+It also shows what that removed trend looks like, of the form $\rho_{eq}-\rho_{eq,F_{10.7}}$.
+
+\begin{figure}[htp!]
+\centering
+\includegraphics[scale=0.35]{paperfigures/stormavs-dst-nof107.png}
+\includegraphics[scale=0.35]{paperfigures/f107removed.png}
+\caption{$\rho_{eq}$ with $F_{10.7}$ removed, and Difference from original}
+\label{nof107}
+\end{figure}
+
+Similarly, looking at the 1 day averaged data with and without the $F_{10.7}$ dependence, Figure \ref{nof107day} shows that the results of \cite{Takahashi2010} hold only once the dependence has been removed.
+The 27 day trend couldn't be determined as not enough valid data existed to test it.
+
+\begin{figure}[htp!]
+\centering
+\includegraphics[scale=0.35]{paperfigures/stormavs-dst-day.png}
+\includegraphics[scale=0.35]{paperfigures/stormavs-dst-day-nof107.png}
+\caption{Original $\rho_{eq}$, and with $F_{10.7}$ dependence removed, both at 1-day averages}
+\label{nof107day}
+\end{figure}
+
+\newpage
+\footnotesize
 \bibliographystyle{vplainnat}

### 2015-06-02 paper.tex
Added changes

@@
 \usepackage[compact]{titlesec}
+\usepackage{abstract}
 
@@
 \begin{document}
-\title{Relationship solar wind, $D_{st}$, and plasmasphere mass density on on-hour time scales}
-\author{Victoir Veibell\footnote{vveibell@gmu.edu}}
-\author{R.S. Weigel\footnote{rweigel@gmu.edu}}
+\title{Relationship between solar wind, $D_{st}$, and plasmasphere mass density on on-hour time scales}
+\author{
+Victoir Veibell\footnote{vveibell@gmu.edu}
+\and
+R.S. Weigel\footnote{rweigel@gmu.edu}}
 
@@
 We consider solar wind conditions surrounding time intervals of large negative excursions of the $D_{st}$ index and large positive excursions of plasmaspheric mass density.
-Consistent with previous results, that a sudden decrease in $D_{st}$ is associated with an increase in equatorial mass density.
+Consistent with previous results, a sudden decrease in $D_{st}$ is associated with an increase in equatorial mass density.
 We find ...
@@
 
+\saythanks
 % while adding a level of depth and specification to the applicability of their results.
@@
 %This paper intends to investigate solar wind and magnetospheric conditions immediately before geomagnetic storm onset to determine trends and useful correlations, specifically looking at the effects on equatorial mass density ($\rho_{eq}$).
-
 In this paper we test the relationship of short timescale effects on mass density from $D_{ST}$, $F_{10.7}$, and $B_Z$, in comparison to the long time scales presented in \cite{Takahashi2010,Takahashi2006}, as well as looking at other preconditioning factors by analysis of hourly data within a day surrounding storm onsets.
@@
 
-%I think this opening is cliche by now. (Although I am guilty of using it.)
-%Storms consisting of high energy particles in the magnetosphere have the capacity to damage satellites and ground-based electrical systems.
-Learning how they behave and what sort of preconditioning goes into making stronger storms helps to forecast storms and mitigate damage caused.
-
-% does't -> does not.  Contractions are colloq.
-\cite{Takahashi2006} considered the relaptionship between geomagnetic activity and average ion mass ($M$).
+\cite{Takahashi2006} considered the relationship between geomagnetic activity and average ion mass ($M$).
 A scatter plot of log$_{10}(M)$ versus $-D_{st}$ showed an increasing trend.
@@
 
-% I use ``state'' when I mean ``said, but I don't necessarily agree with some aspect of the analysis''.
-The sentence containing the word ``state'' is usually followed by a sentence starting with ``However''.
 \cite{Takahashi2010} found that spikes in the Disturbance Storm Time ($D_{ST}$) index coincide with with significant changes in $\rho_{eq}$ at an L-shell of 6.8$R_E$.

### 2015-06-02 paper.tex

@@
 \begin{abstract}
-We consider solar wind conditions surrounding time intervals of large negative excursions of the $D_{st}$ index and large positive excursions of plasmaspheric mass density.
-Consistent with previous results, a sudden decrease in $D_{st}$ is associated with an increase in equatorial mass density.
-We find ...
+This paper looks at how various magnetosphere conditions behave around the onset of geomagnetic storms.
+It confirms results from previous papers that a sudden drop in $D_{ST}$ correlates with a spike in equatorial mass density, while adding a level of depth and specification to the applicability of their results.
+It compares data at 1-hour averages to data at 1-day averages, and briefly to data at 27-day averages to examine if the trend holds at varying time scales and finds that it does, so long as the data is pre-processed to linearly remove a large time scale $F_{10.7}$ dependence.
 \vspace{2em}
@@
 
-%This paper intends to investigate solar wind and magnetospheric conditions immediately before geomagnetic storm onset to determine trends and useful correlations, specifically looking at the effects on equatorial mass density ($\rho_{eq}$).
-In this paper we test the relationship of short timescale effects on mass density from $D_{ST}$, $F_{10.7}$, and $B_Z$, in comparison to the long time scales presented in \cite{Takahashi2010,Takahashi2006}, as well as looking at other preconditioning factors by analysis of hourly data within a day surrounding storm onsets.
-
-%Keep the following for now.  Not sure where we will put it.
-%We also hope that by looking at all possible storms under less stringent qualifications, instead of hand selected storms with specific selection criteria, our results will be more generalizable and less prone to bias.
-
-\cite{Takahashi2006} considered the relationship between geomagnetic activity and average ion mass ($M$).
-A scatter plot of log$_{10}(M)$ versus $-D_{st}$ showed an increasing trend.
-The scatter plot of log$_{10}(M)$ versus $K_p$ had near zero correlation, but a positive trend was found when log$_{10}(M)$ versus 1.5-day averaged $K_p$ was considered, and this trend persisted when 3-day averages were used.
-
-\cite{Takahashi2010} found that spikes in the Disturbance Storm Time ($D_{ST}$) index coincide with with significant changes in $\rho_{eq}$ at an L-shell of 6.8$R_E$.
+\cite{Takahashi2010} state that spikes in the Disturbance Storm Time ($D_{ST}$) index coincide with with significant changes in $\rho_{eq}$ at an L-shell of 6.8$R_E$.
 For five storms over a 20 day period two had $\rho_{eq}$ spikes after the $D_{ST}$ drop, two had $\rho_{eq}$ spikes before the drop, and one showed little change in $\rho_{eq}$.
 They then show an epoch analysis where $\rho_{eq}$ is seen to spike the day of a $D_{ST}$ drop, using a daily average of 30 minute $\rho_{eq}$ and one hour $D_{ST}$ measurements.
+
+The prior paper, \cite{Takahashi2006}, show how trends in storm dependence on mass/density only appear in longer timescales.
+Looking at $Kp$ vs mass ($amu$) in the range of 6 to 7 $R_E$, a trend shows up in the 1.5 day averages that doesn't appear in the 3 hour averages.
 

### 2015-06-03 paper.tex
Edits to text; changes for figures in comments

@@
 \begin{document}
-\title{Relationship between solar wind, $D_{st}$, and plasmasphere mass density on on-hour time scales}
+\title{Relationship between solar wind, $D_{st}$, and plasmasphere mass density on one-hour time scales}
 \author{
@@
 This paper looks at how various magnetosphere conditions behave around the onset of geomagnetic storms.
-It confirms results from previous papers that a sudden drop in $D_{ST}$ correlates with a spike in equatorial mass density, while adding a level of depth and specification to the applicability of their results.
+It confirms results from previous papers that a sudden drop in $D_{st}$ correlates with a spike in equatorial mass density, while adding a level of depth and specification to the applicability of their results.
 It compares data at 1-hour averages to data at 1-day averages, and briefly to data at 27-day averages to examine if the trend holds at varying time scales and finds that it does, so long as the data is pre-processed to linearly remove a large time scale $F_{10.7}$ dependence.
+By then looking at an hourly average of variables from 24 hours before storm onset to 48 hours after, short timescale trends can be discerned.
+
 \vspace{2em}
@@
 
-\cite{Takahashi2010} state that spikes in the Disturbance Storm Time ($D_{ST}$) index coincide with with significant changes in $\rho_{eq}$ at an L-shell of 6.8$R_E$.
-For five storms over a 20 day period two had $\rho_{eq}$ spikes after the $D_{ST}$ drop, two had $\rho_{eq}$ spikes before the drop, and one showed little change in $\rho_{eq}$.
-They then show an epoch analysis where $\rho_{eq}$ is seen to spike the day of a $D_{ST}$ drop, using a daily average of 30 minute $\rho_{eq}$ and one hour $D_{ST}$ measurements.
+\cite{Takahashi2006}, show how trends in storm dependence on mass/density only appear in longer timescales.
+Looking at $K_p$ vs mass ($amu$) in the range of 6 to 7 $R_E$, a trend shows up in the 1.5 day averages that doesn't appear in the 3 hour averages.
 
-The prior paper, \cite{Takahashi2006}, show how trends in storm dependence on mass/density only appear in longer timescales.
-Looking at $Kp$ vs mass ($amu$) in the range of 6 to 7 $R_E$, a trend shows up in the 1.5 day averages that doesn't appear in the 3 hour averages.
+\cite{Denton2006} show how $D_{st}$ affects the distribution of plasma density along different magnetic latitudes, and specifically along the same field lines as looked at in later papers (6-8$R_E$).
+Though this shows that the trends for density may differ between field lines, it's mentioned mostly as a point for future research as the data used in this paper is already adjusted for one field line, as described by \cite{Takahashi2010}.
 
-\cite{Lavraud2006} show that storms preceded by a northward interplanetary magnetic field (IMF) tend to have higher plasma density than those preceded by a southward IMF, and suggest an increased geoeffectiveness from a northward IMF and dense plasma sheet.
+\cite{Yao2008} looks at the differences in how $D_{st}$ correlates with number density for different ions in different regions (ring current and plasma sheet), but still finds a general correlation during each of the four storms selected.
 
-\cite{Tsurutani1997} show how the density of a corotating interaction region (CIR) shows strong preconditioning for a drop in $D_{ST}$ and spike in magnetic field intensity.
+\cite{Takahashi2010} state that spikes in the Disturbance Storm Time ($D_{st}$) index coincide with with significant changes in $\rho_{eq}$ at an L-shell of 6.8$R_E$.
+For five storms over a 20 day period two had $\rho_{eq}$ spikes after the $D_{st}$ drop, two had $\rho_{eq}$ spikes before the drop, and one showed little change in $\rho_{eq}$.
+They then show an epoch analysis where $\rho_{eq}$ is seen to spike the day of a $D_{st}$ drop, using a daily average of 30 minute $\rho_{eq}$ and one hour $D_{st}$ measurements.
+
+%\cite{Lavraud2006} show that storms preceded by a northward interplanetary magnetic field (IMF) tend to have higher plasma density than those preceded by a southward IMF, and suggest an increased geoeffectiveness from a northward IMF and dense plasma sheet.
+
+%\cite{Tsurutani1997} show how the density of a corotating interaction region (CIR) shows strong preconditioning for a drop in $D_{st}$ and spike in magnetic field intensity.
 Assuming a reasonable amount of coupling between that region's density and the plasmaspheric density, this result could be relatable to others focusing on the plasmasphere.
 
-\cite{Denton2006} show how $D_{ST}$ affects the distribution of plasma density along different magnetic latitudes, and specifically along the same field lines as looked at in later papers (6-8$R_E$).
-Though this shows that the trends for density may differ between field lines, it's mentioned mostly as a point for future research as the data used in this paper is already adjusted for one field line, as described by \cite{Takahashi2010}.
+\section{Data}
 
-\section{Previous Results}
-We will briefly compare our results to other published results to verify our methods and handling of data.
+For solar wind data, we use the \cite{Reconstruction}, which has a time coverage of 1972-2013.
 
-Our work takes the datasets from \cite{Denton} and \cite{Reconstruction}, uses a mean interpolation to take the mass density parameter from a highly non-uniform 15 minute grid of the former to the contiguous one hour grid of the latter, and looks for storms based on the definition of storm periods provided by \cite{Takahashi2010}, namely when $D_{ST}<-50nT$.
-The former has a time coverage of 1980-1991, but covered by different satellites in different years (sometimes with overlap), and the latter data set covers 1972-2013.
-By then looking at an hourly average of variables from 24 hours before storm onset to 48 hours after, short timescale trends can be discerned.
+Mass density data are from \cite{Denton}, which has a time coverage of 1980-1991 and is on a 15-minute time grid with many gaps.
+A mean interpolation method was used to one-hour grid of the solar wind averages.
+GIVE MORE DETAILS ABOUT THIS.
+NEED ENOUGH INFORMATION TO BE ABLE TO REPRODUCE RESULTS GIVEN ONLY TWO DATA SETS.
+
+Figure~\label{AllData} shows values of solar wind averages and mass density used in this study.
 
@@
 
-\subsection{DST Storm}
+We will briefly compare our results to other published results to verify our methods and handling of data.
+
+\subsection{D$_{st}$ Events}
 Two storm indicators are looked at in this study.
-The first is looking for a drop in DST below the threshhold of $-50nT$ specified in \cite{Takahashi2010}, dubbed the "onset", and then considering the timeframe a storm until $D_{ST}$ passes back above the $-50nT$ threshold.
+The first is looking for a drop in DST below the threshhold of $-50nT$ specified in \cite{Takahashi2010}, dubbed the "onset", and then considering the timeframe a storm until $D_{st}$ passes back above the $-50nT$ threshold.
 This method finds 669 such periods between May 1983 and August 1991 with an average duration of 9 hours and a median duration of 3 hours.
 A subset of longer duration storms will be looked at later.
-Figure \ref{DSTstorm} shows the average values of $B_Z$, $V_{SW}$, $D_{ST}$, $F_{10.7}$, and Mass Density for a period of 24 hours before and 48 hours after a storm onset, as well as a plot of mass density with the found storm times highlighted.
-
-\begin{figure}[htp]
-\centering
-\includegraphics[scale=0.35]{paperfigures/alldata.png}
-\includegraphics[scale=0.35]{paperfigures/massdensitystorms.png}
-\caption{All used data (left) and selected storm times highlighted (right). $\rho_{eq}$ interpolated to 1-hour averages}
-\label{DSTstorm}
-\end{figure}
+Figure \ref{AllData} shows the average values of $B_Z$, $V_{SW}$, $D_{st}$, $F_{10.7}$, and Mass Density for a period of 24 hours before and 48 hours after a storm onsppet, as well as a plot of mass density with the found storm times highlighted.
 
 This figure shows a definite spike in the $Z$ component of the magnetic field, as well as the defined drop in $DST$, but no obvious change in mass density at an hourly timescale.
-This points to an issue with only looking at long-timescale trends between density and $D_{ST}$, and allows for the possibility that other factors are influencing the long term correlation since there's no obvious connection on a short timescale.
-One possibility is that, as suggested in \cite{Takahashi2010}, $F_{10.7}$ plays a significant role in driving long term density values which biases the long term correlation of density and $D_{ST}$.
+This points to an issue with only looking at long-timescale trends between density and $D_{st}$, and allows for the possibility that other factors are influencing the long term correlation since there's no obvious connection on a short timescale.
+One possibility is that, as suggested in \cite{Takahashi2010}, $F_{10.7}$ plays a significant role in driving long term density values which biases the long term correlation of density and $D_{st}$.
 
-\subsection{Mass Density Storm}
+\subsection{Mass Density Events}
 Figure \ref{MassStorm} shows this same algorithm, but looking for a rise in mass density over a value of 40$g/cm^3$.
 This results in 130 storms with a mean duration of 32 hours and a median duration of 17 hours, marked in red on the left figure.
-
-\begin{figure}[htp!]
-\centering
-\includegraphics[scale=0.35]{paperfigures/stormavs-dst.png}
-\includegraphics[scale=0.35]{paperfigures/stormavs-mass.png}
-\caption{$D_{ST}<-40nT$ onset, Mass Density $>40 amu/cm^3$}
-\label{MassStorm}
-\end{figure}
 
@@
 
-\begin{figure}[htp!]
-\centering
-\includegraphics[scale=0.35]{paperfigures/stormavs-md12.png}
-\includegraphics[scale=0.35]{paperfigures/stormavs-m70.png}
-\caption{Duration $>$ 12 hours, Mass Density $>70 amu/cm^3$}
-\label{Mspec}
-\end{figure}
+Neither of these seem to indicate anything too significant, so looking at $D_{st}$ storms instead to look for something that causes a significant change in Mass Density results in Figure \ref{Dspec}.
+This shows that by either looking only at $D_{st}$ storms that last longer than an hour (left) or at storms where the onset condition is $D_{st}<-80nT$, a spike in mass density is seen, but also a definite lack of data availability to the point where that spike may be coming from less than five of the total 143 storms.
 
-Neither of these seem to indicate anything too significant, so looking at $D_{ST}$ storms instead to look for something that causes a significant change in Mass Density results in Figure \ref{Dspec}.
-This shows that by either looking only at $D_{ST}$ storms that last longer than an hour (left) or at storms where the onset condition is $D_{ST}<-80nT$, a spike in mass density is seen, but also a definite lack of data availability to the point where that spike may be coming from less than five of the total 143 storms.
+Unforunately there are no storms in this time frame that are longer than 12 hours with $D_{st}$ minima lower than $-80nT$ that have existing mass density data around onset, so an analysis of this particular relationship can't be made.
 
-\begin{figure}[htp!]
-\centering
-\includegraphics[scale=0.35]{paperfigures/stormavs-dd12.png}
-\includegraphics[scale=0.35]{paperfigures/stormavs-d80.png}
-\caption{$D_{ST}$ Storms $>$ 12 hours, $D_{ST}<-80nT$}
-\label{Dspec}
-\end{figure}
+\subsection{Change in $\rho_{eq}$}
+If instead of looking for storms based on a threshold of $\rho_{eq}$, we instead look for a certain amount of change in $\rho_{eq}$ as the basis for storm onset, we get Figure \ref{rhochange}.
 
-Unforunately there are no storms in this time frame that are longer than 12 hours with $D_{ST}$ minima lower than $-80nT$ that have existing mass density data around onset, so an analysis of this particular relationship can't be made.
+Both raw change and percent change were done in case of bias towards high or low $\rho_{eq}$ periods, respectively.
+This shows a distinct lack of correlation in either case to a change in $D_{st}$.
+The percent change in $\rho_{eq}$ does, however, seem to be preconditioned by changes in $B_z$ and $F_{10.7}$.
 
 \section{F10.7 dependence}
-In an effort to analyze the dependence of mass density on $F_{10.7}$, a few tests were performed.
+In an effort to analyze the dependence of $\rho_{eq}$ on $F_{10.7}$, a few tests were performed.
 \cite{Takahashi2010} mention a strong correlation between the two.
-The long term correlation could be a bias for $D_{ST}$'s effects, so a linear model was created, recreating mass density purely from $F_{10.7}$ in the form of $\rho_{eq}(t)=A*F_{10.7}(t)$.
-This re-created density shows around a 45\% correlation with the actual density, suggesting a strong influence, while doing the same procedure with $DST$ shows only a 20-25\% correlation.
+The long term correlation could be a bias for $D_{st}$'s effects, so a linear model was created, recreating mass density purely from $F_{10.7}$ in the form of $\rho_{eq}(t)=A*F_{10.7}(t)$.
+This re-created $\rho_{eq}$ shows around a 45\% correlation with the actual $\rho_{eq}$, suggesting a strong influence, while doing the same procedure with $DST$ shows only a 20-25\% correlation.
 
-Taking this re-created data set and subtracting it from the original should remove the $F_{10.7}$ dependence from the data, and allow for a less biased analysis of the relationship between $D_{ST}$ and mass density.
+Taking this re-created data set and subtracting it from the original should remove the $F_{10.7}$ dependence from the data, and allow for a less biased analysis of the relationship between $D_{st}$ and $\rho_{eq}$.
 Figure \ref{nof107} shows the stack plot for the reduced $F_{10.7}$, where a more distinct peak after storm onset can be seen.
@@
 
-\begin{figure}[htp!]
-\centering
-\includegraphics[scale=0.35]{paperfigures/stormavs-dst-nof107.png}
-\includegraphics[scale=0.35]{paperfigures/f107removed.png}
-\caption{$\rho_{eq}$ with $F_{10.7}$ removed, and Difference from original}
-\label{nof107}
-\end{figure}
-
 Similarly, looking at the 1 day averaged data with and without the $F_{10.7}$ dependence, Figure \ref{nof107day} shows that the results of \cite{Takahashi2010} hold only once the dependence has been removed.
 The 27 day trend couldn't be determined as not enough valid data existed to test it.
-
-\begin{figure}[htp!]
-\centering
-\includegraphics[scale=0.35]{paperfigures/stormavs-dst-day.png}
-\includegraphics[scale=0.35]{paperfigures/stormavs-dst-day-nof107.png}
-\caption{Original $\rho_{eq}$, and with $F_{10.7}$ dependence removed, both at 1-day averages}
-\label{nof107day}
-\end{figure}
 
@@
 
+\section{Figures}
+
+\begin{figure}[htp]
+\centering
+\includegraphics[scale=0.7]{paperfigures/alldata.eps}
+\caption{Overview of data used in this study.
+The top four panels are from \cite{Reconstruction} and the bottom panel is based on \cite{Denton} after interpolation and averaging described in the text.}
+\label{AllData}
+\end{figure}
+\clearpage
+
+% Remove title from both figures.  D_ST -> D_st Bz -> B_z in labels.  Change non-nan data points to ``# of values''.
+% Change x-label to be ``Time from start of event (hr)'' and put vertical lines in each panel at t = 0 (somewhere I have a code called vertline.m)
+\begin{figure}[htp]
+\centering
+(a)
+\includegraphics[scale=0.7]{paperfigures/massdensitystorms.eps}
+(b)
+\includegraphics[scale=0.7]{paperfigures/dststorms.eps}
+\caption{Averages around time of (a) 669 $\rho_{eq}$ and (b) 130 $D_{st}$ events along with thresholds used to define an event.
+The number of values used in the averages for mass density is shown in the bottom panel (a) and (b).}
+\label{DSTstorm}
+\end{figure}
+\clearpage
+
+\begin{figure}[htp!]
+\centering
+(a)
+\includegraphics[scale=0.7]{paperfigures/stormavs-dst.png}
+(b)
+\includegraphics[scale=0.7]{paperfigures/stormavs-mass.png}
+\caption{(a) Average of solar wind and near-Earth measurements around the time D_${st}$ crossed below -40~nT onset.
+(b) Same as (a) except around time intervals where mass density crossed above $40 amu/cm^3$.
+The bottom panel shows the number of mass density data points that were used for the average.}
+\label{MassStorm}
+\end{figure}
+\clearpage
+
+\begin{figure}[htp!]
+\centering
+\includegraphics[scale=0.7]{paperfigures/stormavs-md12.png}
+\includegraphics[scale=0.7]{paperfigures/stormavs-m70.png}
+\caption{(a) Same as \ref{fig:MassStorm}(a) except with constraint that D$_{st}$ stayed below -40~nT for at least 12~hours.
+(b) Same as \ref{fig:MassStorm}(b) except for constrain that mass density crossed above $70 amu/cm^3$.}
+\label{Mspec}
+\end{figure}
+\clearpage
+
+\begin{figure}[htp!]
+\centering
+\includegraphics[scale=0.7]{paperfigures/stormavs-dd12.png}
+\includegraphics[scale=0.7]{paperfigures/stormavs-d80.png}
+\caption{$D_{st}$ Storms $>$ 12 hours, $D_{st}<-80nT$}
+\label{Dspec}
+\end{figure}
+\clearpage
+
+\begin{figure}[htp!]
+\centering
+\includegraphics[scale=0.7]{paperfigures/stormavs-diffden-10amu.png}
+\includegraphics[scale=0.7]{paperfigures/stormavs-diffden-30percent.png}
+\caption{diff($\rho_{eq}$) $>$ 20$\frac{amu}{hour}$, diff($\rho_{eq}$) $>$ 30$\frac{\%}{hour}$}
+\label{rhochange}
+\end{figure}
+\clearpage
+
+\begin{figure}[htp!]
+\centering
+\includegraphics[scale=0.7]{paperfigures/stormavs-dst-nof107.png}
+\includegraphics[scale=0.7]{paperfigures/f107removed.png}
+\caption{$\rho_{eq}$ with $F_{10.7}$ removed, and Difference from original}
+\label{nof107}
+\end{figure}
+\clearpage
+
+\begin{figure}[htp!]
+\centering
+\includegraphics[scale=0.7]{paperfigures/stormavs-dst-day.png}
+\includegraphics[scale=0.7]{paperfigures/stormavs-dst-day-nof107.png}
+\caption{Original $\rho_{eq}$, and with $F_{10.7}$ dependence removed, both at 1-day averages}
+\label{nof107day}
+\end{figure}
+
 \end{document}

### 2015-06-05 paper.tex

@@
 
-\section{Data}
+\section{Data Preparation}
+Starting from the data provided by \cite{Denton} for $\rho_{eq}$ and $F_{10.7}$ from 1980-1991, and \cite{Reconstruction} for all other variables from 1972-2013, the data were prepared to get all variables on the same consecutive time-grid.
+Since the latter was pre-adjusted to have data on a consecutive one-hour grid, the former variables were adjusted to be compatible.
+First, since the data covers multiple Geostationary Operational Environmental Satellites (GOES), one in particular (GOES 7) was selected to avoid overlapping data points.
 
-For solar wind data, we use the \cite{Reconstruction}, which has a time coverage of 1972-2013.
+Second, the various forms of "bad data" were converted from their respective set value to NaNs (e.g.
+9999 becomes NaN).
+It was then condensed in range to match the time range from \cite{Reconstruction} down to the same start and end hours, and then interpolated from the GOES 15-minute grid to the one-hour grid by taking the median of all valid non-NaN data points within half an hour to either side of each hour.
+When no valid points existed in that hour period, a NaN was kept for the sake of the uniform time grid.
 
-Mass density data are from \cite{Denton}, which has a time coverage of 1980-1991 and is on a 15-minute time grid with many gaps.
-A mean interpolation method was used to one-hour grid of the solar wind averages.
-GIVE MORE DETAILS ABOUT THIS.
-NEED ENOUGH INFORMATION TO BE ABLE TO REPRODUCE RESULTS GIVEN ONLY TWO DATA SETS.
+The only other point to note in this section: For finding storm times, all NaNs were linearly interpolated out of the data in order to aid in finding storms that may have had their onset point missing.
+Though this may skew the onset time slightly, it's thought to be less skewed than trying to determine start and end times with the NaNs in place.
+This interpolation was only used for determining storm times, and not for any analysis.
+
+\section{Results}
 
@@
 \centering
-(a)
-\includegraphics[scale=0.7]{paperfigures/stormavs-dst.png}
-(b)
-\includegraphics[scale=0.7]{paperfigures/stormavs-mass.png}
+\includegraphics[scale=0.5]{paperfigures/stormavs-dst.eps}
+\includegraphics[scale=0.5]{paperfigures/stormavs-mass.eps}
 \caption{(a) Average of solar wind and near-Earth measurements around the time D_${st}$ crossed below -40~nT onset.

### 2015-06-05 paper.tex
Updated pdf

@@
 
-Figure~\label{AllData} shows values of solar wind averages and mass density used in this study.
-
-\section{Results}
-
-We will briefly compare our results to other published results to verify our methods and handling of data.
+Figure \ref{AllData} shows values of solar wind averages and mass density used in this study. We will briefly compare our results to other published results to verify our methods and handling of data.
 
@@
 \includegraphics[scale=0.5]{paperfigures/stormavs-mass.eps}
-\caption{(a) Average of solar wind and near-Earth measurements around the time D_${st}$ crossed below -40~nT onset.
+\caption{(a) Average of solar wind and near-Earth measurements around the time $D_{st}$ crossed below -40~nT onset.
 (b) Same as (a) except around time intervals where mass density crossed above $40 amu/cm^3$.

### 2015-06-05 paper.tex
Data Preparation Edits

--- 2015-06-03 paper.tex
@@
 
-\section{Data}
+\section{Data Preparation}
 
-For solar wind data, we use the \cite{Reconstruction}, which has a time coverage of 1972-2013.
+The parameters $\rho_{eq}$ and $F_{10.7}$ used in this work are from the data associated with \cite{Denton}, with data available from 1980-1991; all other variables are from \cite{Reconstruction} over the time range of 1972-2013, which are on a 1-hour time grid.
+In cases where $\rho_{eq}$ was available from multiple Geostationary Operational Environmental Satellites (GOES) satellites at the same time, the value from GOES 7 was selected to avoid overlapping data points.
+$\rho_{eq}$ is the inferred mass density based on the 3rd harmonic frequency of magnetic field measurements.
+The smallest cadence for $\rho_{eq}$ values is 10 minutes.
+To compute an hourly average over the same time range as the solar wind parameters, the median of all values in a given hourly range was used.
+Fill values were used for hours when no measurements were available.
 
-Mass density data are from \cite{Denton}, which has a time coverage of 1980-1991 and is on a 15-minute time grid with many gaps.
-A mean interpolation method was used to one-hour grid of the solar wind averages.
-GIVE MORE DETAILS ABOUT THIS.
-NEED ENOUGH INFORMATION TO BE ABLE TO REPRODUCE RESULTS GIVEN ONLY TWO DATA SETS.
+In this work events are considered when $D_{st}$ or $\rho_{eq}$ crosses a threshold value.  In finding events, all fill values were replaced with linearly interpolated values.  
+% unless the gap was larger than X hours?
 
-Figure~\label{AllData} shows values of solar wind averages and mass density used in this study.
+% Though this may skew the onset time slightly, it's thought to be less skewed than trying to determine start and end times with the NaNs in place.
+This interpolation was only used for determining storm times, and not for any analysis.
+% If you say this, you need to do an experiement.  A review will say ``seems like it is an easy statement to check.  Why didn't you?''
+
+% http://www.dartmouth.edu/~rdenton/Data/DentonTakahashiGOES1980-1991MassDensityWithHeader.txt
+% This looks like a 10 minute grid, not 15 minute?
 
@@
 
-We will briefly compare our results to other published results to verify our methods and handling of data.
+Figure \ref{AllData} shows values of solar wind averages and mass density used in this study. We will briefly compare our results to other published results to verify our methods and handling of data.
 
@@
 \centering
-(a)
-\includegraphics[scale=0.7]{paperfigures/stormavs-dst.png}
-(b)
-\includegraphics[scale=0.7]{paperfigures/stormavs-mass.png}
-\caption{(a) Average of solar wind and near-Earth measurements around the time D_${st}$ crossed below -40~nT onset.
+\includegraphics[scale=0.5]{paperfigures/stormavs-dst.eps}
+\includegraphics[scale=0.5]{paperfigures/stormavs-mass.eps}
+\caption{(a) Average of solar wind and near-Earth measurements around the time $D_{st}$ crossed below -40~nT onset.
 (b) Same as (a) except around time intervals where mass density crossed above $40 amu/cm^3$.

### 2015-06-18 paper.tex
Added significance tests and NaN tests

@@
 \begin{abstract}
-This paper looks at how various magnetosphere conditions behave around the onset of geomagnetic storms.
+This paper looks at how various magnetosphere conditions behave around the onset of geomagnetic events.
 It confirms results from previous papers that a sudden drop in $D_{st}$ correlates with a spike in equatorial mass density, while adding a level of depth and specification to the applicability of their results.
 It compares data at 1-hour averages to data at 1-day averages, and briefly to data at 27-day averages to examine if the trend holds at varying time scales and finds that it does, so long as the data is pre-processed to linearly remove a large time scale $F_{10.7}$ dependence.
-By then looking at an hourly average of variables from 24 hours before storm onset to 48 hours after, short timescale trends can be discerned.
+By then looking at an hourly average of variables from 24 hours before event onset to 48 hours after, short timescale trends can be discerned.
 
@@
 In this work events are considered when $D_{st}$ or $\rho_{eq}$ crosses a threshold value.  In finding events, all fill values were replaced with linearly interpolated values.
-% unless the gap was larger than X hours?
 
@@
 
-% http://www.dartmouth.edu/~rdenton/Data/DentonTakahashiGOES1980-1991MassDensityWithHeader.txt
-% This looks like a 10 minute grid, not 15 minute?
+To check for potential bias in the data as used by our analysis, we checked how the data availability varied with hour, shown in Figure \ref{nanperhour}.
+We also looked at how storm conditions affected data availability.
+Both a two sample t-test for difference in means and a Wilcoxon rank sum test showed significance at the 1\% level that $D_{st}$ during periods with available data was of a different distribution than $D_{st}$ during periods missing data.
+When testing for other significant $D_{st}$ differences, the Wilcoxon test was significant while the t-test was not in pre-noon vs post-noon distributions, as well as $\rho_{eq}>40$ vs $\rho_{eq}<40$ distributions indicating perhaps an increase in variability without an increase in mean.
 
@@
 \subsection{D$_{st}$ Events}
-Two storm indicators are looked at in this study.
-The first is looking for a drop in DST below the threshhold of $-50nT$ specified in \cite{Takahashi2010}, dubbed the "onset", and then considering the timeframe a storm until $D_{st}$ passes back above the $-50nT$ threshold.
+Two event indicators are looked at in this study.
+The first is looking for a drop in DST below the threshhold of $-50nT$ specified in \cite{Takahashi2010}, dubbed the "onset", and then considering the timeframe a event until $D_{st}$ passes back above the $-50nT$ threshold.
 This method finds 669 such periods between May 1983 and August 1991 with an average duration of 9 hours and a median duration of 3 hours.
-A subset of longer duration storms will be looked at later.
-Figure \ref{AllData} shows the average values of $B_Z$, $V_{SW}$, $D_{st}$, $F_{10.7}$, and Mass Density for a period of 24 hours before and 48 hours after a storm onsppet, as well as a plot of mass density with the found storm times highlighted.
+A subset of longer duration events will be looked at later.
+Figure \ref{AllData} shows the average values of $B_Z$, $V_{SW}$, $D_{st}$, $F_{10.7}$, and Mass Density for a period of 24 hours before and 48 hours after a event onsppet, as well as a plot of mass density with the found event times highlighted.
 
@@
 Figure \ref{MassStorm} shows this same algorithm, but looking for a rise in mass density over a value of 40$g/cm^3$.
-This results in 130 storms with a mean duration of 32 hours and a median duration of 17 hours, marked in red on the left figure.
+This results in 130 events with a mean duration of 32 hours and a median duration of 17 hours, marked in red on the left figure.
 
-This shows that when using all data for mass density derived storms, almost no significant changes can be seen around storm onset.
+This shows that when using all data for mass density derived events, almost no significant changes can be seen around event onset.
 
-\section{More specific storms}
-It's hypothesized that progressively picking more specific storm criteria will allow for the possibility of more significant results, at the expense of more bias in the selection process and potentially less overall usefulness of the results.
-That said, the predictability of extreme storms is of definite interest, so an attempt has been made to find some reproducible method of prediction.
-Looking at storms that last longer than 12 hours and storms with an onset threshhold greater than $70g/cm^3$ results in the left and right sides of Figure \ref{Mspec} respectively.
+\section{More specific events}
+It's hypothesized that progressively picking more specific event criteria will allow for the possibility of more significant results, at the expense of more bias in the selection process and potentially less overall usefulness of the results.
+That said, the predictability of extreme events is of definite interest, so an attempt has been made to find some reproducible method of prediction.
+Looking at events that last longer than 12 hours and events with an onset threshhold greater than $70g/cm^3$ results in the left and right sides of Figure \ref{Mspec} respectively.
 
-Neither of these seem to indicate anything too significant, so looking at $D_{st}$ storms instead to look for something that causes a significant change in Mass Density results in Figure \ref{Dspec}.
-This shows that by either looking only at $D_{st}$ storms that last longer than an hour (left) or at storms where the onset condition is $D_{st}<-80nT$, a spike in mass density is seen, but also a definite lack of data availability to the point where that spike may be coming from less than five of the total 143 storms.
+Neither of these seem to indicate anything too significant, so looking at $D_{st}$ events instead to look for something that causes a significant change in Mass Density results in Figure \ref{Dspec}.
+This shows that by either looking only at $D_{st}$ events that last longer than an hour (left) or at events where the onset condition is $D_{st}<-80nT$, a spike in mass density is seen, but also a definite lack of data availability to the point where that spike may be coming from less than five of the total 143 events.
 
-Unforunately there are no storms in this time frame that are longer than 12 hours with $D_{st}$ minima lower than $-80nT$ that have existing mass density data around onset, so an analysis of this particular relationship can't be made.
+Unforunately there are no events in this time frame that are longer than 12 hours with $D_{st}$ minima lower than $-80nT$ that have existing mass density data around onset, so an analysis of this particular relationship can't be made.
 
 \subsection{Change in $\rho_{eq}$}
-If instead of looking for storms based on a threshold of $\rho_{eq}$, we instead look for a certain amount of change in $\rho_{eq}$ as the basis for storm onset, we get Figure \ref{rhochange}.
+If instead of looking for events based on a threshold of $\rho_{eq}$, we instead look for a certain amount of change in $\rho_{eq}$ as the basis for event onset, we get Figure \ref{rhochange}.
 
@@
 Taking this re-created data set and subtracting it from the original should remove the $F_{10.7}$ dependence from the data, and allow for a less biased analysis of the relationship between $D_{st}$ and $\rho_{eq}$.
-Figure \ref{nof107} shows the stack plot for the reduced $F_{10.7}$, where a more distinct peak after storm onset can be seen.
+Figure \ref{nof107} shows the stack plot for the reduced $F_{10.7}$, where a more distinct peak after event onset can be seen.
 It also shows what that removed trend looks like, of the form $\rho_{eq}-\rho_{eq,F_{10.7}}$.
@@
 \centering
+\includegraphics[scale=0.5]{paperfigures/nansbyhour.eps}
+\includegraphics[scale=0.5]{paperfigures/nansbyhour_storm.eps}
+\caption{(a) Number of NaN points per hour of observation in the total data set (b) Data availability relative to average event hour in events where $D_{st}<-80nT$}
+\label{nanperhour}
+\end{figure}
+\clearpage
+
+\begin{figure}[htp]
+\centering
 \includegraphics[scale=0.7]{paperfigures/alldata.eps}
@@
 
-% Remove title from both figures.  D_ST -> D_st Bz -> B_z in labels.  Change non-nan data points to ``# of values''.
 % Change x-label to be ``Time from start of event (hr)'' and put vertical lines in each panel at t = 0 (somewhere I have a code called vertline.m)
@@
 \centering
-\includegraphics[scale=0.7]{paperfigures/stormavs-md12.png}
-\includegraphics[scale=0.7]{paperfigures/stormavs-m70.png}
-\caption{(a) Same as \ref{fig:MassStorm}(a) except with constraint that D$_{st}$ stayed below -40~nT for at least 12~hours.
-(b) Same as \ref{fig:MassStorm}(b) except for constrain that mass density crossed above $70 amu/cm^3$.}
+\includegraphics[scale=0.5]{paperfigures/stormavs-dd12.eps}
+\includegraphics[scale=0.5]{paperfigures/stormavs-d80.eps}
+\caption{(a) Same as \ref{fig:MassStorm}(a) except with constraint that $D_{st}$ stayed below -40~nT for at least 12~hours.
+(b) Same as \ref{fig:MassStorm}(b) except for constrain that $D_{st}$ crossed below $-80 nT$.}
 \label{Mspec}
@@
 \centering
-\includegraphics[scale=0.7]{paperfigures/stormavs-dd12.png}
-\includegraphics[scale=0.7]{paperfigures/stormavs-d80.png}
-\caption{$D_{st}$ Storms $>$ 12 hours, $D_{st}<-80nT$}
+\includegraphics[scale=0.5]{paperfigures/stormavs-md12.eps}
+\includegraphics[scale=0.5]{paperfigures/stormavs-m70.eps}
+\caption{(a) Same as \ref{fig:MassStorm}(a) except with constraint that $\rho_{eq}$ stayed above 50~nT for at least 12~hours.
+(b) Same as \ref{fig:MassStorm}(b) except for constrain that mass density crossed above $70 amu/cm^3$.}
 \label{Dspec}

### 2015-06-18 Density.m

@@ -189,7 +189,7 @@ end
 
 %Find storm with enough data to analyze
 MassDensityNanSpline=interp1(OMNITime(~isnan(MassDensitySpline)),MassDensitySpline(~isnan(MassDensitySpline)),OMNITime,'linear');
-storms=diff([0 (FILLED(:,15)<-80)' 0]); %DST Storm
+storms=diff([0 (FILLED(:,15)<-40)' 0]); %DST Storm
 %storms=diff([0 (MassDensityNanSpline>40)' 0]); %Mass Density Storm, started at 40
 %storms=[0 diff([0 (diff(MassDensityNanSpline)>10)' 0])];
 %storms=[0 diff([0 (abs(MassDensityNanSpline(2:end)./MassDensityNanSpline(1:end-1))>1.3)' 0])];
@@ -331,6 +331,38 @@ if(MakePaperPlots)
     datetick('x')
     %title('D_{st} Storms')
     print -depsc2 -r200 paperfigures/dststorms.eps
+end
+
+if(MakePaperPlots) %Nans per hour
+    h=figure('Visible',visible);
+    hist(FILLED(isnan(MassDensitySpline),3),[0:23])
+    axis([-1 24 0 3000])
+    xlabel('Hour')
+    ylabel('Frequency')
+    print -depsc2 -r200 paperfigures/nansbyhour.eps
+
+    h=figure('Visible',visible);
+    subplot(2,1,1)
+    plot(xa,AVs(1,:,3))
+    ylabel('Hour average')
+    grid on
+    subplot(2,1,2)
+    plot(xa,AVMDs(1,:),'r')
+    plot(xa,AVnnans,'r')
+    ylabel('Data available')
+    xlabel('Time from event start (hr)')
+    grid on
+    print -depsc2 -r200 nansbyhour_storm.eps
+    
+    %Show DST is significantly different during missing data times
+    [p,h]=ranksum(FILLED(~isnan(MassDensitySpline),15),FILLED(isnan(MassDensitySpline),15),'Alpha',0.01)
+    [h,p]=ttest2(FILLED(~isnan(MassDensitySpline),15),FILLED(isnan(MassDensitySpline),15),'Alpha',0.01)
+    %Or when mass density gets above/below 40
[…]

### 2015-06-25 paper.tex
Updated figures. Fixing text

@@
 They then show an epoch analysis where $\rho_{eq}$ is seen to spike the day of a $D_{st}$ drop, using a daily average of 30 minute $\rho_{eq}$ and one hour $D_{st}$ measurements.
+Figure \ref{DailyAverages} show that the trends observed by \cite{Takahashi2010} hold true in this analysis as well.
 
@@
 
-In this work events are considered when $D_{st}$ or $\rho_{eq}$ crosses a threshold value.  In finding events, all fill values were replaced with linearly interpolated values.
+In this work events are considered when $D_{st}$ or $\rho_{eq}$ crosses a threshold value, as indicated in \ref{StormCutoff}.
+In finding events, all fill values were replaced with linearly interpolated values.
+Figure \ref{AllData} shows the values of $B_Z$, $V_{SW}$, $D_{st}$, $F_{10.7}$, and Mass Density for the duration of the dataset.
 
@@
 % If you say this, you need to do an experiement.  A review will say ``seems like it is an easy statement to check.  Why didn't you?''
-
-To check for potential bias in the data as used by our analysis, we checked how the data availability varied with hour, shown in Figure \ref{nanperhour}.
-We also looked at how storm conditions affected data availability.
-Both a two sample t-test for difference in means and a Wilcoxon rank sum test showed significance at the 1\% level that $D_{st}$ during periods with available data was of a different distribution than $D_{st}$ during periods missing data.
-When testing for other significant $D_{st}$ differences, the Wilcoxon test was significant while the t-test was not in pre-noon vs post-noon distributions, as well as $\rho_{eq}>40$ vs $\rho_{eq}<40$ distributions indicating perhaps an increase in variability without an increase in mean.
 
@@
 Two event indicators are looked at in this study.
-The first is looking for a drop in DST below the threshhold of $-50nT$ specified in \cite{Takahashi2010}, dubbed the "onset", and then considering the timeframe a event until $D_{st}$ passes back above the $-50nT$ threshold.
+The first is looking for a drop in DST below the threshhold of $-40nT$ specified in \cite{Takahashi2010}, dubbed the "onset", and then considering the timeframe an event until $D_{st}$ passes back above the $-40nT$ threshold.
 This method finds 669 such periods between May 1983 and August 1991 with an average duration of 9 hours and a median duration of 3 hours.
+Figure \ref{Storms} shows the average values of all events over a window of 24 hours before onset and 48 hours after.
+Figure \ref{Storms}a shows events selected by looking for event onsets where $D_{st}$ crossed a threshold of $-40nT$.
+The dashed red lines indicate plus and minus one standard deviation of values from all events that went into the average.
+The final plot in the stack shows both $\rho_{eq}$ and a bar plot of how many valid data points went into the $\rho_{eq}$ average.
+Since $\rho_{eq}$ comes from a sparser dataset, it has less valid points contributing to the averages than the other variables in the stack.
 A subset of longer duration events will be looked at later.
-Figure \ref{AllData} shows the average values of $B_Z$, $V_{SW}$, $D_{st}$, $F_{10.7}$, and Mass Density for a period of 24 hours before and 48 hours after a event onsppet, as well as a plot of mass density with the found event times highlighted.
 
@@
 \subsection{Mass Density Events}
-Figure \ref{MassStorm} shows this same algorithm, but looking for a rise in mass density over a value of 40$g/cm^3$.
+Figure \ref{Storms}b shows this same algorithm, but looking for a rise in mass density over a value of 40$g/cm^3$.
 This results in 130 events with a mean duration of 32 hours and a median duration of 17 hours, marked in red on the left figure.
@@
 
-Similarly, looking at the 1 day averaged data with and without the $F_{10.7}$ dependence, Figure \ref{nof107day} shows that the results of \cite{Takahashi2010} hold only once the dependence has been removed.
-The 27 day trend couldn't be determined as not enough valid data existed to test it.
+\section{Appendix}
+\subsection{Bias}
+
+To check for potential bias in the data as used by our analysis, we checked how the data availability varied with hour, shown in Figure \ref{nanperhour}.
+We also looked at how storm conditions affected data availability.
+Both a two sample t-test for difference in means and a Wilcoxon rank sum test showed significance at the 1\% level that $D_{st}$ during periods with available data was of a different distribution than $D_{st}$ during periods missing data.
+When testing for other significant $D_{st}$ differences, the Wilcoxon test was significant while the t-test was not in pre-noon vs post-noon distributions, as well as $\rho_{eq}>40$ vs $\rho_{eq}<40$ distributions indicating perhaps an increase in variability without an increase in mean.
+
+While the GOES Satellites tend to keep an average geostationary distance of around $L=6.8R_E$ shown in \cite{Takahashi2010}, the actual plasmapause location varies significantly , as shown in \cite{OBrien2003}.
+This means that during periods of large $D_{st}$ the plasmapause may be far from the point of measurement of $\rho_{eq}$ creating a discord in the correlation.
+\cite{Gallagher2000} provides a model for $\rho_{eq}$ at a range of L-shells and a brief discussion of the elemental contributions.
 
@@
 \label{nanperhour}
+\end{figure}
+\clearpage
+
+\begin{figure}[htp!]
+\centering
+\includegraphics[scale=0.5]{paperfigures/stormavs-dst-day.eps}
+\includegraphics[scale=0.5]{paperfigures/stormavs-dst-27day.eps}
+\caption{One-day and 27-day averaged $D_{st}$ storms}
+\label{DailyAverages}
 \end{figure}
@@
 The number of values used in the averages for mass density is shown in the bottom panel (a) and (b).}
-\label{DSTstorm}
+\label{StormCutoff}
 \end{figure}
@@
 The bottom panel shows the number of mass density data points that were used for the average.}
-\label{MassStorm}
+\label{Storms}
 \end{figure}
@@
 \centering
-\includegraphics[scale=0.7]{paperfigures/stormavs-diffden-10amu.png}
-\includegraphics[scale=0.7]{paperfigures/stormavs-diffden-30percent.png}
-\caption{diff($\rho_{eq}$) $>$ 20$\frac{amu}{hour}$, diff($\rho_{eq}$) $>$ 30$\frac{\%}{hour}$}
+\includegraphics[scale=0.5]{paperfigures/stormavs-diffden-10amu.eps}
+\includegraphics[scale=0.5]{paperfigures/stormavs-diffden-30percent.eps}
+\caption{diff($\rho_{eq}$) $>$ 10$\frac{amu}{hour}$, diff($\rho_{eq}$) $>$ 30$\frac{\%}{hour}$}
 \label{rhochange}
@@
 \centering
-\includegraphics[scale=0.7]{paperfigures/stormavs-dst-nof107.png}
-\includegraphics[scale=0.7]{paperfigures/f107removed.png}
-\caption{$\rho_{eq}$ with $F_{10.7}$ removed, and Difference from original}
+\includegraphics[scale=0.5]{paperfigures/stormavs-dst-nof107.eps}
+\includegraphics[scale=0.6]{paperfigures/f107removed.eps}
+\caption{$D_{st}$ events where $\rho_{eq}$ has $F_{10.7}$ dependence removed, and Difference between original $\rho_{eq}$ and $F_{10.7}$-less $\rho_{eq}$}
 \label{nof107}
@@
 
-\begin{figure}[htp!]
-\centering
-\includegraphics[scale=0.7]{paperfigures/stormavs-dst-day.png}
-\includegraphics[scale=0.7]{paperfigures/stormavs-dst-day-nof107.png}
-\caption{Original $\rho_{eq}$, and with $F_{10.7}$ dependence removed, both at 1-day averages}
-\label{nof107day}
-\end{figure}
-
 \end{document}

### 2015-06-25 Density.m

@@ -246,6 +246,7 @@ AVMDMatBars=[AVMDs(1,:)-nanstd(AVMDMat(:,:))./sqrt(sum(~isnan(AVMDMat(:,:)))) ; 
 MakePlots=0;
 MakePaperPlots=1;
 visible='off';
+visible='on';
 
 %Compare the two densities
 if(MakePlots)
@@ -289,24 +290,25 @@ if(MakePaperPlots)
     xa=(1:length(AVMDs))-timewidth-1;
     h=figure('Visible',visible);
     orient tall;
-    h2=subplot('position',subplotstack(5,2));plot(xa,AVs(1,:,6),'+-'); ylabel('V_{SW} (km/s)');%V_sw
+    h2=subplot('position',subplotstack(5,2));plot(xa,AVs(1,:,6),'+-'); text(0.01,0.9,'V_{SW} (km/s)','Units','normalized','FontSize',12); %ylabel('V_{SW} (km/s)');%V_sw
     hold on; plot(xa,AVMatBars(:,:,6),'r-.'); 
-    h1=subplot('position',subplotstack(5,1));plot(xa,AVs(1,:,5),'+-'); ylabel('B_z (nT)'); %Bz
+    h1=subplot('position',subplotstack(5,1));plot(xa,AVs(1,:,5),'+-'); text(0.01,0.9,'B_z (nT)','Units','normalized','FontSize',12); %ylabel('B_z (nT)'); %Bz
     hold on; plot(xa,AVMatBars(:,:,5),'r-.');
-    h3=subplot('position',subplotstack(5,3));plot(xa,AVs(1,:,15),'+-');ylabel('D_{st} (nT)'); %dst
+    h3=subplot('position',subplotstack(5,3));plot(xa,AVs(1,:,15),'+-'); text(0.01,0.9,'D_{st} (nT)','Units','normalized','FontSize',12); %ylabel('D_{st} (nT)'); %dst
     hold on; plot(xa,AVMatBars(:,:,15),'r-.'); 
-    h4=subplot('position',subplotstack(5,4));plot(xa,AVs(1,:,29),'+-');ylabel('F10.7 (s.f.u.)');%f107
+    h4=subplot('position',subplotstack(5,4));plot(xa,AVs(1,:,29),'+-'); text(0.01,0.9,'F_{10.7} (s.f.u)','Units','normalized','FontSize',12); %ylabel('F10.7 (s.f.u.)');%f107
[…]

### 2015-06-30 paper.tex
Updated plots. Adding CC plot and updated F10.7 analysis

@@
 It compares data at 1-hour averages to data at 1-day averages, and briefly to data at 27-day averages to examine if the trend holds at varying time scales and finds that it does, so long as the data is pre-processed to linearly remove a large time scale $F_{10.7}$ dependence.
-By then looking at an hourly average of variables from 24 hours before event onset to 48 hours after, short timescale trends can be discerned.
+By then looking at an hourly average of parameters from 24 hours before event onset to 48 hours after, short timescale trends can be discerned.
 
@@
 They then show an epoch analysis where $\rho_{eq}$ is seen to spike the day of a $D_{st}$ drop, using a daily average of 30 minute $\rho_{eq}$ and one hour $D_{st}$ measurements.
-Figure \ref{DailyAverages} show that the trends observed by \cite{Takahashi2010} hold true in this analysis as well.
 
@@
 
-The parameters $\rho_{eq}$ and $F_{10.7}$ used in this work are from the data associated with \cite{Denton}, with data available from 1980-1991; all other variables are from \cite{Reconstruction} over the time range of 1972-2013, which are on a 1-hour time grid.
+The parameters $\rho_{eq}$ and $F_{10.7}$ used in this work are from the data associated with \cite{Denton}, with data available from 1980-1991; all other parameters are from \cite{Reconstruction} over the time range of 1972-2013, which are on a 1-hour time grid.
 In cases where $\rho_{eq}$ was available from multiple Geostationary Operational Environmental Satellites (GOES) satellites at the same time, the value from GOES 7 was selected to avoid overlapping data points.
@@
 
+\subsection{Previous Results}
+Figure \ref{DailyAverages} show that the trends observed by \cite{Takahashi2010} for one day averages only seems to hold true for the one-day averaged data, and only after the $F_{10.7}$ dependence is removed.
+The correlation seen between $log(\rho_{eq\_27d})$ and $F_{10.7\_27d}$ isn't quite as good in this data as in \cite{Takahashi2010}, but shows the same trend as seen in Figure \ref{ccplot}.
+
 \subsection{D$_{st}$ Events}
@@
 The final plot in the stack shows both $\rho_{eq}$ and a bar plot of how many valid data points went into the $\rho_{eq}$ average.
-Since $\rho_{eq}$ comes from a sparser dataset, it has less valid points contributing to the averages than the other variables in the stack.
+Since $\rho_{eq}$ comes from a sparser dataset, it has less valid points contributing to the averages than the other parameters in the stack.
 A subset of longer duration events will be looked at later.
@@
 
-Unforunately there are no events in this time frame that are longer than 12 hours with $D_{st}$ minima lower than $-80nT$ that have existing mass density data around onset, so an analysis of this particular relationship can't be made.
+Unfortunately there are no events in this time frame that are longer than 12 hours with $D_{st}$ minima lower than $-80nT$ that have existing mass density data around onset, so an analysis of this particular relationship can't be made.
 
@@
 \centering
-\includegraphics[scale=0.5]{paperfigures/nansbyhour.eps}
-\includegraphics[scale=0.5]{paperfigures/nansbyhour_storm.eps}
-\caption{(a) Number of NaN points per hour of observation in the total data set (b) Data availability relative to average event hour in events where $D_{st}<-80nT$}
-\label{nanperhour}
+\includegraphics[scale=0.7]{paperfigures/alldata.eps}
+\caption{Overview of data used in this study.
+The top four panels are from \cite{Reconstruction} and the bottom panel is based on \cite{Denton} after interpolation and averaging described in the text.
+Dashed lines indicate default event cutoff thresholds.}
+\label{AllData}
 \end{figure}
@@
 
-\begin{figure}[htp]
+\begin{figure}[htp!]
 \centering
-\includegraphics[scale=0.7]{paperfigures/alldata.eps}
-\caption{Overview of data used in this study.
-The top four panels are from \cite{Reconstruction} and the bottom panel is based on \cite{Denton} after interpolation and averaging described in the text.}
-\label{AllData}
+\includegraphics[scale=0.5]{paperfigures/stormavs-dst-day-nof107.eps}
+\includegraphics[scale=0.5]{paperfigures/stormavs-dst-27day-nof107.eps}
+\caption{One-day and 27-day averaged $D_{st}$ storms with $F_{10.7}$ dependence removed}
+\label{DailyAveragesNoF107}
+\end{figure}
+\clearpage
+
+\begin{figure}[htp!]
+\centering
+\includegraphics[scale=0.7]{paperfigures/ccplot.eps}
+\caption{Correlation between $log(\rho_{eq\_27d})$ and $F_{10.7\_27d}$ }
+\label{ccplot}
 \end{figure}
@@
 \includegraphics[scale=0.5]{paperfigures/stormavs-d80.eps}
-\caption{(a) Same as \ref{fig:MassStorm}(a) except with constraint that $D_{st}$ stayed below -40~nT for at least 12~hours.
-(b) Same as \ref{fig:MassStorm}(b) except for constrain that $D_{st}$ crossed below $-80 nT$.}
+\caption{(a) Same as \ref{fig:Storms}(a) except with constraint that $D_{st}$ stayed below -40~nT for at least 12~hours.
+(b) Same as \ref{fig:Storms}(b) except for constrain that $D_{st}$ crossed below $-80 nT$.}
 \label{Mspec}
@@
 \caption{(a) Same as \ref{fig:MassStorm}(a) except with constraint that $\rho_{eq}$ stayed above 50~nT for at least 12~hours.
-(b) Same as \ref{fig:MassStorm}(b) except for constrain that mass density crossed above $70 amu/cm^3$.}
+(b) Same as \ref{fig:Storms}(b) except for constrain that mass density crossed above $70 amu/cm^3$.}
 \label{Dspec}
@@
 
+\begin{figure}[htp]
+\centering
+\includegraphics[scale=0.5]{paperfigures/nansbyhour.eps}
+\includegraphics[scale=0.5]{paperfigures/nansbyhour_storm.eps}
+\caption{(a) Number of NaN points per hour of observation in the total data set (b) Data availability relative to average event hour in events where $D_{st}<-80nT$}
+\label{nanperhour}
+\end{figure}
+\clearpage
+
 \end{document}

### 2015-07-02 Density.m
New scatter plots

@@ -177,12 +177,12 @@ end
 FILLED=[FILLED F107];
 headers{end+1}='F107';
 
-LongTimeScale=24*27;%24*27; %How many hours to average over
+LongTimeScale=24;%24*27; %How many hours to average over
 LongTimeInc=LongTimeScale*(OMNITime(2)-OMNITime(1));
 if(LongTimeScale>0)
-    MassDensitySpline=interp1(OMNITime,MassDensitySpline,OMNITime(1):LongTimeInc:OMNITime(end));
+    MassDensitySpline=interptest(OMNITime,MassDensitySpline,OMNITime(1):LongTimeInc:OMNITime(end));
     %F107Spline=interp1(OMNITime,F107Spline,OMNITime(1):LongTimeInc:OMNITime(end));
-    FILLED=interp1(OMNITime,FILLED,OMNITime(1):LongTimeInc:OMNITime(end));
+    FILLED=interptest(OMNITime,FILLED,OMNITime(1):LongTimeInc:OMNITime(end));
     OMNITime=OMNITime(1):LongTimeInc:OMNITime(end);
 end
 
@@ -261,8 +261,8 @@ end
 if(MakePaperPlots && removef107)
     h=figure('Visible',visible);
     %plot(OMNITime,MassDensitySplineOriginal-(MassDensitySpline-nanmean(MassDensitySplineOriginal)),'-')
-    plot(OMNITime,MassDensitySplineOriginal,'r-')
-    hold on; plot(OMNITime,MassDensitySpline,'b-')
+    plot(OMNITime,MassDensitySplineOriginal,'r.')
+    hold on; plot(OMNITime,MassDensitySpline,'b.')
     legend('Original','F_{10.7} Removed');
     %title('F10.7 trend')
     ylabel('\rho_{eq} (amu/cm^3)')
@@ -331,7 +331,7 @@ if(MakePaperPlots && LongTimeScale==24*27 && ~removef107) %Correlation plot of F
 end
 
 
-if(MakePaperPlots) %Nans per hour
+if(MakePaperPlots && LongTimeScale==0) %Nans per hour
     h=figure('Visible',visible);
     hist(FILLED(isnan(MassDensitySpline),3),0:23)
     axis([-1 24 0 3000])
@@ -350,7 +350,7 @@ if(MakePaperPlots) %Nans per hour
     ylabel('Data available')
     xlabel('Time from event start (hr)')
     grid on
[…]

### 2015-07-07 paper.tex
New scatter plots
Adding takahashi matched figure

@@
 Two event indicators are looked at in this study.
-The first is looking for a drop in DST below the threshhold of $-40nT$ specified in \cite{Takahashi2010}, dubbed the "onset", and then considering the timeframe an event until $D_{st}$ passes back above the $-40nT$ threshold.
+The first is looking for a drop in DST below the threshold of $-40nT$ specified in \cite{Takahashi2010}, dubbed the "onset", and then considering the timeframe an event until $D_{st}$ passes back above the $-40nT$ threshold.
 This method finds 669 such periods between May 1983 and August 1991 with an average duration of 9 hours and a median duration of 3 hours.
@@
 \includegraphics[scale=0.5]{paperfigures/stormavs-dst-day.eps}
-\includegraphics[scale=0.5]{paperfigures/stormavs-dst-27day.eps}
-\caption{One-day and 27-day averaged $D_{st}$ storms}
+\includegraphics[scale=0.5]{paperfigures/stormavs-dst-day-50.eps}
+\caption{One-day averaged $D_{st}$ storms at thresholds of $-40nT$ and $-50nT$}
 \label{DailyAverages}
@@
 \centering
-\includegraphics[scale=0.5]{paperfigures/stormavs-dst-day-nof107.eps}
-\includegraphics[scale=0.5]{paperfigures/stormavs-dst-27day-nof107.eps}
-\caption{One-day and 27-day averaged $D_{st}$ storms with $F_{10.7}$ dependence removed}
-\label{DailyAveragesNoF107}
-\end{figure}
-\clearpage
-
-\begin{figure}[htp!]
-\centering
-\includegraphics[scale=0.7]{paperfigures/ccplot.eps}
-\caption{Correlation between $log(\rho_{eq\_27d})$ and $F_{10.7\_27d}$ }
+\includegraphics[scale=0.42]{paperfigures/ccplot.eps}
+\includegraphics[scale=0.42]{paperfigures/DSTvsMD.eps}
+\includegraphics[scale=0.42]{paperfigures/DstMDAllData.eps}
+\caption{(a) Correlation between $log(\rho_{eq\_27d})$ and $F_{10.7\_27d}$. (b) $D_{st}$ against $\rho_{eq}$ at one hour and one-day median values. (c) All data of $D_{st}$ and $\rho_{eq}$ }
 \label{ccplot}
@@
 \centering
-\includegraphics[scale=0.5]{paperfigures/stormavs-dst.eps}
-\includegraphics[scale=0.5]{paperfigures/stormavs-mass.eps}
+\includegraphics[scale=0.45]{paperfigures/stormavs-dst.eps}
+\includegraphics[scale=0.45]{paperfigures/stormavs-mass.eps}
 \caption{(a) Average of solar wind and near-Earth measurements around the time $D_{st}$ crossed below -40~nT onset.
@@
 \centering
-\includegraphics[scale=0.5]{paperfigures/stormavs-dd12.eps}
-\includegraphics[scale=0.5]{paperfigures/stormavs-d80.eps}
+\includegraphics[scale=0.45]{paperfigures/stormavs-dd12.eps}
+\includegraphics[scale=0.45]{paperfigures/stormavs-d80.eps}
 \caption{(a) Same as \ref{fig:Storms}(a) except with constraint that $D_{st}$ stayed below -40~nT for at least 12~hours.
@@
 \centering
-\includegraphics[scale=0.5]{paperfigures/stormavs-md12.eps}
-\includegraphics[scale=0.5]{paperfigures/stormavs-m70.eps}
+\includegraphics[scale=0.45]{paperfigures/stormavs-md12.eps}
+\includegraphics[scale=0.45]{paperfigures/stormavs-m70.eps}
 \caption{(a) Same as \ref{fig:MassStorm}(a) except with constraint that $\rho_{eq}$ stayed above 50~nT for at least 12~hours.

### 2015-07-07 Density.m

@@ -17,7 +17,7 @@ FILLED=dlmread('WGhourFS_72_13.txt',',',1,0);
 
 %Find a good storm
 
-%FILLED=FILLED(FILLED(:,1)>1980,:); %Just to get into Denton time
+FILLED=FILLED(FILLED(:,1)>1988,:); %Just to get into Denton time
 OMNITime=datenum(FILLED(:,1),1,0)+FILLED(:,2)+FILLED(:,3)/24;
 
 startt=727547.333333;
@@ -145,6 +145,11 @@ getFtime=getFtime+(F107time<max(DentonTime));
 getFtime=(getFtime==2);
 F107time=F107time(getFtime);
 F107=F107(getFtime);
+getFtime=F107time>=min(OMNITime);
+getFtime=getFtime+(F107time<=max(OMNITime));
+getFtime=(getFtime==2);
+F107time=F107time(getFtime);
+F107=F107(getFtime);
 
 
 OverlayFilled=FILLED;
@@ -169,7 +174,7 @@ else
     %F107Spline=interptest(DentonTime,F107,OMNITime,(OMNITime(2)-OMNITime(1))/2);
     MassDensitySpline=MassDensitySpline';
     %F107Spline=F107Spline';
-    save('InterpedVals','MassDensitySpline','F107Spline');
+    save('InterpedVals','MassDensitySpline');%,'F107Spline');
 end
 
 %FILLED=[FILLED F107Spline]; %When F107 is from Denton, use spline
@@ -178,6 +183,24 @@ FILLED=[FILLED F107];
 headers{end+1}='F107';
 
 LongTimeScale=24;%24*27; %How many hours to average over
+
+%Find storm with enough data to analyze
+MassDensityNanSpline=interp1(OMNITime(~isnan(MassDensitySpline)),MassDensitySpline(~isnan(MassDensitySpline)),OMNITime,'linear');
+storms=diff([0 (FILLED(:,15)<-50)' 0]); %DST Storm
+%storms=diff([0 (MassDensityNanSpline>40)' 0]); %Mass Density Storm, started at 40
+%storms=[0 diff([0 (diff(MassDensityNanSpline)>10)' 0])];
+%storms=[0 diff([0 (abs(MassDensityNanSpline(2:end)./MassDensityNanSpline(1:end-1))>1.3)' 0])];
+starti=find(storms>0);
+endi=find(storms<0)-1;
[…]

### 2015-07-07 interptest.m

@@ -4,9 +4,9 @@ if nargin == 3
 end
 
 %tic
-datanew=1:length(tnew);
+datanew=zeros(length(tnew),min(size(x)));
 for i=1:length(tnew)
-    datanew(i)=nanmedian(x(t>(tnew(i)-dt) & t<(tnew(i)+dt))); 
+    datanew(i,:)=nanmedian(x(t>(tnew(i)-dt) & t<(tnew(i)+dt),:)); 
 end
 %toc
 %datanew;

### 2015-07-14 paper.tex
Sanity checks for Takahashi 2010 Fig 11

@@
 \section{Results}
-
 Figure \ref{AllData} shows values of solar wind averages and mass density used in this study. We will briefly compare our results to other published results to verify our methods and handling of data.
@@
 \subsection{Previous Results}
-Figure \ref{DailyAverages} show that the trends observed by \cite{Takahashi2010} for one day averages only seems to hold true for the one-day averaged data, and only after the $F_{10.7}$ dependence is removed.
+Figure \ref{DailyAverages} show that the trends observed by \cite{Takahashi2010} for one day averages only seems to hold true for the one-day averaged data.
+Namely that a drop in median daily $D_{st}$ between 1989 and 1991 coincides with a significant spike in $\rho_{eq}$.
 The correlation seen between $log(\rho_{eq\_27d})$ and $F_{10.7\_27d}$ isn't quite as good in this data as in \cite{Takahashi2010}, but shows the same trend as seen in Figure \ref{ccplot}.
@@
 \subsection{Bias}
+In an attempt to reproduce Figure 11 from \cite{Takahashi2010}, an ambiguity in data-handling was found.
+It is unknown how they got from hourly $\rho_{eq}$ to daily medians, whether in one step or two steps, so attempts were made to reproduce all possibilities and compare in order to find a data-handling method with the least bias.
+These attempts are shown in Figure \ref{blockmedian}.
+This also shows the effect of only considering events with a minimum before noon.
+All show a similar spike in $\rho_{eq}$ at the time of $D_{st}$ minimum, though none quite reproduce the exact values seen in \cite{Takahashi2010}.
+Figure \ref{allstorms} shows where the median falls for all of the found storms during that period, as a sanity check for why the prior work would get median values nearing $30 amu/cm^3$.
 
@@
 
-While the GOES Satellites tend to keep an average geostationary distance of around $L=6.8R_E$ shown in \cite{Takahashi2010}, the actual plasmapause location varies significantly , as shown in \cite{OBrien2003}.
+While the GOES Satellites tend to keep an average geostationary distance of around $L=6.8R_E$ shown in \cite{Takahashi2010}, the actual plasmapause location varies significantly, as shown in \cite{OBrien2003}.
 This means that during periods of large $D_{st}$ the plasmapause may be far from the point of measurement of $\rho_{eq}$ creating a discord in the correlation.
@@
 \centering
-\includegraphics[scale=0.5]{paperfigures/stormavs-dst-day.eps}
-\includegraphics[scale=0.5]{paperfigures/stormavs-dst-day-50.eps}
-\caption{One-day averaged $D_{st}$ storms at thresholds of $-40nT$ and $-50nT$}
+\includegraphics[scale=0.45]{paperfigures/stormavs-dst-day.eps}
+\includegraphics[scale=0.45]{paperfigures/stormavs-dst-50-tak.eps}
+\caption{(a) One-day medians of $D_{st}$ storms at a threshold of $-40nT$ and (b) verifying \cite{Takahashi2010} Fig. 11 conditions: $D_{st}<-50nT$ between 1989 and 1991}
 \label{DailyAverages}
@@
 \centering
+\includegraphics[scale=0.75]{paperfigures/blockmedian.eps}
+\includegraphics[scale=0.75]{paperfigures/blockmedian-prenoon.eps}
+\caption{Comparing median values calculated as median of all 1-hour points in the 12 day block, and as the daily median of all hourly-mediated storms.
+(b) Same, but only storms starting between 0-12 UTC}
+\label{blockmedian}
+\end{figure}
+\clearpage
+
+\begin{figure}[htp]
+\centering
+\includegraphics[scale=0.9]{paperfigures/allstorms.eps}
+\caption{Comparing all storms to their median and $1\sigma$ range}
+\label{allstorms}
+\end{figure}
+\clearpage
+
+\begin{figure}[htp]
+\centering
 \includegraphics[scale=0.5]{paperfigures/nansbyhour.eps}

### 2015-07-14 Density.m

@@ -194,6 +194,15 @@ starti=find(storms>0);
 endi=find(storms<0)-1;
 duration=endi-starti+1;
 
+while(1) %Shift start points to next local minimum 
+    ind=FILLED(starti+1,15)<FILLED(starti,15);
+    if(sum(ind)==0)
+        break
+    end
+    starti(ind)=starti(ind)+1;
+end
+
+
 %{
 if(LongTimeScale>0); %Maybe add unique? And figure out how to make duration work then
    starti=(ceil(starti./LongTimeScale))+1; %Not entirely sure why it's off by 1
@@ -240,6 +249,14 @@ end
 while(endi(end)+maxwidth>length(MassDensitySpline))
     starti(end)=[]; endi(end)=[];
 end
+
+cutconditions=0;
+if(cutconditions) %Cut down found storms to only include pre-noon conditions
+   endi(FILLED(starti,3)>12)=[];
+   duration(FILLED(starti,3)>12)=[];
+   starti(FILLED(starti,3)>12)=[];
+end
+
 for i=1:length(starti)
     datanum=sum(~isnan(MassDensitySpline(starti(i):endi(i))));
     %if(datanum>(endi(i)-starti(i))/2 && datanum>18)
@@ -250,8 +267,8 @@ for i=1:length(starti)
     %fprintf('%6f - %3d \n',OMNITime(starti(i)),endi(i)-starti(i))
     % end
 end
-AVs=nanmean(AVMat,1);
-AVMDs=nanmean(AVMDMat);
+AVs=nanmedian(AVMat,1);
+AVMDs=nanmedian(AVMDMat);
 AVnnans=sum(~isnan(AVMDMat));
 AVMatBars=[AVs(1,:,:)-nanstd(AVMat(:,:,:))./sqrt(sum(~isnan(AVMat(:,:,:)))) ; AVs(1,:,:)+nanstd(AVMat(:,:,:))./sqrt(sum(~isnan(AVMat(:,:,:))))];
 AVMDMatBars=[AVMDs(1,:)-nanstd(AVMDMat(:,:))./sqrt(sum(~isnan(AVMDMat(:,:)))) ; AVMDs(1,:)+nanstd(AVMDMat(:,:))./sqrt(sum(~isnan(AVMDMat(:,:))))];
@@ -260,6 +277,7 @@ AVs=squeeze(AVs);
 if(LongTimeScale>1)
     AVs=interptest(-timewidth:1:timewidth*2,AVs,-timewidth:LongTimeScale:timewidth*2);
[…]

### 2015-07-23 paper.tex
Updated code, comparing densities

@@
 \subsection{Bias}
-In an attempt to reproduce Figure 11 from \cite{Takahashi2010}, an ambiguity in data-handling was found.
-It is unknown how they got from hourly $\rho_{eq}$ to daily medians, whether in one step or two steps, so attempts were made to reproduce all possibilities and compare in order to find a data-handling method with the least bias.
+While attempting to reproduce Figure 11 from \cite{Takahashi2010}, an ambiguity in data-handling was found.
+It is unknown how they got from hourly $\rho_{eq}$ to daily medians, whether in one step or two steps, and whether the hourly medians are an hour ahead of each hour grid point, or a median of points a half hour to either side, so attempts were made to reproduce all possibilities and compare in order to find a data-handling method with the least bias.
 These attempts are shown in Figure \ref{blockmedian}.
@@
 Figure \ref{allstorms} shows where the median falls for all of the found storms during that period, as a sanity check for why the prior work would get median values nearing $30 amu/cm^3$.
+Both authors of this paper conducted independent trials to confirm that the data and analysis don't quite yield the results of Figure 11 in \cite{Takahashi2010} with the processes described in that paper, but the same general trend is still seen.
 

### 2015-07-23 Density.m

@@ -3,11 +3,14 @@ function Density
 close all;clear all;
 
 %Read filled dataset from Kondrashov(2014)
-FILLED=dlmread('WGhourFS_72_13.txt',',',1,0);
+if(~exist('data/WGhourFS_72_13.txt'))
+    urlwrite('http://mag.gmu.edu/git-data/victoirv/Density/data/WGhourFS_72_13.txt','data/WGhourFS_72_13.txt');
+end
+FILLED=dlmread('data/WGhourFS_72_13.txt',',',1,0);
 FILLED=FILLED(FILLED(:,1)>1980,:); %Just to get into Denton time
 FILLED=FILLED(FILLED(:,1)>1988,:);
 FILLED=FILLED(FILLED(:,1)<1992,:); %For comparing to Takahashi 2010 Fig 11
-headers=textread('WGhourFS_72_13.txt','%s',28,'delimiter',',');
+headers=textread('data/WGhourFS_72_13.txt','%s',28,'delimiter',',');
 VBS=1/2*FILLED(:,6).*(abs(FILLED(:,5))-FILLED(:,5));
 VBz=FILLED(:,6).*FILLED(:,5);
 BS=1/2*(abs(FILLED(:,5))-FILLED(:,5));

### 2015-07-23 Density2.m

@@ -2,7 +2,7 @@
 
 clear all;
 % http://github.com/rweigel/m-rsw/time
-addpath('../../m-rsw/time')
+addpath('../vveibell/m-rsw/time')
 
 % Read WGhourFS dataset from Kondrashov(2014)
 
@@ -125,6 +125,11 @@ else
     save(fnamem,'OH','ODN','OF107','ODst','OData');
 end
 
+
+%Move OMNI to Takahashi 2010 Fig 11 window
+ODN(ODN<datenum('Jan-01 1989'))=[];
+ODN(ODN>datenum('Jan-01 1992'))=[];
+
 % Select overlapping windows
 Io = max([ODN(1),DDN(1),KDN(1)]);
 If = min([ODN(end),DDN(end),KDN(end)]);
@@ -183,7 +188,7 @@ figure(1);clf;hold on;
     xlabel(['Minutes since ',datestr(DDN(1))])
     set(gca,'XLim',[0,1440-1])
 
-I = find(ODst(1:end-1) > -30 & ODst(2:end) < -30);
+I = find(ODst(1:end-1) > -50 & ODst(2:end) < -50);
 
 k = 1;
 for i = 1:length(I)

### 2015-07-23 interptest.m

@@ -6,7 +6,8 @@ end
 %tic
 datanew=zeros(length(tnew),min(size(x)));
 for i=1:length(tnew)
-    datanew(i,:)=nanmedian(x(t>=(tnew(i)-dt) & t<(tnew(i)+dt),:)); 
+    datanew(i,:)=nanmedian(x(t>=(tnew(i)-dt) & t<(tnew(i)+dt),:)); %Center
+    %datanew(i,:)=nanmedian(x(t>=(tnew(i)) & t<(tnew(i)+2*dt),:)); %Forwards time
 end
 %toc
 %datanew;

### 2015-07-23 paper.tex
Updated figures

@@
 
-In this work events are considered when $D_{st}$ or $\rho_{eq}$ crosses a threshold value, as indicated in \ref{StormCutoff}.
+In this work events are considered when $D_{st}$ or $\rho_{eq}$ crosses a threshold value, as indicated in \ref{AllData}.
 In finding events, all fill values were replaced with linearly interpolated values.
@@
 All show a similar spike in $\rho_{eq}$ at the time of $D_{st}$ minimum, though none quite reproduce the exact values seen in \cite{Takahashi2010}.
-Figure \ref{allstorms} shows where the median falls for all of the found storms during that period, as a sanity check for why the prior work would get median values nearing $30 amu/cm^3$.
+Figure \ref{allstorms} shows where the median falls for all of the found events during that period, as a sanity check for why the prior work would get median values nearing $30 amu/cm^3$.
 Both authors of this paper conducted independent trials to confirm that the data and analysis don't quite yield the results of Figure 11 in \cite{Takahashi2010} with the processes described in that paper, but the same general trend is still seen.
@@
 
+\clearpage
 \section{Figures}
@@
 \centering
-\includegraphics[scale=0.7]{paperfigures/alldata.eps}
+\includegraphics[scale=0.45]{paperfigures/alldata.eps}
 \caption{Overview of data used in this study.
 The top four panels are from \cite{Reconstruction} and the bottom panel is based on \cite{Denton} after interpolation and averaging described in the text.
-Dashed lines indicate default event cutoff thresholds.}
+Dashed horizontal lines indicate default event cutoff thresholds.}
 \label{AllData}
+\end{figure}
+
+\begin{figure}[htp!]
+\centering
+\includegraphics[scale=0.42]{paperfigures/DstMDAllData.eps}
+\includegraphics[scale=0.42]{paperfigures/ccplot.eps}
+\includegraphics[scale=0.42]{paperfigures/DSTvsMD.eps}
+\caption{(a) All data of $D_{st}$ and $\rho_{eq}$ (b) Correlation between $log(\rho_{eq\_27d})$ and $F_{10.7\_27d}$. (c) $D_{st}$ against $\rho_{eq}$ at one hour and one-day median values.  }
+\label{ccplot}
 \end{figure}
@@
 \centering
+\includegraphics[scale=0.45]{paperfigures/stormavs-dst-50-tak.eps}
 \includegraphics[scale=0.45]{paperfigures/stormavs-dst-day.eps}
-\includegraphics[scale=0.45]{paperfigures/stormavs-dst-50-tak.eps}
-\caption{(a) One-day medians of $D_{st}$ storms at a threshold of $-40nT$ and (b) verifying \cite{Takahashi2010} Fig. 11 conditions: $D_{st}<-50nT$ between 1989 and 1991}
+\caption{(a) Verifying \cite{Takahashi2010} Fig. 11 conditions: $D_{st}<-50nT$ between 1989 and 1991 and (b) One-day medians of $D_{st}$ events at a threshold of $-40nT$}
 \label{DailyAverages}
 \end{figure}
-\clearpage
-
-\begin{figure}[htp!]
-\centering
-\includegraphics[scale=0.42]{paperfigures/ccplot.eps}
-\includegraphics[scale=0.42]{paperfigures/DSTvsMD.eps}
-\includegraphics[scale=0.42]{paperfigures/DstMDAllData.eps}
-\caption{(a) Correlation between $log(\rho_{eq\_27d})$ and $F_{10.7\_27d}$. (b) $D_{st}$ against $\rho_{eq}$ at one hour and one-day median values. (c) All data of $D_{st}$ and $\rho_{eq}$ }
-\label{ccplot}
-\end{figure}
-\clearpage
-
-% Change x-label to be ``Time from start of event (hr)'' and put vertical lines in each panel at t = 0 (somewhere I have a code called vertline.m)
-\begin{figure}[htp]
-\centering
-(a)
-\includegraphics[scale=0.7]{paperfigures/massdensitystorms.eps}
-(b)
-\includegraphics[scale=0.7]{paperfigures/dststorms.eps}
-\caption{Averages around time of (a) 669 $\rho_{eq}$ and (b) 130 $D_{st}$ events along with thresholds used to define an event.
-The number of values used in the averages for mass density is shown in the bottom panel (a) and (b).}
-\label{StormCutoff}
-\end{figure}
-\clearpage
 
@@
 \includegraphics[scale=0.45]{paperfigures/stormavs-mass.eps}
-\caption{(a) Average of solar wind and near-Earth measurements around the time $D_{st}$ crossed below -40~nT onset.
-(b) Same as (a) except around time intervals where mass density crossed above $40 amu/cm^3$.
+\caption{(a) Average of solar wind and near-Earth measurements around the time $D_{st}$ crossed below $-50~nT$ onset.
+(b) Same as (a) except around time intervals where mass density crossed above $40~amu/cm^3$.
 The bottom panel shows the number of mass density data points that were used for the average.}
@@
 \includegraphics[scale=0.45]{paperfigures/stormavs-dd12.eps}
-\includegraphics[scale=0.45]{paperfigures/stormavs-d80.eps}
-\caption{(a) Same as \ref{fig:Storms}(a) except with constraint that $D_{st}$ stayed below -40~nT for at least 12~hours.
-(b) Same as \ref{fig:Storms}(b) except for constrain that $D_{st}$ crossed below $-80 nT$.}
+\includegraphics[scale=0.45]{paperfigures/stormavs-md12.eps}
+\caption{(a) Same as Figure \ref{Storms}(a) except with constraint that $D_{st}$ stayed below $-50~nT$ for at least 12~hours.
+(b) Same as Figure \ref{Storms}(b) except for constrain that $\rho_{eq}$ stayed above $50~amu/cm^3$ for at least 12 hours.}
 \label{Mspec}
 \end{figure}
-\clearpage
 
@@
 \centering
-\includegraphics[scale=0.45]{paperfigures/stormavs-md12.eps}
+\includegraphics[scale=0.45]{paperfigures/stormavs-d80.eps}
 \includegraphics[scale=0.45]{paperfigures/stormavs-m70.eps}
-\caption{(a) Same as \ref{fig:MassStorm}(a) except with constraint that $\rho_{eq}$ stayed above 50~nT for at least 12~hours.
-(b) Same as \ref{fig:Storms}(b) except for constrain that mass density crossed above $70 amu/cm^3$.}
+\caption{(a) Same as Figure \ref{Storms}(a) except with constraint that $D_{st}$ crossed below $-80nT$ (b) Same as Figure \ref{Storms}(b) except for constrain that $\rho_{eq}$ crossed above $70~amu/cm^3$.}
 \label{Dspec}
@@
 \centering
-\includegraphics[scale=0.5]{paperfigures/stormavs-diffden-10amu.eps}
-\includegraphics[scale=0.5]{paperfigures/stormavs-diffden-30percent.eps}
-\caption{diff($\rho_{eq}$) $>$ 10$\frac{amu}{hour}$, diff($\rho_{eq}$) $>$ 30$\frac{\%}{hour}$}
+\includegraphics[scale=0.45]{paperfigures/stormavs-diffden-10amu.eps}
+\includegraphics[scale=0.45]{paperfigures/stormavs-diffden-30percent.eps}
+\caption{(a) diff($\rho_{eq}$) $>$ 10$\frac{amu}{hour}$. (b) diff($\rho_{eq}$) $>$ 30$\frac{\%}{hour}$}
 \label{rhochange}
 \end{figure}
-\clearpage
 
@@
 \centering
-\includegraphics[scale=0.5]{paperfigures/stormavs-dst-nof107.eps}
-\includegraphics[scale=0.6]{paperfigures/f107removed.eps}
+\includegraphics[scale=0.45]{paperfigures/stormavs-dst-nof107.eps}
+\includegraphics[scale=0.5]{paperfigures/f107removed.eps}
 \caption{$D_{st}$ events where $\rho_{eq}$ has $F_{10.7}$ dependence removed, and Difference between original $\rho_{eq}$ and $F_{10.7}$-less $\rho_{eq}$}
@@
 \includegraphics[scale=0.75]{paperfigures/blockmedian-prenoon.eps}
-\caption{Comparing median values calculated as median of all 1-hour points in the 12 day block, and as the daily median of all hourly-mediated storms.
-(b) Same, but only storms starting between 0-12 UTC}
+\caption{Comparing median values calculated as median of all 1-hour points in the 12 day block, and as the daily median of all hourly-mediated events.
+(b) Same, but only events starting between 0-12 UTC}
 \label{blockmedian}
@@
 \includegraphics[scale=0.9]{paperfigures/allstorms.eps}
-\caption{Comparing all storms to their median and $1\sigma$ range}
+\caption{Comparing all events to their median and $1\sigma$ range}
 \label{allstorms}

### 2015-07-23 Density.m

@@ -8,8 +8,8 @@ if(~exist('data/WGhourFS_72_13.txt'))
 end
 FILLED=dlmread('data/WGhourFS_72_13.txt',',',1,0);
 FILLED=FILLED(FILLED(:,1)>1980,:); %Just to get into Denton time
-FILLED=FILLED(FILLED(:,1)>1988,:);
-FILLED=FILLED(FILLED(:,1)<1992,:); %For comparing to Takahashi 2010 Fig 11
+%FILLED=FILLED(FILLED(:,1)>1988,:);
+%FILLED=FILLED(FILLED(:,1)<1992,:); %For comparing to Takahashi 2010 Fig 11
 headers=textread('data/WGhourFS_72_13.txt','%s',28,'delimiter',',');
 VBS=1/2*FILLED(:,6).*(abs(FILLED(:,5))-FILLED(:,5));
 VBz=FILLED(:,6).*FILLED(:,5);
@@ -105,8 +105,8 @@ MassDensityNanSpline=interp1(OMNITime(~isnan(MassDensitySpline)),MassDensitySpli
 FILLED=[FILLED F107];
 headers{end+1}='F107';
 
-LongTimeScale=24;%24*27; %How many hours to average over. Best stick to 1, 24, or 24*27
-
+LongTimeScale=1;%24*27; %How many hours to average over. Best stick to 1, 24, or 24*27
+cutoffduration=1; %If you want to get rid of short (spurious?) storms, set larger than 1
 %Select kind of storm to look for
 stormcase=1;
 switch stormcase
@@ -118,6 +118,16 @@ switch stormcase
         storms=[0 diff([0 (diff(MassDensityNanSpline)>10)' 0])];
     case 4
         storms=[0 diff([0 (abs(MassDensityNanSpline(2:end)./MassDensityNanSpline(1:end-1))>1.3)' 0])];
+    case 5
+        storms=diff([0 (FILLED(:,15)<-50)' 0]);
+        cutoffduration=12; %12 hour DST storm
+    case 6
+        storms=diff([0 (MassDensityNanSpline>40)' 0]);
+        cutoffduration=12;
+    case 7
+         storms=diff([0 (FILLED(:,15)<-80)' 0]);
+    case 8
+        storms=diff([0 (MassDensityNanSpline>70)' 0]);        
 end
 starti=find(storms>0);
 endi=find(storms<0)-1;
[…]

### 2015-07-28 Density.m
Updating figures and code

@@ -107,27 +107,63 @@ headers{end+1}='F107';
 
 LongTimeScale=1;%24*27; %How many hours to average over. Best stick to 1, 24, or 24*27
 cutoffduration=1; %If you want to get rid of short (spurious?) storms, set larger than 1
+cutconditions=0; %Look at only pre-noon
+removef107=0;
+DSTCut=0;
+MDCut=0;
+figurename='paperfigures/stormavs-';
 %Select kind of storm to look for
 stormcase=1;
 switch stormcase
     case 1
         storms=diff([0 (FILLED(:,15)<-50)' 0]); %DST Storm
+        DSTCut=-50;
+        figurename=strcat(figurename,'dst.eps');
     case 2
         storms=diff([0 (MassDensityNanSpline>40)' 0]); %Mass Density Storm, started at 40
+        MDCut=40;
+        figurename=strcat(figurename,'mass.eps');
     case 3
         storms=[0 diff([0 (diff(MassDensityNanSpline)>10)' 0])];
+        figurename=strcat(figurename,'diffden-10amu.eps');
     case 4
         storms=[0 diff([0 (abs(MassDensityNanSpline(2:end)./MassDensityNanSpline(1:end-1))>1.3)' 0])];
+        figurename=strcat(figurename,'diffden-30percent.eps');
     case 5
         storms=diff([0 (FILLED(:,15)<-50)' 0]);
+        DSTCut=-50;
         cutoffduration=12; %12 hour DST storm
+        figurename=strcat(figurename,'dd12.eps');
     case 6
         storms=diff([0 (MassDensityNanSpline>40)' 0]);
+        MDCut=40;
         cutoffduration=12;
+        figurename=strcat(figurename,'md12.eps');
     case 7
          storms=diff([0 (FILLED(:,15)<-80)' 0]);
+         DSTCut=-80;
+         figurename=strcat(figurename,'d80.eps');
     case 8
-        storms=diff([0 (MassDensityNanSpline>70)' 0]);        
+        storms=diff([0 (MassDensityNanSpline>70)' 0]);  
+        MDCut=70;
+        figurename=strcat(figurename,'m70.eps');
+    case 9
[…]

### 2015-07-29 paper.tex
Updating figures and code
Edits to paper

@@
 
-The parameters $\rho_{eq}$ and $F_{10.7}$ used in this work are from the data associated with \cite{Denton}, with data available from 1980-1991; all other parameters are from \cite{Reconstruction} over the time range of 1972-2013, which are on a 1-hour time grid.
-In cases where $\rho_{eq}$ was available from multiple Geostationary Operational Environmental Satellites (GOES) satellites at the same time, the value from GOES 7 was selected to avoid overlapping data points.
+The parameters $\rho_{eq}$ and $F_{10.7}$ used in this work are from the dataset associated with \cite{Denton}, with data available from 1980-1991; all other parameters are from \cite{Reconstruction} over the time range of 1972-2013, which are on a 1-hour time grid.
 $\rho_{eq}$ is the inferred mass density based on the 3rd harmonic frequency of magnetic field measurements.
@@
 Fill values were used for hours when no measurements were available.
+In cases where $\rho_{eq}$ was available from multiple Geostationary Operational Environmental Satellites (GOES) satellites at the same time in the \cite{Denton} dataset, the value from GOES 7 was selected to avoid overlapping data points.
+An overview of the data is given in Figure~\ref{AllData}.
 
-In this work events are considered when $D_{st}$ or $\rho_{eq}$ crosses a threshold value, as indicated in \ref{AllData}.
+In this work events defined to occur when $D_{st}$ or $\rho_{eq}$ crosses a threshold value, as indicated in by horizontal dashed lines in the respective panels of Figure~\ref{AllData}.
 In finding events, all fill values were replaced with linearly interpolated values.
-Figure \ref{AllData} shows the values of $B_Z$, $V_{SW}$, $D_{st}$, $F_{10.7}$, and Mass Density for the duration of the dataset.
+Figure \ref{AllData} shows the values of $B_z$, $V_{SW}$, $D_{st}$, $F_{10.7}$, and Mass Density for the duration of the dataset.
 
@@
 \caption{Overview of data used in this study.
-The top four panels are from \cite{Reconstruction} and the bottom panel is based on \cite{Denton} after interpolation and averaging described in the text.
-Dashed horizontal lines indicate default event cutoff thresholds.}
+The top four panels show parameters from \cite{Reconstruction} and the bottom panel is based on $\rho_{eq}$ from \cite{Denton} after interpolation and averaging described in the text.
+Dashed horizontal lines in the $D_{st}$ and $\rho_{eq}$ panels indicate sample event cutoff thresholds of $D_{st}=-50~nT$ and $\rho_{eq}$=40~amu/cm^3$}.
 \label{AllData}
@@
 \centering
-\includegraphics[scale=0.42]{paperfigures/DstMDAllData.eps}
+\includegraphics[scale=0.42]{paperfigures/F107MDAllData.eps}
 \includegraphics[scale=0.42]{paperfigures/ccplot.eps}
-\includegraphics[scale=0.42]{paperfigures/DSTvsMD.eps}
+\includegraphics[scale=0.42]{paperfigures/F107vsMD.eps}
 \caption{(a) All data of $D_{st}$ and $\rho_{eq}$ (b) Correlation between $log(\rho_{eq\_27d})$ and $F_{10.7\_27d}$. (c) $D_{st}$ against $\rho_{eq}$ at one hour and one-day median values.  }
@@
 \includegraphics[scale=0.45]{paperfigures/stormavs-dst-day.eps}
-\caption{(a) Verifying \cite{Takahashi2010} Fig. 11 conditions: $D_{st}<-50nT$ between 1989 and 1991 and (b) One-day medians of $D_{st}$ events at a threshold of $-40nT$}
+\caption{(a) Verifying \cite{Takahashi2010} Fig. 11 conditions: $D_{st}<-50nT$ between 1989 and 1991 and (b) Same as (a) but for 1987 to 1991, and not just pre-noon events}
 \label{DailyAverages}

### 2015-07-29 paper.tex
Minor edits to Previous Results section

@@
 \usepackage{graphicx}
-\usepackage{subfigure}
 \usepackage{fancyhdr}
@@
 \usepackage{abstract}
+\usepackage{subcaption}
 
@@
 \begin{abstract}
-This paper looks at how various magnetosphere conditions behave around the onset of geomagnetic events.
-It confirms results from previous papers that a sudden drop in $D_{st}$ correlates with a spike in equatorial mass density, while adding a level of depth and specification to the applicability of their results.
-It compares data at 1-hour averages to data at 1-day averages, and briefly to data at 27-day averages to examine if the trend holds at varying time scales and finds that it does, so long as the data is pre-processed to linearly remove a large time scale $F_{10.7}$ dependence.
+This paper compares various magnetosphere conditions around the onset of geomagnetic events.
+It confirms results from previous papers that a sudden drop in $D_{st}$ correlates with a spike in equatorial mass density under certain conditions, while adding a level of depth and specification to the applicability of their results.
+It compares data at 1-hour averages to data at 1-day averages to examine if the trend holds at varying time scales and finds that it does, so long as the data is pre-processed to linearly remove a large time scale $F_{10.7}$ dependence.
 By then looking at an hourly average of parameters from 24 hours before event onset to 48 hours after, short timescale trends can be discerned.
@@
 \saythanks
-% while adding a level of depth and specification to the applicability of their results.
-It compares data at 1-hour averages to data at 1-day averages, and briefly to data at 27-day averages to examine if the trend holds at varying time scales and finds that it does, so long as the data is pre-processed to linearly remove a large time scale $F_{10.7}$ dependence.
 
@@
 In cases where $\rho_{eq}$ was available from multiple Geostationary Operational Environmental Satellites (GOES) satellites at the same time in the \cite{Denton} dataset, the value from GOES 7 was selected to avoid overlapping data points.
+In the dataset, measurements from GOES 7 had the longest time span of coverage.
 An overview of the data is given in Figure~\ref{AllData}.
+
+% How does GOES 7 only effect result.
 
@@
 \subsection{Previous Results}
+
+Figure~\ref{ccplot:a} shows the long-term trends of $log(\rho_{eq})$ and $F_{10.7}$ by computing the median in 27-day windows using all non--fill hourly values.
+A scatter plot of these two lines is shown in Figure~\ref{ccplot:b}.
+The linear correlation is found to be $0.87$.
+In comparison, \cite{Takahashi2010} found a correlation coefficient of $0.94$ using measurements from all satellites in the time interval of 1980 to 1992.
+
+The correlation seen between 27-day averages $log(\rho_{eq\_27d})$ and $F_{10.7\_27d}$ isn't quite as good in this data as in \cite{Takahashi2010}, but shows the same trend as seen in Figure \ref{ccplot}.
+
 Figure \ref{DailyAverages} show that the trends observed by \cite{Takahashi2010} for one day averages only seems to hold true for the one-day averaged data.
 Namely that a drop in median daily $D_{st}$ between 1989 and 1991 coincides with a significant spike in $\rho_{eq}$.
-The correlation seen between $log(\rho_{eq\_27d})$ and $F_{10.7\_27d}$ isn't quite as good in this data as in \cite{Takahashi2010}, but shows the same trend as seen in Figure \ref{ccplot}.
 
@@
 \centering
-\includegraphics[scale=0.42]{paperfigures/F107MDAllData.eps}
-\includegraphics[scale=0.42]{paperfigures/ccplot.eps}
-\includegraphics[scale=0.42]{paperfigures/F107vsMD.eps}
-\caption{(a) All data of $D_{st}$ and $\rho_{eq}$ (b) Correlation between $log(\rho_{eq\_27d})$ and $F_{10.7\_27d}$. (c) $D_{st}$ against $\rho_{eq}$ at one hour and one-day median values.  }
+\subcaptionbox{All data of $F_{10.7\_27d}$ and $\rho_{eq\_27d}$ \label{ccplot:a}}
+{\includegraphics[scale=0.42]{paperfigures/F107MDAllData.eps}}
+\subcaptionbox{ Correlation between $log(\rho_{eq\_27d})$ and $F_{10.7\_27d}$, compare to \cite{Takahashi2010} Fig. 14  \label{ccplot:b}}
+{\includegraphics[scale=0.42]{paperfigures/ccplot.eps}}
+\subcaptionbox{$D_{st}$ against $\rho_{eq}$ at one hour and one-day median values. \label{ccplot:c}}
+{\includegraphics[scale=0.42]{paperfigures/F107vsMD.eps}}
+\caption{Correlation and comparisons between $F_{10.7}$ and $\rho_{eq}$}
 \label{ccplot}
@@
 \includegraphics[scale=0.5]{paperfigures/nansbyhour_storm.eps}
-\caption{(a) Number of NaN points per hour of observation in the total data set (b) Data availability relative to average event hour in events where $D_{st}<-80nT$}
+\caption{(a) Number of NaN points per hour of observation in the total data set (b) $\rho_{eq}$ data availability relative to average event hour in events where $D_{st}<-80nT$}
 \label{nanperhour}

### 2015-07-30 Density.m
Updating figures for satellite 6

@@ -2,14 +2,21 @@ function Density
 
 close all;clear all;
 
+TakahashiCond=0;
+satnum=6;
+
 %Read filled dataset from Kondrashov(2014)
 if(~exist('data/WGhourFS_72_13.txt'))
     urlwrite('http://mag.gmu.edu/git-data/victoirv/Density/data/WGhourFS_72_13.txt','data/WGhourFS_72_13.txt');
 end
-FILLED=dlmread('data/WGhourFS_72_13.txt',',',1,0);
+FILLED=dlmread('data/WGhourFS_72_13.txt',',',1,0); 
+%Data from supplementary section of http://onlinelibrary.wiley.com/doi/10.1002/2014GL059741/full
 FILLED=FILLED(FILLED(:,1)>1980,:); %Just to get into Denton time
-%FILLED=FILLED(FILLED(:,1)>1988,:);
-%FILLED=FILLED(FILLED(:,1)<1992,:); %For comparing to Takahashi 2010 Fig 11
+
+if(TakahashiCond)
+    FILLED=FILLED(FILLED(:,1)>1988,:);
+    FILLED=FILLED(FILLED(:,1)<1992,:); %For comparing to Takahashi 2010 Fig 11
+end
 headers=textread('data/WGhourFS_72_13.txt','%s',28,'delimiter',',');
 VBS=1/2*FILLED(:,6).*(abs(FILLED(:,5))-FILLED(:,5));
 VBz=FILLED(:,6).*FILLED(:,5);
@@ -18,13 +25,14 @@ OMNIDensity=FILLED(:,7);
 OMNITime=datenum(FILLED(:,1),1,0)+FILLED(:,2)+FILLED(:,3)/24;
 %VBS=1/2*Plasma_bulk_speed.*(abs(Bz_GSM)-Bz_GSM);
 
+
 %Get Denton data (mostly just for mass density)
-if(exist('DentonDensityAndTime.mat','file'))
-    load('DentonDensityAndTime')
+if(exist(sprintf('DentonDensityAndTime_%d.mat',satnum),'file'))
+    load(sprintf('DentonDensityAndTime_%d',satnum))
 else
-    urlwrite('http://mag.gmu.edu/git-data/victoirv/Density/massdensity.txt','/tmp/massdensity.txt');
-    IN=dlmread('/tmp/massdensity.txt');
-    IN(IN(:,1)~=7,:)=[]; %Only use satellite 7 (6 should also work)
[…]

### 2015-07-30 paper.tex

@@
 \usepackage{abstract}
-\usepackage{subcaption}
+\usepackage[position=t,singlelinecheck=off,justification=raggedleft]{subcaption}
 
@@
 \centering
-\subcaptionbox{All data of $F_{10.7\_27d}$ and $\rho_{eq\_27d}$ \label{ccplot:a}}
+\subcaptionbox{\label{ccplot:a}}
 {\includegraphics[scale=0.42]{paperfigures/F107MDAllData.eps}}
-\subcaptionbox{ Correlation between $log(\rho_{eq\_27d})$ and $F_{10.7\_27d}$, compare to \cite{Takahashi2010} Fig. 14  \label{ccplot:b}}
+\subcaptionbox{\label{ccplot:b}}
 {\includegraphics[scale=0.42]{paperfigures/ccplot.eps}}
-\subcaptionbox{$D_{st}$ against $\rho_{eq}$ at one hour and one-day median values. \label{ccplot:c}}
-{\includegraphics[scale=0.42]{paperfigures/F107vsMD.eps}}
-\caption{Correlation and comparisons between $F_{10.7}$ and $\rho_{eq}$}
+\caption{(a) All data of $F_{10.7\_27d}$ and $\rho_{eq\_27d}$. (b) Correlation between $log(\rho_{eq})$ and $F_{10.7}$ at hour, day, and 27-day intervals; compare to \cite{Takahashi2010} Fig. 14}
 \label{ccplot}

### 2015-07-30 Density2.m
Additions for Density2.m

@@ -2,208 +2,303 @@
 
 clear all;
 % http://github.com/rweigel/m-rsw/time
-addpath('../vveibell/m-rsw/time')
-
-% Read WGhourFS dataset from Kondrashov(2014)
-
-% WGhourFS_72_13.txt from http:// on DATE
-fnamem = 'data/WGhourFS_72_13.mat';
-fnamet = 'data/WGhourFS_72_13.txt';
-
-if exist(fnamem,'file')
-    fprintf('Loading %s\n',fnamem)
-    load('./data/WGhourFS_72_13.mat')
-else
-
-    if(~exist(fnamet,'file'))
-        url = ['http://mag.gmu.edu/git-data/victoirv/Density/',fnamet];
-        fprintf('Getting %s\n',url);
-        urlwrite(url,fnamet);
-    end
-
-    fprintf('Reading %s\n',fnamet)
-
-    KHead = textread(fnamet,'%s',28,'delimiter',',');
-    KData = dlmread(fnamet,',',1,0);
-
-    KVBs = 1/2*KData(:,6).*(abs(KData(:,5))-KData(:,5));
-    KVBz = KData(:,6).*KData(:,5);
-    KBs  = 1/2*(abs(KData(:,5))-KData(:,5));
-
-    KDensity = KData(:,7);
-
-    [Y,M,D] = ymd(KData(:,2),KData(:,1),'day');
-
-    KTo = [Y(1),M(1),D(1),KData(1,3)];
-
-    KDNo = datenum([Y(1),M(1),D(1)]); % Datenum of first row.
-    KDN  = datenum([Y,M,D]);          % Datenum of each row.
-
-    KH  = KData(:,3);
-
-    fprintf('Saving %s\n',fnamem)
-    save(fnamem,'KH','KDN','KVBs','KVBz','KBs','KDensity','KData','KHead')
+if ~exist('m-rsw')
+    system('git clone http://github.com/rweigel/m-rsw')
+    addpath('./m-rsw/time')
 end
 
-%Get Denton data (mostly just for mass density)
-fnamem = 'data/massdensity.mat';
-fnamet = 'data/massdensity.txt';
-if(exist(fnamem,'file'))
-    fprintf('Loading %s\n',fnamem)
-    load(fnamem)
-else
-    if(~exist(fnamet,'file'))
-        url = ['http://mag.gmu.edu/git-data/victoirv/Density/',fnamet];
[…]

### 2015-07-30 plotcmds.m

@@ -1,0 +1,43 @@
+function plotcmds(fname,writeimgs)
+%PLOTCMDS
+
+% Prefix filenames with name of script that generated.
+s = dbstack;
+base = ['./figures/',s(end).name,'_',fname];
+
+if ~exist('./figures')
+	mkdir('./figures')
+end
+
+a = get(gcf,'Children');
+for i = 1:length(a)
+	b = get(a(i));
+	if isfield(b,'Location') % The legend object.
+		set(a(i),'Color','none'); % Set legend background to transparent.
+	else
+		set(get(a(i),'Title'),'FontSize',14)
+		set(get(a(i),'XLabel'),'FontSize',14)
+		set(get(a(i),'YLabel'),'FontSize',14)
+	end
+end
+
+if (nargin == 2 && ~writeimgs)
+	return
+end
+
+fprintf('plotcmds: Writing (using print)\n  %s.eps\n',base);
+print('-depsc',sprintf('%s.eps',base))
+fprintf('  Done. \n',base);
+
+if exist('/usr/local/bin/convert')
+	fprintf('plotcmds: Writing (using convert on eps)\n  %s.png\n',base);
+	% MATLAB does not allow quality parameter for png.
+	% Use convert if available to create a better image.
+	com = sprintf('convert -quality 100 -density 150 %s.eps %s.png',base,base);
+	system(com);
+	fprintf('  Done.\n',base);
+else
+	fprintf('plotcmds: Writing (using print)\n  %s.png\n',base);
+	print('-dpng',sprintf('%s.png',base))
+	fprintf('  Done.\n',base);
+end

### 2015-07-30 paper.tex

@@
 The top four panels show parameters from \cite{Reconstruction} and the bottom panel is based on $\rho_{eq}$ from \cite{Denton} after interpolation and averaging described in the text.
-Dashed horizontal lines in the $D_{st}$ and $\rho_{eq}$ panels indicate sample event cutoff thresholds of $D_{st}=-50~nT$ and $\rho_{eq}$=40~amu/cm^3$}.
+Dashed horizontal lines in the $D_{st}$ and $\rho_{eq}$ panels indicate sample event cutoff thresholds of $D_{st}=-50~nT$ and $\rho_{eq}=40~amu/cm^3$}.
 \label{AllData}

### 2015-07-30 Density2.m
Clear storm variables and check for no events in Density2.m

@@ -248,6 +248,7 @@ for sat = [2,3,5,6,7]
     fprintf('cc(OF107,log10(DDensityMean)   = %.3f\n',tmp(2));
 
     I = find(DDstMedian(1:end-1) > -50 & DDstMedian(2:end) < -50);
+    clear *Storm*
 
     k = 1;
     for i = 1:length(I)
@@ -261,44 +262,49 @@ for sat = [2,3,5,6,7]
         k = k+1;
     end
 
-    t = [-24:24];
-    figure(1);clf;hold on;grid on;
-        plot(t,nanmean(DDensityMedianStorm),'b','LineWidth',3)
-        plot(t,nanmean(-DDstStorm),'g','LineWidth',3)
-        plot(t,nanmean(DNGoodStorm),'k','LineWidth',1)
-        title(sprintf('GOES-%d; %s-%s',sat,datestr(Io),datestr(If)))
-        xlabel('Time since onset [hrs]')
-        legend('Density [amu/cm^3]','-Dst [nT]','# values','Location','NorthWest')
-        fname = sprintf('Dst_Event_GOES%d_%s_%s',sat,datestr(Io,29),datestr(If,29));
-        title(sprintf('GOES-%d; %s-%s; %d Dst Events',sat,datestr(Io),datestr(If),length(I)));
-        set(gca,'XTick',[-24:2:24])
-        plotcmds(fname,1)
+    if (length(I) > 0)
+        t = [-24:24];
+        figure(1);clf;hold on;grid on;
+            plot(t,nanmean(DDensityMedianStorm),'b','LineWidth',3)
+            plot(t,nanmean(-DDstStorm),'g','LineWidth',3)
+            plot(t,nanmean(DNGoodStorm),'k','LineWidth',1)
+            title(sprintf('GOES-%d; %s-%s',sat,datestr(Io),datestr(If)))
+            xlabel('Time since onset [hrs]')
+            legend('Density [amu/cm^3]','-Dst [nT]','# values','Location','NorthWest')
+            fname = sprintf('Dst_Event_GOES%d_%s_%s',sat,datestr(Io,29),datestr(If,29));
+            title(sprintf('GOES-%d; %s-%s; %d Dst Events',sat,datestr(Io),datestr(If),length(I)));
+            set(gca,'XTick',[-24:2:24])
+            plotcmds(fname,1)
+    end
 
     I = find(DDensityMedian(1:end-1) < 30 & DDensityMedian(2:end) > 30);
+    clear *Storm*
 
[…]

### 2015-08-25 paper.tex
Comparing to Weigel2010 Fig 8

@@
 \usepackage[position=t,singlelinecheck=off,justification=raggedleft]{subcaption}
-
 \usepackage[authoryear,square]{natbib}
@@
 \section{Data Preparation}
-
-The parameters $\rho_{eq}$ and $F_{10.7}$ used in this work are from the dataset associated with \cite{Denton}, with data available from 1980-1991; all other parameters are from \cite{Reconstruction} over the time range of 1972-2013, which are on a 1-hour time grid.
+The parameters $\rho_{eq}$ used in this work is from the dataset associated with \cite{Denton}, with data available from 1980-1991 on a non-uniform 10 minute grid.
+The $F_{10.7}$ parameter comes from the OMNIWeb data collection at \cite{OMNIWeb} and covers 1980-2000 on an hourly grid, but with one daily value repeated for each hour of the day.
+All other parameters are from \cite{Reconstruction} over the time range of 1972-2013, which are on a 1-hour time grid.
 $\rho_{eq}$ is the inferred mass density based on the 3rd harmonic frequency of magnetic field measurements.
@@
 Fill values were used for hours when no measurements were available.
-In cases where $\rho_{eq}$ was available from multiple Geostationary Operational Environmental Satellites (GOES) satellites at the same time in the \cite{Denton} dataset, the value from GOES 7 was selected to avoid overlapping data points.
-In the dataset, measurements from GOES 7 had the longest time span of coverage.
+In cases where $\rho_{eq}$ was available from multiple Geostationary Operational Environmental Satellites (GOES) satellites at the same time in the \cite{Denton} dataset, the value from GOES 6 was selected to avoid overlapping data points.
+In the dataset, measurements from GOES 6 had the longest time span of coverage.
 An overview of the data is given in Figure~\ref{AllData}.
 
-% How does GOES 7 only effect result.
-
-In this work events defined to occur when $D_{st}$ or $\rho_{eq}$ crosses a threshold value, as indicated in by horizontal dashed lines in the respective panels of Figure~\ref{AllData}.
+In this work events are defined to occur when $D_{st}$ or $\rho_{eq}$ crosses a threshold value, as indicated in by horizontal dashed lines in the respective panels of Figure~\ref{AllData}.
 In finding events, all fill values were replaced with linearly interpolated values.
@@
 \includegraphics[scale=0.45]{paperfigures/stormavs-dst-50-tak.eps}
-\includegraphics[scale=0.45]{paperfigures/stormavs-dst-day.eps}
-\caption{(a) Verifying \cite{Takahashi2010} Fig. 11 conditions: $D_{st}<-50nT$ between 1989 and 1991 and (b) Same as (a) but for 1987 to 1991, and not just pre-noon events}
+\rule[1ex]{5cm}{0.5pt}
+\includegraphics[scale=0.45]{paperfigures/stormavs-mass-tak.eps}
+\caption{(a) Verifying \cite{Takahashi2010} Fig. 11 conditions: $D_{st}<-50nT$ between 1989 and 1991 and (b) Same as (a) but for $\rho_{eq}$ events}
 \label{DailyAverages}
@@
 \centering
+\includegraphics[scale=0.45]{paperfigures/stormavs-dst-day.eps}
+\rule[1ex]{5cm}{0.5pt}
+\includegraphics[scale=0.45]{paperfigures/stormavs-mass-day.eps}
+\caption{Daily averages for all events in full time range for (a) $D_{st}<-50~nT$ events and (b) $\rho_{eq}>40~amu/cm^3$ events}
+\label{DailyAveragesAllData}
+\end{figure}
+\clearpage
+
+\begin{figure}[htp!]
+\centering
 \includegraphics[scale=0.45]{paperfigures/stormavs-dst.eps}
+\rule[1ex]{5cm}{0.5pt}
 \includegraphics[scale=0.45]{paperfigures/stormavs-mass.eps}
@@
 \end{figure}
-\clearpage
 
@@
 \includegraphics[scale=0.45]{paperfigures/stormavs-dd12.eps}
+\rule[1ex]{5cm}{0.5pt}
 \includegraphics[scale=0.45]{paperfigures/stormavs-md12.eps}
@@
 \end{figure}
+\clearpage
 
@@
 \includegraphics[scale=0.45]{paperfigures/stormavs-d80.eps}
+\rule[1ex]{5cm}{0.5pt}
 \includegraphics[scale=0.45]{paperfigures/stormavs-m70.eps}
@@
 \label{Dspec}
+\end{figure}
+
+\begin{figure}[htp!]
+\centering
+\includegraphics[scale=0.45]{paperfigures/stormavs-diffden-10amu.eps}
+\rule[1ex]{5cm}{0.5pt}
+\includegraphics[scale=0.45]{paperfigures/stormavs-diffden-30percent.eps}
+\caption{(a) diff($\rho_{eq}$) $>$ 10$\frac{amu}{hour}$. (b) diff($\rho_{eq}$) $>$ 30$\frac{\%}{hour}$}
+\label{rhochange}
 \end{figure}
@@
 \centering
-\includegraphics[scale=0.45]{paperfigures/stormavs-diffden-10amu.eps}
-\includegraphics[scale=0.45]{paperfigures/stormavs-diffden-30percent.eps}
-\caption{(a) diff($\rho_{eq}$) $>$ 10$\frac{amu}{hour}$. (b) diff($\rho_{eq}$) $>$ 30$\frac{\%}{hour}$}
-\label{rhochange}
-\end{figure}
-
-\begin{figure}[htp!]
-\centering
 \includegraphics[scale=0.45]{paperfigures/stormavs-dst-nof107.eps}
-\includegraphics[scale=0.5]{paperfigures/f107removed.eps}
+\includegraphics[scale=0.45]{paperfigures/f107removed.eps}
 \caption{$D_{st}$ events where $\rho_{eq}$ has $F_{10.7}$ dependence removed, and Difference between original $\rho_{eq}$ and $F_{10.7}$-less $\rho_{eq}$}
@@
 \centering
-\includegraphics[scale=0.75]{paperfigures/blockmedian.eps}
-\includegraphics[scale=0.75]{paperfigures/blockmedian-prenoon.eps}
+\includegraphics[scale=0.45]{paperfigures/blockmedian.eps}
+\includegraphics[scale=0.45]{paperfigures/blockmedian-prenoon.eps}
 \caption{Comparing median values calculated as median of all 1-hour points in the 12 day block, and as the daily median of all hourly-mediated events.

### 2015-08-25 Density.m

@@ -175,7 +175,7 @@ switch stormcase
         cutconditions=1;
         %cutoffduration=12;
         figurename=strcat(figurename,'dst-50-tak-hour.eps');
-    case 13
+    case 13 %Full time range, daily medians
         storms=diff([0 (FILLED(:,15)<-50)' 0]);
         DSTCut=-50;
         LongTimeScale=24;
@@ -294,7 +294,7 @@ if(MakePlots)
 end
 
 %Median of medians vs block median
-if(MakePaperPlots && LongTimeScale==24)
+if(MakePaperPlots && LongTimeScale==24 && stormcase==10)
     h=figure('Visible',visible);
     plot(xa(2:end),AVMDblock)
     hold on; plot(xa(2:end),AVMDs(2:end),'r')
@@ -386,6 +386,22 @@ if(MakePaperPlots && stormcase==1)
     legend(sprintf('F_{10.7}>%2.0f',highsplit),sprintf('%2.0f>F_{10.7}>%2.0f',highsplit,medf107),sprintf('%2.0f>F_{10.7}>%2.0f',medf107,lowsplit),sprintf('%2.0f>F_{10.7}',lowsplit),'Location','SouthWest');
     title(sprintf('%d events of D_{st} > %dnT for %d-%d',length(starti),DSTCut,year(OMNITime(1)),year(OMNITime(end))))
     print -depsc2 -r200 paperfigures/HighLowF107Bz.eps
+    
+    
+    h=figure('Visible',visible);
+    medrho=nanmedian(MassDensitySpline);
+    highsplitrho=nanmedian(MassDensitySpline(MassDensitySpline>medrho));
+    lowsplitrho=nanmedian(MassDensitySpline(MassDensitySpline<medrho));
+    midhighrhobz=nanmedian(AVMat(MassDensitySpline(starti)>medrho & MassDensitySpline(starti)<highsplitrho,:,5),1);
+    midlowrhobz=nanmedian(AVMat(MassDensitySpline(starti)<medrho & MassDensitySpline(starti)>lowsplitrho,:,5),1);
+    highrhobz=nanmedian(AVMat(MassDensitySpline(starti)>highsplitrho,:,5),1);
+    lowrhobz=nanmedian(AVMat(MassDensitySpline(starti)<lowsplitrho,:,5),1);
+    plot(xa,[highrhobz; midhighrhobz; midlowrhobz; lowrhobz]);
[…]

### 2015-08-25 Density.m
Moving pngs

@@ -338,6 +338,7 @@ if(MakePaperPlots && stormcase==1)
     xlabel('Year')
     %set(gcf,'NextPlot','add'); axes; h = title(sprintf('All data',length(duration)));set(gca,'Visible','off');set(h,'Visible','on');
     print -depsc2 -r200 paperfigures/alldata.eps
+    print -dpng -r200 paperfigures/PNGs/alldata.png
     
     
     h=figure('Visible',visible);
@@ -347,6 +348,7 @@ if(MakePaperPlots && stormcase==1)
     plot(xa,AVMDs(1,:),'r','LineWidth',3);
     hold on; plot(xa,AVMDMatBars(:,:),'r-.','LineWidth',2);
     print -depsc2 -r200 paperfigures/allstorms.eps
+    print -dpng -r200 paperfigures/PNGs/allstorms.png
     
     h=figure('Visible',visible);
     medf107=nanmedian(FILLED(:,end));
@@ -362,6 +364,7 @@ if(MakePaperPlots && stormcase==1)
     legend(sprintf('F_{10.7}>%2.0f',highsplit),sprintf('%2.0f>F_{10.7}>%2.0f',highsplit,medf107),sprintf('%2.0f>F_{10.7}>%2.0f',medf107,lowsplit),sprintf('%2.0f>F_{10.7}',lowsplit),'Location','SouthWest');
     title(sprintf('%d events of D_{st} < %dnT for %d-%d',length(starti),DSTCut,year(OMNITime(1)),year(OMNITime(end))))
     print -depsc2 -r200 paperfigures/HighLowF107dst.eps
+    print -dpng -r200 paperfigures/PNGs/HighLowF107dst.png
     
     h=figure('Visible',visible);
     midhighf107rho=nanmedian(AVMDMat(FILLED(starti,29)>medf107 & FILLED(starti,29)<highsplit,:),1);
@@ -374,6 +377,7 @@ if(MakePaperPlots && stormcase==1)
     legend(sprintf('F_{10.7}>%2.0f',highsplit),sprintf('%2.0f>F_{10.7}>%2.0f',highsplit,medf107),sprintf('%2.0f>F_{10.7}>%2.0f',medf107,lowsplit),sprintf('%2.0f>F_{10.7}',lowsplit),'Location','SouthWest');
[…]

### 2015-08-31 Density2.m
Mods to Density2.m and regrid.m

@@ -7,7 +7,8 @@ if ~exist('m-rsw')
     addpath('./m-rsw/time')
 end
 
-for sat = [2,3,5,6,7]
+%for sat = [2,3,5,6,7]
+for sat = [6]
 
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
     % Read WGhourFS dataset from Kondrashov (2014)
@@ -153,11 +154,13 @@ for sat = [2,3,5,6,7]
 
         DData = IN;
         fprintf('Saving %s\n',fnamem);
-        save(fnamem,'DHM','DDN','DBz','DVsw','DDensitySW','DDst','DF107','DDensity','DMLT','DData');
+        save(fnamem,'DHM','DDN','DBz','DVsw','DDensitySW',...
+                'DDst','DF107','DDensity','DMLT','DData');
     end
 
     % Select overlapping windows
     Io = max([ODN(1),DDN(1),KDN(1)]);
+    Io = datenum('1989-01-01');
     If = min([ODN(end),DDN(end),KDN(end)]);
 
     fprintf('Overlapping time window is %s through %s\n',datestr(Io),datestr(If));
@@ -176,14 +179,16 @@ for sat = [2,3,5,6,7]
     DHM = DHM(ID,:);
     DBz = DBz(ID);
     DVsw = DVsw(ID);
-    DDensitySW = DDensity(ID);
+    DDensitySW = DDensitySW(ID);
     DF107 = DF107(ID);
+    DDst  = DDst(ID);
     DDensity = DDensity(ID);
     DMLT = DMLT(ID);
     %[DDN(1),DHM(1),DF107(1);DDN(end),DHM(end,:),DF107(end)]
 
-    fprintf('Computing means and medians in 1-hour time windows for Denton data.\n')
-    [DDNMedian,DHMMedian,DXMedian,DXMean,DNGood] = regrid(DDN,DHM,[DBz,DVsw,DDensitySW,DDst,DF107,DMLT,DDensity]);
+    fprintf('Computing means and medians in 1-hour windows for Denton data.\n')
+    [DDNMedian,DHMMedian,DXMedian,DXMean,DNGood] = ....
+        regrid(DDN,DHM,[DBz,DVsw,DDensitySW,DDst,DF107,DMLT,DDensity]);
 
[…]

### 2015-08-31 regrid.m

@@ -18,15 +18,6 @@ DNf(To+1)   = DN;
 HMf(To+1,:) = HM;
 Xf(To+1,:)  = X;
 
-% Place NaNs in all rows where last column of Xf (Density) is a NaN
-If = find(isnan(Xf(:,end)));
-Tf(If)    = NaN;
-DNf(If)   = NaN;
-HMf(If,:) = NaN;
-for i = 1:size(Xf,2)-1
-	Xf(If,i) = NaN;
-end
-
 % Reshape 1-min grid arrays have columns with 60 rows
 DNfr = reshape(DNf,60,length(DNf)/60);
 Tfr = reshape(Tf,60,length(Tf)/60);
@@ -55,6 +46,7 @@ for i = 1:Nc
 	XMedian(:,i) = nanmedian(Xfr{i},1);
 	XMean(:,i)   = nanmean(Xfr{i},1);
 end
+
 if (0)
 figure(1);clf;hold on;
     plot(To,X(:,end),'b.','MarkerSize',30)

### 2015-08-31 paper.tex
Fixed to text

--- 2015-07-30 paper.tex
@@
 \begin{abstract}
-This paper compares various magnetosphere conditions around the onset of geomagnetic events.
-It confirms results from previous papers that a sudden drop in $D_{st}$ correlates with a spike in equatorial mass density under certain conditions, while adding a level of depth and specification to the applicability of their results.
+This paper compares various magnetosphere conditions around the onset of geomagnetic events, defined as decreases in $D_{st}$ below a threshold value or $\rho_{eq}$ above a threshold value.
+
+%It confirms results from previous papers that a sudden drop in $D_{st}$ correlates with a spike in equatorial mass density under certain conditions, while adding a level of depth and specification to the applicability of their results.
 It compares data at 1-hour averages to data at 1-day averages to examine if the trend holds at varying time scales and finds that it does, so long as the data is pre-processed to linearly remove a large time scale $F_{10.7}$ dependence.
@@
 \section{Introduction}
-% try is colloqual.  
-% hope is colloqual.
-% intends is colloqual.
 
-\cite{Takahashi2006}, show how trends in storm dependence on mass/density only appear in longer timescales.
-Looking at $K_p$ vs mass ($amu$) in the range of 6 to 7 $R_E$, a trend shows up in the 1.5 day averages that doesn't appear in the 3 hour averages.
+\cite{Takahashi2006} estimated magnetospheric mass density using measurements from the CRRES satellite during a 73-day period and 1991 and found that the average ion mass density, $M=\rho/n_e$, depended on geomagnetic activity, with lower $D_{st}$ values corresponding to slightly average ion mass densities.
+They also found a $K_p$ dependence between the average ion mass and 1.5- and 3-day averages of $K_p$ were compared to $M$.
+Most measurements occurred in the MLT range of 12:00 and 18:00 MLT in the plasma trough (in equatorial plane?)
 
-\cite{Denton2006} show how $D_{st}$ affects the distribution of plasma density along different magnetic latitudes, and specifically along the same field lines as looked at in later papers (6-8$R_E$).
+\cite{Takahashi2010} developed a mass density dataset using measurements from the GOES satellites over the years 1980 through 1992, with most measurements in the range $L=6.8\pm0.2$ The equatorial mass density, $\rho_eq$ was estimated from the estimated mass density a power law dependence on the geocentric radius $R$, $\rho=\rho_{eq}(LR_E/R)$.
+A key result was that when daily-averaged measurements were considered, an enhancment in $\rho_{eq}$ appeared, indicating the possibility of a geomagnetic storm control over $\rho_{eq}$.
+
+\cite{Takahashi2010} noted that downward spikes in the $D_{st}$ index coincide with with significant changes in $\rho_{eq}$ at an L-shell of 6.8~$R_E$.
+For five storms over a 20 day period, two had $\rho_{eq}$ spikes after the $D_{st}$ drop, two had $\rho_{eq}$ spikes before the drop, and one showed little change in $\rho_{eq}$.
+They then show an epoch analysis where $\rho_{eq}$ is seen to spike the day of a $D_{st}$ drop, using a daily average of 30 minute $\rho_{eq}$ and one hour $D_{st}$ measurements.
+
+The results of \cite{Takahashi2006} and \cite{Takahashi2010} are consistent with other results on changes in mass density in the plasma trough region.
+\cite{Hamilton1988} ...
+\cite{Gallagher1988} ....
+\cite{Yao2008} studied the relationship between $D_{st}$ and ion number density for different ions in different regions (ring current and plasma sheet) and found a general correlation during each of the four storms considered.
+
+%\cite{Denton2006} show how $D_{st}$ affects the distribution of plasma density along different magnetic latitudes, and specifically along the same field lines as looked at in later papers (6-8$R_E$).
 Though this shows that the trends for density may differ between field lines, it's mentioned mostly as a point for future research as the data used in this paper is already adjusted for one field line, as described by \cite{Takahashi2010}.
-
-\cite{Yao2008} looks at the differences in how $D_{st}$ correlates with number density for different ions in different regions (ring current and plasma sheet), but still finds a general correlation during each of the four storms selected.
-
-\cite{Takahashi2010} state that spikes in the Disturbance Storm Time ($D_{st}$) index coincide with with significant changes in $\rho_{eq}$ at an L-shell of 6.8$R_E$.
-For five storms over a 20 day period two had $\rho_{eq}$ spikes after the $D_{st}$ drop, two had $\rho_{eq}$ spikes before the drop, and one showed little change in $\rho_{eq}$.
-They then show an epoch analysis where $\rho_{eq}$ is seen to spike the day of a $D_{st}$ drop, using a daily average of 30 minute $\rho_{eq}$ and one hour $D_{st}$ measurements.
 
@@
 The smallest cadence for $\rho_{eq}$ values is 10 minutes.
-To compute an hourly average over the same time range as the solar wind parameters, the median of all values in a given hourly range was used.
-Fill values were used for hours when no measurements were available.
-In cases where $\rho_{eq}$ was available from multiple Geostationary Operational Environmental Satellites (GOES) satellites at the same time in the \cite{Denton} dataset, the value from GOES 7 was selected to avoid overlapping data points.
+To compute an hourly average over the same interval for which the solar wind parameters were averaged, the median of all $\rho_{eq}$ values in a given hourly range was used.
+Fill values were used for hours in which no measurements were available.
+In cases where $\rho_{eq}$ was available from multiple Geostationary Operational Environmental Satellites (GOES) satellites at the same time in the \cite{Denton} dataset, the value from GOES 7 was selected.
 In the dataset, measurements from GOES 7 had the longest time span of coverage.
@@
 In finding events, all fill values were replaced with linearly interpolated values.
-Figure \ref{AllData} shows the values of $B_z$, $V_{SW}$, $D_{st}$, $F_{10.7}$, and Mass Density for the duration of the dataset.
+Figure \ref{AllData} shows the values of $B_z$, $V_{SW}$, $D_{st}$, $F_{10.7}$, and $\rho{eq}$ for the duration of the dataset.
 
@@
 \section{Results}
-Figure \ref{AllData} shows values of solar wind averages and mass density used in this study. We will briefly compare our results to other published results to verify our methods and handling of data.
+Figure \ref{AllData} shows values of solar wind averages and mass density used in this study.
 
-\subsection{Previous Results}
-
-Figure~\ref{ccplot:a} shows the long-term trends of $log(\rho_{eq})$ and $F_{10.7}$ by computing the median in 27-day windows using all non--fill hourly values.
+Figure~\ref{ccplot:a} shows the long-term trends of $log(\rho_{eq})$ and $F_{10.7}$ computed using the median values in 27-day (non-overalpping?) windows using all non--fill hourly values.
 A scatter plot of these two lines is shown in Figure~\ref{ccplot:b}.
 The linear correlation is found to be $0.87$.
-In comparison, \cite{Takahashi2010} found a correlation coefficient of $0.94$ using measurements from all satellites in the time interval of 1980 to 1992.
+In comparison, \cite{Takahashi2010} found a correlation coefficient of $0.94$ using measurements from all satellites in the time interval of 1980 through 1991.
 
-The correlation seen between 27-day averages $log(\rho_{eq\_27d})$ and $F_{10.7\_27d}$ isn't quite as good in this data as in \cite{Takahashi2010}, but shows the same trend as seen in Figure \ref{ccplot}.
+\subsection{D$_{st}$ and $\rho_{eq}$ Events}
 
-Figure \ref{DailyAverages} show that the trends observed by \cite{Takahashi2010} for one day averages only seems to hold true for the one-day averaged data.
-Namely that a drop in median daily $D_{st}$ between 1989 and 1991 coincides with a significant spike in $\rho_{eq}$.
+Two types of events are considered. The first is a drop in $D_{st}$ below the threshold of $-40nT$.  The second is an increase in $\rho_{eq}$ above 40~$amu/cm^3$.
 
-\subsection{D$_{st}$ Events}
-Two event indicators are looked at in this study.
-The first is looking for a drop in DST below the threshold of $-40nT$ specified in \cite{Takahashi2010}, dubbed the "onset", and then considering the timeframe an event until $D_{st}$ passes back above the $-40nT$ threshold.
+Our first analysis uses data only from the time interval 1989-1991.
+In this interval, there were (?) $D_{st}$ events and (?) $\rho_{eq}$ events.
+For both types of events, the hour of the threshold crossing defines the zero epoch time, and for each event $8\cdot24$ hours were kept after each event and $4\cdot24$ hours before each event.
+To compute the epoch averages on a daily time scale, the median value of all measurements for all events centered window of $\pm 12$ hours was computed, and these windows were shifted in increments of $24$~hours.
+(Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians in 1-day bins and then compute the medians accross events.)  Error bars for each parameter were computed using (2x ?) the standard deviation of the number of values used in computing the median dividied by the square root of the number of values used.
+
+In the upper panel of \label{DailyAverages}, $D_{st}$ events are shown.
+The minimum $D_{st}$ median is $-48~nT$.
+Consistent with \cite{Takahashi2010}, $D_{st}$ events corrspond to elevated $\rho_{eq}$, although the magnitude of increase observed here is on the order of $~2 amu/cm^3$ instead of $~10 amu/cm^3$ found in \cite{Takahashi2010}.
+The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute its median and error bars.
+Note that for $D_{st}$, the number of measurements used in computing the medians is much larger as we use all available $D_{st}$ measurements instead of restricting to only values where a non-fill $\rho_{eq}$ value existed.
+
+In the lower panel of \label{DailyAverages}, $\rho_{eq}$ events are shown.
+Here we see that $\rho_{eq}$ enhancements do not clearly correspond to a signature in $D_{st}$, but that there is a trend for such enhancments to occur when $B_{z}$ in the IMF is positive.
+This is consistent with \cite{Takahashi2010} who note that very large increases in $\rho_{eq}$ often corresponded to movement of the plasmasphere to beyond geosynchronous distances.
+
 This method finds 669 such periods between May 1983 and August 1991 with an average duration of 9 hours and a median duration of 3 hours.
@@
 \includegraphics[scale=0.45]{paperfigures/stormavs-dst-50-tak.eps}
-\includegraphics[scale=0.45]{paperfigures/stormavs-dst-day.eps}
-\caption{(a) Verifying \cite{Takahashi2010} Fig. 11 conditions: $D_{st}<-50nT$ between 1989 and 1991 and (b) Same as (a) but for 1987 to 1991, and not just pre-noon events}
+\rule[1ex]{5cm}{0.5pt}
+\includegraphics[scale=0.45]{paperfigures/stormavs-mass-tak.eps}
+\caption{Events in the interval 1989-1991. Upper panel: $D_{st}$ events. Lower panel: $\rho_{eq}$ events.}
 \label{DailyAverages}
@@
 \centering
+\includegraphics[scale=0.45]{paperfigures/stormavs-dst-day.eps}
+\rule[1ex]{5cm}{0.5pt}
+\includegraphics[scale=0.45]{paperfigures/stormavs-mass-day.eps}
+\caption{Events in the interval 1983-1991.  Upper panel: $D_{st}$ events. Lower panel: $\rho_{eq}$ events.}
+\label{DailyAveragesAllData}
+\end{figure}
+\clearpage
+
+\begin{figure}[htp!]
+\centering
 \includegraphics[scale=0.45]{paperfigures/stormavs-dst.eps}
+\rule[1ex]{5cm}{0.5pt}
 \includegraphics[scale=0.45]{paperfigures/stormavs-mass.eps}

### 2015-09-01 paper.tex
Paper updates; code updates

@@
 \usepackage{amssymb,amsmath}
-\usepackage{nicefrac}
 \usepackage[usenames,dvipsnames]{color}
@@
 
-\cite{Takahashi2006} estimated magnetospheric mass density using measurements from the CRRES satellite during a 73-day period and 1991 and found that the average ion mass density, $M=\rho/n_e$, depended on geomagnetic activity, with lower $D_{st}$ values corresponding to slightly average ion mass densities.
-They also found a $K_p$ dependence between the average ion mass and 1.5- and 3-day averages of $K_p$ were compared to $M$.
-Most measurements occurred in the MLT range of 12:00 and 18:00 MLT in the plasma trough (in equatorial plane?)
+\cite{Takahashi2006} estimated magnetospheric mass density using measurements from the CRRES satellite during a 73-day period and 1991 and found that the average ion mass density, $M=\rho/n_e$, correlated with geomagnetic activity, with lower $D_{st}$ values corresponding to slightly average ion mass densities.
+They also found a relationship between the average ion mass and 1.5- and 3-day averages of $K_p$ were compared to $M$.
+Most measurements occurred in the MLT range of 12:00 and 18:00 in the plasma trough (in equatorial plane?)
 
-\cite{Takahashi2010} developed a mass density dataset using measurements from the GOES satellites over the years 1980 through 1992, with most measurements in the range $L=6.8\pm0.2$ The equatorial mass density, $\rho_eq$ was estimated from the estimated mass density a power law dependence on the geocentric radius $R$, $\rho=\rho_{eq}(LR_E/R)$.
-A key result was that when daily-averaged measurements were considered, an enhancment in $\rho_{eq}$ appeared, indicating the possibility of a geomagnetic storm control over $\rho_{eq}$.
+\cite{Takahashi2010} developed a mass density dataset using measurements from the GOES satellites over the years 1980 through 1992, with most measurements in the range $L=6.8\pm0.2$ The equatorial mass density, $\rho_{eq}$ was estimated from the estimated mass density a power law dependence on the geocentric radius $R$, $\rho=\rho_{eq}(LR_E/R)$.
+A key result was that when daily-averaged measurements were considered, an enhancment in $\rho_{eq}$ appeared, indicating the possibility of a solar wind control over $\rho_{eq}$.
 
@@
 Fill values were used for hours in which no measurements were available.
-In cases where $\rho_{eq}$ was available from multiple Geostationary Operational Environmental Satellites (GOES) satellites at the same time in the \cite{Denton} dataset, the value from GOES 7 was selected.
-In the dataset, measurements from GOES 7 had the longest time span of coverage.
+In cases where $\rho_{eq}$ was available from multiple Geostationary Operational Environmental Satellites (GOES) satellites at the same time in the \cite{Denton} dataset, the value from GOES 6 was selected.
+In the dataset, measurements from GOES 6 had the longest time span of coverage.
 An overview of the data is given in Figure~\ref{AllData}.
@@
 
-In this work events defined to occur when $D_{st}$ or $\rho_{eq}$ crosses a threshold value, as indicated in by horizontal dashed lines in the respective panels of Figure~\ref{AllData}.
+In this work, events defined to occur when $D_{st}$ or $\rho_{eq}$ crosses a threshold value, as indicated in by horizontal dashed lines in the respective panels of Figure~\ref{AllData}.
 In finding events, all fill values were replaced with linearly interpolated values.
-Figure \ref{AllData} shows the values of $B_z$, $V_{SW}$, $D_{st}$, $F_{10.7}$, and $\rho{eq}$ for the duration of the dataset.
+Figure \ref{AllData} shows the values of $B_z$, $V_{sw}$, $D_{st}$, $F_{10.7}$, and $\rho_{eq}$ for the duration of the dataset.
 
@@
 A scatter plot of these two lines is shown in Figure~\ref{ccplot:b}.
-The linear correlation is found to be $0.87$.
+The linear correlation is found to be $0.87$ (?
+plot says 0.94!).
 In comparison, \cite{Takahashi2010} found a correlation coefficient of $0.94$ using measurements from all satellites in the time interval of 1980 through 1991.
@@
 
-Two types of events are considered. The first is a drop in $D_{st}$ below the threshold of $-40nT$.  The second is an increase in $\rho_{eq}$ above 40~$amu/cm^3$.
+Two types of events are considered. The first is a drop in $D_{st}$ below the threshold of $-40$~nT.  The second is an increase in $\rho_{eq}$ above $40$~amu/cm$^3$.
 
@@
 To compute the epoch averages on a daily time scale, the median value of all measurements for all events centered window of $\pm 12$ hours was computed, and these windows were shifted in increments of $24$~hours.
-(Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians in 1-day bins and then compute the medians accross events.)  Error bars for each parameter were computed using (2x ?) the standard deviation of the number of values used in computing the median dividied by the square root of the number of values used.
+(Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians in 1-day bins and then compute the medians accross events.)  Error bars for each parameter were computed using the standard deviation (2x ?) of values used in computing the median dividied by the square root of the number of values used.
 
 In the upper panel of \label{DailyAverages}, $D_{st}$ events are shown.
-The minimum $D_{st}$ median is $-48~nT$.
-Consistent with \cite{Takahashi2010}, $D_{st}$ events corrspond to elevated $\rho_{eq}$, although the magnitude of increase observed here is on the order of $~2 amu/cm^3$ instead of $~10 amu/cm^3$ found in \cite{Takahashi2010}.
+The minimum $D_{st}$ median is $-48$~nT.
+Consistent with \cite{Takahashi2010}, $D_{st}$ events corrspond to elevated $\rho_{eq}$, although the magnitude of increase observed here is on the order of $\sim2$~amu/cm$^3$ instead of $\sim10$~amu/cm$^3$ found in \cite{Takahashi2010}.
 The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute its median and error bars.
@@
 
-This method finds 669 such periods between May 1983 and August 1991 with an average duration of 9 hours and a median duration of 3 hours.
+A total of 669 events were found in the interval of May 1983 through August 1991 with an average duration of 9 hours and a median duration of 3 hours.
 Figure \ref{Storms} shows the average values of all events over a window of 24 hours before onset and 48 hours after.
-Figure \ref{Storms}a shows events selected by looking for event onsets where $D_{st}$ crossed a threshold of $-40nT$.
+Figure \ref{Storms}a shows events selected by looking for event onsets where $D_{st}$ crossed a threshold of $-40$~nT.
 The dashed red lines indicate plus and minus one standard deviation of values from all events that went into the average.
@@
 
-This figure shows a definite spike in the $Z$ component of the magnetic field, as well as the defined drop in $DST$, but no obvious change in mass density at an hourly timescale.
+This figure shows a definite spike in the $Z$ component of the magnetic field, as well as the defined drop in $D_{st}$, but no obvious change in mass density at an hourly timescale.
 This points to an issue with only looking at long-timescale trends between density and $D_{st}$, and allows for the possibility that other factors are influencing the long term correlation since there's no obvious connection on a short timescale.
@@
 \subsection{Mass Density Events}
-Figure \ref{Storms}b shows this same algorithm, but looking for a rise in mass density over a value of 40$g/cm^3$.
+Figure \ref{Storms}b shows this same algorithm, but looking for a rise in mass density over a value of $40$~amu/cm$^3$.
 This results in 130 events with a mean duration of 32 hours and a median duration of 17 hours, marked in red on the left figure.
@@
 Neither of these seem to indicate anything too significant, so looking at $D_{st}$ events instead to look for something that causes a significant change in Mass Density results in Figure \ref{Dspec}.
-This shows that by either looking only at $D_{st}$ events that last longer than an hour (left) or at events where the onset condition is $D_{st}<-80nT$, a spike in mass density is seen, but also a definite lack of data availability to the point where that spike may be coming from less than five of the total 143 events.
+This shows that by either looking only at $D_{st}$ events that last longer than an hour (left) or at events where the onset condition is $D_{st}<-80$~nT, a spike in mass density is seen, but also a definite lack of data availability to the point where that spike may be coming from less than five of the total 143 events.
 
-Unfortunately there are no events in this time frame that are longer than 12 hours with $D_{st}$ minima lower than $-80nT$ that have existing mass density data around onset, so an analysis of this particular relationship can't be made.
+Unfortunately there are no events in this time frame that are longer than 12 hours with $D_{st}$ minima lower than $-80$~nT that have existing mass density data around onset, so an analysis of this particular relationship can't be made.
 
@@
 \cite{Takahashi2010} mention a strong correlation between the two.
-The long term correlation could be a bias for $D_{st}$'s effects, so a linear model was created, recreating mass density purely from $F_{10.7}$ in the form of $\rho_{eq}(t)=A*F_{10.7}(t)$.
-This re-created $\rho_{eq}$ shows around a 45\% correlation with the actual $\rho_{eq}$, suggesting a strong influence, while doing the same procedure with $DST$ shows only a 20-25\% correlation.
+The long term correlation could be a bias for $D_{st}$'s effects, so a linear model was created, recreating mass density purely from $F_{10.7}$ in the form of $\rho_{eq}(t)=A\cdot F_{10.7}(t)$.
+This re-created $\rho_{eq}$ shows around a 45\% correlation with the actual $\rho_{eq}$, suggesting a strong influence, while doing the same procedure with $D_{st}$ shows only a 20-25\% correlation.
 
@@
 All show a similar spike in $\rho_{eq}$ at the time of $D_{st}$ minimum, though none quite reproduce the exact values seen in \cite{Takahashi2010}.
-Figure \ref{allstorms} shows where the median falls for all of the found events during that period, as a sanity check for why the prior work would get median values nearing $30 amu/cm^3$.
+Figure \ref{allstorms} shows where the median falls for all of the found events during that period, as a sanity check for why the prior work would get median values nearing $30$~amu/cm$^3$.
 Both authors of this paper conducted independent trials to confirm that the data and analysis don't quite yield the results of Figure 11 in \cite{Takahashi2010} with the processes described in that paper, but the same general trend is still seen.
@@
 \footnotesize
-\bibliographystyle{vplainnat}
-
+\bibliographystyle{plainnat}
 \bibliography{reportbib}
@@
 The top four panels show parameters from \cite{Reconstruction} and the bottom panel is based on $\rho_{eq}$ from \cite{Denton} after interpolation and averaging described in the text.
-Dashed horizontal lines in the $D_{st}$ and $\rho_{eq}$ panels indicate sample event cutoff thresholds of $D_{st}=-50~nT$ and $\rho_{eq}=40~amu/cm^3$}.
+Dashed horizontal lines in the $D_{st}$ and $\rho_{eq}$ panels indicate sample event cutoff thresholds of $D_{st}=-50$~nT and $\rho_{eq}=40$~amu/cm$^3$}.
 \label{AllData}
@@
 {\includegraphics[scale=0.42]{paperfigures/ccplot.eps}}
-\caption{(a) All data of $F_{10.7\_27d}$ and $\rho_{eq\_27d}$. (b) Correlation between $log(\rho_{eq})$ and $F_{10.7}$ at hour, day, and 27-day intervals; compare to \cite{Takahashi2010} Fig. 14}
+\caption{(a) 27-day averages of $F_{10.7}$ and $\rho_{eq}$.
+(b) Correlation between $log(\rho_{eq})$ and $F_{10.7}$ using hour, day, and 27-day averaging intervals; compare to \cite{Takahashi2010} Fig.~14.}
 \label{ccplot}
@@
 \includegraphics[scale=0.45]{paperfigures/stormavs-mass.eps}
-\caption{(a) Average of solar wind and near-Earth measurements around the time $D_{st}$ crossed below $-50~nT$ onset.
-(b) Same as (a) except around time intervals where mass density crossed above $40~amu/cm^3$.
-The bottom panel shows the number of mass density data points that were used for the average.}
+\caption{(a) Average of solar wind and near-Earth measurements around the time $D_{st}$ crossed below $-50$~nT onset.
+(b) Same as (a) except around time intervals where mass density crossed above $40$~amu/cm$^3$.}
 \label{Storms}
@@
 \includegraphics[scale=0.45]{paperfigures/stormavs-md12.eps}
-\caption{(a) Same as Figure \ref{Storms}(a) except with constraint that $D_{st}$ stayed below $-50~nT$ for at least 12~hours.
-(b) Same as Figure \ref{Storms}(b) except for constrain that $\rho_{eq}$ stayed above $50~amu/cm^3$ for at least 12 hours.}
+\caption{(a) Same as Figure \ref{Storms}(a) except with constraint that $D_{st}$ stayed below $-50$~nT for at least 12~hours.
+(b) Same as Figure \ref{Storms}(b) except for constrain that $\rho_{eq}$ stayed above $50$~amu/cm$^3$ for at least 12 hours.}
 \label{Mspec}
@@
 \includegraphics[scale=0.45]{paperfigures/stormavs-m70.eps}
-\caption{(a) Same as Figure \ref{Storms}(a) except with constraint that $D_{st}$ crossed below $-80nT$ (b) Same as Figure \ref{Storms}(b) except for constrain that $\rho_{eq}$ crossed above $70~amu/cm^3$.}
+\caption{(a) Same as Figure \ref{Storms}(a) except with constraint that $D_{st}$ crossed below $-80$~nT (b) Same as Figure \ref{Storms}(b) except for constrain that $\rho_{eq}$ crossed above $70~amu/cm^3$.}
 \label{Dspec}
@@
 \includegraphics[scale=0.5]{paperfigures/nansbyhour_storm.eps}
-\caption{(a) Number of NaN points per hour of observation in the total data set (b) $\rho_{eq}$ data availability relative to average event hour in events where $D_{st}<-80nT$}
+\caption{(a) Number of NaN points per hour of observation in the total data set (b) $\rho_{eq}$ data availability relative to average event hour in events where $D_{st}<-80$~nT.}
 \label{nanperhour}

### 2015-09-01 Density2.m

@@ -160,7 +160,7 @@ for sat = [6]
 
     % Select overlapping windows
     Io = max([ODN(1),DDN(1),KDN(1)]);
-    Io = datenum('1989-01-01');
+    %Io = datenum('1989-01-01');
     If = min([ODN(end),DDN(end),KDN(end)]);
 
     fprintf('Overlapping time window is %s through %s\n',datestr(Io),datestr(If));
@@ -173,6 +173,16 @@ for sat = [6]
     KDensitySW = KDensitySW(IK);
     KDst  = KDst(IK);
     KData = KData(IK,:);
+
+    IO = find(ODN>=Io & ODN <=If);
+    ODN = ODN(IO);
+    OH = OH(IO);
+    OBz = OBz(IO);
+    OVsw = OVsw(IO);
+    OF107 = OF107(IO);
+    ODst = ODst(IO);
+    OData = OData(IO,:);
+    %[ODN(1),OH(1);ODN(end),OH(end)]
 
     ID  = find(DDN>=Io & DDN <=If);
     DDN = DDN(ID);
@@ -205,16 +215,6 @@ for sat = [6]
     DF107Mean = DXMean(:,5);
     DMLTMean = DXMean(:,6);
     DDensityMean = DXMean(:,7);
-
-    IO = find(ODN>=Io & ODN <=If);
-    ODN = ODN(IO);
-    OH = OH(IO);
-    OBz = OBz(IO);
-    OVsw = OVsw(IO);
-    OF107 = OF107(IO);
-    ODst = ODst(IO);
-    OData = OData(IO,:);
-    %[ODN(1),OH(1);ODN(end),OH(end)]
 
     tmp = corrcoef(KBz,OBz,'rows','complete');
     fprintf('cc(KBz,OBz)                    = %.3f\n',tmp(2));
@@ -254,57 +254,63 @@ for sat = [6]
 
     %I = find(DDstMedian(1:end-1) > -50 & DDstMedian(2:end) < -50);
     %I = find(ODst(1:end-1) > -50 & ODst(2:end) < -50);
-    I = find(KDst(1:end-1) > -50 & KDst(2:end) <= -50);
+    I = find(KDst(1:end-1) >= -50 & KDst(2:end) < -50);
     %I = find(KDst(1:end-1) > -50 & KDst(2:end) < -50);
     clear *Storm*
 
-    Nd = 2;
-    k = 1;
-    for i = 1:length(I)-1
-        a = I(i)-24*Nd+12;
-        b = I(i)+24*Nd-12;
[…]

### 2015-09-01 regrid.m

@@ -12,13 +12,13 @@ Tf  = NaN*ones(n,1);
 DNf = NaN*ones(n,1);
 HMf = NaN*ones(n,2);
 
-% Replace NaNs with valid values.
+% Replace NaNs with valid values. f = filled.
 Tf(To+1)    = To;
 DNf(To+1)   = DN;
 HMf(To+1,:) = HM;
 Xf(To+1,:)  = X;
 
-% Reshape 1-min grid arrays have columns with 60 rows
+% Reshape 1-min grid arrays have columns with 60 rows. r = reshaped.
 DNfr = reshape(DNf,60,length(DNf)/60);
 Tfr = reshape(Tf,60,length(Tf)/60);
 
@@ -45,20 +45,4 @@ for i = 1:Nc
 	% Find median and mean of non-nan points in 60-minute windows.
 	XMedian(:,i) = nanmedian(Xfr{i},1);
 	XMean(:,i)   = nanmean(Xfr{i},1);
-end
-
-if (0)
-figure(1);clf;hold on;
-    plot(To,X(:,end),'b.','MarkerSize',30)
-    plot(Tf,Xf(:,end),'g.','MarkerSize',20)
-    plot(TMedian,XMedian(:,end),'k.','MarkerSize',10)
-    for i = 1:100
-        text(TMedian(i),XMedian(i,end)*1.01,num2str(NGood(i)));
-    end
-    legend('Original Data','Original on 1-min grid','Median in 60 minute window')
-    for i = 600:60:1400
-    	plot([i,i],[3,11],'k')
-    end
-    xlabel(['Minutes since ',datestr(DN(1))])
-    set(gca,'XLim',[0,1440-1])
 end

### 2015-09-02 paper.tex
minor fixes

--- 2015-08-31 paper.tex
@@
 
-Two types of events are considered. The first is a drop in $D_{st}$ below the threshold of $-40nT$.  The second is an increase in $\rho_{eq}$ above 40~$amu/cm^3$.
+Two types of events are considered. The first is a drop in $D_{st}$ below the threshold of $-40$~nT.  The second is an increase in $\rho_{eq}$ above 40~amu/cm$^3$.
 
 Our first analysis uses data only from the time interval 1989-1991.
-In this interval, there were (?) $D_{st}$ events and (?) $\rho_{eq}$ events.
 For both types of events, the hour of the threshold crossing defines the zero epoch time, and for each event $8\cdot24$ hours were kept after each event and $4\cdot24$ hours before each event.
-To compute the epoch averages on a daily time scale, the median value of all measurements for all events centered window of $\pm 12$ hours was computed, and these windows were shifted in increments of $24$~hours.
-(Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians in 1-day bins and then compute the medians accross events.)  Error bars for each parameter were computed using (2x ?) the standard deviation of the number of values used in computing the median dividied by the square root of the number of values used.
+To compute the epoch averages on a daily time scale, the median value of all measurements for all events centered on a window of $\pm 12$ hours was computed, and these windows were shifted in increments of $24$~hours.
+(Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians in 1-day bins and then compute the medians accross events.)  Error bars for each parameter were computed using (2x ?) the standard deviation of the number of values used in computing the median divided by the square root of the number of values used.
 
 In the upper panel of \label{DailyAverages}, $D_{st}$ events are shown.
-The minimum $D_{st}$ median is $-48~nT$.
-Consistent with \cite{Takahashi2010}, $D_{st}$ events corrspond to elevated $\rho_{eq}$, although the magnitude of increase observed here is on the order of $~2 amu/cm^3$ instead of $~10 amu/cm^3$ found in \cite{Takahashi2010}.
+The minimum $D_{st}$ median is $-48$~nT.
+Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$, although the magnitude of increase observed here is ~2 amu/cm$^3$ instead of the value of ~10 amu/cm$^3$ found in \cite{Takahashi2010}.
 The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute its median and error bars.
-Note that for $D_{st}$, the number of measurements used in computing the medians is much larger as we use all available $D_{st}$ measurements instead of restricting to only values where a non-fill $\rho_{eq}$ value existed.
+Note that for $D_{st}$, the number of measurements used in computing the medians is much larger as we use all available $D_{st}$ measurements instead of restricting to only values where a non--fill $\rho_{eq}$ value existed.
 

### 2015-09-02 Density2.m

@@ -6,6 +6,9 @@ if ~exist('m-rsw')
     system('git clone http://github.com/rweigel/m-rsw')
     addpath('./m-rsw/time')
 end
+if ~exist('data')
+    mkdir('data');
+end
 
 %for sat = [2,3,5,6,7]
 for sat = [6]
@@ -267,7 +270,8 @@ for sat = [6]
         %if (I(i+1) < I(i) + 12),continue,end
         if (a < 1),continue,end
         if (b > length(DDensityMedian)),break,end
-        fprintf('Event at %s %.1f %.1f %.1f\n',datestr(Io+I(i)/24),KDst(I(i)),KDst(I(i)+1),KDst(I(i)+2))
+        fprintf('Event at %s %.1f %.1f %.1f\n',...
+            datestr(Io+I(i)/24),KDst(I(i)),KDst(I(i)+1),KDst(I(i)+2))
         DDensityStorm(k,:) = DDensityMedian(a:b);
         DDstStorm(k,:)  = DDstMedian(a:b);
         ODstStorm(k,:)  = ODst(a:b);
@@ -303,7 +307,8 @@ for sat = [6]
             %plot(tc,DDensityStorm1Day,'k.','MarkerSize',30)
             title(sprintf('GOES-%d; %s-%s',sat,datestr(Io),datestr(If)))
             xlabel('Time since onset [hrs]')
-            legend('Density [amu/cm^3]','-Dst [nT]','-Dst [nT] (OMNI)','F10.7/10',...
+            legend('Density [amu/cm^3]','-Dst [nT]',...
+                    '-Dst [nT] (OMNI)','F10.7/10',...
                     '# values','Location','NorthWest')
             fname = sprintf('Dst_Events_GOES%d_%s_%s',...
                     sat,datestr(Io,29),datestr(If,29));

### 2015-09-02 paper.tex
Moving tables to subdir

--- 2015-09-01 paper.tex
@@
 
+Two types of events are considered. The first is a drop in $D_{st}$ below the threshold of $-40$~nT.  The second is an increase in $\rho_{eq}$ above 40~amu/cm$^3$.
+
+Our first analysis uses data only from the time interval 1989-1991.
+For both types of events, the hour of the threshold crossing defines the zero epoch time, and for each event $8\cdot24$ hours were kept after each event and $4\cdot24$ hours before each event.
+To compute the epoch averages on a daily time scale, the median value of all measurements for all events centered on a window of $\pm 12$ hours was computed, and these windows were shifted in increments of $24$~hours.
+(Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians in 1-day bins and then compute the medians accross events.)  Error bars for each parameter were computed using (2x ?) the standard deviation of the number of values used in computing the median divided by the square root of the number of values used.
+
+In the upper panel of \label{DailyAverages}, $D_{st}$ events are shown.
+The minimum $D_{st}$ median is $-48$~nT.
+Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$, although the magnitude of increase observed here is ~2 amu/cm$^3$ instead of the value of ~10 amu/cm$^3$ found in \cite{Takahashi2010}.
+The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute its median and error bars.
+Note that for $D_{st}$, the number of measurements used in computing the medians is much larger as we use all available $D_{st}$ measurements instead of restricting to only values where a non--fill $\rho_{eq}$ value existed.
+
+In the lower panel of \label{DailyAverages}, $\rho_{eq}$ events are shown.
+Here we see that $\rho_{eq}$ enhancements do not clearly correspond to a signature in $D_{st}$, but that there is a trend for such enhancments to occur when $B_{z}$ in the IMF is positive.
+This is consistent with \cite{Takahashi2010} who note that very large increases in $\rho_{eq}$ often corresponded to movement of the plasmasphere to beyond geosynchronous distances.
+
+This method finds 669 such periods between May 1983 and August 1991 with an average duration of 9 hours and a median duration of 3 hours.
+Figure \ref{Storms} shows the average values of all events over a window of 24 hours before onset and 48 hours after.
+Figure \ref{Storms}a shows events selected by looking for event onsets where $D_{st}$ crossed a threshold of $-40nT$.
+The dashed red lines indicate plus and minus one standard deviation of values from all events that went into the average.
+The final plot in the stack shows both $\rho_{eq}$ and a bar plot of how many valid data points went into the $\rho_{eq}$ average.
+Since $\rho_{eq}$ comes from a sparser dataset, it has less valid points contributing to the averages than the other parameters in the stack.
+A subset of longer duration events will be looked at later.
+
+This figure shows a definite spike in the $Z$ component of the magnetic field, as well as the defined drop in $DST$, but no obvious change in mass density at an hourly timescale.
+This points to an issue with only looking at long-timescale trends between density and $D_{st}$, and allows for the possibility that other factors are influencing the long term correlation since there's no obvious connection on a short timescale.
+One possibility is that, as suggested in \cite{Takahashi2010}, $F_{10.7}$ plays a significant role in driving long term density values which biases the long term correlation of density and $D_{st}$.
+
 Two types of events are considered. The first is a drop in $D_{st}$ below the threshold of $-40$~nT.  The second is an increase in $\rho_{eq}$ above $40$~amu/cm$^3$.
@@
 Looking at events that last longer than 12 hours and events with an onset threshhold greater than $70g/cm^3$ results in the left and right sides of Figure \ref{Mspec} respectively.
+
+Neither of these seem to indicate anything too significant, so looking at $D_{st}$ events instead to look for something that causes a significant change in Mass Density results in Figure \ref{Dspec}.
+This shows that by either looking only at $D_{st}$ events that last longer than an hour (left) or at events where the onset condition is $D_{st}<-80nT$, a spike in mass density is seen, but also a definite lack of data availability to the point where that spike may be coming from less than five of the total 143 events.
+
+Unfortunately there are no events in this time frame that are longer than 12 hours with $D_{st}$ minima lower than $-80nT$ that have existing mass density data around onset, so an analysis of this particular relationship can't be made.
 
@@
 
-\begin{figure}[htp]
+\begin{figure}[htp!]
 \centering

### 2015-09-03 paper.tex
New bibfile name for consistency; Makefile fixes

@@
 They also found a relationship between the average ion mass and 1.5- and 3-day averages of $K_p$ were compared to $M$.
-Most measurements occurred in the MLT range of 12:00 and 18:00 in the plasma trough (in equatorial plane?)
+Most measurements occurred in the MLT range of 12:00 and 18:00 in the plasma trough, and CRRES had a nearly equatorial orbit.
 
-\cite{Takahashi2010} developed a mass density dataset using measurements from the GOES satellites over the years 1980 through 1992, with most measurements in the range $L=6.8\pm0.2$ The equatorial mass density, $\rho_{eq}$ was estimated from the estimated mass density a power law dependence on the geocentric radius $R$, $\rho=\rho_{eq}(LR_E/R)$.
-A key result was that when daily-averaged measurements were considered, an enhancment in $\rho_{eq}$ appeared, indicating the possibility of a solar wind control over $\rho_{eq}$.
+\cite{Takahashi2010} developed a mass density dataset using measurements from the GOES satellites over the years 1980 through 1992, with most measurements in the range $L=6.8\pm0.2$.
+The equatorial mass density, $\rho_{eq}$ was estimated from the estimated mass density using a power law dependence on the geocentric distance to the field line of the observation, $R$, $\rho=\rho_{eq}(LR_E/R)$.
+The mass density $\rho$ was estimated using the the Alfven wave velocity relationship, $V_A=(\mu_0\rho)^{1/2}$, a magnetic field model, and a numerical solution to a wave equation with an ionospheric boundary and the assumption of an infinitely conducting ionosphere.
 
 \cite{Takahashi2010} noted that downward spikes in the $D_{st}$ index coincide with with significant changes in $\rho_{eq}$ at an L-shell of 6.8~$R_E$.
-For five storms over a 20 day period, two had $\rho_{eq}$ spikes after the $D_{st}$ drop, two had $\rho_{eq}$ spikes before the drop, and one showed little change in $\rho_{eq}$.
-They then show an epoch analysis where $\rho_{eq}$ is seen to spike the day of a $D_{st}$ drop, using a daily average of 30 minute $\rho_{eq}$ and one hour $D_{st}$ measurements.
+For five storms over a 20-day period, two had $\rho_{eq}$ spikes after the $D_{st}$ drop, two had $\rho_{eq}$ spikes before the drop, and one showed little change in $\rho_{eq}$.
+A key result was that when daily-averaged measurements were considered, an enhancment in $\rho_{eq}$ appeared on the same day as minimum $D_{st}$, indicating the possibility of a solar wind control over $\rho_{eq}$.
 
 The results of \cite{Takahashi2006} and \cite{Takahashi2010} are consistent with other results on changes in mass density in the plasma trough region.
-\cite{Hamilton1988} ...
-\cite{Gallagher1988} ....
 \cite{Yao2008} studied the relationship between $D_{st}$ and ion number density for different ions in different regions (ring current and plasma sheet) and found a general correlation during each of the four storms considered.
+
+\cite{Hamilton1988} ... \cite{Gallagher1988} ....
 
@@
 
-The parameters $\rho_{eq}$ and $F_{10.7}$ used in this work are from the dataset associated with \cite{Denton}, with data available from 1980-1991; all other parameters are from \cite{Reconstruction} over the time range of 1972-2013, which are on a 1-hour time grid.
-$\rho_{eq}$ is the inferred mass density based on the 3rd harmonic frequency of magnetic field measurements.
+The parameters $\rho_{eq}$ and $F_{10.7}$ used in this work are from the dataset associated with \cite{Denton}, with data available from 1980 through 1991; all other parameters are from \cite{Reconstruction} over the time range of 1972 through 2013, which are on a 1--hour time grid.
+$\rho_{eq}$ is the inferred equatorial mass density based on the 3rd harmonic torodial frequency of magnetic field measurements.
 The smallest cadence for $\rho_{eq}$ values is 10 minutes.
@@
 In the dataset, measurements from GOES 6 had the longest time span of coverage.
-An overview of the data is given in Figure~\ref{AllData}.
+An overview of the data is shown in Figure~\ref{AllData}.
 
@@
 \bibliographystyle{plainnat}
-\bibliography{reportbib}
+\bibliography{paper}
 
@@
 \subcaptionbox{\label{ccplot:a}}
-{\includegraphics[scale=0.42]{paperfigures/F107MDAllData.eps}}
+{\includegraphics[scale=0.40]{paperfigures/F107MDAllData.eps}}
 \subcaptionbox{\label{ccplot:b}}
-{\includegraphics[scale=0.42]{paperfigures/ccplot.eps}}
+{\includegraphics[scale=0.40]{paperfigures/ccplot.eps}}
 \caption{(a) 27-day averages of $F_{10.7}$ and $\rho_{eq}$.
@@
 
-\begin{figure}[htp!]
+\begin{figure}[tp!]
 \centering
-\includegraphics[scale=0.45]{paperfigures/stormavs-dst-50-tak.eps}
-\rule[1ex]{5cm}{0.5pt}
-\includegraphics[scale=0.45]{paperfigures/stormavs-mass-tak.eps}
+\includegraphics[scale=0.40]{paperfigures/stormavs-dst-50-tak.eps}
+\rule[1ex]{5cm}{1pt}
+\includegraphics[scale=0.40]{paperfigures/stormavs-mass-tak.eps}
 \caption{Events in the interval 1989-1991. Upper panel: $D_{st}$ events. Lower panel: $\rho_{eq}$ events.}
@@
 
-\begin{figure}[htp!]
+\begin{figure}[tp!]
 \centering
-\includegraphics[scale=0.45]{paperfigures/stormavs-dst-day.eps}
-\rule[1ex]{5cm}{0.5pt}
-\includegraphics[scale=0.45]{paperfigures/stormavs-mass-day.eps}
+\includegraphics[scale=0.40]{paperfigures/stormavs-dst-day.eps}
+\rule[1ex]{5cm}{1pt}
+\includegraphics[scale=0.40]{paperfigures/stormavs-mass-day.eps}
 \caption{Events in the interval 1983-1991.  Upper panel: $D_{st}$ events. Lower panel: $\rho_{eq}$ events.}
@@
 
-\begin{figure}[htp!]
+\begin{figure}[tp!]
 \centering
-\includegraphics[scale=0.45]{paperfigures/stormavs-dst.eps}
-\rule[1ex]{5cm}{0.5pt}
-\includegraphics[scale=0.45]{paperfigures/stormavs-mass.eps}
+\includegraphics[scale=0.40]{paperfigures/stormavs-dst.eps}
+\rule[1ex]{5cm}{1pt}
+\includegraphics[scale=0.40]{paperfigures/stormavs-mass.eps}
 \caption{(a) Average of solar wind and near-Earth measurements around the time $D_{st}$ crossed below $-50$~nT onset.
@@
 
-\begin{figure}[htp!]
+\begin{figure}[tp!]
 \centering
-\includegraphics[scale=0.45]{paperfigures/stormavs-dd12.eps}
-\rule[1ex]{5cm}{0.5pt}
-\includegraphics[scale=0.45]{paperfigures/stormavs-md12.eps}
+\includegraphics[scale=0.40]{paperfigures/stormavs-dd12.eps}
+\rule[1ex]{5cm}{1pt}
+\includegraphics[scale=0.40]{paperfigures/stormavs-md12.eps}
 \caption{(a) Same as Figure \ref{Storms}(a) except with constraint that $D_{st}$ stayed below $-50$~nT for at least 12~hours.
@@
 
-\begin{figure}[htp!]
+\begin{figure}[tp!]
 \centering
-\includegraphics[scale=0.45]{paperfigures/stormavs-d80.eps}
-\rule[1ex]{5cm}{0.5pt}
-\includegraphics[scale=0.45]{paperfigures/stormavs-m70.eps}
+\includegraphics[scale=0.40]{paperfigures/stormavs-d80.eps}
+\rule[1ex]{5cm}{1pt}
+\includegraphics[scale=0.40]{paperfigures/stormavs-m70.eps}
 \caption{(a) Same as Figure \ref{Storms}(a) except with constraint that $D_{st}$ crossed below $-80$~nT (b) Same as Figure \ref{Storms}(b) except for constrain that $\rho_{eq}$ crossed above $70~amu/cm^3$.}
@@
 
-\begin{figure}[htp!]
+\begin{figure}[tp!]
 \centering
-\includegraphics[scale=0.45]{paperfigures/stormavs-diffden-10amu.eps}
-\rule[1ex]{5cm}{0.5pt}
-\includegraphics[scale=0.45]{paperfigures/stormavs-diffden-30percent.eps}
+\includegraphics[scale=0.40]{paperfigures/stormavs-diffden-10amu.eps}
+\rule[1ex]{5cm}{1pt}
+\includegraphics[scale=0.40]{paperfigures/stormavs-diffden-30percent.eps}
 \caption{(a) diff($\rho_{eq}$) $>$ 10$\frac{amu}{hour}$. (b) diff($\rho_{eq}$) $>$ 30$\frac{\%}{hour}$}
@@
 
-\begin{figure}[htp!]
+\begin{figure}[tp!]
 \centering
-\includegraphics[scale=0.45]{paperfigures/stormavs-dst-nof107.eps}
-\includegraphics[scale=0.45]{paperfigures/f107removed.eps}
+\includegraphics[scale=0.40]{paperfigures/stormavs-dst-nof107.eps}
+\includegraphics[scale=0.40]{paperfigures/f107removed.eps}
 \caption{$D_{st}$ events where $\rho_{eq}$ has $F_{10.7}$ dependence removed, and Difference between original $\rho_{eq}$ and $F_{10.7}$-less $\rho_{eq}$}
@@
 
-\begin{figure}[htp]
+\begin{figure}[tp]
 \centering
-\includegraphics[scale=0.45]{paperfigures/blockmedian.eps}
-\includegraphics[scale=0.45]{paperfigures/blockmedian-prenoon.eps}
+\includegraphics[scale=0.40]{paperfigures/blockmedian.eps}
+\includegraphics[scale=0.40]{paperfigures/blockmedian-prenoon.eps}
 \caption{Comparing median values calculated as median of all 1-hour points in the 12 day block, and as the daily median of all hourly-mediated events.
@@
 
-\begin{figure}[htp]
+\begin{figure}[tp]
 \centering

### 2015-09-03 paper.tex
Small fixes. Adding F10.7 figures to paper.

@@
 A scatter plot of these two lines is shown in Figure~\ref{ccplot:b}.
-The linear correlation is found to be $0.87$ (?
-plot says 0.94!).
-In comparison, \cite{Takahashi2010} found a correlation coefficient of $0.94$ using measurements from all satellites in the time interval of 1980 through 1991.
+The linear correlation is found to be $0.94$ matching the value found by \cite{Takahashi2010} who used measurements from all satellites in the time interval of 1980 through 1991.
 
@@
 The minimum $D_{st}$ median is $-48$~nT.
-Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$, although the magnitude of increase observed here is ~2 amu/cm$^3$ instead of the value of ~10 amu/cm$^3$ found in \cite{Takahashi2010}.
+Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$, although the magnitude of increase observed here is $\sim2$ amu/cm$^3$ instead of the value of ~10 amu/cm$^3$ found in \cite{Takahashi2010}.
 The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute its median and error bars.
@@
 Figure \ref{Storms} shows the average values of all events over a window of 24 hours before onset and 48 hours after.
-Figure \ref{Storms}a shows events selected by looking for event onsets where $D_{st}$ crossed a threshold of $-40nT$.
+Figure \ref{Storms}a shows events selected by looking for event onsets where $D_{st}$ crossed a threshold of $-40$~nT.
 The dashed red lines indicate plus and minus one standard deviation of values from all events that went into the average.
@@
 \subsection{Change in $\rho_{eq}$}
-If instead of looking for events based on a threshold of $\rho_{eq}$, we instead look for a certain amount of change in $\rho_{eq}$ as the basis for event onset, we get Figure \ref{rhochange}.
-
-Both raw change and percent change were done in case of bias towards high or low $\rho_{eq}$ periods, respectively.
-This shows a distinct lack of correlation in either case to a change in $D_{st}$.
-The percent change in $\rho_{eq}$ does, however, seem to be preconditioned by changes in $B_z$ and $F_{10.7}$.
+Instead of looking for events based on a threshold of $\rho_{eq}$, we instead looked for a certain amount of change in $\rho_{eq}$ as the basis for event onset.
+Both raw change and percent change were done in case of bias towards high or low $\rho_{eq}$ periods, respectively, but neither showed any correlation to a change in $D_{st}$.
 
@@
 
-Taking this re-created data set and subtracting it from the original should remove the $F_{10.7}$ dependence from the data, and allow for a less biased analysis of the relationship between $D_{st}$ and $\rho_{eq}$.
-Figure \ref{nof107} shows the stack plot for the reduced $F_{10.7}$, where a more distinct peak after event onset can be seen.
-It also shows what that removed trend looks like, of the form $\rho_{eq}-\rho_{eq,F_{10.7}}$.
+Figure \ref{f107bin} takes the events and bins them by the value of $F_{10.7}$ at event onset, then looks at both $\rho_{eq}$ and $B_z$.
+A significant difference is seen in $\rho_{eq}$ between events taking place during periods of high $F_{10.7}$ and low $F_{10.7}$, while a much less significant, but still noticeable, difference is seen in $B_z$.
 
@@
 \includegraphics[scale=0.40]{paperfigures/stormavs-m70.eps}
-\caption{(a) Same as Figure \ref{Storms}(a) except with constraint that $D_{st}$ crossed below $-80$~nT (b) Same as Figure \ref{Storms}(b) except for constrain that $\rho_{eq}$ crossed above $70~amu/cm^3$.}
+\caption{(a) Same as Figure \ref{Storms}(a) except with constraint that $D_{st}$ crossed below $-80$~nT (b) Same as Figure \ref{Storms}(b) except for constrain that $\rho_{eq}$ crossed above $70$~amu/cm$^3$.}
 \label{Dspec}
@@
 \centering
-\includegraphics[scale=0.40]{paperfigures/stormavs-dst-nof107.eps}
-\includegraphics[scale=0.40]{paperfigures/f107removed.eps}
-\caption{$D_{st}$ events where $\rho_{eq}$ has $F_{10.7}$ dependence removed, and Difference between original $\rho_{eq}$ and $F_{10.7}$-less $\rho_{eq}$}
-\label{nof107}
+\includegraphics[scale=0.40]{paperfigures/HighLowF107rho.eps}
+\includegraphics[scale=0.40]{paperfigures/HighLowF107Bz.eps}
+\includegraphics[scale=0.40]{paperfigures/HighLowF107valid.eps}
+\caption{Binning events by $F_{10.7}$ value at onset for $\rho_{eq}$ and, in the middle panel, $B_z$. Lower panel shows number of valid points in each bin}
+\label{f107bin}
 \end{figure}

### 2015-09-03 paper.tex
Paper edits

--- 2015-09-03 paper.tex
@@
 \cite{Takahashi2010} developed a mass density dataset using measurements from the GOES satellites over the years 1980 through 1992, with most measurements in the range $L=6.8\pm0.2$.
-The equatorial mass density, $\rho_{eq}$ was estimated from the estimated mass density using a power law dependence on the geocentric distance to the field line of the observation, $R$, $\rho=\rho_{eq}(LR_E/R)$.
-The mass density $\rho$ was estimated using the the Alfven wave velocity relationship, $V_A=(\mu_0\rho)^{1/2}$, a magnetic field model, and a numerical solution to a wave equation with an ionospheric boundary and the assumption of an infinitely conducting ionosphere.
+The equatorial mass density, $\rho_{eq}$ was estimated from the estimated mass density using a power law dependence on the geocentric distance to the field line of the observation, $R$, $\rho=\rho_{eq}L/(R/R_E)$.
+The mass density $\rho$ was estimated using the the Alfven wave velocity relationship, $V_A=B/\sqrt{\mu_0\rho}$, a magnetic field model, and a numerical solution to a wave equation with an ionospheric boundary and the assumption of an infinitely conducting ionosphere.
 
@@
 In finding events, all fill values were replaced with linearly interpolated values.
-Figure \ref{AllData} shows the values of $B_z$, $V_{sw}$, $D_{st}$, $F_{10.7}$, and $\rho_{eq}$ for the duration of the dataset.
 
@@
 
-Figure~\ref{ccplot:a} shows the long-term trends of $log(\rho_{eq})$ and $F_{10.7}$ computed using the median values in 27-day (non-overalpping?) windows using all non--fill hourly values.
+Figure~\ref{ccplot:a} shows the long-term trends of $\log(\rho_{eq})$ and $F_{10.7}$ computed using the median values in 27-day (non-overalpping?) windows using all non--fill hourly values.
 A scatter plot of these two lines is shown in Figure~\ref{ccplot:b}.
@@
 
-\subsection{D$_{st}$ and $\rho_{eq}$ Events}
+\subsection{$D_{st}$ and $\rho_{eq}$ Events}
 
@@
 
-In the upper panel of \label{DailyAverages}, $D_{st}$ events are shown.
+In the upper panel of \ref{DailyAverages}, $D_{st}$ events are shown.
 The minimum $D_{st}$ median is $-48$~nT.
-Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$, although the magnitude of increase observed here is ~2 amu/cm$^3$ instead of the value of ~10 amu/cm$^3$ found in \cite{Takahashi2010}.
+Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$, although the magnitude of increase observed here is $\sim 2$ amu/cm$^3$ instead of the value of $\sim 10$ amu/cm$^3$ found in \cite{Takahashi2010}.
 The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute its median and error bars.
@@
 
-In the lower panel of \label{DailyAverages}, $\rho_{eq}$ events are shown.
+In the lower panel of \ref{DailyAverages}, $\rho_{eq}$ events are shown.
 Here we see that $\rho_{eq}$ enhancements do not clearly correspond to a signature in $D_{st}$, but that there is a trend for such enhancments to occur when $B_{z}$ in the IMF is positive.
@@
 
-In the upper panel of \label{DailyAverages}, $D_{st}$ events are shown.
+In the upper panel of \ref{DailyAverages}, $D_{st}$ events are shown.
 The minimum $D_{st}$ median is $-48$~nT.
@@
 That said, the predictability of extreme events is of definite interest, so an attempt has been made to find some reproducible method of prediction.
-Looking at events that last longer than 12 hours and events with an onset threshhold greater than $70g/cm^3$ results in the left and right sides of Figure \ref{Mspec} respectively.
+Looking at events that last longer than 12 hours and events with an onset threshhold greater than $70$g/cm$^3$ results in the left and right sides of Figure \ref{Mspec} respectively.
 
 Neither of these seem to indicate anything too significant, so looking at $D_{st}$ events instead to look for something that causes a significant change in Mass Density results in Figure \ref{Dspec}.
-This shows that by either looking only at $D_{st}$ events that last longer than an hour (left) or at events where the onset condition is $D_{st}<-80nT$, a spike in mass density is seen, but also a definite lack of data availability to the point where that spike may be coming from less than five of the total 143 events.
+This shows that by either looking only at $D_{st}$ events that last longer than an hour (left) or at events where the onset condition is $D_{st}<-80$~nT, a spike in mass density is seen, but also a definite lack of data availability to the point where that spike may be coming from less than five of the total 143 events.
 
-Unfortunately there are no events in this time frame that are longer than 12 hours with $D_{st}$ minima lower than $-80nT$ that have existing mass density data around onset, so an analysis of this particular relationship can't be made.
+Unfortunately there are no events in this time frame that are longer than 12 hours with $D_{st}$ minima lower than $-80$~nT that have existing mass density data around onset, so an analysis of this particular relationship can't be made.
 
@@
 \caption{(a) 27-day averages of $F_{10.7}$ and $\rho_{eq}$.
-(b) Correlation between $log(\rho_{eq})$ and $F_{10.7}$ using hour, day, and 27-day averaging intervals; compare to \cite{Takahashi2010} Fig.~14.}
+(b) Correlation between $\log(\rho_{eq})$ and $F_{10.7}$ using hour, day, and 27-day averaging intervals; compare to \cite{Takahashi2010} Fig.~14.}
 \label{ccplot}

### 2015-09-03 paper.tex

--- 2015-09-03 paper.tex
@@
 
-In the upper panel of \label{DailyAverages}, $D_{st}$ events are shown.
+In the upper panel of \ref{DailyAverages}, $D_{st}$ events are shown.
 The minimum $D_{st}$ median is $-48$~nT.
-Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$, although the magnitude of increase observed here is $\sim2$ amu/cm$^3$ instead of the value of ~10 amu/cm$^3$ found in \cite{Takahashi2010}.
+Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$, although the magnitude of increase observed here is $\sim 2$ amu/cm$^3$ instead of the value of $\sim 10$ amu/cm$^3$ found in \cite{Takahashi2010}.
 The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute its median and error bars.
@@
 That said, the predictability of extreme events is of definite interest, so an attempt has been made to find some reproducible method of prediction.
-Looking at events that last longer than 12 hours and events with an onset threshhold greater than $70g/cm^3$ results in the left and right sides of Figure \ref{Mspec} respectively.
+Looking at events that last longer than 12 hours and events with an onset threshhold greater than $70$g/cm$^3$ results in the left and right sides of Figure \ref{Mspec} respectively.
 

### 2015-09-08 paper.tex
page-based axis ranges, storm based medians

@@
 
-Figure~\ref{ccplot:a} shows the long-term trends of $log(\rho_{eq})$ and $F_{10.7}$ computed using the median values in 27-day (non-overalpping?) windows using all non--fill hourly values.
-A scatter plot of these two lines is shown in Figure~\ref{ccplot:b}.
+Figure~\ref{ccplot} shows the long-term trends of $log(\rho_{eq})$ and $F_{10.7}$ computed using the median values in 27-day (non-overalpping?) windows using all non--fill hourly values.
+A scatter plot of these two lines is shown in Figure~\ref{ccplot}.
 The linear correlation is found to be $0.94$ matching the value found by \cite{Takahashi2010} who used measurements from all satellites in the time interval of 1980 through 1991.
@@
 To compute the epoch averages on a daily time scale, the median value of all measurements for all events centered window of $\pm 12$ hours was computed, and these windows were shifted in increments of $24$~hours.
-(Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians in 1-day bins and then compute the medians accross events.)  Error bars for each parameter were computed using the standard deviation (2x ?) of values used in computing the median dividied by the square root of the number of values used.
+(Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians in 1-day bins and then compute the medians accross events.)  Error bars for each parameter were computed using the standard deviation of values used in computing the median dividied by the square root of the number of values used.
 
@@
 Figure \ref{f107bin} takes the events and bins them by the value of $F_{10.7}$ at event onset, then looks at both $\rho_{eq}$ and $B_z$.
+Error bars calculated in the same manner as before are added to the highest and lowest bins.
 A significant difference is seen in $\rho_{eq}$ between events taking place during periods of high $F_{10.7}$ and low $F_{10.7}$, while a much less significant, but still noticeable, difference is seen in $B_z$.
+Also of interest is how $\rho_{eq}$ only sharply reacts to $D_{st}$ events during periods of high $F_{10.7}$.
+The positive relationship seen in \cite{Takahashi2010} could be due to the short time period looked at, and that it coincides with periods of higher $F_{10.7}$.
 
@@
 \centering
-\subcaptionbox{\label{ccplot:a}}
-{\includegraphics[scale=0.40]{paperfigures/F107MDAllData.eps}}
-\subcaptionbox{\label{ccplot:b}}
-{\includegraphics[scale=0.40]{paperfigures/ccplot.eps}}
+\includegraphics[scale=0.40]{paperfigures/F107MDAllData.eps}
+\includegraphics[scale=0.40]{paperfigures/ccplot.eps}
 \caption{(a) 27-day averages of $F_{10.7}$ and $\rho_{eq}$.

### 2015-09-08 Density.m

@@ -1,8 +1,13 @@
-function Density
+function Density(stormcase)
+if nargin < 1
+  stormcase=1;
+end
 
-close all;clear all;
-
-TakahashiCond=0;
+if(any(stormcase==10:12))
+    TakahashiCond=1;
+else
+    TakahashiCond=0;
+end
 satnum=6;
 
 %Read filled dataset from Kondrashov(2014)
@@ -108,6 +113,11 @@ MassDensityNanSpline=interp1(OMNITime(~isnan(MassDensitySpline)),MassDensitySpli
 FILLED=[FILLED F107];
 headers{end+1}='F107';
 
+yranges=zeros(3,4,2);
+yranges(1,:,:)=[-2 2; 350 550; -60 0; 150 230];
+yranges(2,:,:)=[-8 3; 350 600; -90 0; 160 210];
+yranges(3,:,:)=[-8 3; 350 580; -60 0; 170 200];
+
 LongTimeScale=1;%24*27; %How many hours to average over. Best stick to 1, 24, or 24*27
 cutoffduration=1; %If you want to get rid of short (spurious?) storms, set larger than 1
 cutconditions=0; %Look at only pre-noon
@@ -116,45 +126,54 @@ DSTCut=0;
 MDCut=0;
 figurename='paperfigures/stormavs-';
 %Select kind of storm to look for
-stormcase=1;
+
 switch stormcase
     case 1
         storms=diff([0 (FILLED(:,15)<-50)' 0]); %DST Storm
         DSTCut=-50;
         figurename=strcat(figurename,'dst.eps');
+        yr=2;
     case 2
         storms=diff([0 (MassDensityNanSpline>40)' 0]); %Mass Density Storm, started at 40
         MDCut=40;
         figurename=strcat(figurename,'mass.eps');
+        yr=2;
     case 3
         storms=[0 diff([0 (diff(MassDensityNanSpline)>10)' 0])];
         figurename=strcat(figurename,'diffden-10amu.eps');
+        yr=3;
     case 4
         storms=[0 diff([0 (abs(MassDensityNanSpline(2:end)./MassDensityNanSpline(1:end-1))>1.3)' 0])];
         figurename=strcat(figurename,'diffden-30percent.eps');
+        yr=3;
     case 5
         storms=diff([0 (FILLED(:,15)<-50)' 0]);
         DSTCut=-50;
[…]

### 2015-09-22 paper.tex
Adding new figures to paper

@@
 \centering
-\includegraphics[scale=0.40]{paperfigures/HighLowF107rho.eps}
+\includegraphics[scale=0.40]{paperfigures/HighLowF107rhoeq.eps}
 \includegraphics[scale=0.40]{paperfigures/HighLowF107Bz.eps}
@@
 
+\section{Appendix}
+\hfill
+\begin{figure}[htp!]
+\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst30.eps}
+\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst30-valid.eps}
+\caption{$D_{st} < -30$ nT events, $\rho_{eq}$ binned by $F_{10.7}$. Lower panel: valid hourly points}
+\end{figure}
+\hfill
+\begin{figure}[htp!]
+\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-rhoeq40.eps}
+\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-rhoeq40-valid.eps}
+\caption{$\rho_{eq} > 40$ amu/cm$^3$ events, $\rho_{eq}$ binned by $F_{10.7}$}
+\end{figure}
+\clearpage
+
+\begin{figure}[htp!]
+\includegraphics[scale=0.40]{paperfigures/HighLowF107rhoeq-AE300.eps}
+\includegraphics[scale=0.40]{paperfigures/HighLowF107rhoeq-AE300-valid.eps}
+\includegraphics[scale=0.35]{paperfigures/stormavs-AE.eps}
+\caption{Top: $AE > 400$ nT events, $\rho_{eq}$ binned by $F_{10.7}$ Bottom: averages of $AE > 400$ events}
+\end{figure}
+\hfill
+\begin{figure}[htp!]
+\includegraphics[scale=0.45]{paperfigures/HighLowDstrhoeq-AE400.eps}
+\includegraphics[scale=0.45]{paperfigures/HighLowDstrhoeq-Dst50.eps}
+\caption{Top: $AE > 400$ nT events. Bottom: $D_{st} < -50$ nT events. Both $\rho_{eq}$ binned by $D_{st}$.}
+\end{figure}
+\clearpage
+
+\begin{figure}[htp!]
+\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-random.eps}
+\includegraphics[scale=0.45]{paperfigures/stormavs-random.eps}
+\caption{Top: $\rho_{eq}$ binned by $F_{10.7}$ for randomly selected times. Bottom: averages of randomly selected times}
+\end{figure}
+
+\begin{figure}[htp!]
+\includegraphics[scale=0.45]{paperfigures/HighLowDstBz-Dst50.eps}
+\includegraphics[scale=0.45]{paperfigures/HighLowDstBz-AE400.eps}
+\caption{Top: $B_z$ binned by $D_{st}$ for $D_{st} < -50$ nT events. Bottom: $B_z$ binned by $D_{st}$ for $AE > 400$ nT events}
+\end{figure}
+\clearpage
+
+\begin{figure}[htp!]
+\includegraphics[scale=0.45]{paperfigures/rhoMLT.eps}
+\includegraphics[scale=0.45]{paperfigures/rhoLT.eps}
+\caption{Median $\rho_{eq}$ vs magnetic local time and universal time}
+\end{figure}
+
+\begin{figure}[htp!]
+\includegraphics[scale=0.45]{paperfigures/DstLT.eps}
+\includegraphics[scale=0.45]{paperfigures/AELT.eps}
+\caption{Median $D_{st}$ vs universal time, and median AE vs universal time}
+\end{figure}
+\clearpage
+
+\begin{figure}[htp!]
+\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-sat6.eps}
+\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-sat7.eps}
+\caption{GOES Satellite 6 and 7}
+\end{figure}
+
+\begin{figure}[htp!]
+\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-sat2.eps}
+\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-sat5.eps}
+\caption{GOES Satellite 2 and 5}
+\end{figure}
+\clearpage
+
+\begin{figure}[htp!]
+\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-tak.eps}
+\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-detrend.eps}
+\caption{Top: From 89-91. Bottom: With $\rho_{eq}$ LT medians subtracted}
+\end{figure}
+
+\begin{figure}[htp!]
+\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst80.eps}
+\includegraphics[scale=0.45]{paperfigures/AEbyhour.eps}
+\caption{Top: $D_{st}<-80$~nT. Bottom: $AE$ events by their hour of onset}
+\end{figure}
+
 \end{document}

### 2015-09-22 Density.m

@@ -270,6 +270,12 @@ switch stormcase
         figurename=strcat(figurename,'dst-detrended.eps');
         yr=2;
         MakeBinPlots=1;
+    case 19
+        DSTCut=-80;
+        storms=diff([0 (FILLED(:,15)<DSTCut)' 0]); %DST Storm
+        figurename=strcat(figurename,'dst80.eps');
+        yr=2;
+        MakeBinPlots=1;
 end
 starti=find(storms>0);
 endi=find(storms<0)-1;

### 2015-12-08 paper.tex
Adding random event plot to paper
paper edits

@@
 \begin{document}
-\title{Relationship between solar wind, $D_{st}$, and plasmasphere mass density on one-hour time scales}
+\title{Relationship between solar wind, $D_{st}$, and plasmasphere trough mass density on one-hour time scales}
 \author{
@@
 
-\cite{Takahashi2006} estimated magnetospheric mass density using measurements from the CRRES satellite during a 73-day period and 1991 and found that the average ion mass density, $M=\rho/n_e$, correlated with geomagnetic activity, with lower $D_{st}$ values corresponding to slightly average ion mass densities.
+\cite{Takahashi2006} estimated magnetospheric mass density using measurements from the CRRES satellite during a 73-day period and 1991 and found that the average ion mass density, $M=\rho/n_e$, correlated with geomagnetic activity, with lower $D_{st}$ values corresponding to slightly higher average ion mass densities.
 They also found a relationship between the average ion mass and 1.5- and 3-day averages of $K_p$ were compared to $M$.
@@
 \cite{Takahashi2010} developed a mass density dataset using measurements from the GOES satellites over the years 1980 through 1992, with most measurements in the range $L=6.8\pm0.2$.
-The equatorial mass density, $\rho_{eq}$ was estimated from the estimated mass density using a power law dependence on the geocentric distance to the field line of the observation, $R$, $\rho=\rho_{eq}L/(R/R_E)$.
-The mass density $\rho$ was estimated using the the Alfven wave velocity relationship, $V_A=B/\sqrt{\mu_0\rho}$, a magnetic field model, and a numerical solution to a wave equation with an ionospheric boundary and the assumption of an infinitely conducting ionosphere.
+The mass density $\rho$ was estimated using the the Alfven wave velocity relationship, $V_A=B/\sqrt{\mu_0\rho}$, a magnetic field model, and a numerical solution to a wave equation with an ionospheric boundary and the assumption of a zero resistance ionosphere.
+The equatorial mass density, $\rho_{eq}$, was estimated from the estimated mass density using a power law dependence on the geocentric distance to the field line of the observation, $R$, $\rho=\rho_{eq}L/(R/R_E)$.
 
@@
 The results of \cite{Takahashi2006} and \cite{Takahashi2010} are consistent with other results on changes in mass density in the plasma trough region.
-\cite{Yao2008} studied the relationship between $D_{st}$ and ion number density for different ions in different regions (ring current and plasma sheet) and found a general correlation during each of the four storms considered.
+\cite{Yao2008} studied the relationship between $D_{st}$ and ion number density for different ion species in different regions (ring current and plasma sheet) and found a general correlation during each of the four storms considered.
 
@@
 \centering
-\includegraphics[scale=0.45]{paperfigures/alldata.eps}
+\includegraphics[scale=0.45]{paperfigures/alldata-GOES6-1983-1991.eps}
 \caption{Overview of data used in this study.
@@
 \begin{figure}[htp!]
-\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-sat6.eps}
-\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-sat7.eps}
+\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES6-1983-1991.eps}
+\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES7-1987-1991.eps}
 \caption{GOES Satellite 6 and 7}
@@
 \begin{figure}[htp!]
-\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-sat2.eps}
-\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-sat5.eps}
+\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES2-1981-1983.eps}
+\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES5-1983-1987.eps}
 \caption{GOES Satellite 2 and 5}
@@
 \begin{figure}[htp!]
-\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-tak.eps}
-\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-detrend.eps}
-\caption{Top: From 89-91. Bottom: With $\rho_{eq}$ LT medians subtracted}
+\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES6-1989-1991.eps}
+\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst80.eps}
+\caption{Top: From 89-91 (compare to Takahashi 2010). Bottom:  $D_{st}<-80$~nT.}
 \end{figure}
@@
 \begin{figure}[htp!]
-\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst80.eps}
 \includegraphics[scale=0.45]{paperfigures/AEbyhour.eps}
-\caption{Top: $D_{st}<-80$~nT. Bottom: $AE$ events by their hour of onset}
+\caption{$AE$ events by their hour of onset}
+\end{figure}
+\clearpage
+
+\begin{figure}[htp!]
+\includegraphics[scale=0.45]{paperfigures/DstRhoThresh-1983-1991.eps}
+\includegraphics[scale=0.45]{paperfigures/DstRhoThresh-1987-1991.eps}
+\caption{High $F_{10.7}$ events - Low $F_{10.7}$ events, both with baselines removed. 83-91 and 87-91}
+\end{figure}
+
+\begin{figure}[htp!]
+\includegraphics[scale=0.45]{paperfigures/DstRhoThresh-1983-1987.eps}
+\includegraphics[scale=0.45]{paperfigures/DstRhoThresh-1981-1983.eps}
+\includegraphics[scale=0.45]{paperfigures/RandRhoThresh-1983-1991.eps}
+\caption{High $F_{10.7}$ events - Low $F_{10.7}$ events, both with baselines removed. 83-87 and 81-83. Bottom: Random "events" from 1983-1991}
+\end{figure}
+\clearpage
+
+\begin{figure}[htp!]
+\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES6-1983-1991.eps}
+\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES7-1987-1991.eps}
+\caption{Comparing GOES 6 to GOES 7}
+\end{figure}
+
+\begin{figure}[htp!]
+\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES6-1983-1987.eps}
+\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES6-1987-1991.eps}
+\caption{GOES 6 from 83-87 and 87-91}
 \end{figure}

### 2015-12-10 paper.tex
Updated paper

@@
 
-Two types of events are considered. The first is a drop in $D_{st}$ below the threshold of $-40$~nT.  The second is an increase in $\rho_{eq}$ above 40~amu/cm$^3$.
+Two types of events are considered. The first is a drop in $D_{st}$ below the threshold of $-50$~nT.  The second is an increase in $\rho_{eq}$ above 40~amu/cm$^3$.
 
@@
 To compute the epoch averages on a daily time scale, the median value of all measurements for all events centered on a window of $\pm 12$ hours was computed, and these windows were shifted in increments of $24$~hours.
-(Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians in 1-day bins and then compute the medians accross events.)  Error bars for each parameter were computed using (2x ?) the standard deviation of the number of values used in computing the median divided by the square root of the number of values used.
+(Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians in 1-day bins and then compute the medians accross events.)  Error bars for each parameter were computed using the standard deviation of the number of values used in computing the median divided by the square root of the number of values used.
 
@@
 
-In the lower panel of \ref{DailyAverages}, $\rho_{eq}$ events are shown.
-Here we see that $\rho_{eq}$ enhancements do not clearly correspond to a signature in $D_{st}$, but that there is a trend for such enhancments to occur when $B_{z}$ in the IMF is positive.
+In the lower panel of \ref{DailyAverages} it is shown that all trends seen in the analysis of 1989-1991 also hold for the entire run of GOES 6 over 1983-1991, including the magnitude of change in $\rho_{eq}$ across event onset.
+
+It was found that $\rho_{eq}$ enhancements do not clearly correspond to a signature in $D_{st}$, but that there is a trend for such enhancements to occur when $B_{z}$ in the IMF is positive.
 This is consistent with \cite{Takahashi2010} who note that very large increases in $\rho_{eq}$ often corresponded to movement of the plasmasphere to beyond geosynchronous distances.
@@
 
-A total of 669 events were found in the interval of May 1983 through August 1991 with an average duration of 9 hours and a median duration of 3 hours.
+A total of 668 events were found in the interval of May 1983 through August 1991 with an average duration of 9 hours and a median duration of 3 hours.
 Figure \ref{Storms} shows the average values of all events over a window of 24 hours before onset and 48 hours after.
-Figure \ref{Storms}a shows events selected by looking for event onsets where $D_{st}$ crossed a threshold of $-40$~nT.
+Figure \ref{Storms}a shows events selected by looking for event onsets where $D_{st}$ crossed a threshold of $-50$~nT.
 The dashed red lines indicate plus and minus one standard deviation of values from all events that went into the average.
@@
 
-\subsection{Mass Density Events}
-Figure \ref{Storms}b shows this same algorithm, but looking for a rise in mass density over a value of $40$~amu/cm$^3$.
-This results in 130 events with a mean duration of 32 hours and a median duration of 17 hours, marked in red on the left figure.
-
-This shows that when using all data for mass density derived events, almost no significant changes can be seen around event onset.
-
 \section{More specific events}
@@
 That said, the predictability of extreme events is of definite interest, so an attempt has been made to find some reproducible method of prediction.
-Looking at events that last longer than 12 hours and events with an onset threshhold greater than $70$g/cm$^3$ results in the left and right sides of Figure \ref{Mspec} respectively.
+Looking at events that last longer than 12 hours and events with an onset threshhold less than $-80$nT results in Figure \ref{Dspec}.
+A spike in mass density is seen, but also a definite lack of data availability to the point where that spike may be coming from less than five of the total 211 events.
 
-Neither of these seem to indicate anything too significant, so looking at $D_{st}$ events instead to look for something that causes a significant change in Mass Density results in Figure \ref{Dspec}.
-This shows that by either looking only at $D_{st}$ events that last longer than an hour (left) or at events where the onset condition is $D_{st}<-80$~nT, a spike in mass density is seen, but also a definite lack of data availability to the point where that spike may be coming from less than five of the total 143 events.
-
-Unfortunately there are no events in this time frame that are longer than 12 hours with $D_{st}$ minima lower than $-80$~nT that have existing mass density data around onset, so an analysis of this particular relationship can't be made.
-
-Neither of these seem to indicate anything too significant, so looking at $D_{st}$ events instead to look for something that causes a significant change in Mass Density results in Figure \ref{Dspec}.
-This shows that by either looking only at $D_{st}$ events that last longer than an hour (left) or at events where the onset condition is $D_{st}<-80$~nT, a spike in mass density is seen, but also a definite lack of data availability to the point where that spike may be coming from less than five of the total 143 events.
-
-Unfortunately there are no events in this time frame that are longer than 12 hours with $D_{st}$ minima lower than $-80$~nT that have existing mass density data around onset, so an analysis of this particular relationship can't be made.
+Unfortunately there are no events in this time frame that are longer than 12 hours with $D_{st}$ minima lower than $-80$~nT that have existing mass density data around onset, so an analysis of this particular combination of factors can't be made.
 
@@
 \cite{Takahashi2010} mention a strong correlation between the two.
-The long term correlation could be a bias for $D_{st}$'s effects, so a linear model was created, recreating mass density purely from $F_{10.7}$ in the form of $\rho_{eq}(t)=A\cdot F_{10.7}(t)$.
+The long term correlation could be a bias for $D_{st}$'s effects, so a linear model was created, recreating mass density purely from $F_{10.7}$ in the form of $\rho_{eq}(t)=a\cdot F_{10.7}(t)$.
 This re-created $\rho_{eq}$ shows around a 45\% correlation with the actual $\rho_{eq}$, suggesting a strong influence, while doing the same procedure with $D_{st}$ shows only a 20-25\% correlation.
@@
 The positive relationship seen in \cite{Takahashi2010} could be due to the short time period looked at, and that it coincides with periods of higher $F_{10.7}$.
+
+Looking at GOES 2,5,6, and 7 (Figures \ref{GOES67,GOES25}) shows that this post-onset $D_{st}$ spike happens in almost every case for periods of high $F_{10.7}$.
 
@@
 \rule[1ex]{5cm}{1pt}
-\includegraphics[scale=0.40]{paperfigures/stormavs-mass-tak.eps}
-\caption{Events in the interval 1989-1991. Upper panel: $D_{st}$ events. Lower panel: $\rho_{eq}$ events.}
+\includegraphics[scale=0.40]{paperfigures/stormavs-dst-day.eps}
+\caption{Events in the interval 1989-1991. Upper panel: $D_{st}$ events. Lower panel: Events in the interval 1983-1991.}
 \label{DailyAverages}
@@
 \centering
-\includegraphics[scale=0.40]{paperfigures/stormavs-dst-day.eps}
-\rule[1ex]{5cm}{1pt}
-\includegraphics[scale=0.40]{paperfigures/stormavs-mass-day.eps}
-\caption{Events in the interval 1983-1991.  Upper panel: $D_{st}$ events. Lower panel: $\rho_{eq}$ events.}
-\label{DailyAveragesAllData}
-\end{figure}
-\clearpage
-
-\begin{figure}[tp!]
-\centering
 \includegraphics[scale=0.40]{paperfigures/stormavs-dst.eps}
 \rule[1ex]{5cm}{1pt}
-\includegraphics[scale=0.40]{paperfigures/stormavs-mass.eps}
+\includegraphics[scale=0.40]{paperfigures/stormavs-dd12.eps}
 \caption{(a) Average of solar wind and near-Earth measurements around the time $D_{st}$ crossed below $-50$~nT onset.
-(b) Same as (a) except around time intervals where mass density crossed above $40$~amu/cm$^3$.}
+(b) Same as (a) except for constraint that $D_{st}$ stayed below $-50$~nT for at least 12~hours.}
 \label{Storms}
@@
 
-\begin{figure}[tp!]
-\centering
-\includegraphics[scale=0.40]{paperfigures/stormavs-dd12.eps}
-\rule[1ex]{5cm}{1pt}
-\includegraphics[scale=0.40]{paperfigures/stormavs-md12.eps}
-\caption{(a) Same as Figure \ref{Storms}(a) except with constraint that $D_{st}$ stayed below $-50$~nT for at least 12~hours.
-(b) Same as Figure \ref{Storms}(b) except for constrain that $\rho_{eq}$ stayed above $50$~amu/cm$^3$ for at least 12 hours.}
-\label{Mspec}
-\end{figure}
 \clearpage
@@
 \rule[1ex]{5cm}{1pt}
-\includegraphics[scale=0.40]{paperfigures/stormavs-m70.eps}
-\caption{(a) Same as Figure \ref{Storms}(a) except with constraint that $D_{st}$ crossed below $-80$~nT (b) Same as Figure \ref{Storms}(b) except for constrain that $\rho_{eq}$ crossed above $70$~amu/cm$^3$.}
+\caption{(a) Same as Figure \ref{Storms}(a) except with constraint that $D_{st}$ crossed below $-80$~nT }
 \label{Dspec}
 \end{figure}
-
-\begin{figure}[tp!]
-\centering
-\includegraphics[scale=0.40]{paperfigures/stormavs-diffden-10amu.eps}
-\rule[1ex]{5cm}{1pt}
-\includegraphics[scale=0.40]{paperfigures/stormavs-diffden-30percent.eps}
-\caption{(a) diff($\rho_{eq}$) $>$ 10$\frac{amu}{hour}$. (b) diff($\rho_{eq}$) $>$ 30$\frac{\%}{hour}$}
-\label{rhochange}
-\end{figure}
-\clearpage
 
@@
 
-\begin{figure}[tp]
-\centering
-\includegraphics[scale=0.40]{paperfigures/blockmedian.eps}
-\includegraphics[scale=0.40]{paperfigures/blockmedian-prenoon.eps}
-\caption{Comparing median values calculated as median of all 1-hour points in the 12 day block, and as the daily median of all hourly-mediated events.
-(b) Same, but only events starting between 0-12 UTC}
-\label{blockmedian}
+\clearpage
+
+\begin{figure}[htp!]
+\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES6-1983-1991.eps}
+\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES7-1987-1991.eps}
+\caption{GOES Satellite 6 and 7}
+\label{GOES67}
+\end{figure}
+
+\begin{figure}[htp!]
+\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES2-1981-1983.eps}
+\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES5-1983-1987.eps}
+\caption{GOES Satellite 2 and 5}
+\label{GOES25}
 \end{figure}
@@
 
-\begin{figure}[tp]
-\centering
-\includegraphics[scale=0.9]{paperfigures/allstorms.eps}
-\caption{Comparing all events to their median and $1\sigma$ range}
-\label{allstorms}
+\begin{figure}[htp!]
+\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES6-1989-1991.eps}
+\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst80.eps}
+\caption{Top: GOES 6 from 89-91 (compare to Takahashi 2010). Bottom:  $D_{st}<-80$~nT.}
 \end{figure}
-\clearpage
 
-\begin{figure}[tp]
-\centering
-\includegraphics[scale=0.5]{paperfigures/nansbyhour.eps}
-\includegraphics[scale=0.5]{paperfigures/nansbyhour_storm.eps}
-\caption{(a) Number of NaN points per hour of observation in the total data set (b) $\rho_{eq}$ data availability relative to average event hour in events where $D_{st}<-80$~nT.}
-\label{nanperhour}
+\begin{figure}[htp!]
+\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES6-1983-1987.eps}
+\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES6-1987-1991.eps}
+\caption{GOES 6 from 83-87 and 87-91}
 \end{figure}
@@
 \begin{figure}[htp!]
-\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES6-1983-1991.eps}
-\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES7-1987-1991.eps}
-\caption{GOES Satellite 6 and 7}
-\end{figure}
-
-\begin{figure}[htp!]
-\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES2-1981-1983.eps}
-\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES5-1983-1987.eps}
-\caption{GOES Satellite 2 and 5}
-\end{figure}
-\clearpage
-
-\begin{figure}[htp!]
-\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES6-1989-1991.eps}
-\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst80.eps}
-\caption{Top: From 89-91 (compare to Takahashi 2010). Bottom:  $D_{st}<-80$~nT.}
-\end{figure}
-
-\begin{figure}[htp!]
-\includegraphics[scale=0.45]{paperfigures/AEbyhour.eps}
-\caption{$AE$ events by their hour of onset}
-\end{figure}
-\clearpage
-
-\begin{figure}[htp!]
 \includegraphics[scale=0.45]{paperfigures/DstRhoThresh-1983-1991.eps}
@@
 
-\begin{figure}[htp!]
-\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES6-1983-1991.eps}
-\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES7-1987-1991.eps}
-\caption{Comparing GOES 6 to GOES 7}
-\end{figure}
-
-\begin{figure}[htp!]
-\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES6-1983-1987.eps}
-\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES6-1987-1991.eps}
-\caption{GOES 6 from 83-87 and 87-91}
-\end{figure}
-
 \end{document}

### 2015-12-10 Density.m

@@ -70,8 +70,8 @@ else
     DBS=1/2*IN(uniquerows,32).*(abs(DBz)-DBz);
     AE=IN(uniquerows,12);
     MLT=IN(uniquerows,8);
-    MassDensity=IN(uniquerows,85); %85 is at magnetic equator, 88 is at spacecraft
-    M=IN(uniquerows,85)./IN(uniquerows,65); %65 is nei_n or electron density topside ionosphere
+    MassDensity=IN(uniquerows,88); %88 is rho_eq
+    M=IN(uniquerows,88)./IN(uniquerows,68); %65 is nei_n or electron density topside ionosphere
     
     save(sprintf('DentonDensityAndTime_%d',satnum),'DentonTime','MassDensity','DBz','MLT','DBS','DVsw','AE','M');
 end
@@ -599,6 +599,7 @@ if(MakePaperPlots && removef107)
 end
 
 if(MakePaperPlots && stormcase==1)
+    figure('Visible',visible);
     xa=(-12:1:24);
     idx=arrayfun(@colon,starti(1:5)-12,starti(1:5)+24,'Uniform',false);
     plot(repmat(xa,5,1)',reshape(MassDensitySpline([idx{:}]),37,5),'r')

### 2016-02-26 paper.tex
Mass rearranging, hopefully better plot organization

@@
 \usepackage[authoryear,square]{natbib}
+\usepackage{aas_macros}
 \pagestyle{fancy}
@@
 \fancyhead[L]{}
+
+\newcommand{\vinote}[1]{\textcolor{red}{\textbf{#1}}} %If you want \inote{#} instead of just \note #, for inline notes
+\def\vnote#1\par{\textcolor{red}{\textbf{#1}}\\} %Make note bold and red, re-add newline
+\newcommand{\req}{\ensuremath{\rho_{eq}}}
 
@@
 
+\vnote More detail
+
 %It confirms results from previous papers that a sudden drop in $D_{st}$ correlates with a spike in equatorial mass density under certain conditions, while adding a level of depth and specification to the applicability of their results.
@@
 \section{Introduction}
+\cite{Gallagher1988EmpiricalModelPlasmasphere} \vinote{Too far back?} first models the the plasmasphere as a simple linear fit dependent on L shell, geographic height, geomagnetic latitude, and $K_p$.
+\cite{Hamilton1988RingCurrentDevelopment} simultaneously analyzes a strong geomagnetic storm by comparing empirical energy measurements of the ring current to $D_{st}$, along with measuring ring current compositions before, during, and after the storm.
 
-\cite{Takahashi2006} estimated magnetospheric mass density using measurements from the CRRES satellite during a 73-day period and 1991 and found that the average ion mass density, $M=\rho/n_e$, correlated with geomagnetic activity, with lower $D_{st}$ values corresponding to slightly higher average ion mass densities.
-They also found a relationship between the average ion mass and 1.5- and 3-day averages of $K_p$ were compared to $M$.
-Most measurements occurred in the MLT range of 12:00 and 18:00 in the plasma trough, and CRRES had a nearly equatorial orbit.
+\cite{Lotoaniu1999PlasmaMassDensity} uses CRRES to compare in-situ measured plasma mass density to that inferred by ground-based ULF wave measurements extended to the plasmatrough.
 
-\cite{Takahashi2010} developed a mass density dataset using measurements from the GOES satellites over the years 1980 through 1992, with most measurements in the range $L=6.8\pm0.2$.
+\cite{Takahashi2006} estimated magnetospheric mass density using measurements from the CRRES satellite during a 73-day period in 1991 and found that the average ion mass, $M=\rho/n_e$, correlated with geomagnetic activity, with more negative $D_{st}$ values corresponding to slightly higher average ion mass densities.
+They also found a relationship between the average ion mass and 1.5- and 3-day averages of $K_p$, with an increasing correlation as $K_p$ was smoothed to longer timescales.
+The CRRES measurements used occurred in the MLT range of 12:00 and 18:00 mostly in the plasma trough (between 2-7$R_E$) on an elliptical, nearly equatorial orbit.
+
+\cite{Takahashi2010} developed a mass density dataset using measurements from the GOES satellites over the years 1980 through 1992, with most measurements in the range $L=6.8\pm0.2 R_E$.
 The mass density $\rho$ was estimated using the the Alfven wave velocity relationship, $V_A=B/\sqrt{\mu_0\rho}$, a magnetic field model, and a numerical solution to a wave equation with an ionospheric boundary and the assumption of a zero resistance ionosphere.
-The equatorial mass density, $\rho_{eq}$, was estimated from the estimated mass density using a power law dependence on the geocentric distance to the field line of the observation, $R$, $\rho=\rho_{eq}L/(R/R_E)$.
+The equatorial mass density, $\rho_{eq}$, was derived from the estimated mass density using a power law dependence on the geocentric distance to the field line of the observation, $R$, $\rho=\rho_{eq}L/(R/R_E)$.
 
-\cite{Takahashi2010} noted that downward spikes in the $D_{st}$ index coincide with with significant changes in $\rho_{eq}$ at an L-shell of 6.8~$R_E$.
+\cite{Takahashi2010} \vinote{Necessary repetition?} noted that downward spikes in the $D_{st}$ index coincide with with significant changes in $\rho_{eq}$ at an L-shell of 6.8~$R_E$.
 For five storms over a 20-day period, two had $\rho_{eq}$ spikes after the $D_{st}$ drop, two had $\rho_{eq}$ spikes before the drop, and one showed little change in $\rho_{eq}$.
@@
 \cite{Yao2008} studied the relationship between $D_{st}$ and ion number density for different ion species in different regions (ring current and plasma sheet) and found a general correlation during each of the four storms considered.
-
-\cite{Hamilton1988} ... \cite{Gallagher1988} ....
 
@@
 In this work, events defined to occur when $D_{st}$ or $\rho_{eq}$ crosses a threshold value, as indicated in by horizontal dashed lines in the respective panels of Figure~\ref{AllData}.
-In finding events, all fill values were replaced with linearly interpolated values.
+In finding $\rho_{eq}$ events, all fill values were replaced with linearly interpolated values.
 
@@
 That said, the predictability of extreme events is of definite interest, so an attempt has been made to find some reproducible method of prediction.
-Looking at events that last longer than 12 hours and events with an onset threshhold less than $-80$nT results in Figure \ref{Dspec}.
-A spike in mass density is seen, but also a definite lack of data availability to the point where that spike may be coming from less than five of the total 211 events.
-
-Unfortunately there are no events in this time frame that are longer than 12 hours with $D_{st}$ minima lower than $-80$~nT that have existing mass density data around onset, so an analysis of this particular combination of factors can't be made.
+Looking at events that last longer than 12 hours and events with an onset threshhold less than $-80$nT finds both result in a spike in mass density, but also a definite lack of data availability to the point where that spike may be coming from less than five of the total 211 events.
 
 \subsection{Change in $\rho_{eq}$}
-Instead of looking for events based on a threshold of $\rho_{eq}$, we instead looked for a certain amount of change in $\rho_{eq}$ as the basis for event onset.
+Instead of looking for events based on a threshold of $D_{st}$, we instead looked for a certain amount of change in $\rho_{eq}$ as the basis for event onset.
 Both raw change and percent change were done in case of bias towards high or low $\rho_{eq}$ periods, respectively, but neither showed any correlation to a change in $D_{st}$.
@@
 
-Looking at GOES 2,5,6, and 7 (Figures \ref{GOES67,GOES25}) shows that this post-onset $D_{st}$ spike happens in almost every case for periods of high $F_{10.7}$.
+Looking at GOES 2,5,6, and 7 shows that this post-onset $D_{st}$ spike happens in almost every case for periods of high $F_{10.7}$.
+Creating a linear model directly relating variables (and combinations of variables) to $\rho_{eq}$ also shows that $F_{10.7}$ most often has the highest correlation with $\rho_{eq}$.
+A sample of these correlations is shown in Table \ref{perltable}.
+The correlations were made by training a one-input linear model of 5-hour post-onset medians of each variable (or variables) against the median of $\rho_{eq}$ at, and four hours after, event onset.
+This was done by randomly sampling half of the data, generating the model, and testing against the other half, doing this process 100 times and then taking the median correlations.
+
+\input{"tables/perltable.tex"}
 
@@
 \centering
-\includegraphics[scale=0.40]{paperfigures/F107MDAllData.eps}
+\includegraphics[scale=0.40]{paperfigures/F107MD27d-GOES6.eps}
 \includegraphics[scale=0.40]{paperfigures/ccplot.eps}
@@
 \centering
-\includegraphics[scale=0.40]{paperfigures/stormavs-d80.eps}
-\rule[1ex]{5cm}{1pt}
-\caption{(a) Same as Figure \ref{Storms}(a) except with constraint that $D_{st}$ crossed below $-80$~nT }
-\label{Dspec}
-\end{figure}
-
-\begin{figure}[tp!]
-\centering
 \includegraphics[scale=0.40]{paperfigures/HighLowF107rhoeq.eps}
@@
 \label{f107bin}
+\end{figure}
+
+\clearpage
+
+\section{Appendix}
+\hfill
+
+\begin{figure}[htp!]
+\centering
+\includegraphics[scale=0.40]{paperfigures/stormavs-d80.eps}
+\rule[1ex]{5cm}{1pt}
+\caption{(a) Same as Figure \ref{Storms}(a) except with constraint that $D_{st}$ crossed below $-80$~nT }
+\label{Dspec}
 \end{figure}
@@
 
-\section{Appendix}
 \hfill
@@
 
-\begin{figure}[htp!]
-\includegraphics[scale=0.45]{paperfigures/DstRhoThresh-1983-1991.eps}
-\includegraphics[scale=0.45]{paperfigures/DstRhoThresh-1987-1991.eps}
-\caption{High $F_{10.7}$ events - Low $F_{10.7}$ events, both with baselines removed. 83-91 and 87-91}
-\end{figure}
-
-\begin{figure}[htp!]
-\includegraphics[scale=0.45]{paperfigures/DstRhoThresh-1983-1987.eps}
-\includegraphics[scale=0.45]{paperfigures/DstRhoThresh-1981-1983.eps}
-\includegraphics[scale=0.45]{paperfigures/RandRhoThresh-1983-1991.eps}
-\caption{High $F_{10.7}$ events - Low $F_{10.7}$ events, both with baselines removed. 83-87 and 81-83. Bottom: Random "events" from 1983-1991}
-\end{figure}
-\clearpage
-
 \end{document}

### 2016-02-26 BasicPlots.m

@@ -1,0 +1,89 @@
+
+%Variables histogrammed against MLT
+if(MakePaperPlots && stormcase==1)
+    avrhos=zeros(1,24);
+    for i=1:24
+        avrhos(i)=nanmedian(MassDensity(round(MLT)==(i-1)));
+    end
+    figure('Visible',visible);
+    plot(0:23,avrhos,'+-')
+    ylabel('Median \rho_{eq} (amu/cm^3)')
+    xlabel('MLT (hour)')
+    set(findobj('type','axes'),'xgrid','on','ygrid','on','box','on','xtick',[0:4:23])
+    print -depsc2 -r200 paperfigures/rhoMLT.eps
+    print -dpng -r200 paperfigures/PNGs/rhoMLT.png
+    
+    DHr=str2num(datestr(DentonTime,'HH'));
+    for i=1:24
+        avrhos(i)=nanmedian(MassDensity(DHr==(i-1)));
+    end
+    h=figure('Visible',visible);
+    plot(0:23,avrhos,'+-')
+    ylabel('Median \rho_{eq} (amu/cm^3)')
+    xlabel('Local Time (hour)')
+    set(findobj('type','axes'),'xgrid','on','ygrid','on','box','on','xtick',[0:4:23])
+    print -depsc2 -r200 paperfigures/rhoLT.eps
+    print -dpng -r200 paperfigures/PNGs/rhoLT.png
+    
+    for i=1:24
+        avrhos(i)=nanmedian(AE(DHr==(i-1)));
+    end
+    figure('Visible',visible);
+    plot(0:23,avrhos,'+-')
+    ylabel('Median AE (nT)')
+    xlabel('Local Time (hour)')
+    set(findobj('type','axes'),'xgrid','on','ygrid','on','box','on','xtick',[0:4:23])
+    print -depsc2 -r200 paperfigures/AELT.eps
+    print -dpng -r200 paperfigures/PNGs/AELT.png
+    
+    for i=1:24
+        avrhos(i)=nanmedian(FILLED(FILLED(:,3)==(i-1),15));
+    end
+    figure('Visible',visible);
+    plot(0:23,avrhos,'+-')
+    ylabel('Median D_{st} (nT)')
+    xlabel('Local Time (hour)')
+    set(findobj('type','axes'),'xgrid','on','ygrid','on','box','on','xtick',[0:4:23])
+    print -depsc2 -r200 paperfigures/DstLT.eps
[…]

### 2016-02-26 DataProofPlots.m

@@ -1,0 +1,40 @@
+%Show ten events to make point about data availability
+if(MakePaperPlots && stormcase==1)
+    figure('Visible',visible);
+    xevents=(-12:1:24);
+    idx=arrayfun(@colon,starti(1:5)-12,starti(1:5)+24,'Uniform',false);
+    plot(repmat(xevents,5,1)',reshape(MassDensitySpline([idx{:}]),37,5),'r')
+    hold on;
+    idx2=arrayfun(@colon,starti(end-4:end)-12,starti(end-4:end)+24,'Uniform',false);
+    plot(repmat(xevents,5,1)',reshape(MassDensitySpline([idx2{:}]),37,5),'b')
+    ylabel('\rho_{eq} (amu/cm^3)')
+    xlabel('Hours from onset')
+    title(sprintf('First 5 (red) and last 5 (blue) events from %d-%d',sy,ey));
+    print -depsc2 -r200 paperfigures/TenEvents.eps
+    print -dpng -r200 paperfigures/PNGs/TenEvents.png
+end
+
+%Compare the two densities
+if(MakePlots)
+    figure('Visible',visible); plot(FILLEDTime,MassDensitySpline);hold on; 
+    plot(FILLEDTime,OMNIDensity,'r')
+    legend('Denton','OMNI','Location','NorthEast')
+    title('OMNI Density vs Denton Density')
+    ylabel('Density')
+    xlabel('Time')
+    datetick
+    print -dpng figures/densitycomp.png
+    print -depsc2 figures/densitycomp.eps
+end
+
+%Showing 'detrending' by removing F10.7 influencex`
+if(MakePaperPlots && removef107)
+    figure('Visible',visible);
+    plot(FILLEDTime,MassDensitySplineOriginal,'r.')
+    hold on; plot(FILLEDTime,MassDensitySpline,'b.')
+    legend('Original','F_{10.7} Removed');
+    ylabel('\rho_{eq} (amu/cm^3)')
+    xlabel('Year')
+    datetick
+    print -depsc2 -r200 paperfigures/f107removed.eps
+end

### 2016-02-26 Density.m

@@ -1,13 +1,13 @@
-function Density(stormcase,satnum,cutyears)
+function Density(stormcase,satnum,cuttime)
 if nargin < 1
     stormcase=1;
     satnum=6;
-    cutyears=[1900 2100]; %Just to use all data. The years only serve to constrict, if possible
+    cuttime=[0 datenum('Jan-01-2100')]; %Just to use all data. The years only serve to constrict, if possible
 elseif nargin < 2
     satnum=6;
-    cutyears=[1900 2100];
+    cuttime=[0 datenum('Jan-01-2100')];
 elseif nargin < 3
-    cutyears=[1900 2100];
+    cuttime=[0 datenum('Jan-01-2100')];
 end
 
 if(any(stormcase==10:12))
@@ -42,12 +42,12 @@ yranges(4,:,:)=[-3 2; 400 550; -30 -10; 80 120];
 
 LongTimeScale=1;%24*27; %How many hours to average over. Best stick to 1, 24, or 24*27
 cutoffduration=1; %Minimum duration of events, in hours
-cutconditions=0; %1=Look at only pre-noon
-removef107=0;
-DSTCut=0;
+cutconditions=0; %1=Look at only pre-noon. Change in FindStorms.m for other conditions
+removef107=0; %Remove an IR predicted f10.7 dependence from mass density
+DSTCut=0; %Set to 0 here, then if set by a case the code knows what variable to draw a threshold on
 MDCut=0;
 AECut=0;
-nnanalysis=0;
+nnanalysis=0; %Also set 0 here, changed on per-case basis.
 ccanalysis=0;
 figurename='paperfigures/stormavs-';
 %Select kind of storm to look for
@@ -205,54 +205,29 @@ switch stormcase
         figurename=strcat(figurename,'dst.eps');
         yr=2;
 end
-starti=find(storms>0);
-endi=find(storms<0)-1;
-duration=endi-starti+1;
 
-%Shift event start points to next local DST minimum 
-while(0) 
-    ind=FILLED(starti+1,15)<FILLED(starti,15);
-    if(sum(ind)==0)
-        break
-    end
-    starti(ind)=starti(ind)+1;
-end
 
-durationcaveat=''; %empty string if no cutoff set 
[…]

### 2016-02-26 DentonData.m

@@ -96,8 +96,8 @@ end
 %Get everything onto the same time grid
 gettime=FILLEDTime>min(DentonTime);
 gettime=gettime+(FILLEDTime<max(DentonTime));
-gettime=gettime+(FILLEDTime<datenum(cutyears(2)+1,1,1)); %If user wants to cut down time range. Assuming they want entire end year
-gettime=gettime+(FILLEDTime>datenum(cutyears(1),1,1));
+gettime=gettime+(FILLEDTime<cuttime(2)); %If user wants to cut down time range. 
+gettime=gettime+(FILLEDTime>cuttime(1));
 gettime=(gettime==4);
 
 

### 2016-02-26 FindStorms.m

@@ -1,0 +1,35 @@
+function [starti,endi,duration]=FindStorms(storms,FILLED,cutoffduration,cutconditions,maxwidth)
+
+starti=find(storms>0);
+endi=find(storms<0)-1;
+duration=endi-starti+1;
+
+%Shift event start points to next local DST minimum 
+while(0) 
+    ind=FILLED(starti+1,15)<FILLED(starti,15);
+    if(sum(ind)==0)
+        break
+    end
+    starti(ind)=starti(ind)+1;
+end
+
+if(cutoffduration>1)
+    starti=starti(duration>cutoffduration);
+    endi=endi(duration>cutoffduration);
+    duration=duration(duration>cutoffduration);
+end
+
+%Remove storms where the window of interest extends past existing data
+while(starti(1)-maxwidth<1)
+    starti(1)=[]; endi(1)=[];
+end
+while(starti(end)+maxwidth>=length(FILLED(:,1)))
+    starti(end)=[]; endi(end)=[];
+end
+
+%Cut down found storms to only include pre-noon conditions
+if(cutconditions) 
+   endi(MLTFit(starti)>12 | MLTFit(starti)<6)=[];
+   duration(MLTFit(starti)>12 | MLTFit(starti)<6)=[];
+   starti(MLTFit(starti)>12 | MLTFit(starti)<6)=[];
+end

### 2016-02-26 OldPlots.m

@@ -1,0 +1,336 @@
+%%%%%%%%%%%%%%%%%%%%%%
+%Older plots, possibly for thesis, just batch comparing variables and
+%making correlation tables
+
+
+
+VBS=1/2*FILLED(:,6).*(abs(FILLED(:,5))-FILLED(:,5));
+VBz=FILLED(:,6).*FILLED(:,5);
+BS=1/2*(abs(FILLED(:,5))-FILLED(:,5));
+OMNIDensity=FILLED(:,7);
+
+%Get re-scaled values for the sake of plotting overlays
+OverlayFilled=FILLED;
+OHr=FILLED(:,3);
+DHr=hour(DentonTime);
+for i=1:length(headers)
+    OverlayFilled(:,i)=((250-150).*(OverlayFilled(:,i)-min(OverlayFilled(:,i))))./(max(OverlayFilled(:,i))-min(OverlayFilled(:,i))) + 150;
+end
+OverlayBS=((250-150).*(BS-min(BS)))./(max(BS)-min(BS)) + 150;
+OverlayVBS=((250-150).*(VBS-min(VBS)))./(max(VBS)-min(VBS)) + 150;
+OverlayVBz=((250-150).*(VBz-min(VBz)))./(max(VBz)-min(VBz)) + 150;
+OverlayF107=((250-150).*(F107-min(F107)))./(max(F107)-min(F107)) + 150;
+OverlayDBz=((250-150).*(DBz-min(DBz)))./(max(DBz)-min(DBz)) + 150;
+OverlayDBS=((250-150).*(DBS-min(DBS)))./(max(DBS)-min(DBS)) + 150;
+
+
+if(MakePlots) %Stack plots
+    for i=1:length(headers)
+        subplot('position',subplotstack(5,mod(i,4)+1));plot(AVs(:,i),'+-');
+        ylabel(headers{i})
+        if(mod(i,4)==0 || i==length(headers))
+            subplot('position',subplotstack(5,5)); [AX,H1,H2]=plotyy(1:length(AVMDs),AVMDs(1,:),1:length(AVMDs),AVnnans,'plot','bar');
+            set(AX(2),'Xlim',[1 length(AVMDs)]); set(AX(1),'Xlim',[1 length(AVMDs)]); set(get(H2,'child'),'facea',.3); set(H1,'marker','+','color','red'); set(AX(1),'YColor','r');
[…]

### 2016-02-26 PlotReproductions.m

@@ -1,0 +1,102 @@
+
+%Proof of Median of medians vs block median. Takahashi 2010 Figure 11
+if(MakePaperPlots && stormcase==10)
+    h=figure('Visible',visible);
+    plot(xa(2:end),AVMDblock)
+    hold on; plot(xa(2:end),AVMDs(2:end),'r')
+    plot(xa(2:end),AVMD2(2:end),'k')
+    xlabel('Time from minimum of event (day)')
+    ylabel('\rho_{eq} (amu/cm^3)')
+    legend('Block median','MoM storm, day','MoM day, storm')
+    print -depsc2 -r200 paperfigures/blockmedian.eps
+end
+
+%Tak2006 Fig 10 Kp vs M
+if(MakePaperPlots && stormcase==1)
+   figure('Visible',visible);
+   subplot(311)
+   x=starti;y=starti;
+   for i=1:length(starti)
+    x(i)=nanmedian(FILLED(starti(i)-3:starti(i),13) );
+    y(i)=nanmean(FILLED(starti(i)-3:starti(i),32).*exp(-(3:-1:0)./3)');
+   end
+   plot(x,y,'.'); %KP vs M
+   bins=unique(x); ymid=bins; ysd=bins;
+   for i=1:length(bins)
+       ymid(i)=nanmedian(y(x==bins(i)));
+       ysd(i)=nanstd(y(x==bins(i)));
+   end
+   hold on; plot(bins, ymid,'r-.','MarkerSize',10); plot(bins, ymid-ysd,'k-.','MarkerSize',10); plot(bins, ymid+ysd,'k-.','MarkerSize',10);
+   title(sprintf('%d events from GOES-%d, %d-%d',length(~isnan(y)),satnum,sy,ey))
+   legend('3 hour means')
+   
+   subplot(312) %Go from 1 hour to 1 day
+   for i=1:length(starti)
+    x(i)=nanmedian(FILLED(starti(i)-24:starti(i),13));
+    y(i)=nanmean(FILLED(starti(i)-24:starti(i),32).*exp(-(24:-1:0)./24)');
+   end
+   plot(x,y,'.');
+   bins=unique(x); ymid=bins; ysd=bins;
+   for i=1:length(bins)
+       ymid(i)=nanmedian(y(x==bins(i)));
+       ysd(i)=nanstd(y(x==bins(i)));
+   end
[…]

### 2016-02-26 stackplot.m

@@ -1,15 +1,19 @@
-function stackplot(Time,Data, labels, satnum, ylims, datelimits)
+function stackplot(Time,Data, labels, satnum, ylims, datelimits,visible)
 %To ignore ylimits, pass ylims=0
 %TODO: include filename argument?
 
 if(nargin < 5)
     ylims=0;
     datelimits=[0 datenum('Jan-01-3001')];
+    visible='off';
 elseif nargin < 6
     datelimits=[0 datenum('Jan-01-3001')];
+    visible='off';
+elseif nargin < 7
+    visible='off';
 end
 
-h=figure;%('Visible',visible);
+h=figure('Visible',visible);
 orient tall;
 hold on;
 numvars=length(labels);

### 2016-02-26 paper.tex
Introduction additions

@@
 \section{Introduction}
-\cite{Gallagher1988EmpiricalModelPlasmasphere} \vinote{Too far back?} first models the the plasmasphere as a simple linear fit dependent on L shell, geographic height, geomagnetic latitude, and $K_p$.
-\cite{Hamilton1988RingCurrentDevelopment} simultaneously analyzes a strong geomagnetic storm by comparing empirical energy measurements of the ring current to $D_{st}$, along with measuring ring current compositions before, during, and after the storm.
 
-\cite{Lotoaniu1999PlasmaMassDensity} uses CRRES to compare in-situ measured plasma mass density to that inferred by ground-based ULF wave measurements extended to the plasmatrough.
+The plasma trough is the transition region between the high density and low temperature plasmasphere and the lower density and, in the equatorial plane, higher energy magnetosphere \citep{Mayr1987}.
+Although there are well--validated models of the plasmasphere density as a function of $L$ (\cite{Gallagher1988EmpiricalModelPlasmasphere}, \cite{Lemaire}, \cite{Takahashi2006}, and \cite{Takahashi2010}) and plasmapause boundaries (\cite{Lemaire}, \cite{Moldwin}, \cite{OBrien}), the dependence of the plasma trough on solar wind conditions has not been extensively studied.
+
+\cite{Gallagher1988EmpiricalModelPlasmasphere} modeled the the plasmasphere as a simple linear fit dependent on $L$ shell, geographic altitude, geomagnetic latitude, and $K_p$.
+\vnote{What was major finding?} \cite{Hamilton1988RingCurrentDevelopment} analyzed a strong geomagnetic storm and compared energy measurements of the ring current to $D_{st}$, along with measurements of ring current compositions before, during, and after the storm.
+\vnote{What did they find/conclude?}
+
+\cite{Lotoaniu1999PlasmaMassDensity} used measurements from the \vnote{???} instrument on the CRRES sateelite and compared in-situ measured plasma mass density to that inferred by ground-based ULF wave measurements that extended to the plasmatrough.
+\vnote{What did they find/conclude?}
 
@@
 
-\cite{Takahashi2010} developed a mass density dataset using measurements from the GOES satellites over the years 1980 through 1992, with most measurements in the range $L=6.8\pm0.2 R_E$.
-The mass density $\rho$ was estimated using the the Alfven wave velocity relationship, $V_A=B/\sqrt{\mu_0\rho}$, a magnetic field model, and a numerical solution to a wave equation with an ionospheric boundary and the assumption of a zero resistance ionosphere.
+\cite{Denton2006} showed a relationship between $D_{st}$ and the field line distribution of plasma density, and specifically along the same field lines as looked at in later papers (6-8$R_E$).
+They found that the distribution depends on $L$,.
+
+\cite{Takahashi2010} developed a mass density dataset using measurements from the SEM \vnote{Check instrument} instruments on the GOES satellites from 1980 through 1992, with most measurements in the range $L=6.8\pm0.2 R_E$.
+The mass density $\rho$ was estimated using the the Alf\v'en wave velocity relationship, $V_A=B/\sqrt{\mu_0\rho}$, a magnetic field model, and a numerical solution to a wave equation with an ionospheric boundary and the assumption of a zero resistance ionosphere.
 The equatorial mass density, $\rho_{eq}$, was derived from the estimated mass density using a power law dependence on the geocentric distance to the field line of the observation, $R$, $\rho=\rho_{eq}L/(R/R_E)$.
 
-\cite{Takahashi2010} \vinote{Necessary repetition?} noted that downward spikes in the $D_{st}$ index coincide with with significant changes in $\rho_{eq}$ at an L-shell of 6.8~$R_E$.
-For five storms over a 20-day period, two had $\rho_{eq}$ spikes after the $D_{st}$ drop, two had $\rho_{eq}$ spikes before the drop, and one showed little change in $\rho_{eq}$.
+\cite{Takahashi2010} noted that downward spikes in the $D_{st}$ index coincided with with significant changes in $\rho_{eq}$ at for $L$ near 6.8~$R_E$.
+For five storms, two had $\rho_{eq}$ spikes after the $D_{st}$ drop, two had $\rho_{eq}$ spikes before the drop, and one showed little change in $\rho_{eq}$.
 A key result was that when daily-averaged measurements were considered, an enhancment in $\rho_{eq}$ appeared on the same day as minimum $D_{st}$, indicating the possibility of a solar wind control over $\rho_{eq}$.
@@
 
-%\cite{Denton2006} show how $D_{st}$ affects the distribution of plasma density along different magnetic latitudes, and specifically along the same field lines as looked at in later papers (6-8$R_E$).
-Though this shows that the trends for density may differ between field lines, it's mentioned mostly as a point for future research as the data used in this paper is already adjusted for one field line, as described by \cite{Takahashi2010}.
-
-%\cite{Lavraud2006} show that storms preceded by a northward interplanetary magnetic field (IMF) tend to have higher plasma density than those preceded by a southward IMF, and suggest an increased geoeffectiveness from a northward IMF and dense plasma sheet.
-
-%\cite{Tsurutani1997} show how the density of a corotating interaction region (CIR) shows strong preconditioning for a drop in $D_{st}$ and spike in magnetic field intensity.
-Assuming a reasonable amount of coupling between that region's density and the plasmaspheric density, this result could be relatable to others focusing on the plasmasphere.
+In this work we consider the dependence of plasmaspheric mass density in the \cite{Takahashi2010} in more detail in an attempt to identify the solar wind processes that drives changes in the plasma trough density.
 

### 2016-02-26 paper.tex
Changed plots, updating pdf

@@
 \newcommand{\req}{\ensuremath{\rho_{eq}}}
+\newcommand{\inote}[1]{\textcolor{blue}{\textbf{#1}}} %Inline notes in blue
+\def\note#1\par{\textcolor{blue}{\textbf{#1}}\\}
 
@@
 
-The plasma trough is the transition region between the high density and low temperature plasmasphere and the lower density and, in the equatorial plane, higher energy magnetosphere \citep{Mayr1987}.
-Although there are well--validated models of the plasmasphere density as a function of $L$ (\cite{Gallagher1988EmpiricalModelPlasmasphere}, \cite{Lemaire}, \cite{Takahashi2006}, and \cite{Takahashi2010}) and plasmapause boundaries (\cite{Lemaire}, \cite{Moldwin}, \cite{OBrien}), the dependence of the plasma trough on solar wind conditions has not been extensively studied.
+The plasma trough is the transition region between the high density and low temperature plasmasphere and the lower density and, in the equatorial plane, higher energy magnetosphere \citep{Mayr1968ModelMagnetosphereTemperature}.
+Although there are well--validated models of the plasmasphere density as a function of $L$ (\cite{Gallagher1988EmpiricalModelPlasmasphere}, \cite{LemaireEarthsPlasmasphere}, \cite{Takahashi2006}, and \cite{Takahashi2010}) and plasmapause boundaries (\cite{LemaireEarthsPlasmasphere}, \cite{Moldwin2002ModelPlasmapause}, \cite{OBrien2003EmpiricalPlasmapause}), the dependence of the plasma trough on solar wind conditions has not been extensively studied.
 
 \cite{Gallagher1988EmpiricalModelPlasmasphere} modeled the the plasmasphere as a simple linear fit dependent on $L$ shell, geographic altitude, geomagnetic latitude, and $K_p$.
-\vnote{What was major finding?} \cite{Hamilton1988RingCurrentDevelopment} analyzed a strong geomagnetic storm and compared energy measurements of the ring current to $D_{st}$, along with measurements of ring current compositions before, during, and after the storm.
-\vnote{What did they find/conclude?}
+\inote{What was major finding?} \cite{Hamilton1988RingCurrentDevelopment} analyzed a strong geomagnetic storm and compared energy measurements of the ring current to $D_{st}$, along with measurements of ring current compositions before, during, and after the storm.
+\inote{What did they find/conclude?}
 
-\cite{Lotoaniu1999PlasmaMassDensity} used measurements from the \vnote{???} instrument on the CRRES sateelite and compared in-situ measured plasma mass density to that inferred by ground-based ULF wave measurements that extended to the plasmatrough.
-\vnote{What did they find/conclude?}
+\cite{Lotoaniu1999PlasmaMassDensity} used measurements from the \inote{???} instrument on the CRRES sateelite and compared in-situ measured plasma mass density to that inferred by ground-based ULF wave measurements that extended to the plasmatrough.
+\inote{What did they find/conclude?}
 
@@
 
-\cite{Takahashi2010} developed a mass density dataset using measurements from the SEM \vnote{Check instrument} instruments on the GOES satellites from 1980 through 1992, with most measurements in the range $L=6.8\pm0.2 R_E$.
+\cite{Takahashi2010} developed a mass density dataset using measurements from the SEM \inote{Check instrument} instruments on the GOES satellites from 1980 through 1992, with most measurements in the range $L=6.8\pm0.2 R_E$.
 The mass density $\rho$ was estimated using the the Alf\v'en wave velocity relationship, $V_A=B/\sqrt{\mu_0\rho}$, a magnetic field model, and a numerical solution to a wave equation with an ionospheric boundary and the assumption of a zero resistance ionosphere.

### 2016-02-26 DataProofPlots.m

@@ -1,6 +1,6 @@
 %Show ten events to make point about data availability
 if(MakePaperPlots && stormcase==1)
-    figure('Visible',visible);
+    h=figure('Visible',visible);
     xevents=(-12:1:24);
     idx=arrayfun(@colon,starti(1:5)-12,starti(1:5)+24,'Uniform',false);
     plot(repmat(xevents,5,1)',reshape(MassDensitySpline([idx{:}]),37,5),'r')
@@ -12,11 +12,12 @@ if(MakePaperPlots && stormcase==1)
     title(sprintf('First 5 (red) and last 5 (blue) events from %d-%d',sy,ey));
     print -depsc2 -r200 paperfigures/TenEvents.eps
     print -dpng -r200 paperfigures/PNGs/TenEvents.png
+    if(strcmp(visible,'off')),close(h);end;
 end
 
 %Compare the two densities
 if(MakePlots)
-    figure('Visible',visible); plot(FILLEDTime,MassDensitySpline);hold on; 
+    h=figure('Visible',visible); plot(FILLEDTime,MassDensitySpline);hold on; 
     plot(FILLEDTime,OMNIDensity,'r')
     legend('Denton','OMNI','Location','NorthEast')
     title('OMNI Density vs Denton Density')
@@ -25,11 +26,12 @@ if(MakePlots)
     datetick
     print -dpng figures/densitycomp.png
     print -depsc2 figures/densitycomp.eps
+    if(strcmp(visible,'off')),close(h);end;
 end
 
 %Showing 'detrending' by removing F10.7 influencex`
 if(MakePaperPlots && removef107)
-    figure('Visible',visible);
+    h=figure('Visible',visible);
     plot(FILLEDTime,MassDensitySplineOriginal,'r.')
     hold on; plot(FILLEDTime,MassDensitySpline,'b.')
     legend('Original','F_{10.7} Removed');
@@ -37,4 +39,5 @@ if(MakePaperPlots && removef107)
     xlabel('Year')
     datetick
     print -depsc2 -r200 paperfigures/f107removed.eps
+    if(strcmp(visible,'off')),close(h);end;
 end

### 2016-02-26 FindStorms.m

@@ -1,4 +1,5 @@
-function [starti,endi,duration]=FindStorms(storms,FILLED,cutoffduration,cutconditions,maxwidth,MLTFit)
+function [starti,endi,duration]=FindStorms(storms,cutoffduration,cutconditions,maxwidth,MLTFit,FILLED)
+%If reproduction of DST shifted events is needed, pass FILLED
 
 starti=find(storms>0);
 endi=find(storms<0)-1;
@@ -23,7 +24,7 @@ end
 while(starti(1)-maxwidth<1)
     starti(1)=[]; endi(1)=[];
 end
-while(starti(end)+maxwidth>=length(FILLED(:,1)))
+while(starti(end)+maxwidth>=length(storms)-1)
     starti(end)=[]; endi(end)=[];
 end
 

### 2016-02-26 PlotReproductions.m

@@ -9,11 +9,12 @@ if(MakePaperPlots && stormcase==10)
     ylabel('\rho_{eq} (amu/cm^3)')
     legend('Block median','MoM storm, day','MoM day, storm')
     print -depsc2 -r200 paperfigures/blockmedian.eps
+    if(strcmp(visible,'off')),close(h);end;
 end
 
 %Tak2006 Fig 10 Kp vs M
 if(MakePaperPlots && stormcase==1)
-   figure('Visible',visible);
+   h=figure('Visible',visible);
    subplot(311)
    x=starti;y=starti;
    for i=1:length(starti)
@@ -61,6 +62,7 @@ if(MakePaperPlots && stormcase==1)
    legend('3 day means')
    
    print -depsc2 -r200 paperfigures/KpvsM.eps
+   if(strcmp(visible,'off')),close(h);end;
 
 
 %%%%%%%%%%%
@@ -82,6 +84,7 @@ if(MakePaperPlots && stormcase==1)
     grid on
     print('-depsc2', '-r200', sprintf('paperfigures/F107MD27d-GOES%d.eps',satnum))
     print('-dpng', '-r200', sprintf('paperfigures/PNGs/F107MD27d-GOES%d.png',satnum))
+    if(strcmp(visible,'off')),close(h);end;
     
     h=figure('Visible',visible);
     NewTime=FILLEDTime(1):24*(FILLEDTime(2)-FILLEDTime(1)):FILLEDTime(end);
@@ -99,4 +102,5 @@ if(MakePaperPlots && stormcase==1)
     grid on
     print('-depsc2', '-r200', sprintf('paperfigures/F107MD1d-GOES%d.eps',satnum))
     print('-dpng', '-r200', sprintf('paperfigures/PNGs/F107MD1d-GOES%d.png',satnum))
+    if(strcmp(visible,'off')),close(h);end;
 end

### 2016-02-26 binplot.m

@@ -44,6 +44,7 @@ set(objh,'linewidth',2);
 title(sprintf('%d evenly-binned events of %s %s (%s) for GOES%d: %d-%d',length(events),eventname,plotthresh,eventunits,satnum,timerange(1),timerange(2)))
 print('-depsc2','-r200',sprintf('paperfigures/HighLow%s%s-%s%s-GOES%d-%d-%d.eps',safesortname,safeplotname,safeeventname,safethresh,satnum,timerange(1),timerange(2)))
 print('-dpng','-r200',sprintf('paperfigures/PNGs/HighLow%s%s-%s%s-GOES%d-%d-%d.png',safesortname,safeplotname,safeeventname,safethresh,satnum,timerange(1),timerange(2)))
+if(strcmp(visible,'off')),close(h);end;
 
 if(sum(sum(isnan(plotter)))) %If any nan points
     h=figure('Visible',visible);
@@ -61,4 +62,5 @@ if(sum(sum(isnan(plotter)))) %If any nan points
     set(findobj('type','axes'),'xgrid','on','ygrid','on','box','on','xtick',[-timewidth:timewidth/2:timewidth*2]./LongTimeScale)
     print('-depsc2','-r200',sprintf('paperfigures/HighLow%s%s-%s%s-GOES%d-%d-%d-valid.eps',safesortname,safeplotname,safeeventname,safethresh,satnum,timerange(1),timerange(2)))
     print('-dpng','-r200',sprintf('paperfigures/PNGs/HighLow%s%s-%s%s-GOES%d-%d-%d-valid.png',safesortname,safeplotname,safeeventname,safethresh,satnum,timerange(1),timerange(2)))
+    if(strcmp(visible,'off')),close(h);end;
 end

### 2016-02-26 paper.tex
Updates in data section

--- 2016-02-26 paper.tex
@@
 
-The parameters $\rho_{eq}$ and $F_{10.7}$ used in this work are from the dataset associated with \cite{Denton}, with data available from 1980 through 1991; all other parameters are from \cite{Reconstruction} over the time range of 1972 through 2013, which are on a 1--hour time grid.
+The parameters $\rho_{eq}$ and $F_{10.7}$ used in this work are from the dataset associated with \cite{Denton}, with data available from 1980 through 1991; all other parameters are from \cite{Reconstruction} from 1972 through 2013, which are on a 1--hour time grid.
 $\rho_{eq}$ is the inferred equatorial mass density based on the 3rd harmonic torodial frequency of magnetic field measurements.
@@
 To compute an hourly average over the same interval for which the solar wind parameters were averaged, the median of all $\rho_{eq}$ values in a given hourly range was used.
-Fill values were used for hours in which no measurements were available.
+Fill (NaN) values were used for hours in which no measurements were available.
 In cases where $\rho_{eq}$ was available from multiple Geostationary Operational Environmental Satellites (GOES) satellites at the same time in the \cite{Denton} dataset, the value from GOES 6 was selected.
@@
 In finding $\rho_{eq}$ events, all fill values were replaced with linearly interpolated values.
-
-% Though this may skew the onset time slightly, it's thought to be less skewed than trying to determine start and end times with the NaNs in place.
-This interpolation was only used for determining storm times, and not for any analysis.
-% If you say this, you need to do an experiement.  A review will say ``seems like it is an easy statement to check.  Why didn't you?''
 

### 2016-02-26 paper.tex
Updates in data preparation

@@
 
-% How does GOES 7 only effect result.
-
 In this work, events defined to occur when $D_{st}$ or $\rho_{eq}$ crosses a threshold value, as indicated in by horizontal dashed lines in the respective panels of Figure~\ref{AllData}.
@@
 
-\section{Results}
-Figure \ref{AllData} shows values of solar wind averages and mass density used in this study.
+Figure \ref{AllData} shows values of solar wind averages and mass density from GOES 6.
+The corresponding 27-day correlations for GOES 2, 5, and 7 are 0.81, 0.78, and 0.87, and the time range of coverage of measurements from these satellites are 1980-01-01/1983-05-16, 1983-01-01/1987-02-28, and 1983-05-27/1991-08-29
 
-Figure~\ref{ccplot} shows the long-term trends of $log(\rho_{eq})$ and $F_{10.7}$ computed using the median values in 27-day (non-overalpping?) windows using all non--fill hourly values.
+Figure~\ref{ccplot} shows the long-term trends of GOES 6 based $log(\rho_{eq})$ and $F_{10.7}$ computed using the median values in 27-day (non-overalpping?) windows using all non--fill hourly values.
 A scatter plot of these two lines is shown in Figure~\ref{ccplot}.
 The linear correlation is found to be $0.94$ matching the value found by \cite{Takahashi2010} who used measurements from all satellites in the time interval of 1980 through 1991.
+
+\section{Results}
 
@@
 \caption{Overview of data used in this study.
-The top four panels show parameters from \cite{Reconstruction} and the bottom panel is based on $\rho_{eq}$ from \cite{Denton} after interpolation and averaging described in the text.
-Dashed horizontal lines in the $D_{st}$ and $\rho_{eq}$ panels indicate sample event cutoff thresholds of $D_{st}=-50$~nT and $\rho_{eq}=40$~amu/cm$^3$}.
+The top four panels show parameters from \cite{Reconstruction} and the bottom panel contains $\rho_{eq}$ based on GOES 6 measurements from \cite{Denton} after interpolation and averaging described in the text.
+Dashed horizontal lines in the $D_{st}$ and $\rho_{eq}$ panels indicate sample event cutoff thresholds of $D_{st} = -50$~nT and $\rho_{eq} = 40$~amu/cm$^3$}.
 \label{AllData}

### 2016-02-26 paper.tex
Plot modifications

--- 2016-02-26 paper.tex
@@
 \cite{Gallagher1988EmpiricalModelPlasmasphere} modeled the the plasmasphere as a simple linear fit dependent on $L$ shell, geographic altitude, geomagnetic latitude, and $K_p$.
-\inote{What was major finding?} \cite{Hamilton1988RingCurrentDevelopment} analyzed a strong geomagnetic storm and compared energy measurements of the ring current to $D_{st}$, along with measurements of ring current compositions before, during, and after the storm.
+They found they could accurately model geomagnetically active conditions  \cite{Hamilton1988RingCurrentDevelopment} analyzed a strong geomagnetic storm and compared energy measurements of the ring current to $D_{st}$, along with measurements of ring current compositions before, during, and after the storm.
 \inote{What did they find/conclude?}
@@
 
-The parameters $\rho_{eq}$ and $F_{10.7}$ used in this work are from the dataset associated with \cite{Denton}, with data available from 1980 through 1991; all other parameters are from \cite{Reconstruction} from 1972 through 2013, which are on a 1--hour time grid.
+The parameters $\rho_{eq}$ and $F_{10.7}$ used in this work are from the dataset associated with \cite{Denton}, with data available from 1980 through 1991; all other parameters are from \cite{Reconstruction} over the time range of 1972 through 2013, which are on a 1--hour time grid.
 $\rho_{eq}$ is the inferred equatorial mass density based on the 3rd harmonic torodial frequency of magnetic field measurements.
@@
 To compute an hourly average over the same interval for which the solar wind parameters were averaged, the median of all $\rho_{eq}$ values in a given hourly range was used.
-Fill (NaN) values were used for hours in which no measurements were available.
+Fill values were used for hours in which no measurements were available.
 In cases where $\rho_{eq}$ was available from multiple Geostationary Operational Environmental Satellites (GOES) satellites at the same time in the \cite{Denton} dataset, the value from GOES 6 was selected.
@@
 In finding $\rho_{eq}$ events, all fill values were replaced with linearly interpolated values.
+
+% Though this may skew the onset time slightly, it's thought to be less skewed than trying to determine start and end times with the NaNs in place.
+This interpolation was only used for determining storm times, and not for any analysis.
+% If you say this, you need to do an experiement.  A review will say ``seems like it is an easy statement to check.  Why didn't you?''
 
@@
 \includegraphics[scale=0.40]{paperfigures/F107MD27d-GOES6.eps}
-\includegraphics[scale=0.40]{paperfigures/ccplot.eps}
+\includegraphics[scale=0.40]{paperfigures/ccplot-GOES6.eps}
 \caption{(a) 27-day averages of $F_{10.7}$ and $\rho_{eq}$.

### 2016-02-26 ComplexPlots.m

@@ -1,0 +1,221 @@
+
+
+if(MakePaperPlots && stormcase==1)
+    stackplot(FILLEDTime, [FILLED(:,[5,6,15,30]) MassDensitySpline'],{'B_z (nT)','V_{SW} (km/s)','D_{st} (nT)','F_{10.7} (s.f.u.)','\rho_{eq} (amu/cm^3)'},satnum,[3 DSTCut])
+    
+    if(satnum==6 && sy<=1989 && ey>=1989) %Make March 1989 Geomagnetic storm plot (if necessary time range still exists)
+        stackplot(FILLEDTime, [FILLED(:,[5,6,15,30]) MassDensitySpline'],{'B_z (nT)','V_{SW} (km/s)','D_{st} (nT)','F_{10.7} (s.f.u.)','\rho_{eq} (amu/cm^3)'},satnum,[],[],[datenum('Mar-10-1989') datenum('Mar-18-1989')])
+    end
+
+    h=figure('Visible',visible);
+    plot(-timewidth:1:timewidth*2,AVMDMat,'.')
+    hold on;
+    xa=(-timewidth:LongTimeScale:timewidth*2);
+    plot(xa,AVMDs(1,:),'r','LineWidth',3);
+    hold on; plot(xa,AVMDMatBars(:,:),'r-.','LineWidth',2);
+    print -depsc2 -r200 paperfigures/allstorms.eps
+    print -dpng -r200 paperfigures/PNGs/allstorms.png    
+    if(strcmp(visible,'off')),close(h);end;
+end
+
+if(MakePaperPlots && MakeBinPlots)
+    if(DSTCut<0)
+        plotthresh=sprintf('< %d',DSTCut);
+        stormtype='D_{st}'; stormunits='nT';
+    elseif(AECut>0)
+        plotthresh=sprintf('> %d',AECut);
+        stormtype='AE'; stormunits='nT';
+    elseif(stormcase==17)
+        plotthresh='';
+        stormtype='random'; stormunits='';
+    else
+        plotthresh=sprintf('> %d',MDCut);
+        stormtype='\rho_{eq}'; stormunits='amu/cm^3';
+    end
+    
+    %plot dst, sort by f10.7
+    binplot(AVMat(:,:,15),FILLED(:,30),starti,timewidth,LongTimeScale,plotthresh,{'D_{st}';'F_{10.7}';stormtype},{'nT';'s.f.u';stormunits},[sy; ey],satnum,visible);
[…]

### 2016-02-26 Density.m

@@ -1,14 +1,19 @@
-function Density(stormcase,satnum,cuttime)
+function Density(stormcase,satnum,cuttime,skiptoplots)
 if nargin < 1
     stormcase=1;
-    satnum=6;
-    cuttime=[0 datenum('Jan-01-2100')]; %Just to use all data. The years only serve to constrict, if possible
-elseif nargin < 2
-    satnum=6;
-    cuttime=[0 datenum('Jan-01-2100')];
-elseif nargin < 3
-    cuttime=[0 datenum('Jan-01-2100')];
 end
+if nargin < 2
+    satnum=6;
+end
+if nargin < 3
+    cuttime=[0 datenum('Jan-01-2100')]; %Just to use all data. The years only serve to constrict, if possible
+end
+if nargin < 4
+    skiptoplots=0;
+end
+
+savefilename=sprintf('data/DensitySaveState_%d_%d_%2.2f_%2.2f.mat',stormcase,satnum,cuttime(1),cuttime(2));
+if(~(exist(savefilename,'file') && skiptoplots))
 
 if(any(stormcase==10:12))
     TakahashiCond=1;
@@ -284,6 +289,12 @@ if(nnanalysis)
 end
 
 
+save(savefilename)
+
+else
+    load(savefilename)
+end
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%    PLOT SECTION    %%%%%%%%%%%%%%%%%%%%%%%%%%
@@ -303,223 +314,12 @@ BasicPlots
 %Plots meant to reproduce a previously published figure
 PlotReproductions
 
-
 %Every plot left here is more advanced analysis
+ComplexPlots
 
 profile viewer
 
-if(MakePaperPlots && stormcase==1)
-    stackplot(FILLEDTime, [FILLED(:,[5,6,15,30]) MassDensitySpline'],{'B_z (nT)','V_{SW} (km/s)','D_{st} (nT)','F_{10.7} (s.f.u.)','\rho_{eq} (amu/cm^3)'},satnum,[3 DSTCut])
-    
-    if(satnum==6 && sy<=1989 && ey>=1989) %Make March 1989 Geomagnetic storm plot (if necessary time range still exists)
[…]

### 2016-02-26 PlotReproductions.m

@@ -74,15 +74,20 @@ if(MakePaperPlots && stormcase==1)
     y=log10(interptest(FILLEDTime,MassDensitySpline',NewTime));
     cc=corrcoef(x,y,'rows','pairwise');
     [AX,H1,H2]=plotyy(NewTime,x,NewTime,y,'plot','plot');
-    set(H1,'marker','.','color','red'); set(AX(1),'YColor','r'); set(AX(2),'XTick',[]);
+    set(H1,'marker','.','color','blue'); set(AX(1),'YColor','r'); set(AX(2),'XTick',[]);
+    set(H2,'marker','.','color','red'); set(AX(2),'YColor','b');
+    ylim(AX(1),[0,300])
     ylim(AX(2),[0.5,1.5])
-    ylabel(AX(1),'F_{10.7\_27d}','FontSize',BigFont); ylabel(AX(2),'log(\rho_{eq\_27d})','FontSize',BigFont);
+    ylabel(AX(1),'F_{10.7\_27d} (s.f.u.)','FontSize',BigFont); ylabel(AX(2),'GOES-6 log_{10}[\rho_{eq} (amu/cm^2)]','FontSize',BigFont);
+    set(AX(1),'YTick',0:50:300);
+    %set(AX(2),'YTick',.5:0.25:1.5);
     xlabel('Year','FontSize',BigFont);
-    title(sprintf('Data comparison for GOES %d - CC: %2.2f',satnum,cc(1,2)),'FontSize',BigFont)
+    title('27-day medians','FontSize',BigFont)
     linkaxes(AX,'x')
     datetick('keeplimits');
     grid on
     print('-depsc2', '-r200', sprintf('paperfigures/F107MD27d-GOES%d.eps',satnum))
+    print('-dpdf', sprintf('paperfigures/F107MD27d-GOES%d.pdf',satnum))
     print('-dpng', '-r200', sprintf('paperfigures/PNGs/F107MD27d-GOES%d.png',satnum))
     if(strcmp(visible,'off')),close(h);end;
     

### 2016-02-26 stackplot.m

@@ -53,6 +53,6 @@ xlabel('Time','FontSize',14)
 
 sy=year(Time(1));
 ey=year(Time(end));
-print('-depsc2','-r200',sprintf('paperfigures/alldata-GOES%d-%d-%d.eps',satnum,sy,ey));
+%print('-depsc2',sprintf('paperfigures/alldata-GOES%d-%d-%d.eps',satnum,sy,ey));
+print('-depsc2','-r300',sprintf('paperfigures/alldata-GOES%d-%d-%d.eps',satnum,sy,ey));
 print('-dpng','-r200',sprintf('paperfigures/PNGs/alldata-GOES%d-%d-%d.png',satnum,sy,ey));
-if(strcmp(visible,'off')),close(h);end;

### 2016-02-26 paper.tex
Paper edits

@@
 
-\cite{Gallagher1988EmpiricalModelPlasmasphere} modeled the the plasmasphere as a simple linear fit dependent on $L$ shell, geographic altitude, geomagnetic latitude, and $K_p$.
-They found they could accurately model geomagnetically active conditions  \cite{Hamilton1988RingCurrentDevelopment} analyzed a strong geomagnetic storm and compared energy measurements of the ring current to $D_{st}$, along with measurements of ring current compositions before, during, and after the storm.
-\inote{What did they find/conclude?}
+\cite{Gallagher1988EmpiricalModelPlasmasphere} used the Retarding Ion Mass Spectrometer onboard the Dynamics Explorer 1 satellite to model the the plasmasphere as a simple linear fit dependent on $L$ shell, geographic altitude, geomagnetic latitude, and $K_p$.
+They found they could accurately model geomagnetically active conditions by using a weighted average $K_p$ value and an azimuthal symmetry at smaller L-shells.
+\cite{Hamilton1988RingCurrentDevelopment} analyzed a strong geomagnetic storm and compared energy measurements of the ring current to $D_{st}$, along with measurements of ring current compositions before, during, and after the storm.
+They found $D_{st}$ to be correlated with the inner ring current energy density during and after storm onset, an inward movement of energy density, and a rapid $D_{st}$ recovery from the quick loss of heavier ions.
 
-\cite{Lotoaniu1999PlasmaMassDensity} used measurements from the \inote{???} instrument on the CRRES sateelite and compared in-situ measured plasma mass density to that inferred by ground-based ULF wave measurements that extended to the plasmatrough.
-\inote{What did they find/conclude?}
+\cite{Lotoaniu1999PlasmaMassDensity} used measurements from the Plasma Wave Experiment instrument on the CRRES satellite and compared in-situ measured plasma mass density to that inferred by ground-based ULF wave measurements from the CANOPUS array.
+By extending the ground footprints to the plasmatrough, they found agreement between the two methods for certain plasmapause conditions.
+\vinote{Mention specifics?
+Worth including paper?}
 
@@
 
-\cite{Takahashi2010} developed a mass density dataset using measurements from the SEM \inote{Check instrument} instruments on the GOES satellites from 1980 through 1992, with most measurements in the range $L=6.8\pm0.2 R_E$.
-The mass density $\rho$ was estimated using the the Alf\v'en wave velocity relationship, $V_A=B/\sqrt{\mu_0\rho}$, a magnetic field model, and a numerical solution to a wave equation with an ionospheric boundary and the assumption of a zero resistance ionosphere.
+\cite{Takahashi2010} developed a mass density dataset using measurements from the Space Environment Monitor instruments on the GOES satellites from 1980 through 1992, with most measurements in the range $L=6.8\pm0.2 R_E$.
+The mass density $\rho$ was estimated using the the Alf\v'en wave velocity relationship, $V_A=B/\sqrt{\mu_0\rho}$, \vinote{Connect to harmonic toroidal frequency} a magnetic field model, and a numerical solution to a wave equation with an ionospheric boundary and the assumption of a zero resistance ionosphere.
 The equatorial mass density, $\rho_{eq}$, was derived from the estimated mass density using a power law dependence on the geocentric distance to the field line of the observation, $R$, $\rho=\rho_{eq}L/(R/R_E)$.
@@
 
-\section{Data Preparation}
+\section{Data Preparation and Overview}
 
-The parameters $\rho_{eq}$ and $F_{10.7}$ used in this work are from the dataset associated with \cite{Denton}, with data available from 1980 through 1991; all other parameters are from \cite{Reconstruction} from 1972 through 2013, which are on a 1--hour time grid.
-$\rho_{eq}$ is the inferred equatorial mass density based on the 3rd harmonic torodial frequency of magnetic field measurements.
+The parameters $\rho_{eq}$ and $F_{10.7}$ used in this work are from the dataset associated with \cite{Denton}, with data available from 1980 through 1991; all other parameters are from \cite{Kondrashov2014ReconstructionOfGaps} from 1972 through 2013, which are on a 1--hour time grid.
+$\rho_{eq}$ is the inferred equatorial mass density based on the 3rd harmonic torodial frequency of magnetic field measurements \vinote{More explanation?}.
 The smallest cadence for $\rho_{eq}$ values is 10 minutes.
@@
 In the dataset, measurements from GOES 6 had the longest time span of coverage.
-An overview of the data is shown in Figure~\ref{AllData}.
+An overview of the data used is shown in Figure~\ref{AllData}.
 
-In this work, events defined to occur when $D_{st}$ or $\rho_{eq}$ crosses a threshold value, as indicated in by horizontal dashed lines in the respective panels of Figure~\ref{AllData}.
+In this work, events are defined to occur when $D_{st}$ or $\rho_{eq}$ crosses a threshold value, as indicated in by horizontal dashed lines in the respective panels of Figure~\ref{AllData}.
 In finding $\rho_{eq}$ events, all fill values were replaced with linearly interpolated values.
+\vinote{Not including \req\ events?}
 
-Figure \ref{AllData} shows values of solar wind averages and mass density from GOES 6.
-The corresponding 27-day correlations for GOES 2, 5, and 7 are 0.81, 0.78, and 0.87, and the time range of coverage of measurements from these satellites are 1980-01-01/1983-05-16, 1983-01-01/1987-02-28, and 1983-05-27/1991-08-29
-
-Figure~\ref{ccplot} shows the long-term trends of GOES 6 based $log(\rho_{eq})$ and $F_{10.7}$ computed using the median values in 27-day (non-overalpping?) windows using all non--fill hourly values.
-A scatter plot of these two lines is shown in Figure~\ref{ccplot}.
-The linear correlation is found to be $0.94$ matching the value found by \cite{Takahashi2010} who used measurements from all satellites in the time interval of 1980 through 1991.
+Figure~\ref{ccplot} shows the long-term trends of GOES 6 based $log(\rho_{eq})$ and $F_{10.7}$ computed using the median values in 27-day non-overlapping windows using all non-fill hourly values.
+A scatter plot of these two lines is shown in the lower panel of Figure~\ref{ccplot}.
+The linear correlation for GOES 6 is found to be $0.94$ matching the value found by \cite{Takahashi2010} who used measurements from all satellites in the time interval of 1980 through 1991.
+The corresponding 27-day correlations for GOES 2, 5, and 7 are 0.81, 0.78, and 0.87, and the time range of coverage of measurements from these satellites are 1980-01-01/1983-05-16, 1983-01-01/1987-02-28, and 1983-05-27/1991-08-29 respectively.
 
@@
 
-Two types of events are considered. The first is a drop in $D_{st}$ below the threshold of $-50$~nT.  The second is an increase in $\rho_{eq}$ above 40~amu/cm$^3$.
+Two types of events are considered. The first is a drop in $D_{st}$ below the threshold of -50~nT.  The second is an increase in $\rho_{eq}$ above 40~amu/cm$^3$.
 
-Our first analysis uses data only from the time interval 1989-1991.
+Our first analysis uses data only from the time interval 1989-1991 to correspond with the analysis in \cite{Takahashi2010}.
 For both types of events, the hour of the threshold crossing defines the zero epoch time, and for each event $8\cdot24$ hours were kept after each event and $4\cdot24$ hours before each event.
 To compute the epoch averages on a daily time scale, the median value of all measurements for all events centered on a window of $\pm 12$ hours was computed, and these windows were shifted in increments of $24$~hours.
-(Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians in 1-day bins and then compute the medians accross events.)  Error bars for each parameter were computed using the standard deviation of the number of values used in computing the median divided by the square root of the number of values used.
+(Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians in 1-day bins and then compute the medians across events.)  Error bars for each parameter were computed using the standard deviation of the values used in computing the median divided by the square root of the number of values used.
 
-In the upper panel of \ref{DailyAverages}, $D_{st}$ events are shown.
+In the upper panel of Figure \ref{DailyAverages}, $D_{st}$ events are shown.
 The minimum $D_{st}$ median is $-48$~nT.
@@
 The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute its median and error bars.
-Note that for $D_{st}$, the number of measurements used in computing the medians is much larger as we use all available $D_{st}$ measurements instead of restricting to only values where a non--fill $\rho_{eq}$ value existed.
+Note that for the non-\req\ medians, the number of measurements used in computing the medians is typically equal to the number of events which is much larger than the number of \req\ values as we use all available measurements instead of restricting to only values where a non--fill $\rho_{eq}$ value existed.
+\vinote{Alternate: Note that for $D_{st}$ events, we computed median values using all available data, even when \req\ availability was sparse.}
 
-In the lower panel of \ref{DailyAverages} it is shown that all trends seen in the analysis of 1989-1991 also hold for the entire run of GOES 6 over 1983-1991, including the magnitude of change in $\rho_{eq}$ across event onset.
+In the lower panel of Figure \ref{DailyAverages} it is shown that all trends seen in the analysis of 1989-1991 also hold for the entire run of GOES 6 over 1983-1991, including the magnitude of change in $\rho_{eq}$ across event onset.
 
@@
 
-This method finds 669 such periods between May 1983 and August 1991 with an average duration of 9 hours and a median duration of 3 hours.
+This method finds 669 periods of $D_{st}$ crossing beneath the selected threshold between May 1983 and August 1991 with an average duration of 9 hours and a median duration of 3 hours \vinote{Make sure I defined "duration"}.
 Figure \ref{Storms} shows the average values of all events over a window of 24 hours before onset and 48 hours after.
 Figure \ref{Storms}a shows events selected by looking for event onsets where $D_{st}$ crossed a threshold of $-40$~nT.
-The dashed red lines indicate plus and minus one standard deviation of values from all events that went into the average.
+The dashed red lines indicate plus and minus one standard deviation of values from all events that were used to compute the median.
 The final plot in the stack shows both $\rho_{eq}$ and a bar plot of how many valid data points went into the $\rho_{eq}$ average.
 Since $\rho_{eq}$ comes from a sparser dataset, it has less valid points contributing to the averages than the other parameters in the stack.
-A subset of longer duration events will be looked at later.
 
-This figure shows a definite spike in the $Z$ component of the magnetic field, as well as the defined drop in $D_{st}$, but no obvious change in mass density at an hourly timescale.
+Figure \ref{Storms} shows a definite spike in the $Z$ component of the magnetic field, as well as the defined drop in $D_{st}$, but no obvious change in mass density at an hourly timescale.
 This points to an issue with only looking at long-timescale trends between density and $D_{st}$, and allows for the possibility that other factors are influencing the long term correlation since there's no obvious connection on a short timescale.
@@
 Our first analysis uses data only from the time interval 1989-1991.
-In this interval, there were (?) $D_{st}$ events and (?) $\rho_{eq}$ events.
+In this interval, there were 329 $D_{st}$ events and 70 $\rho_{eq}$ events.
 For both types of events, the hour of the threshold crossing defines the zero epoch time, and for each event $8\cdot24$ hours were kept after each event and $4\cdot24$ hours before each event.
@@
 \caption{Overview of data used in this study.
-The top four panels show parameters from \cite{Reconstruction} and the bottom panel contains $\rho_{eq}$ based on GOES 6 measurements from \cite{Denton} after interpolation and averaging described in the text.
+The top four panels show parameters from \cite{Kondrashov2014ReconstructionOfGaps} and the bottom panel contains $\rho_{eq}$ based on GOES 6 measurements from \cite{Denton} after interpolation and averaging described in the text.
 Dashed horizontal lines in the $D_{st}$ and $\rho_{eq}$ panels indicate sample event cutoff thresholds of $D_{st} = -50$~nT and $\rho_{eq} = 40$~amu/cm$^3$}.
@@
 \includegraphics[scale=0.40]{paperfigures/stormavs-dst-day.eps}
-\caption{Events in the interval 1989-1991. Upper panel: $D_{st}$ events. Lower panel: Events in the interval 1983-1991.}
+\caption{$D_{st}$ events from GOES 6. Upper panel: Events in the interval 1989-1991. Lower panel: Events in the interval 1983-1991.}
 \label{DailyAverages}

### 2016-02-26 ComplexPlots.m

@@ -155,22 +155,22 @@ if(MakePaperPlots)
     hold on; plot(xa,AVMatBars(:,:,6),'r-.'); ylim(yranges(yr,2,:))
     h3=subplot('position',subplotstack(5,3));plot(xa,AVs(:,15),'+-','LineWidth',2); text(0.01,0.9,'D_{st} (nT)','Units','normalized','FontSize',14); %ylabel('D_{st} (nT)'); %dst
     hold on; plot(xa,AVMatBars(:,:,15),'r-.'); ylim(yranges(yr,3,:))
-    if(DSTCut<0), plot([xa(1) xa(end)],[DSTCut DSTCut],'r-.','LineWidth',2); hold off; end
+    if(DSTCut<0), plot([xa(1) xa(end)],[DSTCut DSTCut],'k-.','LineWidth',2); hold off; end
     h4=subplot('position',subplotstack(5,4));plot(xa,AVs(:,30),'+-','LineWidth',2); text(0.01,0.9,'F_{10.7} (s.f.u)','Units','normalized','FontSize',14); %ylabel('F10.7 (s.f.u.)');%f107
     hold on; plot(xa,AVMatBars(:,:,30),'r-.'); ylim(yranges(yr,4,:))
     set(findobj('type','axes'),'xticklabel',{[]})
     xv=[xa(1) xa(end)];
     subplot('position',subplotstack(5,5)); [AX,H5,H6]=plotyy(xa,AVMDs(1,:),xa,AVnnans,'plot','bar');
     hold on; plot(xa,AVMDMatBars(:,:),'r-.'); %ylim(AX(1),[0 90])
-    if(MDCut>0), plot([xa(1) xa(end)],[MDCut MDCut],'r-.','LineWidth',2); end
+    if(MDCut>0), plot([xa(1) xa(end)],[MDCut MDCut],'k-.','LineWidth',2); end
     set(H5,'LineWidth',2);set(AX(2),'Xlim',xv); set(AX(1),'Xlim',xv);  set(H5,'marker','+','color','red'); set(AX(1),'YColor','r'); set(AX(2),'YColor',[0 0.5 0.5]); set(get(H6,'child'),'FaceColor',[0 0.5 0.5]); uistack(AX(1)); set(AX(1),'Color','none'); set(AX(2),'Color','w');
[…]

### 2016-02-26 stackplot.m

@@ -31,7 +31,7 @@ for i=1:numvars
     h(i)=subplot('position',subplotstack(numvars,i));
     plot(Time,Data(:,i),'.','MarkerSize',10);
     if(sum(ThreshLines(:,1)==i)>0)
-        hold on; plot(Time,ones(1,length(Time)).*(ThreshLines(ThreshLines(:,1)==i,2)),'r-.','LineWidth',2)
+        hold on; plot(Time,ones(1,length(Time)).*(ThreshLines(ThreshLines(:,1)==i,2)),'k-.','LineWidth',2)
     end
     text(0.01,0.85,labels{i},'Units','normalized','FontSize',14);
     if(ylims~=0)

### 2016-02-27 ComplexPlots.m
Adding histograms and split plot

@@ -16,6 +16,70 @@ if(MakePaperPlots && stormcase==1)
     print -depsc2 -r200 paperfigures/allstorms.eps
     print -dpng -r200 paperfigures/PNGs/allstorms.png    
     if(strcmp(visible,'off')),close(h);end;
+    
+    
+    h=figure('Visible',visible);    
+    for i=1:length(AVMDMat(1,:))
+        top(i)=nanmean(AVMDMat(AVMat(:,i,5)>0,i));
+        topbar(i)=nanstd(AVMDMat(AVMat(:,i,5)>0,i));
+        bottom(i)=nanmean(AVMDMat(AVMat(:,i,5)<0,i));
+        bottombar(i)=nanstd(AVMDMat(AVMat(:,i,5)<0,i));
+    end
+    
+    plot(xa,top)
+    hold on; 
+    plot(xa,bottom,'r')
+    plot(xa,[top+topbar; top-topbar],'b-.')
+    plot(xa,[bottom+bottombar; bottom-bottombar],'r-.')
+    grid on;
+    legend('B_z > 0','B_z < 0')
+    ylabel('\rho_{eq} (amu/cm^3)')
+    xlabel('Time since onset (hours)')
+    print('-depsc2',sprintf('paperfigures/RhoBinnedBz-%d.eps',satnum));
+    print('-dpng', '-r200', sprintf('paperfigures/PNGs/RhoBinnedBz-%d.png',satnum));  
+    
+    
+    
+    h=figure('Visible',visible);
+    hist(nanmean(AVMDMat(:,20:24),2),0:5:100)
+    h1 = findobj(gca,'Type','patch');
+    %set(h1,'FaceColor','r','EdgeColor','w','facealpha',0.75)
+    hold on;
+    hist(nanmean(AVMDMat(:,25:28),2),0:5:100)
+    h2 = findobj(gca,'Type','patch');
+    %set(h2,'facealpha',0.75);
+    legend('Before and at Onset','After Onset')
+    xlim([-5,105])
+    xlabel('Average \rho_{eq} (amu/cm^3)')
+    ylabel('Count')
+    title('Average \rho_{eq} Four Hours Before and After Storm Onset')
+    %Printing segfaults for some reason...
+    print('-depsc2',sprintf('paperfigures/rhobeforeafter-GOES%d.eps',satnum));
+    print('-dpng', '-r200', sprintf('paperfigures/PNGs/rhobeforeafter-GOES%d.png',satnum));    
[…]

### 2016-02-27 Density.m

@@ -28,7 +28,7 @@ MakeDstThreshPlot=0;
 MakeRandThreshPlot=0;
 visible='off';
 
-profile on
+%profile on
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %Script to read all Denton/OMNI data. In a separate script since multiple
@@ -212,6 +212,12 @@ switch stormcase
         DSTCut=-50;
         figurename=strcat(figurename,'dst.eps');
         yr=2;
+    case 24
+                storms=diff([0 (MassDensityNanSpline>20)' 0]); %Mass Density Storm, started at 40
+        MDCut=20;
+        figurename=strcat(figurename,'mass.eps');
+        yr=2;
+        MakeBinPlots=1;
 end
 
 
@@ -317,7 +323,7 @@ PlotReproductions
 %Every plot left here is more advanced analysis
 ComplexPlots
 
-profile viewer
+%profile viewer
 
 
 

### 2016-02-27 PlotReproductions.m

@@ -78,7 +78,7 @@ if(MakePaperPlots && stormcase==1)
     set(H2,'marker','.','color','red'); set(AX(2),'YColor','b');
     ylim(AX(1),[0,300])
     ylim(AX(2),[0.5,1.5])
-    ylabel(AX(1),'F_{10.7\_27d} (s.f.u.)','FontSize',BigFont); ylabel(AX(2),'GOES-6 log_{10}[\rho_{eq} (amu/cm^2)]','FontSize',BigFont);
+    ylabel(AX(1),'F_{10.7} (s.f.u.)','FontSize',BigFont); ylabel(AX(2),'GOES-6 log_{10}[\rho_{eq} (amu/cm^2)]','FontSize',BigFont);
     set(AX(1),'YTick',0:50:300);
     %set(AX(2),'YTick',.5:0.25:1.5);
     xlabel('Year','FontSize',BigFont);

### 2016-02-27 stackplot.m

@@ -29,7 +29,11 @@ Time(Time>datelimits(2))=[];
 
 for i=1:numvars
     h(i)=subplot('position',subplotstack(numvars,i));
-    plot(Time,Data(:,i),'.','MarkerSize',10);
+    if(i<numvars)
+        plot(Time,Data(:,i),'.','MarkerSize',10);
+    else
+        plot(Time,Data(:,i),'r.','MarkerSize',10); %Plot last subplot in red
+    end
     if(sum(ThreshLines(:,1)==i)>0)
         hold on; plot(Time,ones(1,length(Time)).*(ThreshLines(ThreshLines(:,1)==i,2)),'k-.','LineWidth',2)
     end

### 2016-02-27 ComplexPlots.m
req event figure

@@ -18,6 +18,9 @@ if(MakePaperPlots && stormcase==1)
     if(strcmp(visible,'off')),close(h);end;
     
     
+end
+if(MakePaperPlots && (stormcase==2 || stormcase==24)) 
+    
     h=figure('Visible',visible);    
     for i=1:length(AVMDMat(1,:))
         top(i)=nanmean(AVMDMat(AVMat(:,i,5)>0,i));
@@ -43,7 +46,7 @@ if(MakePaperPlots && stormcase==1)
     h=figure('Visible',visible);
     hist(nanmean(AVMDMat(:,20:24),2),0:5:100)
     h1 = findobj(gca,'Type','patch');
-    %set(h1,'FaceColor','r','EdgeColor','w','facealpha',0.75)
+    set(h1,'FaceColor','r','EdgeColor','w');%,'facealpha',0.75
     hold on;
     hist(nanmean(AVMDMat(:,25:28),2),0:5:100)
     h2 = findobj(gca,'Type','patch');
@@ -65,11 +68,16 @@ if(MakePaperPlots && stormcase==1)
         before(i)=nanmean(randsample(reshape(AVMDMat(:,21:25),[],1),4));
         after(i)=nanmean(randsample(reshape(AVMDMat(:,26:29),[],1),4));
     end
-    hist(before,0:5:100)
+    [n,x]=hist(before,0:2:50);
+    stairs(x,n,'LineWidth',2)
     hold on;
-    hist(after,0:5:100)
+    h1 = findobj(gca,'Type','patch');
+    set(h1,'FaceColor','r','EdgeColor','w');
+    [n,x]=hist(after,0:2:50);
+    stairs(x,n,'Color','r');
     legend('Before and at Onset','After Onset')
-    xlim([-5,105])
+    %xlim([-5,105])
+    axis tight;
     xlabel('Average \rho_{eq} (amu/cm^3)')
     ylabel('Count')
     title('Average \rho_{eq} Four Hours Before and After Storm Onset')

### 2016-02-27 Density.m

@@ -215,8 +215,8 @@ switch stormcase
     case 24
                 storms=diff([0 (MassDensityNanSpline>20)' 0]); %Mass Density Storm, started at 40
         MDCut=20;
-        figurename=strcat(figurename,'mass.eps');
-        yr=2;
+        figurename=strcat(figurename,'mass-gt20-GOES',sprintf('%d',satnum),'.eps');
+        yr=1;
         MakeBinPlots=1;
 end
 

### 2016-02-27 paper.tex
Adding histograms and split plot
req event figure
Misc. edits

@@
 In this work we consider the dependence of plasmaspheric mass density in the \cite{Takahashi2010} in more detail in an attempt to identify the solar wind processes that drives changes in the plasma trough density.
+There are several issues that are addressed in detail: (1) the plasma density measurements are sparse and (2) the dependence on the north/south component of the solar wind magnetic field is expected to be nonlinear.
+For northward IMF, the plasmasphere can expand past geosynchronous orbit where measurements of density are made resulting in an increase in observed density; for southward IMF, events studies have shown an increase in density associated with strong southward IMF [\cite{Takahashi2010}; \cite{Yao2008}].
+Issue (1) is addressed by considering \note{Finish}.
+Issue (2) is addressed by considering epochs and linear correlations independent of the direction of the IMF and also by separation by averages of the northrward and southward IMF.
 
@@
 \includegraphics[scale=0.40]{paperfigures/ccplot-GOES6.eps}
-\caption{(a) 27-day averages of $F_{10.7}$ and $\rho_{eq}$.
-(b) Correlation between $\log(\rho_{eq})$ and $F_{10.7}$ using hour, day, and 27-day averaging intervals; compare to \cite{Takahashi2010} Fig.~14.}
+\caption{Top: 27-day boxcar averages of $F_{10.7}$ and $\rho_{eq}$ from GOES 6.
+Bottom: Correlation between $\log(\rho_{eq})$ and $F_{10.7}$ using hour, day, and 27-day averaging intervals; compare to \cite{Takahashi2010} Fig.~14.}
 \label{ccplot}
@@
 \includegraphics[scale=0.40]{paperfigures/stormavs-dst-day.eps}
-\caption{$D_{st}$ events from GOES 6. Upper panel: Events in the interval 1989-1991. Lower panel: Events in the interval 1983-1991.}
+\caption{$D_{st}$ events from GOES 6. Top: Events in the interval 1989-1991; compare to \cite{Takahashi2010} Fig.~11. Bottom: Events in the interval 1983-1991.}
 \label{DailyAverages}

### 2016-03-04 tables/tableparse.pl
Updating tableparse to also do nonlinear perltable

@@ -1,14 +1,27 @@
 #!/usr/bin/perl
 #Parses tables to combine into one table for the paper
 
+if($#ARGV+1 > 0) {
+ $Type=$ARGV[0];
+ if($Type!~m/(NN|CC)/){
+  print "Type must be NN or CC\n";
+  exit
+  }
+} else {
+ $Type="CC";
+}
 
-open(FH1,"<CCtable-GOES2.txt");
+$TypeString="linear";
+if($Type=~m/NN/)
+{$TypeString="nonlinear";}
+
+open(FH1,"<${Type}table-GOES2.txt");
 my @FH1s=<FH1>;
-open(FH2,"<CCtable-GOES5.txt");
+open(FH2,"<${Type}table-GOES5.txt");
 my @FH2s=<FH2>;
-open(FH3,"<CCtable-GOES6.txt");
+open(FH3,"<${Type}table-GOES6.txt");
 my @FH3s=<FH3>;
-open(FH4,"<CCtable-GOES7.txt");
+open(FH4,"<${Type}table-GOES7.txt");
 my @FH4s=<FH4>;
 close(FH1); 
 close(FH2);
@@ -50,7 +63,7 @@ for $line(@FH4s){
 my @Want=('doy','MLT','Bz','Vsw','Dst','Rhosw','F107','Bz+Vsw','Dst+F107','All');
 
 #Print
-open(FH,">perltable.tex");
+open(FH,">${Type}perltable.tex");
 print FH <<EOF;
 \\begin{table}[h]
 \\small
@@ -64,8 +77,8 @@ print FH "$wanted & $H1{$wanted} & $H2{$wanted} & $H3{$wanted} & $H4{$wanted} \\
 print FH <<EOF;
 \\hline
 \\end{tabular}
-\\caption{Table of linear model correlations showing the median of 100 random samples. Each sample trained on half of the data (via randomly selected rows of the least squares matrix) and tested on the other half} 
-\\label{perltable}
+\\caption{Table of $TypeString model correlations showing the median of 100 random samples. Each sample trained on half of the data (via randomly selected rows of the least squares matrix) and tested on the other half} 
+\\label{${Type}perltable}
 \\end{table}
 EOF
 

### 2016-03-04 paper.tex
Updating tableparse to also do nonlinear perltable
misc

@@
 
-\section{Results}
-
-\subsection{$D_{st}$ and $\rho_{eq}$ Events}
+\section{Epoch Average Results}
 
 Two types of events are considered. The first is a drop in $D_{st}$ below the threshold of -50~nT.  The second is an increase in $\rho_{eq}$ above 40~amu/cm$^3$.
+
+\subsection{$D_{st}$ Events}
 
@@
 
-In the upper panel of Figure \ref{DailyAverages}, $D_{st}$ events are shown.
+In the upper panel of Figure \ref{DailyAveragedDstEvents}, $D_{st}$ events are shown.
 The minimum $D_{st}$ median is $-48$~nT.
@@
 
-In the lower panel of Figure \ref{DailyAverages} it is shown that all trends seen in the analysis of 1989-1991 also hold for the entire run of GOES 6 over 1983-1991, including the magnitude of change in $\rho_{eq}$ across event onset.
+In the lower panel of Figure \ref{DailyAveragedDstEvents} it is shown that all trends seen in the analysis of 1989-1991 also hold for the entire run of GOES 6 over 1983-1991, including the magnitude of change in $\rho_{eq}$ across event onset.
 
@@
 This method finds 669 periods of $D_{st}$ crossing beneath the selected threshold between May 1983 and August 1991 with an average duration of 9 hours and a median duration of 3 hours \vinote{Make sure I defined "duration"}.
-Figure \ref{Storms} shows the average values of all events over a window of 24 hours before onset and 48 hours after.
-Figure \ref{Storms}a shows events selected by looking for event onsets where $D_{st}$ crossed a threshold of $-40$~nT.
+Figure \ref{HourlyAveragedDstEvents} shows the average values of all events over a window of 24 hours before onset and 48 hours after.
+Figure \ref{HourlyAveragedDstEvents}a shows events selected by looking for event onsets where $D_{st}$ crossed a threshold of $-40$~nT.
 The dashed red lines indicate plus and minus one standard deviation of values from all events that were used to compute the median.
@@
 
-Figure \ref{Storms} shows a definite spike in the $Z$ component of the magnetic field, as well as the defined drop in $D_{st}$, but no obvious change in mass density at an hourly timescale.
+Figure \ref{HourlyAveragedDstEvents} shows a definite spike in the $Z$ component of the magnetic field, as well as the defined drop in $D_{st}$, but no obvious change in mass density at an hourly timescale.
 This points to an issue with only looking at long-timescale trends between density and $D_{st}$, and allows for the possibility that other factors are influencing the long term correlation since there's no obvious connection on a short timescale.
@@
 
-In the upper panel of \ref{DailyAverages}, $D_{st}$ events are shown.
+In the upper panel of \ref{DailyAveragedDstEvents}, $D_{st}$ events are shown.
 The minimum $D_{st}$ median is $-48$~nT.
@@
 
-In the lower panel of \ref{DailyAverages}, $\rho_{eq}$ events are shown.
+In the lower panel of \ref{DailyAveragedDstEvents}, $\rho_{eq}$ events are shown.
 Here we see that $\rho_{eq}$ enhancements do not clearly correspond to a signature in $D_{st}$, but that there is a trend for such enhancments to occur when $B_{z}$ in the IMF is positive.
@@
 A total of 668 events were found in the interval of May 1983 through August 1991 with an average duration of 9 hours and a median duration of 3 hours.
-Figure \ref{Storms} shows the average values of all events over a window of 24 hours before onset and 48 hours after.
-Figure \ref{Storms}a shows events selected by looking for event onsets where $D_{st}$ crossed a threshold of $-50$~nT.
+Figure \ref{HourlyAveragedDstEvents} shows the average values of all events over a window of 24 hours before onset and 48 hours after.
+Figure \ref{HourlyAveragedDstEvents}a shows events selected by looking for event onsets where $D_{st}$ crossed a threshold of $-50$~nT.
 The dashed red lines indicate plus and minus one standard deviation of values from all events that went into the average.
@@
 
-\subsection{Change in $\rho_{eq}$}
+\subsection{$\rho_{eq}$ Events}
+
 Instead of looking for events based on a threshold of $D_{st}$, we instead looked for a certain amount of change in $\rho_{eq}$ as the basis for event onset.
 Both raw change and percent change were done in case of bias towards high or low $\rho_{eq}$ periods, respectively, but neither showed any correlation to a change in $D_{st}$.
+
+An alterntive type of event can be defined that corresponds to large increases in $\rho\ $.
+Figure~\ref{HourlyAveragedRhoEvents} shows the epoch time series for events in which an increase of $\req\ $ above $20$~amu/cm$^2$ defines the start of the event.
+Here we see the expected result that such events tend to be associated with positive $B_z^{IMF}$.
+To determine if the sign of $B_z^{IMF}$ influences the $\rho\ $ epoch time series, we separated the events by the average of $B_z^{IMF}$ in a time window of $4$~hours centered on the event start time.
+The epoch curves for $B_z^{IMF}\geq=0$ (257) events and $B_z^{IMF}\ge=0$ (139) have no statistically signifiant difference.
 
@@
 \includegraphics[scale=0.40]{paperfigures/stormavs-dst-day.eps}
-\caption{$D_{st}$ events from GOES 6. Top: Events in the interval 1989-1991; compare to \cite{Takahashi2010} Fig.~11. Bottom: Events in the interval 1983-1991.}
-\label{DailyAverages}
+\caption{$D_{st}$ events from GOES 6 using daily medians. Top: Events in the interval 1989-1991; compare to \cite{Takahashi2010} Fig.~11. Bottom: Events in the interval 1983-1991.}
+\label{DailyAveragedDstEvents}
 \end{figure}
@@
 \includegraphics[scale=0.40]{paperfigures/stormavs-dd12.eps}
-\caption{(a) Average of solar wind and near-Earth measurements around the time $D_{st}$ crossed below $-50$~nT onset.
-(b) Same as (a) except for constraint that $D_{st}$ stayed below $-50$~nT for at least 12~hours.}
-\label{Storms}
+\caption{$D_{st}$ events from GOES 6 using hourly medians.
+Top: Events in the interval 1983-1991; compare to bottom panel {DailyAveragedDstEvents}.
+Bottom: Same as Top except for constraint that $D_{st}$ stayed below $-50$~nT for at least 12~hours.}
+\label{HourlyAveragedDstEvents}
 \end{figure}
@@
 \clearpage
+
+\begin{figure}[htp!]
+	\centering
+	\includegraphics[scale=0.40]{paperfigures/stormavs-mass-gt20-GOES6.eps}
+\caption{$\req\ > 20$~ amu/cm^3 events from GOES 6 using hourly medians.
+As described in the text, there is no statistically significant dependence of the $\req\ $ plot on $B_z$ in the time interval of $\pm 2$~hours around the event.}
+\label{HourlyAveragedRhoEvents}
+\end{figure}
 
@@
 \rule[1ex]{5cm}{1pt}
-\caption{(a) Same as Figure \ref{Storms}(a) except with constraint that $D_{st}$ crossed below $-80$~nT }
+\caption{(a) Same as Figure \ref{HourlyAveragedDstEvents}(a) except with constraint that $D_{st}$ crossed below $-80$~nT }
 \label{Dspec}

### 2016-03-04 paper.tex
Updated figures and tables

--- 2016-02-26 paper.tex
@@
 \usepackage{aas_macros}
+\usepackage{array}
 \pagestyle{fancy}
@@
 
+\newcolumntype{L}{>{$}l<{$}} %To enable math mode in tables (for saying things like B_z)
 \newcommand{\vinote}[1]{\textcolor{red}{\textbf{#1}}} %If you want \inote{#} instead of just \note #, for inline notes
@@
 
-\section{Results}
+\section{Results Epoch}
 
@@
 
-\input{"tables/perltable.tex"}
+\input{"tables/CCperltable.tex"}
 
@@
 \label{Storms}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[htp!]
+	\centering
+	\includegraphics[scale=0.40]{paperfigures/stormavs-mass-gt20-GOES6.eps}
+\caption{$\req\ > 20~ amu/cm^3$ events from GOES6.}
+\label{MassStormsGT20Figure}
+\end{figure}
+
+\begin{figure}[tp!]
+	\centering
+	\includegraphics[scale=0.40]{paperfigures/RhoBinnedBz-case24-t020-tf25-GOES6.eps}
+	\includegraphics[scale=0.40]{paperfigures/RhoBinnedBz-case24-t025-tf30-GOES6.eps}
+	\caption{Binning \req\ events by $B_z$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
+	\label{fig:RhoBinned}
 \end{figure}

### 2016-03-04 Density.m

@@ -41,8 +41,8 @@ DentonData
 %-----------
 
 yranges=zeros(5,5,2);
-yranges(1,:,:)=[-2 2; 350 550; -60 0; 150 230; 12 22];
-yranges(2,:,:)=[-8 3; 350 600; -90 0; 160 210; 12 22];
+yranges(1,:,:)=[-2 2; 350 550; -60 0; 150 230; 8 16];
+yranges(2,:,:)=[-8 3; 350 600; -90 0; 160 210; 8 16];
 yranges(3,:,:)=[-8 3; 350 580; -90 0; 170 200; 12 22];
 yranges(4,:,:)=[-3 2; 400 550; -30 -10; 80 120; 12 22];
 yranges(5,:,:)=[-10 10; 0 1000; -100 0; 00 200; 12 22]; %Made for overwriting with specific cases
@@ -64,89 +64,92 @@ switch stormcase
     case 1
         storms=diff([0 (FILLED(:,15)<-50)' 0]); %DST Storm
         DSTCut=-50;
-        figurename=strcat(figurename,'dst.eps');
+        figurename=strcat(figurename,'dst',sprintf('-GOES%d.eps',satnum));
         yr=2;
         MakeBinPlots=1;
     case 2
         storms=diff([0 (MassDensityNanSpline>40)' 0]); %Mass Density Storm, started at 40
         MDCut=40;
-        figurename=strcat(figurename,'mass.eps');
+        figurename=strcat(figurename,'mass',sprintf('-GOES%d.eps',satnum));
         yr=2;
         MakeBinPlots=1;
     case 3
         storms=[0 diff([0 (diff(MassDensityNanSpline)>10)' 0])];
-        figurename=strcat(figurename,'diffden-10amu.eps');
+        figurename=strcat(figurename,'diffden-10amu',sprintf('-GOES%d.eps',satnum));
         yr=3;
     case 4
         storms=[0 diff([0 (abs(MassDensityNanSpline(2:end)./MassDensityNanSpline(1:end-1))>1.3)' 0])];
-        figurename=strcat(figurename,'diffden-30percent.eps');
+        figurename=strcat(figurename,'diffden-30percent',sprintf('-GOES%d.eps',satnum));
         yr=3;
     case 5
         storms=diff([0 (FILLED(:,15)<-50)' 0]);
         DSTCut=-50;
         cutoffduration=12; %12 hour DST storm
-        figurename=strcat(figurename,'dd12.eps');
[…]

### 2016-03-04 paper.tex
Text improvements

--- 2016-03-04 paper.tex
@@
 
-The plasma trough is the transition region between the high density and low temperature plasmasphere and the lower density and, in the equatorial plane, higher energy magnetosphere \citep{Mayr1968ModelMagnetosphereTemperature}.
-Although there are well--validated models of the plasmasphere density as a function of $L$ (\cite{Gallagher1988EmpiricalModelPlasmasphere}, \cite{LemaireEarthsPlasmasphere}, \cite{Takahashi2006}, and \cite{Takahashi2010}) and plasmapause boundaries (\cite{LemaireEarthsPlasmasphere}, \cite{Moldwin2002ModelPlasmapause}, \cite{OBrien2003EmpiricalPlasmapause}), the dependence of the plasma trough on solar wind conditions has not been extensively studied.
+The plasma trough is the transition region between the high density and low temperature plasmasphere and the lower density and higher energy magnetosphere \citep{Mayr1968ModelMagnetosphereTemperature}.
+Inside of the plasmapause, the density is primarily due to ionospheric photoionization; outside of the plasmapuase, the density has contributions from the co-rotating plasmasphere and conveting magnetosphere plasmas.
 
-\cite{Gallagher1988EmpiricalModelPlasmasphere} used the Retarding Ion Mass Spectrometer onboard the Dynamics Explorer 1 satellite to model the the plasmasphere as a simple linear fit dependent on $L$ shell, geographic altitude, geomagnetic latitude, and $K_p$.
-They found they could accurately model geomagnetically active conditions by using a weighted average $K_p$ value and an azimuthal symmetry at smaller L-shells.
-\cite{Hamilton1988RingCurrentDevelopment} analyzed a strong geomagnetic storm and compared energy measurements of the ring current to $D_{st}$, along with measurements of ring current compositions before, during, and after the storm.
-They found $D_{st}$ to be correlated with the inner ring current energy density during and after storm onset, an inward movement of energy density, and a rapid $D_{st}$ recovery from the quick loss of heavier ions.
-
-\cite{Lotoaniu1999PlasmaMassDensity} used measurements from the Plasma Wave Experiment instrument on the CRRES satellite and compared in-situ measured plasma mass density to that inferred by ground-based ULF wave measurements from the CANOPUS array.
-By extending the ground footprints to the plasmatrough, they found agreement between the two methods for certain plasmapause conditions.
-\vinote{Mention specifics?
-Worth including paper?}
+Although there are well--validated models, as a function of $L$, $MLT$, and geomagnetic activity, of the plasmasphere density (\cite{Gallagher1988EmpiricalModelPlasmasphere}, \cite{LemaireEarthsPlasmasphere}, \cite{Takahashi2006}, and \cite{Takahashi2010}) and plasmapause boundaries (\cite{LemaireEarthsPlasmasphere}, \cite{Moldwin2002ModelPlasmapause}, \cite{OBrien2003EmpiricalPlasmapause}), the dependence of the plasma trough on geomagnetic and solar wind conditions has not been extensively studied until the past decade.
 
@@
 They also found a relationship between the average ion mass and 1.5- and 3-day averages of $K_p$, with an increasing correlation as $K_p$ was smoothed to longer timescales.
-The CRRES measurements used occurred in the MLT range of 12:00 and 18:00 mostly in the plasma trough (between 2-7$R_E$) on an elliptical, nearly equatorial orbit.
+The CRRES measurements used were made in the MLT range of 12:00 and 18:00 and mostly in the plasma trough (between 2-7$R_E$) on an elliptical, nearly equatorial orbit.
 
 \cite{Denton2006} showed a relationship between $D_{st}$ and the field line distribution of plasma density, and specifically along the same field lines as looked at in later papers (6-8$R_E$).
-They found that the distribution depends on $L$,.
+They found that the distribution depends on $L$, \note{finish}.
 
-\cite{Takahashi2010} developed a mass density dataset using measurements from the Space Environment Monitor instruments on the GOES satellites from 1980 through 1992, with most measurements in the range $L=6.8\pm0.2 R_E$.
-The mass density $\rho$ was estimated using the the Alf\v'en wave velocity relationship, $V_A=B/\sqrt{\mu_0\rho}$, \vinote{Connect to harmonic toroidal frequency} a magnetic field model, and a numerical solution to a wave equation with an ionospheric boundary and the assumption of a zero resistance ionosphere.
+\cite{Takahashi2010} developed a mass density dataset using measurements from the Space Environment Monitor instruments on the Geostationary Operational Environmental Satellites (GOES) satellites from 1980 through 1992, with most measurements in the range $L=6.8\pm0.2 R_E$.
+The mass density $\rho$ was estimated using the the Alfv\'en wave velocity relationship, $V_A=B/\sqrt{\mu_0\rho}$, \vinote{Connect to harmonic toroidal frequency} a magnetic field model, and a numerical solution to a wave equation with an ionospheric boundary and the assumption of a zero resistance ionosphere.
 The equatorial mass density, $\rho_{eq}$, was derived from the estimated mass density using a power law dependence on the geocentric distance to the field line of the observation, $R$, $\rho=\rho_{eq}L/(R/R_E)$.
@@
 
-In this work we consider the dependence of plasmaspheric mass density in the \cite{Takahashi2010} in more detail in an attempt to identify the solar wind processes that drives changes in the plasma trough density.
+In this work we consider the dependence of mass density estimates in the \cite{Takahashi2010} and attempt to identify the solar wind processes that drive changes in the plasma trough density.
 There are several issues that are addressed in detail: (1) the plasma density measurements are sparse and (2) the dependence on the north/south component of the solar wind magnetic field is expected to be nonlinear.
-For northward IMF, the plasmasphere can expand past geosynchronous orbit where measurements of density are made resulting in an increase in observed density; for southward IMF, events studies have shown an increase in density associated with strong southward IMF [\cite{Takahashi2010}; \cite{Yao2008}].
+For northward IMF and low solar wind driving of the magnetosphere, the plasmasphere can expand past geosynchronous orbit where measurements of density are made resulting in an increase in observed density that are not due to solar wind driving; for southward IMF, events studies have shown an increase in density associated with strong southward IMF and enhanced magnetospheric activity [\cite{Takahashi2010}; \cite{Yao2008}].
 Issue (1) is addressed by considering \note{Finish}.
@@
 
+--
+
+The dependence of the plasmapause location on geomagnetic activity was observed as early as \note{Cite}.
+\cite{Gallagher1988EmpiricalModelPlasmasphere} used measurements from the Retarding Ion Mass Spectrometer onboard the Dynamics Explorer 1 satellite to model the plasmasphere density with a relationship dependent on $L$ shell, altitude, geomagnetic latitude, and observations grouped by a weighted average of $K_p$.
+The developed statistical model showed significant improvements when a weighted average of $K_p$ over three days was used to group the observations used in the model.
+
+\cite{Lotoaniu1999PlasmaMassDensity} used measurements from the Plasma Wave Experiment instrument on the CRRES satellite and compared in-situ measured plasma mass density to that inferred by ground-based ULF wave measurements from the CANOPUS array.
+By extending the ground footprints to the plasmatrough, they found agreement between the two methods for certain plasmapause conditions.
+\vinote{Mention specifics?
+Worth including paper?}
+
+\cite{Hamilton1988RingCurrentDevelopment} analyzed a strong geomagnetic storm and compared energy measurements of the ring current to $D_{st}$, along with measurements of ring current compositions before, during, and after the storm.
+They found $D_{st}$ to be correlated with the inner ring current energy density during and after storm onset, an inward movement of energy density, and a rapid $D_{st}$ recovery from the quick loss of heavier ions.
+
 \section{Data Preparation and Overview}
 
-The parameters $\rho_{eq}$ and $F_{10.7}$ used in this work are from the dataset associated with \cite{Denton}, with data available from 1980 through 1991; all other parameters are from \cite{Kondrashov2014ReconstructionOfGaps} from 1972 through 2013, which are on a 1--hour time grid.
+The parameters $\rho_{eq}$ and $F_{10.7}$ used in this work are from the dataset associated with \cite{Denton} and used in \cite{Takahashi2010}, with data available from 1980 through 1991; all other parameters are from \cite{Kondrashov2014ReconstructionOfGaps} from 1972 through 2013, which are on a 1--hour time grid.
 $\rho_{eq}$ is the inferred equatorial mass density based on the 3rd harmonic torodial frequency of magnetic field measurements \vinote{More explanation?}.
@@
 Fill (NaN) values were used for hours in which no measurements were available.
-In cases where $\rho_{eq}$ was available from multiple Geostationary Operational Environmental Satellites (GOES) satellites at the same time in the \cite{Denton} dataset, the value from GOES 6 was selected.
+In cases where $\rho_{eq}$ was available from multiple GOES satellites at the same time in the \cite{Denton} dataset, the value from GOES 6 was selected.
 In the dataset, measurements from GOES 6 had the longest time span of coverage.
@@
 
-Two types of events are considered. The first is a drop in $D_{st}$ below the threshold of -50~nT.  The second is an increase in $\rho_{eq}$ above 40~amu/cm$^3$.
+Two types of events are considered.
+The first is a drop in the $D_{st}$ index \vnote{Cite Kyoto} below the threshold of -50~nT.
+These types of events are considered in order to determine if there is a well-defined $\rho_{eq}$ dependence on geomagnetic activity/storms as indicated by $D_{st}$ index.
+It is expected that the plasmasphere will exhibit two responses near these threshold crossings.
+First is the movement of the plasmasphere earthward and the second is a possible increase in density due to enhanced earthward magnetospheric convection.
+The movement of the plasmapause boundary has been well documented and parameterized, most recently by \cite{Moldwin2002ModelPlasmapause} and \cite{OBrien2003EmpiricalPlasmapause}.
+
+The second is an increase in $\rho_{eq}$ above a threshold of 40~amu/cm$^3$.
+It is expected that these increases will typically occur after period of quiet geomagnetic activity that follow a geomagnetic storm.
+In this case, the plasma pause boundary may move outward past the location of measurements and the increase will be due to measurements being made inside the plasmapause.
+A second possible reason for the increase could be due to the above-mentioned increase in magnetospheric convention.
 
@@
 
-Our first analysis uses data only from the time interval 1989-1991 to correspond with the analysis in \cite{Takahashi2010}.
-For both types of events, the hour of the threshold crossing defines the zero epoch time, and for each event $8\cdot24$ hours were kept after each event and $4\cdot24$ hours before each event.
-To compute the epoch averages on a daily time scale, the median value of all measurements for all events centered on a window of $\pm 12$ hours was computed, and these windows were shifted in increments of $24$~hours.
+Our first analysis uses data only from the time interval 1989-1991 that corresponds with the interval used in the analysis in \cite{Takahashi2010}.
+For both types of events, the hour of the threshold crossing defines the zero epoch time, and for each event $4\cdot24$ hours were considered before each event and $8\cdot24$ hours after each event.
+To compute the epoch averages on a daily time scale, the median value of all measurements for all events centered on a window of $\pm 12$ hours of the epoch day was computed, and these averaging windows were shifted in increments of $24$~hours.
 (Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians in 1-day bins and then compute the medians across events.)  Error bars for each parameter were computed using the standard deviation of the values used in computing the median divided by the square root of the number of values used.
 
-In the upper panel of Figure \ref{DailyAveragedDstEvents}, $D_{st}$ events are shown.
+The stack plot in the upper panel of Figure \ref{DailyAveragedDstEvents} shows the epoch averages for these events.
 The minimum $D_{st}$ median is $-48$~nT.
-Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$, although the magnitude of increase observed here is $\sim 2$ amu/cm$^3$ instead of the value of $\sim 10$ amu/cm$^3$ found in \cite{Takahashi2010}.
+Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$, although the magnitude of increase observed here is $1.5$ amu/cm$^3$ (from 18 to 19.5~amu/cm$^3$) instead of the value of $\sim 10$ amu/cm$^3$ found in \cite{Takahashi2010}.
 The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute its median and error bars.
-Note that for the non-\req\ medians, the number of measurements used in computing the medians is typically equal to the number of events which is much larger than the number of \req\ values as we use all available measurements instead of restricting to only values where a non--fill $\rho_{eq}$ value existed.
+Note that for the non-\req\ medians, the number of measurements used in computing the medians is typically equal to the number of events, which is much larger than the number of \req\ values as we use all available measurements instead of restricting to only values where a non--fill $\rho_{eq}$ value existed.
 \vinote{Alternate: Note that for $D_{st}$ events, we computed median values using all available data, even when \req\ availability was sparse.}
 
-In the lower panel of Figure \ref{DailyAveragedDstEvents} it is shown that all trends seen in the analysis of 1989-1991 also hold for the entire run of GOES 6 over 1983-1991, including the magnitude of change in $\rho_{eq}$ across event onset.
+In the lower panel of Figure \ref{DailyAveragedDstEvents} it is shown that all trends seen in the analysis of 1989-1991 also hold for the entire span of measurements from GOES 6, from 1983-1991, including the magnitude of change in $\rho_{eq}$ across event onset.
 
@@
 
-In the lower panel of \ref{DailyAveragedDstEvents}, $\rho_{eq}$ events are shown.
-Here we see that $\rho_{eq}$ enhancements do not clearly correspond to a signature in $D_{st}$, but that there is a trend for such enhancments to occur when $B_{z}$ in the IMF is positive.
-This is consistent with \cite{Takahashi2010} who note that very large increases in $\rho_{eq}$ often corresponded to movement of the plasmasphere to beyond geosynchronous distances.
+Both of the results in \ref{DailyAveragedDstEvents} indicate that there is not a statictically significant change in $\rho_{eq}$ on the day before and day after a threshold crossing in $D_{st}$.
 
+Because the dynamics of the magnetopshere take place on a time scale of less than one day, we have also considered hourly averages as shown in the top panel of \ref{HourlyAveragedDstEvents}.
 A total of 668 events were found in the interval of May 1983 through August 1991 with an average duration of 9 hours and a median duration of 3 hours.
-Figure \ref{HourlyAveragedDstEvents} shows the average values of all events over a window of 24 hours before onset and 48 hours after.
-Figure \ref{HourlyAveragedDstEvents}a shows events selected by looking for event onsets where $D_{st}$ crossed a threshold of $-50$~nT.
-The dashed red lines indicate plus and minus one standard deviation of values from all events that went into the average.
+The error bars were computed in the same way as \ref{DailyAveragedDstEvents}.
+In this plot, the overall trend is similar to that found in the bottom panel of \ref{HourlyAveragedDstEvents} - $\rho_{eq}$ is slighly elevated at the time of the threhshold crossing of $D_{st}$ with respect to the values one day before and after, but the elevation is small and in general not statistically significant.
+
+The bottom panel of \ref{HourlyAveragedDstEvents} contains the events shown in the top panel under the constraint that $D_{st}$ remained below -50~nT for at least twelve hours after the event onset time.
+
+and the event study of \cite{Yao2008} which showed ...
+
 The final plot in the stack shows both $\rho_{eq}$ and a bar plot of how many valid data points went into the $\rho_{eq}$ average.
@@
 Top: Events in the interval 1983-1991; compare to bottom panel {DailyAveragedDstEvents}.
-Bottom: Same as Top except for constraint that $D_{st}$ stayed below $-50$~nT for at least 12~hours.}
+Bottom: Same as Top except for constraint that $D_{st}$ stayed below $-50$~nT for at least 12~hours after crossing below $-50$~nT.}
 \label{HourlyAveragedDstEvents}

### 2016-03-04 paper.tex
Updated figure names

--- 2016-03-04 paper.tex
@@
 \centering
-\includegraphics[scale=0.40]{paperfigures/stormavs-dst-50-tak.eps}
+\includegraphics[scale=0.40]{paperfigures/stormavs-dst-50-tak-GOES6.eps}
 \rule[1ex]{5cm}{1pt}
-\includegraphics[scale=0.40]{paperfigures/stormavs-dst-day.eps}
+\includegraphics[scale=0.40]{paperfigures/stormavs-dst-day-GOES6.eps}
 \caption{$D_{st}$ events from GOES 6. Upper panel: Events in the interval 1989-1991. Lower panel: Events in the interval 1983-1991.}
@@
 \rule[1ex]{5cm}{1pt}
-\includegraphics[scale=0.40]{paperfigures/stormavs-dd12.eps}
+\includegraphics[scale=0.40]{paperfigures/stormavs-dd12-GOES6.eps}
 \caption{(a) Average of solar wind and near-Earth measurements around the time $D_{st}$ crossed below $-50$~nT onset.

### 2016-03-04 paper.tex

--- 2016-03-04 paper.tex
@@
 \centering
-\includegraphics[scale=0.40]{paperfigures/stormavs-dst-50-tak.eps}
+\includegraphics[scale=0.40]{paperfigures/stormavs-dst-50-tak-GOES6.eps}
 \rule[1ex]{5cm}{1pt}
-\includegraphics[scale=0.40]{paperfigures/stormavs-dst-day.eps}
+\includegraphics[scale=0.40]{paperfigures/stormavs-dst-day-GOES6.eps}
 \caption{$D_{st}$ events from GOES 6 using daily medians. Top: Events in the interval 1989-1991; compare to \cite{Takahashi2010} Fig.~11. Bottom: Events in the interval 1983-1991.}
@@
 \rule[1ex]{5cm}{1pt}
-\includegraphics[scale=0.40]{paperfigures/stormavs-dd12.eps}
+\includegraphics[scale=0.40]{paperfigures/stormavs-dd12-GOES6.eps}
 \caption{$D_{st}$ events from GOES 6 using hourly medians.
@@
 \end{figure}
+
+\begin{figure}[tp!]
+	\centering
+	\includegraphics[scale=0.40]{paperfigures/RhoBinnedBz-case24-t020-tf25-GOES6.eps}
+	\includegraphics[scale=0.40]{paperfigures/RhoBinnedBz-case24-t025-tf30-GOES6.eps}
+	\caption{Binning \req\ events by $B_z$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
+	\label{fig:RhoBinned}
+\end{figure}
+
+\clearpage
 

### 2016-03-18 paper.tex

@@
 
-The plasma trough is the transition region between the high density and low temperature plasmasphere and the lower density and higher energy magnetosphere \citep{Mayr1968ModelMagnetosphereTemperature}.
-Inside of the plasmapause, the density is primarily due to ionospheric photoionization; outside of the plasmapuase, the density has contributions from the co-rotating plasmasphere and conveting magnetosphere plasmas.
+The plasma trough is a transition region between the high density and low temperature plasmasphere and the lower density and higher energy magnetosphere \citep{Mayr1968ModelMagnetosphereTemperature}.
+Inside of the plasmapause, the density is primarily due to ionospheric photoionization; outside of the plasmapuase, the density has contributions from the co-rotating plasmasphere and convecting magnetosphere plasmas.
 
-Although there are well--validated models, as a function of $L$, $MLT$, and geomagnetic activity, of the plasmasphere density (\cite{Gallagher1988EmpiricalModelPlasmasphere}, \cite{LemaireEarthsPlasmasphere}, \cite{Takahashi2006}, and \cite{Takahashi2010}) and plasmapause boundaries (\cite{LemaireEarthsPlasmasphere}, \cite{Moldwin2002ModelPlasmapause}, \cite{OBrien2003EmpiricalPlasmapause}), the dependence of the plasma trough on geomagnetic and solar wind conditions has not been extensively studied until the past decade.
+There are well--validated models of the plasmapause boundary, as a function of $L$, $MLT$, and geomagnetic activity (\cite{LemaireEarthsPlasmasphere}, \cite{Moldwin2002ModelPlasmapause}, \cite{OBrien2003EmpiricalPlasmapause}).
+Models also exist for the plasmasphere density (\cite{Gallagher1988EmpiricalModelPlasmasphere}, \cite{LemaireEarthsPlasmasphere}, \cite{Takahashi2006}, and \cite{Takahashi2010}), but and dependence of the plasma trough on geomagnetic and solar wind conditions has not been extensively studied until the past decade.
 
-\cite{Takahashi2006} estimated magnetospheric mass density using measurements from the CRRES satellite during a 73-day period in 1991 and found that the average ion mass, $M=\rho/n_e$, correlated with geomagnetic activity, with more negative $D_{st}$ values corresponding to slightly higher average ion mass densities.
-They also found a relationship between the average ion mass and 1.5- and 3-day averages of $K_p$, with an increasing correlation as $K_p$ was smoothed to longer timescales.
-The CRRES measurements used were made in the MLT range of 12:00 and 18:00 and mostly in the plasma trough (between 2-7$R_E$) on an elliptical, nearly equatorial orbit.
+The dependence of the plasmapause location on geomagnetic activity was observed as early as \note{Cite}.
+\cite{Gallagher1988EmpiricalModelPlasmasphere} used measurements from the Retarding Ion Mass Spectrometer onboard the Dynamics Explorer 1 satellite to model plasmasphere density using a relationship dependent on $L$ shell, altitude, geomagnetic latitude, and observations grouped by a weighted average of $K_p$.
+The developed statistical model showed significant improvements when a weighted average of $K_p$ over three days was used to group the observations used in the model.
+\note{Discuss plasma trough relevance}.
 
-\cite{Denton2006} showed a relationship between $D_{st}$ and the field line distribution of plasma density, and specifically along the same field lines as looked at in later papers (6-8$R_E$).
-They found that the distribution depends on $L$, \note{finish}.
+\cite{Hamilton1988RingCurrentDevelopment} analyzed a strong geomagnetic storm and compared energy measurements of the ring current to $D_{st}$, along with measurements of ring current compositions before, during, and after the storm.
+They found $D_{st}$ to be correlated with the inner ring current energy density during and after storm onset, an inward movement of energy density, and a rapid $D_{st}$ recovery from the quick loss of heavier ions.
 
-\cite{Takahashi2010} developed a mass density dataset using measurements from the Space Environment Monitor instruments on the Geostationary Operational Environmental Satellites (GOES) satellites from 1980 through 1992, with most measurements in the range $L=6.8\pm0.2 R_E$.
+\cite{Takahashi2006} estimated magnetospheric mass density using measurements from the CRRES satellite during a 73-day period in 1991 (obervations were made when CRRESS was in an elliptical, near equatorial orbit).
+They found that the average ion mass, $M=\rho/n_e$, had some correlation with geomagnetic activity, with more negative hourly $D_{st}$ values corresponding to higher $M$ and 1.5- and 3-day averages of $K_p$ corresponding to higher $M$ (3-hour averages of $K_p$had little visual correlation with $M$).
+The mass density estimates were obtained from CRRES observations in the MLT range of 12:00 and 18:00 with most observations having L between 5 and 7 $R_E$, corresponding to the plasma trough region.
+
+\cite{Denton2006} found a weak relationship between $D_{st}$ and and $K_p$ and the field line distribution of $\rho$ using observations of the first three torodial Alfven harmonic fequencies for $L$ in the range of 6-8$R_E$.
+A more pronounced peak in the distribution along a filed line near the equator was fround for lower $D_{st}$ and larger $K_p$.
+The equatorial value of $\rho$ appeared identical for the bins of $D_{st}$ (-142 to -31 nT and -31 to 37 nT) and $K_p$ (1.5 to 3.4 and 3.4 to 5.9) considered .
+
+\cite{Takahashi2010} developed a mass density dataset using measurements from the Space Environment Monitor instruments on the Geostationary Operational Environmental Satellites (GOES) satellites from 1980 through 1992, with most measurements in the range of $L=6.8\pm0.2 R_E$.
 The mass density $\rho$ was estimated using the the Alfv\'en wave velocity relationship, $V_A=B/\sqrt{\mu_0\rho}$, \vinote{Connect to harmonic toroidal frequency} a magnetic field model, and a numerical solution to a wave equation with an ionospheric boundary and the assumption of a zero resistance ionosphere.
 The equatorial mass density, $\rho_{eq}$, was derived from the estimated mass density using a power law dependence on the geocentric distance to the field line of the observation, $R$, $\rho=\rho_{eq}L/(R/R_E)$.
+They found a high correlation between 27 day averages fo F10.7 and 27-day medians of $\rho_{eq}$.
 
-\cite{Takahashi2010} noted that downward spikes in the $D_{st}$ index coincided with with significant changes in $\rho_{eq}$ at for $L$ near 6.8~$R_E$.
+\cite{Takahashi2010} noted that downward spikes in the $D_{st}$ index coincided with with significant changes in $\rho_{eq}$ for $L$ near 6.8~$R_E$.
 For five storms, two had $\rho_{eq}$ spikes after the $D_{st}$ drop, two had $\rho_{eq}$ spikes before the drop, and one showed little change in $\rho_{eq}$.
-A key result was that when daily-averaged measurements were considered, an enhancment in $\rho_{eq}$ appeared on the same day as minimum $D_{st}$, indicating the possibility of a solar wind control over $\rho_{eq}$.
+A key result was that when daily-averaged measurements were considered, an enhancment in $\rho_{eq}$ appeared on the same day as minimum $D_{st}$.
 
-The results of \cite{Takahashi2006} and \cite{Takahashi2010} are consistent with other results on changes in mass density in the plasma trough region.
-\cite{Yao2008} studied the relationship between $D_{st}$ and ion number density for different ion species in different regions (ring current and plasma sheet) and found a general correlation during each of the four storms considered.
+\cite{Yao2008} studied the relationship between $D_{st}$ and ion number density for low-energy $O^+$ in different regions (ring current and plasma sheet) using the TEAMS and ESA instruments on the low-altitude and high-inclination orbiting FAST satellite and found that the average $N_{O^+}$ across the sampled L-sheels (2-14) had a strong correlation (0.88).
+Although the correlation in the plasma trough was not caluclated, the data presented show that the variations in $N_{O^+}$ tended to appear near $D_{st}$ minimum ($\pm$ 2~hours).
 
-In this work we consider the dependence of mass density estimates in the \cite{Takahashi2010} and attempt to identify the solar wind processes that drive changes in the plasma trough density.
-There are several issues that are addressed in detail: (1) the plasma density measurements are sparse and (2) the dependence on the north/south component of the solar wind magnetic field is expected to be nonlinear.
-For northward IMF and low solar wind driving of the magnetosphere, the plasmasphere can expand past geosynchronous orbit where measurements of density are made resulting in an increase in observed density that are not due to solar wind driving; for southward IMF, events studies have shown an increase in density associated with strong southward IMF and enhanced magnetospheric activity [\cite{Takahashi2010}; \cite{Yao2008}].
-Issue (1) is addressed by considering \note{Finish}.
-Issue (2) is addressed by considering epochs and linear correlations independent of the direction of the IMF and also by separation by averages of the northrward and southward IMF.
+The results in the papers discussed indicate that (1) the mass density in the plasma trough region is best correlated with $F10.7$ and (2) there exists a correlation between mass density and the geomagnetic activity indices $K_p$ and $D_{st}$.
+In this work we consider the dependence of mass density estimates in the \cite{Takahashi2010} and attempt to identify a statistical characterization of the relationship between geomagnetic activity and mass density.
+In addition, we attempt to identify solar wind processes may drive this changes.
+
+There are several issues that are addressed in detail: (1) the plasma density measurements are sparse, (2) The plasma trough density has a high correlation with F10.7, as do geomagnetic and solar wind parameters (3) the dependence on the north/south component of the solar wind magnetic field is expected to be nonlinear.
+(For northward IMF and low solar wind driving of the magnetosphere, the plasmasphere can expand past geosynchronous orbit where trough estimates of density are made resulting in an increase in observed density that are not due to solar wind driving; for southward IMF, events studies have shown an increase in density associated with strong southward IMF and enhanced magnetospheric activity [\cite{Takahashi2010}; \cite{Yao2008}]).
+
+Issue (1) is addressed by considering in detail the number of observations that are used in epoch averages around the time of two types of evens, decreases in $D_{st}$ below a threshold, and increases in $\rho_{eq}$ above a threshold.
+Issue (2) is addressed using various methods to remove or isolate F10.7 depenences.
+Issue (3) is addressed by considering epochs and linear correlations independent of the direction of the IMF and also by separation by averages of the northrward and southward IMF.
+
+In addition, we consider the influence of time averaging by comparing results using daily means and meadians and hourly means and medians of solar wind and magentospheric parameters.
 
 --
-
-The dependence of the plasmapause location on geomagnetic activity was observed as early as \note{Cite}.
-\cite{Gallagher1988EmpiricalModelPlasmasphere} used measurements from the Retarding Ion Mass Spectrometer onboard the Dynamics Explorer 1 satellite to model the plasmasphere density with a relationship dependent on $L$ shell, altitude, geomagnetic latitude, and observations grouped by a weighted average of $K_p$.
-The developed statistical model showed significant improvements when a weighted average of $K_p$ over three days was used to group the observations used in the model.
 
@@
 
-\cite{Hamilton1988RingCurrentDevelopment} analyzed a strong geomagnetic storm and compared energy measurements of the ring current to $D_{st}$, along with measurements of ring current compositions before, during, and after the storm.
-They found $D_{st}$ to be correlated with the inner ring current energy density during and after storm onset, an inward movement of energy density, and a rapid $D_{st}$ recovery from the quick loss of heavier ions.
-
 \section{Data Preparation and Overview}
 
-The parameters $\rho_{eq}$ and $F_{10.7}$ used in this work are from the dataset associated with \cite{Denton} and used in \cite{Takahashi2010}, with data available from 1980 through 1991; all other parameters are from \cite{Kondrashov2014ReconstructionOfGaps} from 1972 through 2013, which are on a 1--hour time grid.
-$\rho_{eq}$ is the inferred equatorial mass density based on the 3rd harmonic torodial frequency of magnetic field measurements \vinote{More explanation?}.
+The parameters $\rho_{eq}$ and $F_{10.7}$ used in this work are from the dataset of \cite{Denton}, which was used in \cite{Takahashi2010}; data are available from 1980 through 1991.
+All other parameters used are from \cite{Kondrashov2014ReconstructionOfGaps} from 1972 through 2013, which are on a 1--hour time grid.
+$\rho_{eq}$ is the inferred equatorial mass density based on the 3rd harmonic torodial frequency of magnetic field measurements as described in \cite{Takahashi2010}.
 The smallest cadence for $\rho_{eq}$ values is 10 minutes.
-To compute an hourly average over the same interval for which the solar wind parameters were averaged, the median of all $\rho_{eq}$ values in a given hourly range was used.
+To compute an hourly average over the same interval for which the solar wind parameters were averaged, the median of all $\rho_{eq}$ values in a given hour window was used.
 Fill (NaN) values were used for hours in which no measurements were available.
-In cases where $\rho_{eq}$ was available from multiple GOES satellites at the same time in the \cite{Denton} dataset, the value from GOES 6 was selected.
+In cases where $\rho_{eq}$ was available in the \cite{Denton} dataset from multiple GOES satellites at the same time, the value from GOES 6 was selected.
 In the dataset, measurements from GOES 6 had the longest time span of coverage.
@@
 
-In this work, events are defined to occur when $D_{st}$ or $\rho_{eq}$ crosses a threshold value, as indicated in by horizontal dashed lines in the respective panels of Figure~\ref{AllData}.
+In this work, events are defined to occur when $D_{st}$ or $\rho_{eq}$ crosses a threshold value, as indicated in by horizontal dashed lines in their respective panels of Figure~\ref{AllData}.
 In finding $\rho_{eq}$ events, all fill values were replaced with linearly interpolated values.
@@
 A scatter plot of these two lines is shown in the lower panel of Figure~\ref{ccplot}.
-The linear correlation for GOES 6 is found to be $0.94$ matching the value found by \cite{Takahashi2010} who used measurements from all satellites in the time interval of 1980 through 1991.
-The corresponding 27-day correlations for GOES 2, 5, and 7 are 0.81, 0.78, and 0.87, and the time range of coverage of measurements from these satellites are 1980-01-01/1983-05-16, 1983-01-01/1987-02-28, and 1983-05-27/1991-08-29 respectively.
+The linear correlation for GOES 6 using all measurements is found to be $0.94$, which is the same value documented by \cite{Takahashi2010} who used measurements from all satellites in the time interval of 1980 through 1991 using the constraint $0600 \leq MLT \le 1200$, $K_{p3d}\ge1.0 and $D_{st}\ge -50$~nT.
+Our 27-day correlations for GOES 2, 5, and 7 are 0.81, 0.78, and 0.87, and the time range of coverage of measurements from these satellites are 1980-01-01/1983-05-16, 1983-01-01/1987-02-28, and 1983-05-27/1991-08-29 respectively.
 
@@
 It is expected that the plasmasphere will exhibit two responses near these threshold crossings.
-First is the movement of the plasmasphere earthward and the second is a possible increase in density due to enhanced earthward magnetospheric convection.
-The movement of the plasmapause boundary has been well documented and parameterized, most recently by \cite{Moldwin2002ModelPlasmapause} and \cite{OBrien2003EmpiricalPlasmapause}.
+First is the movement of the plasmasphere earthward and the second is a possible increase in density due to magnetospheric processes \vnote{cite}.
 
-The second is an increase in $\rho_{eq}$ above a threshold of 40~amu/cm$^3$.
+The second type of event is an increase in $\rho_{eq}$ above a threshold of 20~amu/cm$^3$.
 It is expected that these increases will typically occur after period of quiet geomagnetic activity that follow a geomagnetic storm.
-In this case, the plasma pause boundary may move outward past the location of measurements and the increase will be due to measurements being made inside the plasmapause.
-A second possible reason for the increase could be due to the above-mentioned increase in magnetospheric convention.
+In this case, the plasmapause boundary may move outward past the measurement location and the increase will be due to measurements being made inside the plasmapause.
+A second possible reason for the increase could be due to the above-mentioned increase in due to magnetospheric processes.
 
@@
 
-Our first analysis uses data only from the time interval 1989-1991 that corresponds with the interval used in the analysis in \cite{Takahashi2010}.
+Our first analysis uses data only from the time interval 1989-1991, which corresponds with the interval used in the analysis in \cite{Takahashi2010}.
 For both types of events, the hour of the threshold crossing defines the zero epoch time, and for each event $4\cdot24$ hours were considered before each event and $8\cdot24$ hours after each event.
-To compute the epoch averages on a daily time scale, the median value of all measurements for all events centered on a window of $\pm 12$ hours of the epoch day was computed, and these averaging windows were shifted in increments of $24$~hours.
-(Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians in 1-day bins and then compute the medians across events.)  Error bars for each parameter were computed using the standard deviation of the values used in computing the median divided by the square root of the number of values used.
+To compute the epoch averages on a daily time scale, the median value of all available measurements for all events centered on a window of $\pm 12$ hours of the epoch day was computed, and these averaging windows were shifted in increments of $24$~hours.
+(Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians in 1-day bins and then compute the medians across events.)  Error bars for each parameter are the standard deviation of the values used in computing the median divided by the square root of the number of values used.
 
@@
 The minimum $D_{st}$ median is $-48$~nT.
-Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$, although the magnitude of increase observed here is $1.5$ amu/cm$^3$ (from 18 to 19.5~amu/cm$^3$) instead of the value of $\sim 10$ amu/cm$^3$ found in \cite{Takahashi2010}.
-The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute its median and error bars.
-Note that for the non-\req\ medians, the number of measurements used in computing the medians is typically equal to the number of events, which is much larger than the number of \req\ values as we use all available measurements instead of restricting to only values where a non--fill $\rho_{eq}$ value existed.
-\vinote{Alternate: Note that for $D_{st}$ events, we computed median values using all available data, even when \req\ availability was sparse.}
+Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$, although the magnitude of increase observed here is $1.5$ amu/cm$^3$ (from 18 to 19.5~amu/cm$^3$) instead of the increase of $\sim 10$ amu/cm$^3$ found in \cite{Takahashi2010}.
+The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute the medians and error bars.
+For the non-\req\ medians, the number of measurements used in computing the medians is typically equal to the number of events, which is much larger than the number of \req\ values as we used all available measurements instead of restricting to only values where a non--fill $\rho_{eq}$ value existed.
 
-In the lower panel of Figure \ref{DailyAveragedDstEvents} it is shown that all trends seen in the analysis of 1989-1991 also hold for the entire span of measurements from GOES 6, from 1983-1991, including the magnitude of change in $\rho_{eq}$ across event onset.
+In the lower panel of Figure \ref{DailyAveragedDstEvents} it is shown that the trends seen in the analysis of 1989-1991 also hold for the entire span of measurements from GOES 6, which spans 1983-1991 - a small elevation on the day of the event relative to the day before and day after, with averages after the day of the event being lower than that before.
+
+To determine if the magnitude of the density medians on a given day were statistically different than another day, we used a two-population t-test.
+For the interval of 1989-1991, corresponding to the top panel of \ref{DailyAveragedDstEvents}, the null hypothesis that any of the medians from days -1, 0, and 1 are different from each other is rejected with a maximimum p value of \vnote{??}.
+
+   Days     p
+-1 and 0
+-1 and 1
+ 0 and 1
+Results of test on different between means of $\rho_{eq}$ shown in the top panel of \ref{DailyAverage} on days near or on the day of a $D_{st}$ event.
+A difference in the means can be rejected with a probability of false rejection of $p$.
+
+   Days     p
+-1 and 0
+-1 and 1
+ 0 and 1
+Results of test on different between means of $\rho_{eq}$ shown in the bottom panel of \ref{DailyAverage} on days near or on the day of a $D_{st}$ event.
 

### 2016-03-18 paper.tex
Introducton changes

@@
 
+The dependence of the plasmapause location on geomagnetic activity was observed as early as \cite{Carpenter1966}.
 There are well--validated models of the plasmapause boundary, as a function of $L$, $MLT$, and geomagnetic activity (\cite{LemaireEarthsPlasmasphere}, \cite{Moldwin2002ModelPlasmapause}, \cite{OBrien2003EmpiricalPlasmapause}).
@@
 
-The dependence of the plasmapause location on geomagnetic activity was observed as early as \note{Cite}.
-\cite{Gallagher1988EmpiricalModelPlasmasphere} used measurements from the Retarding Ion Mass Spectrometer onboard the Dynamics Explorer 1 satellite to model plasmasphere density using a relationship dependent on $L$ shell, altitude, geomagnetic latitude, and observations grouped by a weighted average of $K_p$.
-The developed statistical model showed significant improvements when a weighted average of $K_p$ over three days was used to group the observations used in the model.
-\note{Discuss plasma trough relevance}.
-
-\cite{Hamilton1988RingCurrentDevelopment} analyzed a strong geomagnetic storm and compared energy measurements of the ring current to $D_{st}$, along with measurements of ring current compositions before, during, and after the storm.
-They found $D_{st}$ to be correlated with the inner ring current energy density during and after storm onset, an inward movement of energy density, and a rapid $D_{st}$ recovery from the quick loss of heavier ions.
-
-\cite{Takahashi2006} estimated magnetospheric mass density using measurements from the CRRES satellite during a 73-day period in 1991 (obervations were made when CRRESS was in an elliptical, near equatorial orbit).
+\cite{Takahashi2006} estimated magnetospheric mass density using measurements from the CRRES satellite during a 73-day period in 1991 (obervations were made when CRRESS was in an elliptical, near equatorial orbit and primarily in the plasma trough region).
 They found that the average ion mass, $M=\rho/n_e$, had some correlation with geomagnetic activity, with more negative hourly $D_{st}$ values corresponding to higher $M$ and 1.5- and 3-day averages of $K_p$ corresponding to higher $M$ (3-hour averages of $K_p$had little visual correlation with $M$).
-The mass density estimates were obtained from CRRES observations in the MLT range of 12:00 and 18:00 with most observations having L between 5 and 7 $R_E$, corresponding to the plasma trough region.
+The mass density estimates were obtained from CRRES observations in the MLT range of 12:00 and 18:00 with most observations having L between 5 and 7 $R_E$.
 
@@
 The equatorial mass density, $\rho_{eq}$, was derived from the estimated mass density using a power law dependence on the geocentric distance to the field line of the observation, $R$, $\rho=\rho_{eq}L/(R/R_E)$.
-They found a high correlation between 27 day averages fo F10.7 and 27-day medians of $\rho_{eq}$.
+They found a high correlation ($\sim 0.93$) between 27-day averages of F10.7 and 27-day medians of $\rho_{eq}$.
 
@@
 \cite{Yao2008} studied the relationship between $D_{st}$ and ion number density for low-energy $O^+$ in different regions (ring current and plasma sheet) using the TEAMS and ESA instruments on the low-altitude and high-inclination orbiting FAST satellite and found that the average $N_{O^+}$ across the sampled L-sheels (2-14) had a strong correlation (0.88).
-Although the correlation in the plasma trough was not caluclated, the data presented show that the variations in $N_{O^+}$ tended to appear near $D_{st}$ minimum ($\pm$ 2~hours).
+Although the correlation in the plasma trough was not calculated, the data presented show that the variations in $N_{O^+}$ tended to appear near $D_{st}$ minimum ($\pm$ 2~hours).
 
 The results in the papers discussed indicate that (1) the mass density in the plasma trough region is best correlated with $F10.7$ and (2) there exists a correlation between mass density and the geomagnetic activity indices $K_p$ and $D_{st}$.
-In this work we consider the dependence of mass density estimates in the \cite{Takahashi2010} and attempt to identify a statistical characterization of the relationship between geomagnetic activity and mass density.
-In addition, we attempt to identify solar wind processes may drive this changes.
+In this work we consider the dependence of mass density estimates in the \cite{Takahashi2010} and attempt to identify and statistically characterize the relationship between geomagnetic activity with mass density in the plasma trough region.
+In addition, we attempt to identify solar wind processes may drive changes in mass density.
 
-There are several issues that are addressed in detail: (1) the plasma density measurements are sparse, (2) The plasma trough density has a high correlation with F10.7, as do geomagnetic and solar wind parameters (3) the dependence on the north/south component of the solar wind magnetic field is expected to be nonlinear.
-(For northward IMF and low solar wind driving of the magnetosphere, the plasmasphere can expand past geosynchronous orbit where trough estimates of density are made resulting in an increase in observed density that are not due to solar wind driving; for southward IMF, events studies have shown an increase in density associated with strong southward IMF and enhanced magnetospheric activity [\cite{Takahashi2010}; \cite{Yao2008}]).
+There are several issues that are addressed in detail: (1) the plasma density measurements are sparse, (2) The plasma trough density has a high correlation with F10.7, and geomagnetic and solar wind parameters also correlate with F10.7, (3) the dependence of mass density on the north/south component of the solar wind magnetic field is expected to be nonlinear.
+For northward IMF, corresponding tolow solar wind driving of the magnetosphere, the plasmasphere can expand past geosynchronous orbit where trough estimates of mass density are made resulting in an increase in observed density that are not due to solar wind driving; for southward IMF, events studies have shown an increase in mass density associated with strong southward IMF and enhanced magnetospheric activity [\cite{Takahashi2010}; \cite{Yao2008}].
 
-Issue (1) is addressed by considering in detail the number of observations that are used in epoch averages around the time of two types of evens, decreases in $D_{st}$ below a threshold, and increases in $\rho_{eq}$ above a threshold.
-Issue (2) is addressed using various methods to remove or isolate F10.7 depenences.
-Issue (3) is addressed by considering epochs and linear correlations independent of the direction of the IMF and also by separation by averages of the northrward and southward IMF.
+Issue (1) is addressed by considering in detail the number of observations that are used in epoch averages around the time of two types of events, decreases in $D_{st}$ below a threshold, and increases in $\rho_{eq}$ above a threshold.
+Issue (2) is addressed using various methods to remove or isolate the F10.7 depenences.
+Issue (3) is addressed by considering epochs and linear correlations independent of the direction of the IMF along with separation of the epoch averages based on the northrward and southward IMF.
 
@@
 --
+
+\cite{Gallagher1988EmpiricalModelPlasmasphere} used measurements from the Retarding Ion Mass Spectrometer onboard the Dynamics Explorer 1 satellite to model plasmasphere density using a relationship dependent on $L$ shell, altitude, geomagnetic latitude, and observations grouped by a weighted average of $K_p$.
+The developed statistical model showed significant improvements when a weighted average of $K_p$ over three days was used to group the observations used in the model.
+\note{Discuss plasma trough relevance}.
+
+\cite{Hamilton1988RingCurrentDevelopment} analyzed a strong geomagnetic storm and compared energy measurements of the ring current to $D_{st}$, along with measurements of ring current compositions before, during, and after the storm.
+They found $D_{st}$ to be correlated with the inner ring current energy density during and after storm onset, an inward movement of energy density, and a rapid $D_{st}$ recovery from the quick loss of heavier ions.
 

### 2016-03-18 NNAnalysis.m
Updated figures and tables.

@@ -1,7 +1,7 @@
 function NNAnalysis(AVMat,AVMDMat,satnum)
 
 loops=40;
-AXmap=containers.Map({'B_z','V_{sw}','F_{10.7}','\rho_{eq}','DoY','\rho_{sw}','D_{st}','MLT'},{[-10 10],[200 800],[50 350],[0 100],[0 356],[0 30],[-100 30],[0 24]});
+AXmap=containers.Map({'B_z','V_{sw}','F_{10.7}','\rho_{eq}','DoY','\rho_{sw}','D_{st}','MLT'},{[-10 10],[200 800],[50 350],[0 70],[0 356],[0 30],[-100 30],[0 24]});
 
 
 disp('NN - B_z')
@@ -64,21 +64,21 @@ PermCols=[2 5 6 15 29 30 31];
 
 table=fopen(sprintf('tables/NNtable-GOES%d.txt',satnum),'w');
 fprintf(table,'<pre>\n');
-fprintf(table,'Vars \t \t  CCtr  NNtr  CCt   NNt   CCv   NNv\n');
+fprintf(table,'Vars \t \t  CCtr  NNtr  CCt   NNt   CCv   NNv  +-CCtr  +-NNtr  +-CCt   +-NNt   +-CCv   +-NNv\n');
 Perms=combnk(1:7,1);
 for i=1:length(Perms)
-    CCMs(:,:)=nntest(nanmedian(AVMat(:,20:24,PermCols(Perms(i,:))),2),nanmedian(AVMDMat(:,25:29),2),1,loops,1);
-    fprintf(table,'%s      \t- %+2.2f %+2.2f %+2.2f %+2.2f %+2.2f %+2.2f \n',strjoin(PermNames(Perms(i,:)),'+'),CCMs(:));
+    [CCMs(:,:), CCMSDs(:,:)]=nntest(nanmedian(AVMat(:,20:24,PermCols(Perms(i,:))),2),nanmedian(AVMDMat(:,25:29),2),1,loops,1);
+    fprintf(table,'%s      \t- %+2.2f %+2.2f %+2.2f %+2.2f %+2.2f %+2.2f %2.2f %2.2f %2.2f %2.2f %2.2f %2.2f \n',strjoin(PermNames(Perms(i,:)),'+'),CCMs(:),CCMSDs(:));
 end
 Perms=combnk(1:7,2);
[…]

### 2016-03-18 nnbehavior2.m

@@ -69,12 +69,12 @@ if(plotv)
     view(0,90)
     title(sprintf('Mean nonlinear predicted %s over %d loops with GOES %d',plotvars{3},loops,satnum))
     colorbar
-    hold on; scatter3(x(:,1),x(:,2),repmat(100000,1,length(x(:,1))),target,'k')
+    hold on; scatter3(x(:,1),x(:,2),repmat(500,1,length(x(:,1))),target,'k')
     yr=AXmap(plotvars{2});
     %set(gca,'YTick',linspace(yr(1),yr(2),10))
     filename=sprintf('figures/NN%s-GOES%d.',strjoin(plotvars,'-'),satnum);
     filename=regexprep(filename,'[^a-zA-Z0-9/]','');
-    print('-depsc2',strcat(filename,'eps'))
+    print('-depsc2','-zbuffer','-r300',strcat(filename,'eps'))
     print('-dpng',strcat(filename,'png'))
     
     figure; surf(xtest(2:end),ytest,testsd,'EdgeColor','none','LineStyle','none','FaceLighting','phong') %Even though phong is deprecated, it's the only one that plots without corruption
@@ -88,8 +88,9 @@ if(plotv)
     
         filename=sprintf('figures/NN%s-sd-GOES%d.',strjoin(plotvars,'-'),satnum);
     filename=regexprep(filename,'[^a-zA-Z0-9/]','');
-    print('-depsc2',strcat(filename,'eps'))
+    print('-depsc2','-zbuffer','-r300',strcat(filename,'eps'))
     print('-dpng',strcat(filename,'png'))
+    
     
     coef=[x ones(length(x),1)]\target;
     coef=nanmedian(coefs,2);
@@ -115,7 +116,7 @@ if(plotv)
     
     filename=sprintf('figures/Linear%s-GOES%d.',strjoin(plotvars,'-'),satnum);
     filename=regexprep(filename,'[^a-zA-Z0-9/]','');
-    print('-depsc2',strcat(filename,'eps'))
+    print('-depsc2','-zbuffer','-r300',strcat(filename,'eps'))
     print('-dpng',strcat(filename,'png'))
     
 end

### 2016-03-18 paper.tex
Compiling paper

@@
 The plasma trough is a transition region between the high density and low temperature plasmasphere and the lower density and higher energy magnetosphere \citep{Mayr1968ModelMagnetosphereTemperature}.
-Inside of the plasmapause, the density is primarily due to ionospheric photoionization; outside of the plasmapuase, the density has contributions from the co-rotating plasmasphere and convecting magnetosphere plasmas.
+Inside of the plasmapause, the density is primarily due to ionospheric photoionization; outside of the plasmapause, the density has contributions from the co-rotating plasmasphere and convecting magnetosphere plasmas.
 
@@
 
-\cite{Takahashi2006} estimated magnetospheric mass density using measurements from the CRRES satellite during a 73-day period in 1991 (obervations were made when CRRESS was in an elliptical, near equatorial orbit and primarily in the plasma trough region).
+\cite{Takahashi2006} estimated magnetospheric mass density using measurements from the CRRES satellite during a 73-day period in 1991 (observations were made when CRRESS was in an elliptical, near equatorial orbit and primarily in the plasma trough region).
 They found that the average ion mass, $M=\rho/n_e$, had some correlation with geomagnetic activity, with more negative hourly $D_{st}$ values corresponding to higher $M$ and 1.5- and 3-day averages of $K_p$ corresponding to higher $M$ (3-hour averages of $K_p$had little visual correlation with $M$).
@@
 
-\cite{Denton2006} found a weak relationship between $D_{st}$ and and $K_p$ and the field line distribution of $\rho$ using observations of the first three torodial Alfven harmonic fequencies for $L$ in the range of 6-8$R_E$.
-A more pronounced peak in the distribution along a filed line near the equator was fround for lower $D_{st}$ and larger $K_p$.
+\cite{Denton2006} found a weak relationship between $D_{st}$ and and $K_p$ and the field line distribution of $\rho$ using observations of the first three toroidal Alfvén harmonic frequencies for $L$ in the range of 6-8$R_E$.
+A more pronounced peak in the distribution along a filed line near the equator was found for lower $D_{st}$ and larger $K_p$.
 The equatorial value of $\rho$ appeared identical for the bins of $D_{st}$ (-142 to -31 nT and -31 to 37 nT) and $K_p$ (1.5 to 3.4 and 3.4 to 5.9) considered .
@@
 For five storms, two had $\rho_{eq}$ spikes after the $D_{st}$ drop, two had $\rho_{eq}$ spikes before the drop, and one showed little change in $\rho_{eq}$.
-A key result was that when daily-averaged measurements were considered, an enhancment in $\rho_{eq}$ appeared on the same day as minimum $D_{st}$.
+A key result was that when daily-averaged measurements were considered, an enhancement in $\rho_{eq}$ appeared on the same day as minimum $D_{st}$.
 
-\cite{Yao2008} studied the relationship between $D_{st}$ and ion number density for low-energy $O^+$ in different regions (ring current and plasma sheet) using the TEAMS and ESA instruments on the low-altitude and high-inclination orbiting FAST satellite and found that the average $N_{O^+}$ across the sampled L-sheels (2-14) had a strong correlation (0.88).
+\cite{Yao2008} studied the relationship between $D_{st}$ and ion number density for low-energy $O^+$ in different regions (ring current and plasma sheet) using the TEAMS and ESA instruments on the low-altitude and high-inclination orbiting FAST satellite and found that the average $N_{O^+}$ across the sampled L-shells (2-14) had a strong correlation (0.88).
 Although the correlation in the plasma trough was not calculated, the data presented show that the variations in $N_{O^+}$ tended to appear near $D_{st}$ minimum ($\pm$ 2~hours).
@@
 Issue (1) is addressed by considering in detail the number of observations that are used in epoch averages around the time of two types of events, decreases in $D_{st}$ below a threshold, and increases in $\rho_{eq}$ above a threshold.
-Issue (2) is addressed using various methods to remove or isolate the F10.7 depenences.
-Issue (3) is addressed by considering epochs and linear correlations independent of the direction of the IMF along with separation of the epoch averages based on the northrward and southward IMF.
+Issue (2) is addressed using various methods to remove or isolate the F10.7 dependences.
+Issue (3) is addressed by considering epochs and linear correlations independent of the direction of the IMF along with separation of the epoch averages based on the northward and southward IMF.
 
-In addition, we consider the influence of time averaging by comparing results using daily means and meadians and hourly means and medians of solar wind and magentospheric parameters.
+In addition, we consider the influence of time averaging by comparing results using daily means and medians and hourly means and medians of solar wind and magnetospheric parameters.
 
@@
 All other parameters used are from \cite{Kondrashov2014ReconstructionOfGaps} from 1972 through 2013, which are on a 1--hour time grid.
-$\rho_{eq}$ is the inferred equatorial mass density based on the 3rd harmonic torodial frequency of magnetic field measurements as described in \cite{Takahashi2010}.
+$\rho_{eq}$ is the inferred equatorial mass density based on the 3rd harmonic toroidal frequency of magnetic field measurements as described in \cite{Takahashi2010}.
 The smallest cadence for $\rho_{eq}$ values is 10 minutes.
@@
 A scatter plot of these two lines is shown in the lower panel of Figure~\ref{ccplot}.
-The linear correlation for GOES 6 using all measurements is found to be $0.94$, which is the same value documented by \cite{Takahashi2010} who used measurements from all satellites in the time interval of 1980 through 1991 using the constraint $0600 \leq MLT \le 1200$, $K_{p3d}\ge1.0 and $D_{st}\ge -50$~nT.
+The linear correlation for GOES 6 using all measurements is found to be $0.94$, which is the same value documented by \cite{Takahashi2010} who used measurements from all satellites in the time interval of 1980 through 1991 using the constraint $0600 \leq MLT \le 1200$, $K_{p3d}\ge1.0$ and $D_{st}\ge -50$~nT.
 Our 27-day correlations for GOES 2, 5, and 7 are 0.81, 0.78, and 0.87, and the time range of coverage of measurements from these satellites are 1980-01-01/1983-05-16, 1983-01-01/1987-02-28, and 1983-05-27/1991-08-29 respectively.
@@
 It is expected that the plasmasphere will exhibit two responses near these threshold crossings.
-First is the movement of the plasmasphere earthward and the second is a possible increase in density due to magnetospheric processes \vnote{cite}.
+First is the movement of the plasmasphere earthward and the second is a possible increase in density due to magnetospheric processes \inote{cite}.
 
@@
 To compute the epoch averages on a daily time scale, the median value of all measurements for all events centered window of $\pm 12$ hours was computed, and these windows were shifted in increments of $24$~hours.
-(Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians in 1-day bins and then compute the medians accross events.)  Error bars for each parameter were computed using the standard deviation of values used in computing the median dividied by the square root of the number of values used.
+(Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians in 1-day bins and then compute the medians across events.)  Error bars for each parameter were computed using the standard deviation of values used in computing the median divided by the square root of the number of values used.
 
@@
 The minimum $D_{st}$ median is $-48$~nT.
-Consistent with \cite{Takahashi2010}, $D_{st}$ events corrspond to elevated $\rho_{eq}$, although the magnitude of increase observed here is on the order of $\sim2$~amu/cm$^3$ instead of $\sim10$~amu/cm$^3$ found in \cite{Takahashi2010}.
+Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$, although the magnitude of increase observed here is on the order of $\sim2$~amu/cm$^3$ instead of $\sim10$~amu/cm$^3$ found in \cite{Takahashi2010}.
 The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute its median and error bars.
@@
 
-Both of the results in \ref{DailyAveragedDstEvents} indicate that there is not a statictically significant change in $\rho_{eq}$ on the day before and day after a threshold crossing in $D_{st}$.
+Both of the results in \ref{DailyAveragedDstEvents} indicate that there is not a statistically significant change in $\rho_{eq}$ on the day before and day after a threshold crossing in $D_{st}$.
 
-Because the dynamics of the magnetopshere take place on a time scale of less than one day, we have also considered hourly averages as shown in the top panel of \ref{HourlyAveragedDstEvents}.
+Because the dynamics of the magnetosphere take place on a time scale of less than one day, we have also considered hourly averages as shown in the top panel of \ref{HourlyAveragedDstEvents}.
 A total of 668 events were found in the interval of May 1983 through August 1991 with an average duration of 9 hours and a median duration of 3 hours.
 The error bars were computed in the same way as \ref{DailyAveragedDstEvents}.
-In this plot, the overall trend is similar to that found in the bottom panel of \ref{HourlyAveragedDstEvents} - $\rho_{eq}$ is slighly elevated at the time of the threhshold crossing of $D_{st}$ with respect to the values one day before and after, but the elevation is small and in general not statistically significant.
+In this plot, the overall trend is similar to that found in the bottom panel of \ref{HourlyAveragedDstEvents} - $\rho_{eq}$ is slightly elevated at the time of the threshold crossing of $D_{st}$ with respect to the values one day before and after, but the elevation is small and in general not statistically significant.
 
@@
 
-An alterntive type of event can be defined that corresponds to large increases in $\rho\ $.
+An alternative type of event can be defined that corresponds to large increases in $\rho\ $.
 Figure~\ref{HourlyAveragedRhoEvents} shows the epoch time series for events in which an increase of $\req\ $ above $20$~amu/cm$^2$ defines the start of the event.
@@
 To determine if the sign of $B_z^{IMF}$ influences the $\rho\ $ epoch time series, we separated the events by the average of $B_z^{IMF}$ in a time window of $4$~hours centered on the event start time.
-The epoch curves for $B_z^{IMF}\geq=0$ (257) events and $B_z^{IMF}\ge=0$ (139) have no statistically signifiant difference.
+The epoch curves for $B_z^{IMF}\geq=0$ (257) events and $B_z^{IMF}\ge=0$ (139) have no statistically significant difference.
 
@@
 	\includegraphics[scale=0.40]{paperfigures/stormavs-mass-gt20-GOES6.eps}
-\caption{$\req\ > 20$~ amu/cm^3 events from GOES 6 using hourly medians.
-As described in the text, there is no statistically significant dependence of the $\req\ $ plot on $B_z$ in the time interval of $\pm 2$~hours around the event.}
+\caption{$\req\ > 20$~ amu/cm$^3$ events from GOES 6 using hourly medians.
+As described in the text, there is no statistically significant dependence of the \req\  plot on $B_z$ in the time interval of $\pm 2$~hours around the event.}
 \label{HourlyAveragedRhoEvents}

### 2016-03-18 nnbehavior2.m

@@ -73,9 +73,9 @@ if(plotv)
     yr=AXmap(plotvars{2});
     %set(gca,'YTick',linspace(yr(1),yr(2),10))
     filename=sprintf('figures/NN%s-GOES%d.',strjoin(plotvars,'-'),satnum);
-    filename=regexprep(filename,'[^a-zA-Z0-9/]','');
-    print('-depsc2','-zbuffer','-r300',strcat(filename,'eps'))
-    print('-dpng',strcat(filename,'png'))
+    filename=regexprep(filename,'[^a-zA-Z0-9/\-]','');
+    print('-depsc2','-zbuffer','-r300',strcat(filename,'.eps'))
+    print('-dpng',strcat(filename,'.png'))
     
     figure; surf(xtest(2:end),ytest,testsd,'EdgeColor','none','LineStyle','none','FaceLighting','phong') %Even though phong is deprecated, it's the only one that plots without corruption
     
@@ -87,9 +87,9 @@ if(plotv)
     view(0,90)
     
         filename=sprintf('figures/NN%s-sd-GOES%d.',strjoin(plotvars,'-'),satnum);
-    filename=regexprep(filename,'[^a-zA-Z0-9/]','');
-    print('-depsc2','-zbuffer','-r300',strcat(filename,'eps'))
-    print('-dpng',strcat(filename,'png'))
+    filename=regexprep(filename,'[^a-zA-Z0-9/\-]','');
+    print('-depsc2','-zbuffer','-r300',strcat(filename,'.eps'))
+    print('-dpng',strcat(filename,'.png'))
     
     
     coef=[x ones(length(x),1)]\target;
@@ -115,9 +115,9 @@ if(plotv)
     hold on; scatter3(x(:,1),x(:,2),repmat(500,1,length(x(:,1))),target,'k')
     
     filename=sprintf('figures/Linear%s-GOES%d.',strjoin(plotvars,'-'),satnum);
-    filename=regexprep(filename,'[^a-zA-Z0-9/]','');
-    print('-depsc2','-zbuffer','-r300',strcat(filename,'eps'))
-    print('-dpng',strcat(filename,'png'))
+    filename=regexprep(filename,'[^a-zA-Z0-9/\-]','');
+    print('-depsc2','-zbuffer','-r300',strcat(filename,'.eps'))
+    print('-dpng',strcat(filename,'.png'))
     
 end
 

### 2016-03-18 paper.tex
rho events

--- 2016-03-18 paper.tex
@@
 
-The parameters $\rho_{eq}$ and $F_{10.7}$ used in this work are from the dataset of \cite{Denton}, which was used in \cite{Takahashi2010}; data are available from 1980 through 1991.
+The parameters $\rho_{eq}$ and $F_{10.7}$ used in this work are from the dataset of \cite{Denton}, which was used in \cite{Takahashi2010}; data are available from 1980 through 1991 from GOES 2,3,5, 6 and 7.
 All other parameters used are from \cite{Kondrashov2014ReconstructionOfGaps} from 1972 through 2013, which are on a 1--hour time grid.
@@
 Fill (NaN) values were used for hours in which no measurements were available.
-In cases where $\rho_{eq}$ was available in the \cite{Denton} dataset from multiple GOES satellites at the same time, the value from GOES 6 was selected.
+In cases where $\rho_{eq}$ was available from multiple GOES satellites at the same time, the value from GOES 6 was selected.
 In the dataset, measurements from GOES 6 had the longest time span of coverage.
@@
 
-In this work, events are defined to occur when $D_{st}$ or $\rho_{eq}$ crosses a threshold value, as indicated in by horizontal dashed lines in their respective panels of Figure~\ref{AllData}.
-In finding $\rho_{eq}$ events, all fill values were replaced with linearly interpolated values.
-\vinote{Not including \req\ events?}
+In this work, events are defined to occur when $D_{st}$ or $\rho_{eq}$ crosses a threshold value, as indicated by horizontal dashed lines in their respective panels of Figure~\ref{AllData}.
+\vinote{need to put line in rho_eq plot.}
 
-Figure~\ref{ccplot} shows the long-term trends of GOES 6 based $log(\rho_{eq})$ and $F_{10.7}$ computed using the median values in 27-day non-overlapping windows using all non-fill hourly values.
+Figure~\ref{ccplot} shows the long-term trends of $log(\rho_{eq})$ from GOES 6 and $F_{10.7}$ computed using the median values in 27-day non-overlapping windows.
 A scatter plot of these two lines is shown in the lower panel of Figure~\ref{ccplot}.
@@
 Our first analysis uses data only from the time interval 1989-1991, which corresponds with the interval used in the analysis in \cite{Takahashi2010}.
-For both types of events, the hour of the threshold crossing defines the zero epoch time, and for each event $4\cdot24$ hours were considered before each event and $8\cdot24$ hours after each event.
+In this interval, there were 329 $D_{st}$ events and 70 $\rho_{eq}$ events.
+For both types of events, the hour of the threshold crossing defines the zero epoch time, and for each event, $4\cdot24$ hours were considered before each event and $8\cdot24$ hours after each event.
 To compute the epoch averages on a daily time scale, the median value of all available measurements for all events centered on a window of $\pm 12$ hours of the epoch day was computed, and these averaging windows were shifted in increments of $24$~hours.
-(Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians in 1-day bins and then compute the medians across events.)  Error bars for each parameter are the standard deviation of the values used in computing the median divided by the square root of the number of values used.
+Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians in 1-day bins and then compute the medians across events.
+Error bars for each parameter are the standard deviation of the values used in computing the median divided by the square root of the number of values used.
 
@@
 
-In the lower panel of Figure \ref{DailyAveragedDstEvents} it is shown that the trends seen in the analysis of 1989-1991 also hold for the entire span of measurements from GOES 6, which spans 1983-1991 - a small elevation on the day of the event relative to the day before and day after, with averages after the day of the event being lower than that before.
+In the lower panel of Figure \ref{DailyAveragedDstEvents} it is shown that the trends seen in the analysis of 1989-1991 also hold for the entire span of measurements from GOES 6, which spans 1983-1991 - a small elevation on the day of the event relative to the day before and day after, with median averages after the day of the event being slightly lower than that before.
 
@@
  0 and 1
-Results of test on different between means of $\rho_{eq}$ shown in the top panel of \ref{DailyAverage} on days near or on the day of a $D_{st}$ event.
+
+Caption: Results of test on different between means of $\rho_{eq}$ shown in the top panel of \ref{DailyAverage} on days near or on the day of a $D_{st}$ event.
 A difference in the means can be rejected with a probability of false rejection of $p$.
@@
  0 and 1
-Results of test on different between means of $\rho_{eq}$ shown in the bottom panel of \ref{DailyAverage} on days near or on the day of a $D_{st}$ event.
 
-It was found that $\rho_{eq}$ enhancements do not clearly correspond to a signature in $D_{st}$, but that there is a trend for such enhancements to occur when $B_{z}$ in the IMF is positive.
-This is consistent with \cite{Takahashi2010} who note that very large increases in $\rho_{eq}$ often corresponded to movement of the plasmasphere to beyond geosynchronous distances.
+Caption: Results of test on different between means of $\rho_{eq}$ shown in the bottom panel of \ref{DailyAverage} on days near or on the day of a $D_{st}$ event.
 
-This method finds 669 periods of $D_{st}$ crossing beneath the selected threshold between May 1983 and August 1991 with an average duration of 9 hours and a median duration of 3 hours \vinote{Make sure I defined "duration"}.
-Figure \ref{HourlyAveragedDstEvents} shows the average values of all events over a window of 24 hours before onset and 48 hours after.
-Figure \ref{HourlyAveragedDstEvents}a shows events selected by looking for event onsets where $D_{st}$ crossed a threshold of $-40$~nT.
-The dashed red lines indicate plus and minus one standard deviation of values from all events that were used to compute the median.
-The final plot in the stack shows both $\rho_{eq}$ and a bar plot of how many valid data points went into the $\rho_{eq}$ average.
-Since $\rho_{eq}$ comes from a sparser dataset, it has less valid points contributing to the averages than the other parameters in the stack.
-
-Figure \ref{HourlyAveragedDstEvents} shows a definite spike in the $Z$ component of the magnetic field, as well as the defined drop in $D_{st}$, but no obvious change in mass density at an hourly timescale.
-This points to an issue with only looking at long-timescale trends between density and $D_{st}$, and allows for the possibility that other factors are influencing the long term correlation since there's no obvious connection on a short timescale.
-One possibility is that, as suggested in \cite{Takahashi2010}, $F_{10.7}$ plays a significant role in driving long term density values which biases the long term correlation of density and $D_{st}$.
-
-Two types of events are considered. The first is a drop in $D_{st}$ below the threshold of $-40$~nT.  The second is an increase in $\rho_{eq}$ above $40$~amu/cm$^3$.
-
-Our first analysis uses data only from the time interval 1989-1991.
-In this interval, there were 329 $D_{st}$ events and 70 $\rho_{eq}$ events.
-For both types of events, the hour of the threshold crossing defines the zero epoch time, and for each event $8\cdot24$ hours were kept after each event and $4\cdot24$ hours before each event.
-To compute the epoch averages on a daily time scale, the median value of all measurements for all events centered window of $\pm 12$ hours was computed, and these windows were shifted in increments of $24$~hours.
-(Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians in 1-day bins and then compute the medians accross events.)  Error bars for each parameter were computed using the standard deviation of values used in computing the median dividied by the square root of the number of values used.
-
-In the upper panel of \ref{DailyAveragedDstEvents}, $D_{st}$ events are shown.
-The minimum $D_{st}$ median is $-48$~nT.
-Consistent with \cite{Takahashi2010}, $D_{st}$ events corrspond to elevated $\rho_{eq}$, although the magnitude of increase observed here is on the order of $\sim2$~amu/cm$^3$ instead of $\sim10$~amu/cm$^3$ found in \cite{Takahashi2010}.
-The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute its median and error bars.
-Note that for $D_{st}$, the number of measurements used in computing the medians is much larger as we use all available $D_{st}$ measurements instead of restricting to only values where a non-fill $\rho_{eq}$ value existed.
-
-Both of the results in \ref{DailyAveragedDstEvents} indicate that there is not a statictically significant change in $\rho_{eq}$ on the day before and day after a threshold crossing in $D_{st}$.
+Both of the results in \ref{DailyAveragedDstEvents} indicate that there is not a statictically significant change in medians of $\rho_{eq}$ on the day before and day after a threshold crossing in $D_{st}$.
 
@@
 In this plot, the overall trend is similar to that found in the bottom panel of \ref{HourlyAveragedDstEvents} - $\rho_{eq}$ is slighly elevated at the time of the threhshold crossing of $D_{st}$ with respect to the values one day before and after, but the elevation is small and in general not statistically significant.
+At this timescale no obvious change in mass density at hourly timescale is visible.
+This points to an issue with only looking at long-timescale trends between density and $D_{st}$, and allows for the possibility that other factors are influencing the long term correlation because there is no obvious connection on a short timescale.
+One possibility is that, as suggested in \cite{Takahashi2010}, $F_{10.7}$ plays a significant role in driving long term density values which biases the long-term correlation of density and $D_{st}$.
 
@@
 
-The final plot in the stack shows both $\rho_{eq}$ and a bar plot of how many valid data points went into the $\rho_{eq}$ average.
-Since $\rho_{eq}$ comes from a sparser dataset, it has less valid points contributing to the averages than the other parameters in the stack.
-A subset of longer duration events will be looked at later.
-
-This figure shows a definite spike in the $Z$ component of the magnetic field, as well as the defined drop in $D_{st}$, but no obvious change in mass density at an hourly timescale.
-This points to an issue with only looking at long-timescale trends between density and $D_{st}$, and allows for the possibility that other factors are influencing the long term correlation since there's no obvious connection on a short timescale.
-One possibility is that, as suggested in \cite{Takahashi2010}, $F_{10.7}$ plays a significant role in driving long term density values which biases the long term correlation of density and $D_{st}$.
-
-\section{More specific events}
-It's hypothesized that progressively picking more specific event criteria will allow for the possibility of more significant results, at the expense of more bias in the selection process and potentially less overall usefulness of the results.
-That said, the predictability of extreme events is of definite interest, so an attempt has been made to find some reproducible method of prediction.
-Looking at events that last longer than 12 hours and events with an onset threshhold less than $-80$nT finds both result in a spike in mass density, but also a definite lack of data availability to the point where that spike may be coming from less than five of the total 211 events.
-
 \subsection{$\rho_{eq}$ Events}
 
-Instead of looking for events based on a threshold of $D_{st}$, we instead looked for a certain amount of change in $\rho_{eq}$ as the basis for event onset.
-Both raw change and percent change were done in case of bias towards high or low $\rho_{eq}$ periods, respectively, but neither showed any correlation to a change in $D_{st}$.
+An alterntive type of event can be defined that corresponds to large increases in $\rho\ $.
+In finding $\rho_{eq}$ events, all fill values were replaced with linearly interpolated values.
+\vinote{Not including \req\ events?}
 
-An alterntive type of event can be defined that corresponds to large increases in $\rho\ $.
 Figure~\ref{HourlyAveragedRhoEvents} shows the epoch time series for events in which an increase of $\req\ $ above $20$~amu/cm$^2$ defines the start of the event.
 Here we see the expected result that such events tend to be associated with positive $B_z^{IMF}$.
-To determine if the sign of $B_z^{IMF}$ influences the $\rho\ $ epoch time series, we separated the events by the average of $B_z^{IMF}$ in a time window of $4$~hours centered on the event start time.
+To determine if the sign of $B_z^{IMF}$ influences the $\rho\ $ epoch time series, we separated the events by the average of $B_z^{IMF}$ in a time window of $4$~hours.
+
+Figure~\label{fig:RhoBinned}(a) shows the 
 The epoch curves for $B_z^{IMF}\geq=0$ (257) events and $B_z^{IMF}\ge=0$ (139) have no statistically signifiant difference.
@@
 \includegraphics[scale=0.40]{paperfigures/ccplot-GOES6.eps}
-\caption{Top: 27-day boxcar averages of $F_{10.7}$ and $\rho_{eq}$ from GOES 6.
-Bottom: Correlation between $\log(\rho_{eq})$ and $F_{10.7}$ using hour, day, and 27-day averaging intervals; compare to \cite{Takahashi2010} Fig.~14.}
+\caption{Top: 27-day medians of $F_{10.7}$ and $\rho_{eq}$ from GOES 6.
+Bottom: Correlation between $\log(\rho_{eq})$ and $F_{10.7}$ using medians in hour, day, and 27-day non-overlapping; compare to \cite{Takahashi2010} Fig.~14.}
 \label{ccplot}

### 2016-03-18 paper.tex

@@
 One possibility is that, as suggested in \cite{Takahashi2010}, $F_{10.7}$ plays a significant role in driving long term density values which biases the long-term correlation of density and $D_{st}$.
+=======
+Results of test on different between means of $\rho_{eq}$ shown in the bottom panel of \ref{DailyAverage} on days near or on the day of a $D_{st}$ event.
+
+It was found that $\rho_{eq}$ enhancements do not clearly correspond to a signature in $D_{st}$, but that there is a trend for such enhancements to occur when $B_{z}$ in the IMF is positive.
+This is consistent with \cite{Takahashi2010} who note that very large increases in $\rho_{eq}$ often corresponded to movement of the plasmasphere to beyond geosynchronous distances.
+
+This method finds 669 periods of $D_{st}$ crossing beneath the selected threshold between May 1983 and August 1991 with an average duration of 9 hours and a median duration of 3 hours \vinote{Make sure I defined "duration"}.
+Figure \ref{HourlyAveragedDstEvents} shows the average values of all events over a window of 24 hours before onset and 48 hours after.
+Figure \ref{HourlyAveragedDstEvents}a shows events selected by looking for event onsets where $D_{st}$ crossed a threshold of $-40$~nT.
+The dashed red lines indicate plus and minus one standard deviation of values from all events that were used to compute the median.
+The final plot in the stack shows both $\rho_{eq}$ and a bar plot of how many valid data points went into the $\rho_{eq}$ average.
+Since $\rho_{eq}$ comes from a sparser dataset, it has less valid points contributing to the averages than the other parameters in the stack.
+
+Figure \ref{HourlyAveragedDstEvents} shows a definite spike in the $Z$ component of the magnetic field, as well as the defined drop in $D_{st}$, but no obvious change in mass density at an hourly timescale.
+This points to an issue with only looking at long-timescale trends between density and $D_{st}$, and allows for the possibility that other factors are influencing the long term correlation since there's no obvious connection on a short timescale.
+One possibility is that, as suggested in \cite{Takahashi2010}, $F_{10.7}$ plays a significant role in driving long term density values which biases the long term correlation of density and $D_{st}$.
+
+Two types of events are considered. The first is a drop in $D_{st}$ below the threshold of $-40$~nT.  The second is an increase in $\rho_{eq}$ above $40$~amu/cm$^3$.
+
+Our first analysis uses data only from the time interval 1989-1991.
+In this interval, there were 329 $D_{st}$ events and 70 $\rho_{eq}$ events.
+For both types of events, the hour of the threshold crossing defines the zero epoch time, and for each event $8\cdot24$ hours were kept after each event and $4\cdot24$ hours before each event.
+To compute the epoch averages on a daily time scale, the median value of all measurements for all events centered window of $\pm 12$ hours was computed, and these windows were shifted in increments of $24$~hours.
+(Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians in 1-day bins and then compute the medians across events.)  Error bars for each parameter were computed using the standard deviation of values used in computing the median divided by the square root of the number of values used.
+
+In the upper panel of \ref{DailyAveragedDstEvents}, $D_{st}$ events are shown.
+The minimum $D_{st}$ median is $-48$~nT.
+Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$, although the magnitude of increase observed here is on the order of $\sim2$~amu/cm$^3$ instead of $\sim10$~amu/cm$^3$ found in \cite{Takahashi2010}.
+The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute its median and error bars.
+Note that for $D_{st}$, the number of measurements used in computing the medians is much larger as we use all available $D_{st}$ measurements instead of restricting to only values where a non-fill $\rho_{eq}$ value existed.
+
+Both of the results in \ref{DailyAveragedDstEvents} indicate that there is not a statistically significant change in $\rho_{eq}$ on the day before and day after a threshold crossing in $D_{st}$.
+
+Because the dynamics of the magnetosphere take place on a time scale of less than one day, we have also considered hourly averages as shown in the top panel of \ref{HourlyAveragedDstEvents}.
+A total of 668 events were found in the interval of May 1983 through August 1991 with an average duration of 9 hours and a median duration of 3 hours.
+The error bars were computed in the same way as \ref{DailyAveragedDstEvents}.
+In this plot, the overall trend is similar to that found in the bottom panel of \ref{HourlyAveragedDstEvents} - $\rho_{eq}$ is slightly elevated at the time of the threshold crossing of $D_{st}$ with respect to the values one day before and after, but the elevation is small and in general not statistically significant.
 

### 2016-03-25 ComplexPlots.m
Updating plots. Interpolation now much faster

@@ -352,20 +352,26 @@ if(MakePaperPlots && stormcase==10) %1-day takahashi. Do for any day plot
         rs2=randsample(AV0,sum(~isnan(AV0)),'true');
         delta(4,i)=(nanmedian(rs1)-nanmedian(rs2));
     end
+    
     figure;
+    subplot(3,1,1)
     hist(delta(1,:))
     hold on;
     plot(nanmedian(AVm1)-nanmedian(AV0),0,'.','MarkerSize',20)
+    title('Bootstrap differences of 1 hour pre-onset and onset')
     
-        figure;
+    subplot(3,1,2)
     hist(delta(2,:))
     hold on;
     plot(nanmedian(AVm1)-nanmedian(AV1),0,'.','MarkerSize',20)
+    title('Bootstrap differences of 1 hour pre-onset and 1 hour post-onset')
     
-        figure;
+    subplot(3,1,3)
     hist(delta(3,:))
     hold on;
     plot(nanmedian(AV1)-nanmedian(AV0),0,'.','MarkerSize',20)
+    title('Bootstrap differences of 1-hour post-onset and onset')
+    
     
     table=fopen('tables/DeltaBootstraps.txt','w');
     Dm10=sum(delta(1,:)>=0)/length(delta(1,:));
@@ -377,8 +383,7 @@ if(MakePaperPlots && stormcase==10) %1-day takahashi. Do for any day plot
     fprintf(table,'-1 1\t%2.2f\t%2.2f%%<=0\n',nanmedian(AVm1)-nanmedian(AV1),Dm11*100);
     fprintf(table,' 1 0\t%2.2f\t%2.2f%%>=0\n',nanmedian(AV1)-nanmedian(AV0),D10*100);
     
-    close(table);
-    delta
+    fclose(table);
     
 end
 

### 2016-03-25 interptest.m

@@ -1,64 +1,88 @@
 function datanew=interptest(t,x,tnew,dt)
+
+if nargin<3
+    error('datanew=interptest(t,x,tnew,dt)')
+end
+
 if nargin == 3
     dt=(tnew(2)-tnew(1))/2; %halfway to the points on either side
 end
 
-tnew=tnew(:); %Force orientation
-t=t(:);
-%{
-
-dt2=floor(dt/(t(2)-t(1)));
-t2=tnew(1)-dt:(t(2)-t(1)):tnew(end)+dt;
-x2=nan(length(t2),min(size(x)));
-
-indices=floor((t-t(1))/(t(2)-t(1))+1); %Indices on expanded uniform grid of t (not tnew yet)
-
-if(tnew(1)>t(1)) %If new time starts later than data provided, cut down x
-    offset=find(diff([0 t'>=(tnew(1)-dt) 0])>0)-1;
-    x2(indices(offset:end)-indices(offset)+1)=x(offset:end);
-else %New time wants data from before data exists
-    offset=find(diff([0 (t(1)-dt)<=tnew' 0])>0)-1; %Find first valid point
-    x2(indices+offset)=x; %Go from nonuniform time grid to uniform time grid with NaNs
+if(tnew(1)<t(1) || tnew(end)>t(end))
+    error('New time must be within existing time')
 end
-
-snip=0;
-while(mod(length(x2),(dt2*2))~=0)
-    x2(end+1)=NaN; %Adding nans shouldn't affect final median, just buffer for size
-    snip=snip+1;
-end
-datanew=reshape(x2,dt2*2,length(x2)/(dt2*2)); %Reshape and median to smaller uniform time grid
-datanew=nanmedian(datanew)';
-datasave=datanew;
-
-if(tnew(1)<t(1))
-    prebuffer=tnew(1):(tnew(2)-tnew(1)):t(1);
-    prebuffer=prebuffer(1:end-1);
-    datanew=[nan(1,length(prebuffer)) datanew];
-end
-if(tnew(end)>t(end))
-    postbuffer=t(end):(tnew(2)-tnew(1)):tnew(end);
-    postbuffer=postbuffer(2:end);
-    datanew=[datanew nan(1,length(postbuffer))];
-end
-
-
-toc
 
 tic
-%}
 
-if(length(x)~=329)
-datanew=zeros(length(tnew),min(size(x)));
-else
-    datanew=zeros(length(tnew),length(x));
+tnew=tnew(:); %Force orientation
[…]

### 2016-03-25 tables/tableparse.pl

@@ -39,7 +39,7 @@ my %H4=();
 
 my $regex = '^(\S+)\s+- .\d\.\d\d (.\d\.\d\d) \d.\d\d (\d.\d\d).*'; #To catch CC test column and test_sd
 if($Type=~m/NN/) {
-$regex = '^(\S+)\s+.*(.\d\.\d\d)[^\d]*$'; #To catch NN validation column
+$regex = '^(\S+)\s+.*(?:\s*.\d\.\d\d){5} (.\d.\d\d) (?:\s*\d.\d\d){5} (\d.\d\d)[^\d]*$'; #To catch NN validation column
 }
 
 for my $line(@FH1s){

### 2016-03-25 ComplexPlots.m
Updating table parsing and interpolation code

@@ -353,25 +353,6 @@ if(MakePaperPlots && stormcase==10) %1-day takahashi. Do for any day plot
         delta(4,i)=(nanmedian(rs1)-nanmedian(rs2));
     end
     
-    figure;
-    subplot(3,1,1)
-    hist(delta(1,:))
-    hold on;
-    plot(nanmedian(AVm1)-nanmedian(AV0),0,'.','MarkerSize',20)
-    title('Bootstrap differences of 1 hour pre-onset and onset')
-    
-    subplot(3,1,2)
-    hist(delta(2,:))
-    hold on;
-    plot(nanmedian(AVm1)-nanmedian(AV1),0,'.','MarkerSize',20)
-    title('Bootstrap differences of 1 hour pre-onset and 1 hour post-onset')
-    
-    subplot(3,1,3)
-    hist(delta(3,:))
-    hold on;
-    plot(nanmedian(AV1)-nanmedian(AV0),0,'.','MarkerSize',20)
-    title('Bootstrap differences of 1-hour post-onset and onset')
-    
     
     table=fopen('tables/DeltaBootstraps.txt','w');
     Dm10=sum(delta(1,:)>=0)/length(delta(1,:));
@@ -384,6 +365,53 @@ if(MakePaperPlots && stormcase==10) %1-day takahashi. Do for any day plot
     fprintf(table,' 1 0\t%2.2f\t%2.2f%%>=0\n',nanmedian(AV1)-nanmedian(AV0),D10*100);
     
     fclose(table);
+    
+    
+    g=figure('Visible',visible);
+    h(1)=subplot('position',subplotstack(3,1));
+    hist(delta(1,:),[-7.5:0.5:5.5])
+    hold on;
+    plot(nanmedian(AVm1)-nanmedian(AV0),0,'.','MarkerSize',20)
+    plot([0 0],get(gca,'ylim'),'k-','LineWidth',1.5)
+    text(0.01,0.9,'1 day pre-onset and onset','Units','normalized','FontSize',14)
+    text(1,max(get(gca,'ylim'))*3/4,sprintf('%2.2f%%>=0',Dm10*100))
+    ylabel('Count')
+    title('Bootstrapped differences of daily \rho_{eq} medians around event onset')
+    
[…]

### 2016-03-25 interptest.m

@@ -8,11 +8,11 @@ if nargin == 3
     dt=(tnew(2)-tnew(1))/2; %halfway to the points on either side
 end
 
+%{
 if(tnew(1)<t(1) || tnew(end)>t(end))
     error('New time must be within existing time')
 end
-
-tic
+%}
 
 tnew=tnew(:); %Force orientation
 t=t(:);
@@ -23,16 +23,21 @@ end
 
 if(min(size(x))~=1) %If x has two dimensions, recursively interpolate over the non-time dimensions
     xdim=setdiff(size(x),size(t));
-    datanew=zeros(length(tnew),xdim);  
+    datanew=NaN(length(tnew),xdim);  
     for i=1:xdim
         datanew(:,i)=interptest(t,x(:,i),tnew,dt);
     end
 else
+    
+    while(t(end)>(tnew(end)+dt))
+        t(end)=[];
+        x(end)=[];
+    end
 
     dt2=floor(dt/(t(2)-t(1)));
     t2=tnew(1)-dt:(t(2)-t(1)):tnew(end)+dt;
     t2(end)=[];  %last point would be first of next bin
-    x2=nan(length(t2),min(size(x)));
+    x2=nan(length(t2),1);
 
     indices=floor((t-t(1))/(t(2)-t(1))+1); %Indices on expanded uniform grid of t (not tnew yet)
 
@@ -51,19 +56,23 @@ else
     end
     datanew=reshape(x2,dt2*2,length(x2)/(dt2*2)); %Reshape and median to smaller uniform time grid
     datanew=nanmedian(datanew)';
+    if(length(datanew)==(length(tnew)+1) && isnan(datanew(end)))
+        datanew(end)=[]; %Because sometimes dt2 has a rounding/precision problem and the algorithm buffers up an additional, empty value
+    end
     datasave=datanew;
 
+    %{
     if(tnew(1)<t(1))
         prebuffer=tnew(1):(tnew(2)-tnew(1)):t(1);
         prebuffer=prebuffer(1:end-1);
-        datanew=[nan(1,length(prebuffer)) datanew];
+        datanew=[nan(length(prebuffer),1); datanew];
     end
     if(tnew(end)>t(end))
         postbuffer=t(end):(tnew(2)-tnew(1)):tnew(end);
         postbuffer=postbuffer(2:end);
-        datanew=[datanew nan(1,length(postbuffer))];
+        datanew=[datanew; nan(length(postbuffer,1))];
     end
-
+%}
 return
 
 end

### 2016-03-25 tables/tableparse.pl

@@ -1,7 +1,7 @@
 #!/usr/bin/perl
 #Parses tables to combine into one table for the paper
-use warnings;
-use strict;
+#use warnings;
+#use strict;
 
 my @Types=('CC','NN');
 
@@ -10,91 +10,162 @@ if($#ARGV+1 > 0) {
  if($ARGV[0]!~m/(NN|CC)/){
   print "Type must be NN or CC\n";
   exit
-  }
+ }
 }
 
 foreach my $Type(@Types){
 
-my $TypeString="linear";
-if($Type=~m/NN/)
-{$TypeString="nonlinear";}
+ my $TypeString="linear";
+ if($Type=~m/NN/)
+ {$TypeString="nonlinear";}
 
-open(FH1,"<${Type}table-GOES2.txt");
-my @FH1s=<FH1>;
-open(FH2,"<${Type}table-GOES5.txt");
-my @FH2s=<FH2>;
-open(FH3,"<${Type}table-GOES6.txt");
-my @FH3s=<FH3>;
-open(FH4,"<${Type}table-GOES7.txt");
-my @FH4s=<FH4>;
-close(FH1); 
-close(FH2);
-close(FH3);
-close(FH4);
 
-my %H1=();
-my %H2=();
-my %H3=();
-my %H4=();
+ my @AoF;
+ open(FH1,"<${Type}table-GOES2.txt");
+ my @FH1s=<FH1>;
+ open(FH2,"<${Type}table-GOES5.txt");
+ my @FH2s=<FH2>;
+ open(FH3,"<${Type}table-GOES6.txt");
+ my @FH3s=<FH3>;
+ open(FH4,"<${Type}table-GOES7.txt");
+ my @FH4s=<FH4>;
+ close(FH1); 
+ close(FH2);
+ close(FH3);
+ close(FH4);
 
-my $regex = '^(\S+)\s+- .\d\.\d\d (.\d\.\d\d) \d.\d\d (\d.\d\d).*'; #To catch CC test column and test_sd
-if($Type=~m/NN/) {
-$regex = '^(\S+)\s+.*(?:\s*.\d\.\d\d){5} (.\d.\d\d) (?:\s*\d.\d\d){5} (\d.\d\d)[^\d]*$'; #To catch NN validation column
-}
+ my $findex=0;
+ @AoF[$findex]=[@FH1s];$findex++;
+ @AoF[$findex]=[@FH2s];$findex++;
[…]

### 2016-04-01 ComplexPlots.m
NN and Linear figures tied in axes, no longer regulated across all figures

@@ -451,22 +451,30 @@ if(MakePaperPlots && stormcase==25)
     x=F10727Day;
     y=log10(MD6);
     [AX,H1,H2]=plotyy(NewTime,x,NewMTime6,y,'plot','plot');
+    
+    Colors=[[0 0.8 0.8]; [0.8 0 0.8]; [0 0 1]; [0.5 0.9 0.2]];
      
     set(H1,'marker','.','MarkerSize',15,'color','red'); set(AX(1),'YColor','r'); set(AX(2),'XTick',[]);
-    set(H2,'LineStyle','-','color','blue'); set(AX(2),'YColor','k');
-        hold(AX(2));
-    H3=plot(AX(2),NewMTime2,log10(MD2),'-','Color',[0 0.5 0.5],'LineWidth',1.25);
-    H4=plot(AX(2),NewMTime5,log10(MD5),'-','Color',[0.5 0 0.5]);
-    H5=plot(AX(2),NewMTime7,log10(MD7),'-','Color',[0.5 0.5 0.2]);
-    ylim(AX(1),[0,300])
-    ylim(AX(2),[0.5,1.5])
+    set(H2,'LineStyle','-','color',Colors(3,:)); set(AX(2),'YColor','k');
+    hold(AX(2));
+    H3=plot(AX(2),NewMTime2,log10(MD2),'-','Color',Colors(1,:),'LineWidth',1.25);
+    H4=plot(AX(2),NewMTime5,log10(MD5),'-','Color',Colors(2,:));
+    H5=plot(AX(2),NewMTime7,log10(MD7),'-','Color',Colors(4,:));
+    plot(AX(2),[NewMTime2(1) NewMTime2(end)],[1.5 1.5],'Color',Colors(1,:),'LineWidth',3)
+    plot(AX(2),[NewMTime5(1) NewMTime5(end)],[1.52 1.52],'Color',Colors(2,:),'LineWidth',3)
+    plot(AX(2),[NewMTime6(1) NewMTime6(end)],[1.54 1.54],'Color',Colors(3,:),'LineWidth',3)
+    plot(AX(2),[NewMTime7(1) NewMTime7(end)],[1.56 1.56],'Color',Colors(4,:),'LineWidth',3)
+    
+    ylim(AX(1),[0,320])
+    ylim(AX(2),[0.5,1.6])
[…]

### 2016-04-01 NNAnalysis.m

@@ -1,7 +1,7 @@
 function NNAnalysis(AVMat,AVMDMat,satnum)
 
 loops=40;
-AXmap=containers.Map({'B_z','V_{sw}','F_{10.7}','\rho_{eq}','DoY','\rho_{sw}','D_{st}','MLT'},{[-10 10],[200 800],[50 350],[0 70],[0 356],[0 30],[-100 30],[0 24]});
+AXmap=containers.Map({'B_z','V_{sw}','F_{10.7}','\rho_{eq}','DoY','\rho_{sw}','D_{st}','MLT'},{[-10 10],[200 800],[50 350],[0 40],[0 356],[0 30],[-100 30],[0 24]});
 
 
 disp('NN - B_z')

### 2016-04-01 nnbehavior2.m

@@ -64,28 +64,30 @@ if(plotv)
     
     ylabel(plotvars{2})
     xlabel(plotvars{1})
-    axis([AXmap(plotvars{1}) AXmap(plotvars{2}) AXmap(plotvars{3})])
-    caxis(AXmap('\rho_{eq}'))
+    %axis([AXmap(plotvars{1}) AXmap(plotvars{2}) AXmap(plotvars{3})])
+    %caxis(AXmap('\rho_{eq}'))    
     view(0,90)
     title(sprintf('Mean nonlinear predicted %s over %d loops with GOES %d',plotvars{3},loops,satnum))
     colorbar
     hold on; scatter3(x(:,1),x(:,2),repmat(500,1,length(x(:,1))),target,'k')
-    yr=AXmap(plotvars{2});
     %set(gca,'YTick',linspace(yr(1),yr(2),10))
+    
+    ax=[xlim; ylim; zlim; caxis];
     filename=sprintf('figures/NN%s-GOES%d.',strjoin(plotvars,'-'),satnum);
     filename=regexprep(filename,'[^a-zA-Z0-9/\-]','');
     print('-depsc2','-zbuffer','-r300',strcat(filename,'.eps'))
     print('-dpng',strcat(filename,'.png'))
     
-    figure; surf(xtest(2:end),ytest,testsd,'EdgeColor','none','LineStyle','none','FaceLighting','phong') %Even though phong is deprecated, it's the only one that plots without corruption
     
+    
+    figure; surf(xtest(2:end),ytest,testsd,'EdgeColor','none','LineStyle','none','FaceLighting','phong') %Even though phong is deprecated, it's the only one that plots without corruption
     ylabel(plotvars{2})
     xlabel(plotvars{1})
-    axis([AXmap(plotvars{1}) AXmap(plotvars{2})])
+    %axis([AXmap(plotvars{1}) AXmap(plotvars{2})])
     title(sprintf('Standard deviation of %d loops predicting %s with GOES %d',loops,plotvars{3},satnum))
     colorbar
     view(0,90)
-    
+    axis(reshape(ax',1,[]))
         filename=sprintf('figures/NN%s-sd-GOES%d.',strjoin(plotvars,'-'),satnum);
     filename=regexprep(filename,'[^a-zA-Z0-9/\-]','');
[…]

### 2016-04-01 tables/tableparse.pl

@@ -144,11 +144,11 @@ EOF
     
     if(@$wanth[0]=~/\+/)
     {
-    my $DiffVal=sprintf("%2.2f",sqrt($H1{"$sat-$wanted-@$wanth[0]"}**2+$H1{"$sat-$wanted-@$wanth[1]"}**2));
+    my $DiffVal=sprintf("%+2.2f",sqrt($H1{"$sat-$wanted-@$wanth[0]"}**2+$H1{"$sat-$wanted-@$wanth[1]"}**2));
      print FH "\\pm$DiffVal "
     }
     else{
-    my $DiffVal=sprintf("%2.2f",$H1{"$sat-$wanted-@$wanth[0]"}-$H1{"$sat-$wanted-@$wanth[1]"});
+    my $DiffVal=sprintf("%+2.2f",$H1{"$sat-$wanted-@$wanth[0]"}-$H1{"$sat-$wanted-@$wanth[1]"});
      print FH "$DiffVal"
     }
    }

### 2016-04-08 tables/tableparse.pl
Updated NN tables and parsing

@@ -84,7 +84,7 @@ foreach my $Type(@Types){
  print FH <<EOF;
  \\begin{table}[h]
  \\small
- \\begin{tabular}{|L|LLLL|}
+ \\begin{tabular}{|C|CCCC|}
  \\hline
 EOF
 
@@ -120,11 +120,11 @@ EOF
 
  #Print difference table
  if($Type=~/NN/){
-  @WantHs=(['NNt','NNtr'],['+-NNt','+-NNtr']);
+  @WantHs=(['NNtr','NNt'],['+-NNtr','+-NNt']);
  }
  else
  {
-  @WantHs=(['CCt','CCtr'],['+-CCt','+-CCtr']);
+  @WantHs=(['CCtr','CCt'],['+-CCtr','+-CCt']);
  }
 
  open(FH,">${Type}difftable.tex");
@@ -135,7 +135,7 @@ EOF
  \\hline
 EOF
 
- print FH 'T-Tr & \text{GOES 2} & \text{GOES 5} & \text{GOES 6} & \text{GOES 7}\\\\ \hline'."\n";
+ print FH 'Tr-T & \text{GOES 2} & \text{GOES 5} & \text{GOES 6} & \text{GOES 7}\\\\ \hline'."\n";
  for my $wanted(@Want){
   print FH "$wanted ";
   for my $sat(@Sats){
@@ -144,7 +144,7 @@ EOF
     
     if(@$wanth[0]=~/\+/)
     {
-    my $DiffVal=sprintf("%+2.2f",sqrt($H1{"$sat-$wanted-@$wanth[0]"}**2+$H1{"$sat-$wanted-@$wanth[1]"}**2));
+    my $DiffVal=sprintf("%2.2f",sqrt($H1{"$sat-$wanted-@$wanth[0]"}**2+$H1{"$sat-$wanted-@$wanth[1]"}**2));
      print FH "\\pm$DiffVal "
     }
     else{
@@ -159,7 +159,7 @@ EOF
  print FH <<EOF;
  \\hline
  \\end{tabular}
- \\caption{Table of differences in $TypeString testing-training models, where each correlation is the median correlation of 100 random samples. Each sample trained on half of the data (via randomly selected rows of the least squares matrix) and tested on the other half} 
+ \\caption{Table of differences in $TypeString training-testing models, where each correlation is the median correlation of 100 random samples. Each sample trained on half of the data (via randomly selected rows of the least squares matrix) and tested on the other half} 
  \\label{${Type}difftable}
  \\end{table}
 EOF

### 2016-04-28 paper.tex
Updating table parsing and interpolation code
misc paper.tex edits

@@
 One possibility is that, as suggested in \cite{Takahashi2010}, $F_{10.7}$ plays a significant role in driving long term density values which biases the long-term correlation of density and $D_{st}$.
-=======
+
 Results of test on different between means of $\rho_{eq}$ shown in the bottom panel of \ref{DailyAverage} on days near or on the day of a $D_{st}$ event.
@@
 The top four panels show parameters from \cite{Kondrashov2014ReconstructionOfGaps} and the bottom panel contains $\rho_{eq}$ based on GOES 6 measurements from \cite{Denton} after interpolation and averaging described in the text.
-Dashed horizontal lines in the $D_{st}$ and $\rho_{eq}$ panels indicate sample event cutoff thresholds of $D_{st} = -50$~nT and $\rho_{eq} = 40$~amu/cm$^3$}.
+Dashed horizontal lines in the $D_{st}$ and $\rho_{eq}$ panels indicate sample event cutoff thresholds of $D_{st} = -50$~nT and $\rho_{eq} = 20$~amu/cm$^3$}.
 \label{AllData}

### 2016-05-06 paper.tex
Fixing plots

--- 2016-03-18 paper.tex
@@
 \newcolumntype{L}{>{$}l<{$}} %To enable math mode in tables (for saying things like B_z)
+\newcolumntype{C}{>{$}c<{$}}
 \newcommand{\vinote}[1]{\textcolor{red}{\textbf{#1}}} %If you want \inote{#} instead of just \note #, for inline notes
@@
 In this work, events are defined to occur when $D_{st}$ or $\rho_{eq}$ crosses a threshold value, as indicated by horizontal dashed lines in their respective panels of Figure~\ref{AllData}.
-\vinote{need to put line in rho_eq plot.}
+\vinote{need to put line in \req\ plot.}
 
@@
 Two types of events are considered.
-The first is a drop in the $D_{st}$ index \vnote{Cite Kyoto} below the threshold of -50~nT.
+The first is a drop in the $D_{st}$ index \vinote{Cite Kyoto} below the threshold of -50~nT.
 These types of events are considered in order to determine if there is a well-defined $\rho_{eq}$ dependence on geomagnetic activity/storms as indicated by $D_{st}$ index.
@@
 This was done by randomly sampling half of the data, generating the model, and testing against the other half, doing this process 100 times and then taking the median correlations.
-
-\input{"tables/CCperltable.tex"}
 
@@
 
+\newpage
+\input{"tables/CCperltable.tex"}
+
 \end{document}

### 2016-05-10 paper.tex
Misc edits and removed figures

@@
 
-\vnote More detail
-
-%It confirms results from previous papers that a sudden drop in $D_{st}$ correlates with a spike in equatorial mass density under certain conditions, while adding a level of depth and specification to the applicability of their results.
-It compares data at 1-hour averages to data at 1-day averages to examine if the trend holds at varying time scales and finds that it does, so long as the data is pre-processed to linearly remove a large time scale $F_{10.7}$ dependence.
-By then looking at an hourly average of parameters from 24 hours before event onset to 48 hours after, short timescale trends can be discerned.
-
 \vspace{2em}
@@
 
-The plasma trough is a transition region between the high density and low temperature plasmasphere and the lower density and higher energy magnetosphere \citep{Mayr1968ModelMagnetosphereTemperature}.
-Inside of the plasmapause, the density is primarily due to ionospheric photoionization; outside of the plasmapause, the density has contributions from the co-rotating plasmasphere and convecting magnetosphere plasmas.
+The plasma trough is a transition region between the higher density and lower temperature plasmasphere and the lower density and higher energy magnetosphere \citep{Mayr1968ModelMagnetosphereTemperature}.
+Inside of the plasmapause, the density is primarily due to ionospheric photoionization; outside of the plasmapause, the density has contributions from the co-rotating plasmasphere and Earthward convecting magnetosphere plasmas.
 
@@
 There are well--validated models of the plasmapause boundary, as a function of $L$, $MLT$, and geomagnetic activity (\cite{LemaireEarthsPlasmasphere}, \cite{Moldwin2002ModelPlasmapause}, \cite{OBrien2003EmpiricalPlasmapause}).
-Models also exist for the plasmasphere density (\cite{Gallagher1988EmpiricalModelPlasmasphere}, \cite{LemaireEarthsPlasmasphere}, \cite{Takahashi2006}, and \cite{Takahashi2010}), but and dependence of the plasma trough on geomagnetic and solar wind conditions has not been extensively studied until the past decade.
+Models also exist for the plasmasphere density (\cite{Gallagher1988EmpiricalModelPlasmasphere}; \cite{LemaireEarthsPlasmasphere}).
+
+The dependence of the plasma trough density on geomagnetic and solar wind conditions has not been extensively studied until the past decade (\cite{Takahashi2006}; \cite{Takahashi2010}; \cite{Denton2016}).
+Earlier works that considered profiles of electron number density found a significant dependence on the plasmasphere boundary on geomagnetic activity, but there the relationship between geomagnetic activty and density in the plasma trough (\cite{Chappell1970}; \cite{Anderson1993}) was not explicitly considered.
+
+\cite{Lotoaniu1999PlasmaMassDensity} used measurements from the Plasma Wave Experiment instrument on the CRRES satellite and compared in-situ measured plasma mass density to that inferred by ground-based ULF wave measurements from the CANOPUS array.
+By extending the ground footprints to the plasmatrough, they found agreement between the two methods for certain plasmapause conditions.
+\vinote{More details}
 
 \cite{Takahashi2006} estimated magnetospheric mass density using measurements from the CRRES satellite during a 73-day period in 1991 (observations were made when CRRESS was in an elliptical, near equatorial orbit and primarily in the plasma trough region).
-They found that the average ion mass, $M=\rho/n_e$, had some correlation with geomagnetic activity, with more negative hourly $D_{st}$ values corresponding to higher $M$ and 1.5- and 3-day averages of $K_p$ corresponding to higher $M$ (3-hour averages of $K_p$had little visual correlation with $M$).
+They found that the average ion mass, $M=\rho/n_e$, had some correlation with geomagnetic activity, with more negative hourly $D_{st}$ values corresponding to higher $M$ and 1.5- and 3-day averages of $K_p$ corresponding to higher $M$ (3-hour averages of $K_p$ had little visual correlation with $M$).
 The mass density estimates were obtained from CRRES observations in the MLT range of 12:00 and 18:00 with most observations having L between 5 and 7 $R_E$.
 
-\cite{Denton2006} found a weak relationship between $D_{st}$ and and $K_p$ and the field line distribution of $\rho$ using observations of the first three toroidal Alfvén harmonic frequencies for $L$ in the range of 6-8$R_E$.
+\cite{Denton2006} found a weak relationship between $D_{st}$ and and $K_p$ and the field line distribution of $\rho$ using observations of the first three toroidal Alfv\'en harmonic frequencies for $L$ in the range of 6-8$R_E$.
 A more pronounced peak in the distribution along a filed line near the equator was found for lower $D_{st}$ and larger $K_p$.
@@
 \cite{Takahashi2010} developed a mass density dataset using measurements from the Space Environment Monitor instruments on the Geostationary Operational Environmental Satellites (GOES) satellites from 1980 through 1992, with most measurements in the range of $L=6.8\pm0.2 R_E$.
-The mass density $\rho$ was estimated using the the Alfv\'en wave velocity relationship, $V_A=B/\sqrt{\mu_0\rho}$, \vinote{Connect to harmonic toroidal frequency} a magnetic field model, and a numerical solution to a wave equation with an ionospheric boundary and the assumption of a zero resistance ionosphere.
+The mass density $\rho$ was estimated using the the Alfv\'en wave velocity relationship, $V_A=B/\sqrt{\mu_0\rho}$ a magnetic field model, and a numerical solution to a wave equation with an ionospheric boundary and the assumption of a zero resistance ionosphere.
 The equatorial mass density, $\rho_{eq}$, was derived from the estimated mass density using a power law dependence on the geocentric distance to the field line of the observation, $R$, $\rho=\rho_{eq}L/(R/R_E)$.
@@
 
-\cite{Yao2008} studied the relationship between $D_{st}$ and ion number density for low-energy $O^+$ in different regions (ring current and plasma sheet) using the TEAMS and ESA instruments on the low-altitude and high-inclination orbiting FAST satellite and found that the average $N_{O^+}$ across the sampled L-shells (2-14) had a strong correlation (0.88).
-Although the correlation in the plasma trough was not calculated, the data presented show that the variations in $N_{O^+}$ tended to appear near $D_{st}$ minimum ($\pm$ 2~hours).
+\cite{Yao2008} studied the relationship between $D_{st}$ and the number density of low-energy $O^+$ in different regions (ring current and plasma sheet) using the TEAMS and ESA instruments on the low-altitude and high-inclination orbiting FAST satellite and found that the average $N_{O^+}$ across the sampled L-shells (2-14) had a strong correlation (0.88) \vnote{With what?}.
+Although the correlation in the plasma trough was not calculated, the data presented \vnote{for X events} show that the variations in $N_{O^+}$ tended to appear near $D_{st}$ minimum ($\pm$ 2~hours).
 
-The results in the papers discussed indicate that (1) the mass density in the plasma trough region is best correlated with $F10.7$ and (2) there exists a correlation between mass density and the geomagnetic activity indices $K_p$ and $D_{st}$.
+\cite{Denton2016} ...
+
+The results in the papers discussed indicate that (1) the mass density in the plasma trough region is best correlated with $F10.7$ and (2) there exists a much weaker relationship between mass density and the geomagnetic activity indices $K_p$ and $D_{st}$.
 In this work we consider the dependence of mass density estimates in the \cite{Takahashi2010} and attempt to identify and statistically characterize the relationship between geomagnetic activity with mass density in the plasma trough region.
-In addition, we attempt to identify solar wind processes may drive changes in mass density.
+In addition, we attempt to identify solar wind processes that may drive changes in mass density.
 
 There are several issues that are addressed in detail: (1) the plasma density measurements are sparse, (2) The plasma trough density has a high correlation with F10.7, and geomagnetic and solar wind parameters also correlate with F10.7, (3) the dependence of mass density on the north/south component of the solar wind magnetic field is expected to be nonlinear.
-For northward IMF, corresponding tolow solar wind driving of the magnetosphere, the plasmasphere can expand past geosynchronous orbit where trough estimates of mass density are made resulting in an increase in observed density that are not due to solar wind driving; for southward IMF, events studies have shown an increase in mass density associated with strong southward IMF and enhanced magnetospheric activity [\cite{Takahashi2010}; \cite{Yao2008}].
+For northward IMF, corresponding to low solar wind driving of the magnetosphere, the plasmasphere can expand past geosynchronous orbit where trough estimates of mass density are made resulting in an increase in observed density that are not due to solar wind driving; for southward IMF, events studies have shown an increase in mass density associated with strong southward IMF and enhanced magnetospheric activity (\cite{Takahashi2010}; \cite{Yao2008}).
 
@@
 
---
-
-\cite{Gallagher1988EmpiricalModelPlasmasphere} used measurements from the Retarding Ion Mass Spectrometer onboard the Dynamics Explorer 1 satellite to model plasmasphere density using a relationship dependent on $L$ shell, altitude, geomagnetic latitude, and observations grouped by a weighted average of $K_p$.
-The developed statistical model showed significant improvements when a weighted average of $K_p$ over three days was used to group the observations used in the model.
-\note{Discuss plasma trough relevance}.
-
-\cite{Hamilton1988RingCurrentDevelopment} analyzed a strong geomagnetic storm and compared energy measurements of the ring current to $D_{st}$, along with measurements of ring current compositions before, during, and after the storm.
-They found $D_{st}$ to be correlated with the inner ring current energy density during and after storm onset, an inward movement of energy density, and a rapid $D_{st}$ recovery from the quick loss of heavier ions.
-
-\cite{Lotoaniu1999PlasmaMassDensity} used measurements from the Plasma Wave Experiment instrument on the CRRES satellite and compared in-situ measured plasma mass density to that inferred by ground-based ULF wave measurements from the CANOPUS array.
-By extending the ground footprints to the plasmatrough, they found agreement between the two methods for certain plasmapause conditions.
-\vinote{Mention specifics?
-Worth including paper?}
-
 \section{Data Preparation and Overview}
@@
 The smallest cadence for $\rho_{eq}$ values is 10 minutes.
-To compute an hourly average over the same interval for which the solar wind parameters were averaged, the median of all $\rho_{eq}$ values in a given hour window was used.
+To compute an hourly median over the same interval for which the solar wind parameters were averaged, the median of all $\rho_{eq}$ values in a given hour window was used.
 Fill (NaN) values were used for hours in which no measurements were available.
@@
 In this work, events are defined to occur when $D_{st}$ or $\rho_{eq}$ crosses a threshold value, as indicated by horizontal dashed lines in their respective panels of Figure~\ref{AllData}.
-\vinote{need to put line in \req\ plot.}
 
@@
 A scatter plot of these two lines is shown in the lower panel of Figure~\ref{ccplot}.
-The linear correlation for GOES 6 using all measurements is found to be $0.94$, which is the same value documented by \cite{Takahashi2010} who used measurements from all satellites in the time interval of 1980 through 1991 using the constraint $0600 \leq MLT \le 1200$, $K_{p3d}\ge1.0$ and $D_{st}\ge -50$~nT.
+The linear correlation for GOES 6 using all measurements is found to be $0.94$, which is the same value documented by \cite{Takahashi2010} who used measurements from all satellites in the time interval of 1980 through 1991 using the constraint $0600 \leq MLT \le 1200$, $K_{p3d}\ge1.0$ \vnote{define} and $D_{st}\ge -50$~nT.
 Our 27-day correlations for GOES 2, 5, and 7 are 0.81, 0.78, and 0.87, and the time range of coverage of measurements from these satellites are 1980-01-01/1983-05-16, 1983-01-01/1987-02-28, and 1983-05-27/1991-08-29 respectively.
@@
 It is expected that the plasmasphere will exhibit two responses near these threshold crossings.
-First is the movement of the plasmasphere earthward and the second is a possible increase in density due to magnetospheric processes \inote{cite}.
+First is the movement of the plasmasphere earthward (\cite{LemaireEarthsPlasmasphere}) and the second is a possible change in density due to magnetospheric processes.
 
 The second type of event is an increase in $\rho_{eq}$ above a threshold of 20~amu/cm$^3$.
-It is expected that these increases will typically occur after period of quiet geomagnetic activity that follow a geomagnetic storm.
-In this case, the plasmapause boundary may move outward past the measurement location and the increase will be due to measurements being made inside the plasmapause.
-A second possible reason for the increase could be due to the above-mentioned increase in due to magnetospheric processes.
+It is expected that these increases will typically occur after period of quiet geomagnetic activity.
+In this case, the plasmapause boundary may move outward past geosynchronous orbit and the increase will be due to measurements being made inside the plasmapause.
+A second possible reason for the increase could be due to magnetospheric processes.
 
@@
 For both types of events, the hour of the threshold crossing defines the zero epoch time, and for each event, $4\cdot24$ hours were considered before each event and $8\cdot24$ hours after each event.
-To compute the epoch averages on a daily time scale, the median value of all available measurements for all events centered on a window of $\pm 12$ hours of the epoch day was computed, and these averaging windows were shifted in increments of $24$~hours.
+To compute the epoch averages on a daily time scale, the median value of all available measurements for all events centered on a window of $\pm 12$ hours of the epoch zero hour was computed, and these averaging windows were shifted in increments of $24$~hours.
 Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians in 1-day bins and then compute the medians across events.
@@
 The minimum $D_{st}$ median is $-48$~nT.
-Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$, although the magnitude of increase observed here is $1.5$ amu/cm$^3$ (from 18 to 19.5~amu/cm$^3$) instead of the increase of $\sim 10$ amu/cm$^3$ found in \cite{Takahashi2010}.
+Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$, although the magnitude of increase observed here is $1.5$ amu/cm$^3$ (from 18 to 19.5~amu/cm$^3$) instead of the increase of $\sim 10$ amu/cm$^3$ found in Figure 11 of \cite{Takahashi2010}.
 The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute the medians and error bars.
@@
 
-Two types of events are considered. The first is a drop in $D_{st}$ below the threshold of $-40$~nT.  The second is an increase in $\rho_{eq}$ above $40$~amu/cm$^3$.
-
-Our first analysis uses data only from the time interval 1989-1991.
-In this interval, there were 329 $D_{st}$ events and 70 $\rho_{eq}$ events.
-For both types of events, the hour of the threshold crossing defines the zero epoch time, and for each event $8\cdot24$ hours were kept after each event and $4\cdot24$ hours before each event.
-To compute the epoch averages on a daily time scale, the median value of all measurements for all events centered window of $\pm 12$ hours was computed, and these windows were shifted in increments of $24$~hours.
-(Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians in 1-day bins and then compute the medians across events.)  Error bars for each parameter were computed using the standard deviation of values used in computing the median divided by the square root of the number of values used.
-
-In the upper panel of \ref{DailyAveragedDstEvents}, $D_{st}$ events are shown.
-The minimum $D_{st}$ median is $-48$~nT.
-Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$, although the magnitude of increase observed here is on the order of $\sim2$~amu/cm$^3$ instead of $\sim10$~amu/cm$^3$ found in \cite{Takahashi2010}.
-The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute its median and error bars.
-Note that for $D_{st}$, the number of measurements used in computing the medians is much larger as we use all available $D_{st}$ measurements instead of restricting to only values where a non-fill $\rho_{eq}$ value existed.
-
-Both of the results in \ref{DailyAveragedDstEvents} indicate that there is not a statistically significant change in $\rho_{eq}$ on the day before and day after a threshold crossing in $D_{st}$.
-
-Because the dynamics of the magnetosphere take place on a time scale of less than one day, we have also considered hourly averages as shown in the top panel of \ref{HourlyAveragedDstEvents}.
-A total of 668 events were found in the interval of May 1983 through August 1991 with an average duration of 9 hours and a median duration of 3 hours.
-The error bars were computed in the same way as \ref{DailyAveragedDstEvents}.
-In this plot, the overall trend is similar to that found in the bottom panel of \ref{HourlyAveragedDstEvents} - $\rho_{eq}$ is slightly elevated at the time of the threshold crossing of $D_{st}$ with respect to the values one day before and after, but the elevation is small and in general not statistically significant.
-
 The bottom panel of \ref{HourlyAveragedDstEvents} contains the events shown in the top panel under the constraint that $D_{st}$ remained below -50~nT for at least twelve hours after the event onset time.
-
-and the event study of \cite{Yao2008} which showed ...
 
@@
 
-\section{Appendix}
-\subsection{Bias}
-While attempting to reproduce Figure 11 from \cite{Takahashi2010}, an ambiguity in data-handling was found.
-It is unknown how they got from hourly $\rho_{eq}$ to daily medians, whether in one step or two steps, and whether the hourly medians are an hour ahead of each hour grid point, or a median of points a half hour to either side, so attempts were made to reproduce all possibilities and compare in order to find a data-handling method with the least bias.
-These attempts are shown in Figure \ref{blockmedian}.
-This also shows the effect of only considering events with a minimum before noon.
-All show a similar spike in $\rho_{eq}$ at the time of $D_{st}$ minimum, though none quite reproduce the exact values seen in \cite{Takahashi2010}.
-Figure \ref{allstorms} shows where the median falls for all of the found events during that period, as a sanity check for why the prior work would get median values nearing $30$~amu/cm$^3$.
-Both authors of this paper conducted independent trials to confirm that the data and analysis don't quite yield the results of Figure 11 in \cite{Takahashi2010} with the processes described in that paper, but the same general trend is still seen.
-
-To check for potential bias in the data as used by our analysis, we checked how the data availability varied with hour, shown in Figure \ref{nanperhour}.
-We also looked at how storm conditions affected data availability.
-Both a two sample t-test for difference in means and a Wilcoxon rank sum test showed significance at the 1\% level that $D_{st}$ during periods with available data was of a different distribution than $D_{st}$ during periods missing data.
-When testing for other significant $D_{st}$ differences, the Wilcoxon test was significant while the t-test was not in pre-noon vs post-noon distributions, as well as $\rho_{eq}>40$ vs $\rho_{eq}<40$ distributions indicating perhaps an increase in variability without an increase in mean.
-
-While the GOES Satellites tend to keep an average geostationary distance of around $L=6.8R_E$ shown in \cite{Takahashi2010}, the actual plasmapause location varies significantly, as shown in \cite{OBrien2003}.
-This means that during periods of large $D_{st}$ the plasmapause may be far from the point of measurement of $\rho_{eq}$ creating a discord in the correlation.
-\cite{Gallagher2000} provides a model for $\rho_{eq}$ at a range of L-shells and a brief discussion of the elemental contributions.
-
 \newpage
@@
 \includegraphics[scale=0.45]{paperfigures/alldata-GOES6-1983-1991.eps}
-\caption{Overview of data used in this study.
+\caption{Overview of data used in this article.
 The top four panels show parameters from \cite{Kondrashov2014ReconstructionOfGaps} and the bottom panel contains $\rho_{eq}$ based on GOES 6 measurements from \cite{Denton} after interpolation and averaging described in the text.
-Dashed horizontal lines in the $D_{st}$ and $\rho_{eq}$ panels indicate sample event cutoff thresholds of $D_{st} = -50$~nT and $\rho_{eq} = 20$~amu/cm$^3$}.
+Dashed horizontal lines in the $D_{st}$ and $\rho_{eq}$ panels indicate sample event cutoff thresholds of $D_{st} = -50$~nT and $\rho_{eq} = 20$~amu/cm$^3$} considered in Section~3.
 \label{AllData}
@@
 \includegraphics[scale=0.40]{paperfigures/ccplot-GOES6.eps}
-\caption{Top: 27-day medians of $F_{10.7}$ and $\rho_{eq}$ from GOES 6.
-Bottom: Correlation between $\log(\rho_{eq})$ and $F_{10.7}$ using medians in hour, day, and 27-day non-overlapping; compare to \cite{Takahashi2010} Fig.~14.}
+\caption{Top: 27-day non-overlapping medians of $F_{10.7}$ and $\log(\rho_{eq})$ from GOES 6.
+Bottom: Correlation between $\log(\rho_{eq})$ and $F_{10.7}$ using medians in non-overlapping hour, day, and 27-day windows.}
 \label{ccplot}
@@
 
-\clearpage
-
-\begin{figure}[tp!]
-\centering
-\includegraphics[scale=0.40]{paperfigures/HighLowF107rhoeq.eps}
-\includegraphics[scale=0.40]{paperfigures/HighLowF107Bz.eps}
-\includegraphics[scale=0.40]{paperfigures/HighLowF107valid.eps}
-\caption{Binning events by $F_{10.7}$ value at onset for $\rho_{eq}$ and, in the middle panel, $B_z$. Lower panel shows number of valid points in each bin}
-\label{f107bin}
-\end{figure}
-
-\clearpage
-
-\section{Appendix}
-\hfill
-
-\begin{figure}[htp!]
-\centering
-\includegraphics[scale=0.40]{paperfigures/stormavs-d80.eps}
-\rule[1ex]{5cm}{1pt}
-\caption{(a) Same as Figure \ref{HourlyAveragedDstEvents}(a) except with constraint that $D_{st}$ crossed below $-80$~nT }
-\label{Dspec}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[htp!]
-\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES6-1983-1991.eps}
-\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES7-1987-1991.eps}
-\caption{GOES Satellite 6 and 7}
-\label{GOES67}
-\end{figure}
-
-\begin{figure}[htp!]
-\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES2-1981-1983.eps}
-\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES5-1983-1987.eps}
-\caption{GOES Satellite 2 and 5}
-\label{GOES25}
-\end{figure}
-\clearpage
-
-\begin{figure}[htp!]
-\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES6-1989-1991.eps}
-\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst80.eps}
-\caption{Top: GOES 6 from 89-91 (compare to Takahashi 2010). Bottom:  $D_{st}<-80$~nT.}
-\end{figure}
-
-\begin{figure}[htp!]
-\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES6-1983-1987.eps}
-\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES6-1987-1991.eps}
-\caption{GOES 6 from 83-87 and 87-91}
-\end{figure}
-\clearpage
-
-\hfill
-\begin{figure}[htp!]
-\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst30.eps}
-\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst30-valid.eps}
-\caption{$D_{st} < -30$ nT events, $\rho_{eq}$ binned by $F_{10.7}$. Lower panel: valid hourly points}
-\end{figure}
-\hfill
-\begin{figure}[htp!]
-\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-rhoeq40.eps}
-\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-rhoeq40-valid.eps}
-\caption{$\rho_{eq} > 40$ amu/cm$^3$ events, $\rho_{eq}$ binned by $F_{10.7}$}
-\end{figure}
-\clearpage
-
-\begin{figure}[htp!]
-\includegraphics[scale=0.40]{paperfigures/HighLowF107rhoeq-AE300.eps}
-\includegraphics[scale=0.40]{paperfigures/HighLowF107rhoeq-AE300-valid.eps}
-\includegraphics[scale=0.35]{paperfigures/stormavs-AE.eps}
-\caption{Top: $AE > 400$ nT events, $\rho_{eq}$ binned by $F_{10.7}$ Bottom: averages of $AE > 400$ events}
-\end{figure}
-\hfill
-\begin{figure}[htp!]
-\includegraphics[scale=0.45]{paperfigures/HighLowDstrhoeq-AE400.eps}
-\includegraphics[scale=0.45]{paperfigures/HighLowDstrhoeq-Dst50.eps}
-\caption{Top: $AE > 400$ nT events. Bottom: $D_{st} < -50$ nT events. Both $\rho_{eq}$ binned by $D_{st}$.}
-\end{figure}
-\clearpage
-
-\begin{figure}[htp!]
-\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-random.eps}
-\includegraphics[scale=0.45]{paperfigures/stormavs-random.eps}
-\caption{Top: $\rho_{eq}$ binned by $F_{10.7}$ for randomly selected times. Bottom: averages of randomly selected times}
-\end{figure}
-
-\begin{figure}[htp!]
-\includegraphics[scale=0.45]{paperfigures/HighLowDstBz-Dst50.eps}
-\includegraphics[scale=0.45]{paperfigures/HighLowDstBz-AE400.eps}
-\caption{Top: $B_z$ binned by $D_{st}$ for $D_{st} < -50$ nT events. Bottom: $B_z$ binned by $D_{st}$ for $AE > 400$ nT events}
-\end{figure}
-\clearpage
-
-\begin{figure}[htp!]
-\includegraphics[scale=0.45]{paperfigures/rhoMLT.eps}
-\includegraphics[scale=0.45]{paperfigures/rhoLT.eps}
-\caption{Median $\rho_{eq}$ vs magnetic local time and universal time}
-\end{figure}
-
-\begin{figure}[htp!]
-\includegraphics[scale=0.45]{paperfigures/DstLT.eps}
-\includegraphics[scale=0.45]{paperfigures/AELT.eps}
-\caption{Median $D_{st}$ vs universal time, and median AE vs universal time}
-\end{figure}
-\clearpage
-
-\newpage
-\input{"tables/CCperltable.tex"}
-
 \end{document}

### 2016-05-11 paper.tex
Re-adding hidden figures

@@
 A scatter plot of these two lines is shown in the lower panel of Figure~\ref{ccplot}.
-The linear correlation for GOES 6 using all measurements is found to be $0.94$, which is the same value documented by \cite{Takahashi2010} who used measurements from all satellites in the time interval of 1980 through 1991 using the constraint $0600 \leq MLT \le 1200$, $K_{p3d}\ge1.0$ \vnote{define} and $D_{st}\ge -50$~nT.
+The linear correlation for GOES 6 using all measurements is found to be $0.94$, which is the same value documented by \cite{Takahashi2010} who used measurements from all satellites in the time interval of 1980 through 1991 using the constraint $0600 \leq MLT \le 1200$, $K_{p3d}\ge1.0$ and $D_{st}\ge -50$~nT.
 Our 27-day correlations for GOES 2, 5, and 7 are 0.81, 0.78, and 0.87, and the time range of coverage of measurements from these satellites are 1980-01-01/1983-05-16, 1983-01-01/1987-02-28, and 1983-05-27/1991-08-29 respectively.

### 2016-05-12 paper/paper.tex
Mass reorganization

--- 2016-05-11 paper.tex
@@
 
-\cite{Yao2008} studied the relationship between $D_{st}$ and the number density of low-energy $O^+$ in different regions (ring current and plasma sheet) using the TEAMS and ESA instruments on the low-altitude and high-inclination orbiting FAST satellite and found that the average $N_{O^+}$ across the sampled L-shells (2-14) had a strong correlation (0.88) \vnote{With what?}.
-Although the correlation in the plasma trough was not calculated, the data presented \vnote{for X events} show that the variations in $N_{O^+}$ tended to appear near $D_{st}$ minimum ($\pm$ 2~hours).
+\cite{Yao2008} studied the relationship between $D_{st}$ and the number density of low-energy $O^+$ in different regions (ring current and plasma sheet) using the TEAMS and ESA instruments on the low-altitude and high-inclination orbiting FAST satellite and found that the average $N_{O^+}$ across the sampled L-shells (2-14) had a strong correlation (0.88) \inote{With what?}.
+Although the correlation in the plasma trough was not calculated, the data presented \inote{for X events} show that the variations in $N_{O^+}$ tended to appear near $D_{st}$ minimum ($\pm$ 2~hours).
 

### 2016-05-12 BasicPlots.m

@@ -10,8 +10,8 @@ if(MakePaperPlots && stormcase==1)
     ylabel('Median \rho_{eq} (amu/cm^3)')
     xlabel('MLT (hour)')
     set(findobj('type','axes'),'xgrid','on','ygrid','on','box','on','xtick',[0:2:24])
-    print -depsc2 -r200 paperfigures/rhoMLT.eps
-    print -dpng -r200 paperfigures/PNGs/rhoMLT.png
+    print -depsc2 -r200 figures/rhoMLT.eps
+    print -dpng -r200 figures/PNGs/rhoMLT.png
     if(strcmp(visible,'off')),close(h);end;
     
     [~,~,~,DHr]=datevec(DentonTime);
@@ -23,8 +23,8 @@ if(MakePaperPlots && stormcase==1)
     ylabel('Median \rho_{eq} (amu/cm^3)')
     xlabel('Local Time (hour)')
     set(findobj('type','axes'),'xgrid','on','ygrid','on','box','on','xtick',[0:4:23])
-    print -depsc2 -r200 paperfigures/rhoLT.eps
-    print -dpng -r200 paperfigures/PNGs/rhoLT.png
+    print -depsc2 -r200 figures/rhoLT.eps
+    print -dpng -r200 figures/PNGs/rhoLT.png
     if(strcmp(visible,'off')),close(h);end;
     
     for i=1:24
@@ -35,8 +35,8 @@ if(MakePaperPlots && stormcase==1)
     ylabel('Median AE (nT)')
     xlabel('Local Time (hour)')
     set(findobj('type','axes'),'xgrid','on','ygrid','on','box','on','xtick',[0:4:23])
-    print -depsc2 -r200 paperfigures/AELT.eps
-    print -dpng -r200 paperfigures/PNGs/AELT.png
+    print -depsc2 -r200 figures/AELT.eps
+    print -dpng -r200 figures/PNGs/AELT.png
     if(strcmp(visible,'off')),close(h);end;
     
     for i=1:24
@@ -47,8 +47,8 @@ if(MakePaperPlots && stormcase==1)
     ylabel('Median D_{st} (nT)')
     xlabel('Local Time (hour)')
     set(findobj('type','axes'),'xgrid','on','ygrid','on','box','on','xtick',[0:4:23])
-    print -depsc2 -r200 paperfigures/DstLT.eps
-    print -dpng -r200 paperfigures/PNGs/DstLT.png
+    print -depsc2 -r200 figures/DstLT.eps
[…]

### 2016-05-12 ComplexPlots.m

@@ -13,8 +13,8 @@ if(MakePaperPlots && stormcase==1)
     xa=(-timewidth:LongTimeScale:timewidth*2);
     plot(xa,AVMDs(1,:),'r','LineWidth',3);
     hold on; plot(xa,AVMDMatBars(:,:),'r-.','LineWidth',2);
-    print -depsc2 -r200 paperfigures/allstorms.eps
-    print -dpng -r200 paperfigures/PNGs/allstorms.png    
+    print -depsc2 -r200 figures/allstorms.eps
+    print -dpng -r200 figures/PNGs/allstorms.png    
     if(strcmp(visible,'off')),close(h);end;
     
 end
@@ -24,53 +24,55 @@ if(MakePaperPlots && stormcase==26) %KP Stack plot
 end
 
 if(MakePaperPlots && (stormcase==2 || stormcase==24 || stormcase==1)) 
-    tw=20:25;
-    
-    topcut=nanmedian(nanmedian(AVMat(:,tw,5),2));
-    bottomcut=nanmedian(nanmedian(AVMat(:,tw,5),2));
-    h=figure('Visible',visible);   
-    top=nanmedian(AVMDMat(nanmedian(AVMat(:,tw,5),2)>=topcut,:));
-    bottom=nanmedian(AVMDMat(nanmedian(AVMat(:,tw,5),2)<bottomcut,:));
-    topbar=nanstd(AVMDMat(nanmedian(AVMat(:,tw,5),2)>=topcut,:))./sqrt(sum(~isnan(AVMDMat(nanmedian(AVMat(:,tw,5),2)>=topcut,:))));
-    bottombar=nanstd(AVMDMat(nanmedian(AVMat(:,tw,5),2)<bottomcut,:))./sqrt(sum(~isnan(AVMDMat(nanmedian(AVMat(:,tw,5),2)<bottomcut,:))));
-    tvals=ttest2(AVMDMat(nanmedian(AVMat(:,tw,5),2)>=topcut,:),AVMDMat(nanmedian(AVMat(:,tw,5),2)<bottomcut,:));
-    tvals(tvals==0)=NaN;
-    %{
-    for i=1:length(AVMDMat(1,:))
-        top(i)=nanmean(AVMDMat(AVMat(:,i,5)>0,i));
-        topbar(i)=nanstd(AVMDMat(AVMat(:,i,5)>0,i));
[…]

### 2016-05-12 Density.m

@@ -56,7 +56,7 @@ MDCut=0;
 AECut=0;
 nnanalysis=0; %Also set 0 here, changed on per-case basis.
 ccanalysis=0;
-figurename='paperfigures/stormavs-';
+figurename='paper/figures/stormavs-';
 BigFont=16; %Set size for larger, readable fonts
 
 %Select kind of storm to look for
@@ -221,7 +221,6 @@ switch stormcase
         figurename=strcat(figurename,'mass-gt20',sprintf('-GOES%d.eps',satnum));
         yr=5;
         yranges(5,:,:)=[-2 2; 350 550; -60 0; 150 230; 10 30];
-        MakeBinPlots=1;
     case 25 %Specifically for 27 day F10.7 vs mass density plot
         storms=diff([0 (FILLED(:,15)<-50)' 0]); %DST Storm
         DSTCut=-50;

### 2016-05-12 binplot.m

@@ -42,8 +42,8 @@ set(findobj('type','axes'),'xgrid','on','ygrid','on','box','on','xtick',[-timewi
 [~,objh]=legend(sprintf('%s>%2.0f',sortname,highsplit),sprintf('%2.0f>%s>%2.0f',highsplit,sortname,medsplit),sprintf('%2.0f>%s>%2.0f',medsplit,sortname,lowsplit),sprintf('%2.0f>%s',lowsplit,sortname),'Location','NorthEast');
 set(objh,'linewidth',2);
 title(sprintf('%d evenly-binned events of %s %s (%s) for GOES%d: %d-%d',length(events),eventname,plotthresh,eventunits,satnum,timerange(1),timerange(2)))
-print('-depsc2','-r200',sprintf('paperfigures/HighLow%s%s-%s%s-GOES%d-%d-%d.eps',safesortname,safeplotname,safeeventname,safethresh,satnum,timerange(1),timerange(2)))
-print('-dpng','-r200',sprintf('paperfigures/PNGs/HighLow%s%s-%s%s-GOES%d-%d-%d.png',safesortname,safeplotname,safeeventname,safethresh,satnum,timerange(1),timerange(2)))
+print('-depsc2','-r200',sprintf('figures/HighLow%s%s-%s%s-GOES%d-%d-%d.eps',safesortname,safeplotname,safeeventname,safethresh,satnum,timerange(1),timerange(2)))
+print('-dpng','-r200',sprintf('figures/PNGs/HighLow%s%s-%s%s-GOES%d-%d-%d.png',safesortname,safeplotname,safeeventname,safethresh,satnum,timerange(1),timerange(2)))
 if(strcmp(visible,'off')),close(h);end;
 
 if(sum(sum(isnan(plotter)))) %If any nan points
@@ -60,7 +60,7 @@ if(sum(sum(isnan(plotter)))) %If any nan points
     title(sprintf('%d evenly-binned events of %s %s (%s) for GOES%d: %d-%d',length(events),eventname,plotthresh,eventunits,satnum,timerange(1),timerange(2)))
     axis tight;
     set(findobj('type','axes'),'xgrid','on','ygrid','on','box','on','xtick',[-timewidth:timewidth/2:timewidth*2]./LongTimeScale)
[…]

### 2016-05-12 paperfigures.m

@@ -1,0 +1,8 @@
+function paperfigures
+
+Density(1,6) %alldata, ccplot, stormavs-dst, F107MD27d
+Density(24,6) %RhoBinned case24
+Density(10,6) %dst-50-tak
+Density(5,6) %dd12
+Density(13,6) %dst-day
+Density(24,6) %mass-gt20

### 2016-05-12 stackplot.m

@@ -58,5 +58,5 @@ xlabel('Time','FontSize',14)
 sy=year(Time(1));
 ey=year(Time(end));
 %print('-depsc2',sprintf('paperfigures/alldata-GOES%d-%d-%d.eps',satnum,sy,ey));
-print('-depsc2','-r300',sprintf('paperfigures/alldata-GOES%d-%d-%d.eps',satnum,sy,ey));
-print('-dpng','-r200',sprintf('paperfigures/PNGs/alldata-GOES%d-%d-%d.png',satnum,sy,ey));
+print('-depsc2','-r300',sprintf('paper/figures/alldata-GOES%d-%d-%d.eps',satnum,sy,ey));
+print('-dpng','-r200',sprintf('paper/figures/PNGs/alldata-GOES%d-%d-%d.png',satnum,sy,ey));

### 2016-05-12 Density.m
Storing for merge

@@ -238,6 +238,11 @@ switch stormcase
         figurename=strcat(figurename,'dst',sprintf('-GOES%d.eps',satnum));
         yr=2;
         MakeBinPlots=1;
+    case 28 %For making specific stack plots of events (i.e. alldata-* plots with specific cuttimes)
+        storms=diff([0 (FILLED(:,15)<-50)' 0]); %DST Storm
+        DSTCut=-50;
+        figurename=strcat(figurename,'dst',sprintf('-GOES%d.eps',satnum));
+        yr=2;
         
 end
 

### 2016-05-12 stackplot.m

@@ -57,6 +57,14 @@ xlabel('Time','FontSize',14)
 
 sy=year(Time(1));
 ey=year(Time(end));
+
+if(sy ~= ey)
 %print('-depsc2',sprintf('paperfigures/alldata-GOES%d-%d-%d.eps',satnum,sy,ey));
 print('-depsc2','-r300',sprintf('paperfigures/alldata-GOES%d-%d-%d.eps',satnum,sy,ey));
 print('-dpng','-r200',sprintf('paperfigures/PNGs/alldata-GOES%d-%d-%d.png',satnum,sy,ey));
+else
+    sy=datestr(Time(1),'ddmmmyyyy');
+    ey=datestr(Time(end),'ddmmmyyyy');
+    print('-depsc2','-r300',sprintf('paperfigures/alldata-GOES%d-%s-%s.eps',satnum,sy,ey));
+    print('-dpng','-r200',sprintf('paperfigures/PNGs/alldata-GOES%d-%s-%s.png',satnum,sy,ey));
+end

### 2016-05-12 paper/paper.tex

@@
 \centering
-\includegraphics[scale=0.45]{paperfigures/alldata-GOES6-1983-1991.eps}
+\includegraphics[scale=0.45]{figures/alldata-GOES6-1983-1991.eps}
 \caption{Overview of data used in this article.
@@
 \centering
-\includegraphics[scale=0.40]{paperfigures/F107MD27d-GOES6.eps}
-\includegraphics[scale=0.40]{paperfigures/ccplot-GOES6.eps}
+\includegraphics[scale=0.40]{figures/F107MD27d-GOES6.eps}
+\includegraphics[scale=0.40]{figures/ccplot-GOES6.eps}
 \caption{Top: 27-day non-overlapping medians of $F_{10.7}$ and $\log(\rho_{eq})$ from GOES 6.
@@
 \centering
-\includegraphics[scale=0.40]{paperfigures/stormavs-dst-50-tak-GOES6.eps}
+\includegraphics[scale=0.40]{figures/stormavs-dst-50-tak-GOES6.eps}
 \rule[1ex]{5cm}{1pt}
-\includegraphics[scale=0.40]{paperfigures/stormavs-dst-day-GOES6.eps}
+\includegraphics[scale=0.40]{figures/stormavs-dst-day-GOES6.eps}
 \caption{$D_{st}$ events from GOES 6 using daily medians. Top: Events in the interval 1989-1991; compare to \cite{Takahashi2010} Fig.~11. Bottom: Events in the interval 1983-1991.}
@@
 \centering
-\includegraphics[scale=0.40]{paperfigures/stormavs-dst.eps}
+\includegraphics[scale=0.40]{figures/stormavs-dst.eps}
 \rule[1ex]{5cm}{1pt}
-\includegraphics[scale=0.40]{paperfigures/stormavs-dd12-GOES6.eps}
+\includegraphics[scale=0.40]{figures/stormavs-dd12-GOES6.eps}
 \caption{$D_{st}$ events from GOES 6 using hourly medians.
@@
 \centering
-\includegraphics[scale=0.40]{paperfigures/stormavs-mass-gt20-GOES6.eps}
+\includegraphics[scale=0.40]{figures/stormavs-mass-gt20-GOES6.eps}
 \caption{$\req\ > 20$~ amu/cm$^3$ events from GOES 6 using hourly medians.
@@
 	\centering
-	\includegraphics[scale=0.40]{paperfigures/RhoBinnedBz-case24-t020-tf25-GOES6.eps}
-	\includegraphics[scale=0.40]{paperfigures/RhoBinnedBz-case24-t025-tf30-GOES6.eps}
+	\includegraphics[scale=0.40]{figures/RhoBinnedBz-case24-t020-tf25-GOES6.eps}
+	\includegraphics[scale=0.40]{figures/RhoBinnedBz-case24-t025-tf30-GOES6.eps}
 	\caption{Binning \req\ events by $B_z$ value (a) at onset and four hours before, and (b) at onset and four hours after.}

### 2016-05-13 paper/paper.tex
Papper edits

@@
 \begin{document}
-\title{Relationship between solar wind, $D_{st}$, and plasmasphere trough mass density on one-hour time scales}
+\title{Solar wind and geomagnetic activity influence on the equatorial plasma mass density at geosynchronous orbit}
 \author{
@@
 \begin{abstract}
-This paper compares various magnetosphere conditions around the onset of geomagnetic events, defined as decreases in $D_{st}$ below a threshold value or $\rho_{eq}$ above a threshold value.
-
+In this work we consider two types of events, determined by decreases in $D_{st}$ below a threshold value or increases in the $\rho_{eq}$ above a threshold value on 1-hour and 1-day time scales using the \cite{Denton2007} dataset.
+From the $D_{st}$ events, we find that there is no statistically significant relationship between either solar wind or geomagnetic activity under conditions of strong geomagnetic activity when hourly or daily averages of $\rho_{eq}$ are considered.
+Although very large geomagnetic storms have been observed to correspond to large increases in the plasma trough mass density, in general $\rho_{eq}$ following the onset of a geomagnetic storm does not depend on the storm intensity or the solar wind parameters $B_{z}$ and $P_{dyn}$.
+From the $\rho_{eq}$ events, we find a weak dependence on $B_{z}$ after the onset of an event, with higher average $B_{z}$ six hours after the event onset corresponding to larger $\rho_{eq}$ events.
 \vspace{2em}
 \end{abstract}
+\hrule
  \end{@twocolumnfalse}
@@
 The dependence of the plasma trough density on geomagnetic and solar wind conditions has not been extensively studied until the past decade (\cite{Takahashi2006}; \cite{Takahashi2010}; \cite{Denton2016}).
-Earlier works that considered profiles of electron number density found a significant dependence on the plasmasphere boundary on geomagnetic activity, but there the relationship between geomagnetic activty and density in the plasma trough (\cite{Chappell1970}; \cite{Anderson1993}) was not explicitly considered.
-
-\cite{Lotoaniu1999PlasmaMassDensity} used measurements from the Plasma Wave Experiment instrument on the CRRES satellite and compared in-situ measured plasma mass density to that inferred by ground-based ULF wave measurements from the CANOPUS array.
-By extending the ground footprints to the plasmatrough, they found agreement between the two methods for certain plasmapause conditions.
-\vinote{More details}
+Earlier works that considered profiles of electron number density found a significant dependence on the plasmasphere boundary on geomagnetic activity (\cite{Chappell1970}; \cite{Anderson1993}), but there the relationship between geomagnetic activity and density in the plasma trough was not explicitly considered.
 
@@
 
-\cite{Yao2008} studied the relationship between $D_{st}$ and the number density of low-energy $O^+$ in different regions (ring current and plasma sheet) using the TEAMS and ESA instruments on the low-altitude and high-inclination orbiting FAST satellite and found that the average $N_{O^+}$ across the sampled L-shells (2-14) had a strong correlation (0.88) \inote{With what?}.
-Although the correlation in the plasma trough was not calculated, the data presented \inote{for X events} show that the variations in $N_{O^+}$ tended to appear near $D_{st}$ minimum ($\pm$ 2~hours).
+\cite{Yao2008} studied the relationship between $D_{st}$ and the number density of low-energy $O^+$ in different regions (ring current and plasma sheet) using the TEAMS and ESA instruments on the low-altitude and high-inclination orbiting FAST satellite and found that the average $N_{O^+}$ across the sampled L-shells (2-14) had a strong correlation (0.88) with the minimum $D_{st}$ of the storm.
+Although the correlation in the plasma trough was not calculated, the data presented for four events show that the variations in $N_{O^+}$ tended to appear near $D_{st}$ minimum ($\pm$ 2~hours).
 
@@
 Issue (1) is addressed by considering in detail the number of observations that are used in epoch averages around the time of two types of events, decreases in $D_{st}$ below a threshold, and increases in $\rho_{eq}$ above a threshold.
-Issue (2) is addressed using various methods to remove or isolate the F10.7 dependences.
+Issue (2) is addressed using various methods to remove or isolate the F10.7 dependence.
 Issue (3) is addressed by considering epochs and linear correlations independent of the direction of the IMF along with separation of the epoch averages based on the northward and southward IMF.
@@
 To determine if the magnitude of the density medians on a given day were statistically different than another day, we used a two-population t-test.
-For the interval of 1989-1991, corresponding to the top panel of \ref{DailyAveragedDstEvents}, the null hypothesis that any of the medians from days -1, 0, and 1 are different from each other is rejected with a maximimum p value of \vnote{??}.
+For the interval of 1989-1991, corresponding to the top panel of \ref{DailyAveragedDstEvents}, the null hypothesis that any of the medians from days -1, 0, and 1 are different from each other is rejected with a maximum p value of.
+The results are shown in Table~\ref{Table1}.
+
+These tests indicate that there is not a statistically significant change in medians of $\rho_{eq}$ on the day before and day after a threshold crossing in $D_{st}$.
 
@@
 
-Both of the results in \ref{DailyAveragedDstEvents} indicate that there is not a statictically significant change in medians of $\rho_{eq}$ on the day before and day after a threshold crossing in $D_{st}$.
-
-Because the dynamics of the magnetopshere take place on a time scale of less than one day, we have also considered hourly averages as shown in the top panel of \ref{HourlyAveragedDstEvents}.
+Because the dynamics of the magnetopshere take place on a time scale of less than one day, we have also considered hourly averages as shown in the top panel of Fig.~\ref{HourlyAveragedDstEvents}.
 A total of 668 events were found in the interval of May 1983 through August 1991 with an average duration of 9 hours and a median duration of 3 hours.
-The error bars were computed in the same way as \ref{DailyAveragedDstEvents}.
-In this plot, the overall trend is similar to that found in the bottom panel of \ref{HourlyAveragedDstEvents} - $\rho_{eq}$ is slighly elevated at the time of the threhshold crossing of $D_{st}$ with respect to the values one day before and after, but the elevation is small and in general not statistically significant.
+The error bars were computed in the same way as Fig.~\ref{DailyAveragedDstEvents}.
+In this plot, the overall trend is similar to that found in the bottom panel of Fig.~\ref{HourlyAveragedDstEvents} - $\rho_{eq}$ is slightly elevated at the time of the threshold crossing of $D_{st}$ with respect to the values one day before and after, but the elevation is small and in general not statistically significant.
 At this timescale no obvious change in mass density at hourly timescale is visible.
@@
 
-Results of test on different between means of $\rho_{eq}$ shown in the bottom panel of \ref{DailyAverage} on days near or on the day of a $D_{st}$ event.
-
-It was found that $\rho_{eq}$ enhancements do not clearly correspond to a signature in $D_{st}$, but that there is a trend for such enhancements to occur when $B_{z}$ in the IMF is positive.
-This is consistent with \cite{Takahashi2010} who note that very large increases in $\rho_{eq}$ often corresponded to movement of the plasmasphere to beyond geosynchronous distances.
-
-This method finds 669 periods of $D_{st}$ crossing beneath the selected threshold between May 1983 and August 1991 with an average duration of 9 hours and a median duration of 3 hours \vinote{Make sure I defined "duration"}.
-Figure \ref{HourlyAveragedDstEvents} shows the average values of all events over a window of 24 hours before onset and 48 hours after.
-Figure \ref{HourlyAveragedDstEvents}a shows events selected by looking for event onsets where $D_{st}$ crossed a threshold of $-40$~nT.
-The dashed red lines indicate plus and minus one standard deviation of values from all events that were used to compute the median.
-The final plot in the stack shows both $\rho_{eq}$ and a bar plot of how many valid data points went into the $\rho_{eq}$ average.
-Since $\rho_{eq}$ comes from a sparser dataset, it has less valid points contributing to the averages than the other parameters in the stack.
-
-Figure \ref{HourlyAveragedDstEvents} shows a definite spike in the $Z$ component of the magnetic field, as well as the defined drop in $D_{st}$, but no obvious change in mass density at an hourly timescale.
-This points to an issue with only looking at long-timescale trends between density and $D_{st}$, and allows for the possibility that other factors are influencing the long term correlation since there's no obvious connection on a short timescale.
-One possibility is that, as suggested in \cite{Takahashi2010}, $F_{10.7}$ plays a significant role in driving long term density values which biases the long term correlation of density and $D_{st}$.
-
-The bottom panel of \ref{HourlyAveragedDstEvents} contains the events shown in the top panel under the constraint that $D_{st}$ remained below -50~nT for at least twelve hours after the event onset time.
+The bottom panel of Fig.~\ref{HourlyAveragedDstEvents} contains the events shown in the top panel under the constraint that $D_{st}$ remained below -50~nT for at least twelve hours after the event onset time.
+In the time period of elevated mass density within 12 hours of the start of the event, there were an average of \inote{X} samples per hourly interval.
+This result is consistent with previous observations of large mass density spikes in the plasma trough region during large geomagnetic storms (\cite{Yao2008}; \cite{Takahashi2010} and the observation that solar wind parameters have very little correlation independent of $F_{10.7}$ (\cite{Denton2016}).
+To determine of this relationship can be observed in the events of the top panel of Fig.~\ref{HourlyAveragedDstEvents}, we sorted the events by the average $D_{st}$ values in the time interval of 0-12 hours, split the events in two and recomputed the epoch averages of $\rho_{eq}$.
+The result is that there is no statistically significant difference in the mass density epoch averages for large versus small storms.
+This indicates that to confirm the $\rho_{eq}$ dependence on large geomagnetic storms would require a dataset with a much larger number of strong geomagnetic storms.
 
@@
 
-An alterntive type of event can be defined that corresponds to large increases in $\rho\ $.
+An alternative type of event can be defined that corresponds to large increases in $\rho\ $.
+Figure~\ref{HourlyAveragedRhoEvents} shows the epoch time series for events in which an increase of $\req\ $ above $20$~amu/cm$^2$ defines the start of the event.
 In finding $\rho_{eq}$ events, all fill values were replaced with linearly interpolated values.
@@
 
-Figure~\ref{HourlyAveragedRhoEvents} shows the epoch time series for events in which an increase of $\req\ $ above $20$~amu/cm$^2$ defines the start of the event.
-Here we see the expected result that such events tend to be associated with positive $B_z^{IMF}$.
+Here we see that such events tend to be associated with positive $B_z^{IMF}$ and low geomagnetic activity (\cite{Denton2016}).
+
 To determine if the sign of $B_z^{IMF}$ influences the $\rho\ $ epoch time series, we separated the events by the average of $B_z^{IMF}$ in a time window of $4$~hours.
 
-Figure~\label{fig:RhoBinned}(a) shows the 
-The epoch curves for $B_z^{IMF}\geq=0$ (257) events and $B_z^{IMF}\ge=0$ (139) have no statistically signifiant difference.
+Figure~\label{fig:RhoBinned}(a) shows the epoch curves for $B_z^{IMF}\geq=0$ (257) events and $B_z^{IMF}\ge=0$ (139) have no statistically significant difference.
 
-\section{F10.7 dependence}
-In an effort to analyze the dependence of $\rho_{eq}$ on $F_{10.7}$, a few tests were performed.
-\cite{Takahashi2010} mention a strong correlation between the two.
-The long term correlation could be a bias for $D_{st}$'s effects, so a linear model was created, recreating mass density purely from $F_{10.7}$ in the form of $\rho_{eq}(t)=a\cdot F_{10.7}(t)$.
-This re-created $\rho_{eq}$ shows around a 45\% correlation with the actual $\rho_{eq}$, suggesting a strong influence, while doing the same procedure with $D_{st}$ shows only a 20-25\% correlation.
-
-Figure \ref{f107bin} takes the events and bins them by the value of $F_{10.7}$ at event onset, then looks at both $\rho_{eq}$ and $B_z$.
-Error bars calculated in the same manner as before are added to the highest and lowest bins.
-A significant difference is seen in $\rho_{eq}$ between events taking place during periods of high $F_{10.7}$ and low $F_{10.7}$, while a much less significant, but still noticeable, difference is seen in $B_z$.
-Also of interest is how $\rho_{eq}$ only sharply reacts to $D_{st}$ events during periods of high $F_{10.7}$.
-The positive relationship seen in \cite{Takahashi2010} could be due to the short time period looked at, and that it coincides with periods of higher $F_{10.7}$.
-
-Looking at GOES 2,5,6, and 7 shows that this post-onset $D_{st}$ spike happens in almost every case for periods of high $F_{10.7}$.
-Creating a linear model directly relating variables (and combinations of variables) to $\rho_{eq}$ also shows that $F_{10.7}$ most often has the highest correlation with $\rho_{eq}$.
-A sample of these correlations is shown in Table \ref{perltable}.
-The correlations were made by training a one-input linear model of 5-hour post-onset medians of each variable (or variables) against the median of $\rho_{eq}$ at, and four hours after, event onset.
-This was done by randomly sampling half of the data, generating the model, and testing against the other half, doing this process 100 times and then taking the median correlations.
+\subsection{Conclusions}
 
@@
 \caption{$D_{st}$ events from GOES 6 using hourly medians.
-Top: Events in the interval 1983-1991; compare to bottom panel {DailyAveragedDstEvents}.
+Top: Events in the interval 1983-1991; compare to bottom panel Fig.~\ref{DailyAveragedDstEvents}.
 Bottom: Same as Top except for constraint that $D_{st}$ stayed below $-50$~nT for at least 12~hours after crossing below $-50$~nT.}

### 2016-05-15 ComplexPlots.m
Plots with fewer dots, more significance tests

@@ -42,6 +42,8 @@ if(MakePaperPlots && (stormcase==2 || stormcase==24 || stormcase==1))
         bottombar=nanstd(AVMDMat(nanmedian(AVMat(:,tw,5),2)<bottomcut,:))./sqrt(sum(~isnan(AVMDMat(nanmedian(AVMat(:,tw,5),2)<bottomcut,:))));
         tvals=ttest2(AVMDMat(nanmedian(AVMat(:,tw,5),2)>=topcut,:),AVMDMat(nanmedian(AVMat(:,tw,5),2)<bottomcut,:));
         tvals(tvals==0)=NaN;
+        tvalid=sum(~isnan(AVMDMat(nanmedian(AVMat(:,tw,5),2)>=topcut,:)));
+        tvalid2=sum(~isnan(AVMDMat(nanmedian(AVMat(:,tw,5),2)<bottomcut,:)));
         %{
         for i=1:length(AVMDMat(1,:))
             top(i)=nanmean(AVMDMat(AVMat(:,i,5)>0,i));
@@ -50,6 +52,36 @@ if(MakePaperPlots && (stormcase==2 || stormcase==24 || stormcase==1))
             bottombar(i)=nanstd(AVMDMat(AVMat(:,i,5)<0,i));
         end
         %}
+        
+        if(nansum(tvals)==1) %That one plot with only 1 significant value
+           h=figure('Visible',visible); [hhist, nhist]=hist(AVMDMat(nanmedian(AVMat(:,tw,5),2)>=topcut,tvals==1),1:2.5:120); hhist=bar(nhist,hhist); set(hhist,'FaceColor','none','EdgeColor','r'); 
+           hold on;[hhist, nhist]=hist(AVMDMat(nanmedian(AVMat(:,tw,5),2)<topcut,tvals==1),1:2.5:120); hhist=bar(nhist,hhist); set(hhist,'FaceColor','none','EdgeColor','b'); 
+           legend('Events with higher median B_z','Events with lower median B_z')
+           xlabel('\rho_{eq} (amu/cm^3)')
+           ylabel('Number of events');
+           print('-depsc2',sprintf('paper/figures/RhoBinnedBz-case%d-t0%d-tf%d-GOES%d-histogram.eps',stormcase,tw(1),tw(end),satnum));
+        end
+        
+        
[…]

### 2016-05-15 Density.m

@@ -42,7 +42,7 @@ DentonData
 
 yranges=zeros(5,5,2);
 yranges(1,:,:)=[-2 2; 350 550; -60 0; 150 230; 8 16];
-yranges(2,:,:)=[-8 3; 350 600; -90 0; 160 210; 8 16];
+yranges(2,:,:)=[-8 3; 350 600; -90 0; 160 210; 10 30];
 yranges(3,:,:)=[-8 3; 350 580; -90 0; 170 200; 12 22];
 yranges(4,:,:)=[-3 2; 400 550; -30 -10; 80 120; 12 22];
 yranges(5,:,:)=[-10 10; 0 1000; -100 0; 00 200; 12 22]; %Made for overwriting with specific cases
@@ -71,8 +71,9 @@ switch stormcase
         storms=diff([0 (MassDensityNanSpline>40)' 0]); %Mass Density Storm, started at 40
         MDCut=40;
         figurename=strcat(figurename,'mass',sprintf('-GOES%d.eps',satnum));
-        yr=2;
+        yr=5;
         MakeBinPlots=1;
+        yranges(5,:,:)=[-1 3; 350 450; -20 0; 180 210; 10 60];
     case 3
         storms=[0 diff([0 (diff(MassDensityNanSpline)>10)' 0])];
         figurename=strcat(figurename,'diffden-10amu',sprintf('-GOES%d.eps',satnum));
@@ -216,7 +217,7 @@ switch stormcase
         figurename=strcat(figurename,'dst',sprintf('-GOES%d.eps',satnum));
         yr=2;
     case 24
-                storms=diff([0 (MassDensityNanSpline>20)' 0]); %Mass Density Storm, started at 40
+                storms=diff([0 (MassDensityNanSpline>20)' 0]); %Mass Density Storm, started at 20
         MDCut=20;
         figurename=strcat(figurename,'mass-gt20',sprintf('-GOES%d.eps',satnum));
         yr=5;
@@ -355,14 +356,14 @@ ComplexPlots
 %Statistical comparisons
 if(stormcase==1)
     %Show DST is significantly different during missing data times
-    [p,h]=ranksum(FILLED(~isnan(MassDensitySpline),15),FILLED(isnan(MassDensitySpline),15),'Alpha',0.01)
[…]

### 2016-05-15 paperfigures.m

@@ -2,7 +2,7 @@ function paperfigures
 
 Density(1,6) %alldata, ccplot, stormavs-dst, F107MD27d
 Density(24,6) %RhoBinned case24
-Density(10,6) %dst-50-tak
+Density(10,6) %dst-50-tak, and significance table
 Density(5,6) %dd12
 Density(13,6) %dst-day
 Density(24,6) %mass-gt20

### 2016-05-15 stackplot.m

@@ -30,7 +30,7 @@ Time(Time>datelimits(2))=[];
 for i=1:numvars
     h(i)=subplot('position',subplotstack(numvars,i));
     if(i<numvars)
-        plot(Time,Data(:,i),'.','MarkerSize',10);
+        plot(Time,Data(:,i),'-','MarkerSize',10);
     else
         plot(Time,Data(:,i),'r.','MarkerSize',10); %Plot last subplot in red
     end
@@ -53,7 +53,7 @@ datetick('x','keeplimits')
 set(findobj('type','axes'),'xtick',get(h(end),'xtick'))
 linkaxes(h,'x')
 axis tight;
-xlabel('Time','FontSize',14)
+xlabel(sprintf('Date from %s through %s',datestr(Time(1),1),datestr(Time(end),1)),'FontSize',14);
 
 sy=year(Time(1));
 ey=year(Time(end));

### 2016-05-18 paper/paper.tex
Plots with fewer dots, more significance tests
Notes, daily difference significance test

@@
 
-   Days     p
--1 and 0
--1 and 1
- 0 and 1
+\input{../tables/DeltaBootstraps.txt}
 
@@
 	\centering
-	\includegraphics[scale=0.40]{figures/RhoBinnedBz-case24-t020-tf25-GOES6.eps}
-	\includegraphics[scale=0.40]{figures/RhoBinnedBz-case24-t025-tf30-GOES6.eps}
+	\includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedBz-case24-t020-tf25-GOES6.eps}
+	\includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedBz-case24-t025-tf30-GOES6.eps}
 	\caption{Binning \req\ events by $B_z$ value (a) at onset and four hours before, and (b) at onset and four hours after.}

### 2016-05-18 ComplexPlots.m

@@ -28,6 +28,7 @@ if(MakePaperPlots && stormcase==26) %KP Stack plot
     stackplot(FILLEDTime, [FILLED(:,[5,6,13,30]) MassDensitySpline'],{'B_z (nT)','V_{SW} (km/s)','Kp','F_{10.7} (s.f.u.)','\rho_{eq} (amu/cm^3)'},satnum,[3 6],yranges(yr,:,:))
 end
 
+
 if(MakePaperPlots && (stormcase==2 || stormcase==24 || stormcase==1)) 
     tws=[20:25; 25:30];
     varnum=5; %5 is Bz, 15 is dst, 8 is p, 6 is Vsw, 13 is kp
@@ -414,7 +415,7 @@ if(MakePaperPlots && stormcase==1)
     
 end
 
-if(MakePaperPlots && stormcase==10) %1-day takahashi. Do for any day plot
+if(MakePaperPlots && (stormcase==10 || stormcase==13)) %1-day takahashi. Do for any day plot
     %Bootstrap test for same daily means
     xa1d=(-timewidth:LongTimeScale:timewidth*2)./LongTimeScale;
     AV1d=interptest(-timewidth:1:timewidth*2,AVMDMat',-timewidth:LongTimeScale:timewidth*2)';
@@ -444,7 +445,7 @@ if(MakePaperPlots && stormcase==10) %1-day takahashi. Do for any day plot
     end
     
     
-    table=fopen('tables/DeltaBootstraps.txt','w');
+    table=fopen(sprintf('tables/DeltaBootstraps-case%d.txt',stormcase),'w');
     Dm10=sum(delta(1,:)>=0)/length(delta(1,:));
     Dm11=sum(delta(2,:)<=0)/length(delta(2,:));
     D10=sum(delta(3,:)>=0)/length(delta(3,:));
@@ -452,12 +453,12 @@ if(MakePaperPlots && stormcase==10) %1-day takahashi. Do for any day plot
     [~,p2]=ttest2(AVm1,AV1);
     [~,p3]=ttest2(AV1,AV0);
     
-    fprintf(table,'\\begin{table}\n\\small\n\\begin{tabular}{|c|cCcc|}\n \\hline \n');
-    fprintf(table,'Days & Diff(medians) & \\%%  & p-val & valid\\\\ \\hline\n');
[…]

### 2016-05-18 ComplexPlots.m
Notes and cleaning up figures

@@ -31,9 +31,9 @@ end
 
 if(MakePaperPlots && (stormcase==2 || stormcase==24 || stormcase==1)) 
     tws=[20:25; 25:30];
-    varnum=5; %5 is Bz, 15 is dst, 8 is p, 6 is Vsw, 13 is kp
+    varnum=30; %5 is Bz, 15 is dst, 8 is p, 6 is Vsw, 13 is kp, 30 is f10.7
     varname=headers{varnum};
-    varunit='nT';
+    varunit='s.f.u.';
     for i=1:2
         tw=tws(i,:);
 

### 2016-05-18 paper/paper.tex

@@
 From the $\rho_{eq}$ events, we find a weak dependence on $B_{z}$ after the onset of an event, with higher average $B_{z}$ six hours after the event onset corresponding to larger $\rho_{eq}$ events.
+\end{abstract}
 \vspace{2em}
-\end{abstract}
 \hrule
+\vspace{2em}
  \end{@twocolumnfalse}
@@
 In the lower panel of Figure \ref{DailyAveragedDstEvents} it is shown that the trends seen in the analysis of 1989-1991 also hold for the entire span of measurements from GOES 6, which spans 1983-1991 - a small elevation on the day of the event relative to the day before and day after, with median averages after the day of the event being slightly lower than that before.
+To determine if the magnitude of the density medians in the top panel of \ref{DailyAveragedDstEvents} on days -1, 0, and 1 are statistically different from each other, we used a two-population bootstrap test.
+A bootstrap median was created by sampling the values used to compute the median on each day with replacement.
+The observed difference between the medians is shown in the table along with the fraction of observations in 1000 bootstrap differences with a different sign than that observed.
+The results are shown in the fourth column of Table~\ref{BootstrapDifferenceTable}.
+The fourth column shows the results of a 2-population t-test and the fifth column indicates ???.
 
-To determine if the magnitude of the density medians on a given day were statistically different than another day, we used a two-population t-test.
-For the interval of 1989-1991, corresponding to the top panel of \ref{DailyAveragedDstEvents}, the null hypothesis that any of the medians from days -1, 0, and 1 are different from each other is rejected with a maximum p value of.
-The results are shown in Table~\ref{Table1}.
+If a statistically significant difference in the medians between two days existed, the fraction is expected to be much smaller ($<$ 5\%).
+In terms of a hypothesis test, we cannot reject the null hypothesis that the medians are the same with a confidence higher than 100 minus the \% value shown in the table; the highest confidence level of 87.6\% is in the difference between day 0 and day 1.
 
 These tests indicate that there is not a statistically significant change in medians of $\rho_{eq}$ on the day before and day after a threshold crossing in $D_{st}$.
+In addition, the observed differences are on the order of only 10\% of the $\rho_{eq}$, which is small compared to the variance in the observations.
 
-\input{../tables/DeltaBootstraps.txt}
+%\input{../tables/DeltaBootstraps.txt}
 
-Caption: Results of test on different between means of $\rho_{eq}$ shown in the top panel of \ref{DailyAverage} on days near or on the day of a $D_{st}$ event.
-A difference in the means can be rejected with a probability of false rejection of $p$.
-
-   Days     p
--1 and 0
--1 and 1
- 0 and 1
-
-Caption: Results of test on different between means of $\rho_{eq}$ shown in the bottom panel of \ref{DailyAverage} on days near or on the day of a $D_{st}$ event.
+\begin{table}
+\small
+\begin{tabular}{|c|cCc|}
+ \hline 
+Days & Observed diff & \%  & p-val \\ \hline
+-1 0 & -0.64 & 28.00\%\geq 0 & 0.23 \\ 
+-1 1 & 0.99 & 22.40\%\leq 0 & 0.86 \\ 
+ 1 0 & -1.63 & 12.40\%\geq 0 & 0.16 \\ 
+\hline
+\end{tabular}
+\caption{Results of test on of means of $\rho_{eq}$ shown in the top panel of Figure~\ref{DailyAveragedDstEvents} between days of threshold crossing  near (day = 1 or -1) or on the day of a $D_{st}$ event (day = 0).}
+\label{BootstrapDifferenceTable}
+\end{table}
 

### 2016-05-24 ComplexPlots.m
Binary storm modeling

@@ -375,6 +375,34 @@ if(MakePaperPlots && MDCut>0) %Add a stack plot for Pressure for mass events
     
 end
 
+if(stormcase==29) %NNBinaryOnset
+    %{
+   F107Day=interptest(FILLEDTime,FILLED(:,30),FILLEDTime(1):24*(FILLEDTime(2)-FILLEDTime(1)):FILLEDTime(end)); 
+   KPDay=interptest(FILLEDTime,FILLED(:,13),FILLEDTime(1):24*(FILLEDTime(2)-FILLEDTime(1)):FILLEDTime(end)); 
+   VSWDay=interptest(FILLEDTime,FILLED(:,6),FILLEDTime(1):24*(FILLEDTime(2)-FILLEDTime(1)):FILLEDTime(end)); 
+   DstDay=interptest(FILLEDTime,FILLED(:,15),FILLEDTime(1):24*(FILLEDTime(2)-FILLEDTime(1)):FILLEDTime(end)); 
+   MDDay=interptest(FILLEDTime,MassDensitySpline',FILLEDTime(1):24*(FILLEDTime(2)-FILLEDTime(1)):FILLEDTime(end));
+    %}
+    
+    
+    %Do it with hourly data first since that's already well defined for
+    %events
+    
+    stormstarts=storms(1:end-1);
+    stormstarts(stormstarts==-1)=0;
+    predict=NNBinaryOnset(FILLED(:,[6 13 15 30]),stormstarts');
+    
+    
+       F107Day=interptest(FILLEDTime,AVs(:,30),FILLEDTime(1):24*(FILLEDTime(2)-FILLEDTime(1)):FILLEDTime(end)); 
+   KPDay=interptest(FILLEDTime,AVs(:,13),FILLEDTime(1):24*(FILLEDTime(2)-FILLEDTime(1)):FILLEDTime(end)); 
+   VSWDay=interptest(FILLEDTime,AVs(:,6),FILLEDTime(1):24*(FILLEDTime(2)-FILLEDTime(1)):FILLEDTime(end)); 
+   DstDay=interptest(FILLEDTime,AVs(:,15),FILLEDTime(1):24*(FILLEDTime(2)-FILLEDTime(1)):FILLEDTime(end)); 
+   
+   
+   
+    
+end
+
 
 %DST vs rho_eq for 1 hour and 1 day
 if(MakePaperPlots && stormcase==1) 

### 2016-05-24 Density.m

@@ -235,15 +235,19 @@ switch stormcase
     case 27 %For doing 3day/27day F107 plots
         storms=diff([0 (FILLED(:,15)<-50)' 0]); %DST Storm
         DSTCut=-50;
-        figurename=strcat(figurename,'dst',sprintf('-GOES%d.eps',satnum));
+        figurename=strcat(figurename,'ignore',sprintf('-GOES%d.eps',satnum));
         yr=2;
         MakeBinPlots=1;
     case 28 %For making specific stack plots of events (i.e. alldata-* plots with specific cuttimes)
         storms=diff([0 (FILLED(:,15)<-50)' 0]); %DST Storm
         DSTCut=-50;
-        figurename=strcat(figurename,'dst',sprintf('-GOES%d.eps',satnum));
+        figurename=strcat(figurename,'ignore',sprintf('-GOES%d.eps',satnum));
         yr=2;
-        
+    case 29
+        storms=diff([0 (FILLED(:,15)<-50)' 0]); %DST Storm
+        DSTCut=-50;
+        figurename=strcat(figurename,'ignore',sprintf('-GOES%d.eps',satnum));
+        yr=2;
 end
 
 

### 2016-05-24 NNBinaryOnset.m

@@ -1,0 +1,40 @@
+function outputs=NNBinaryOnset(x,target)
+
+delays=1;
+
+if(length(size(x))==3) %If sending in multiple variables for each storm and time, just add them as a vector of variables for each storm
+    x=reshape(x,length(x),[]);
+end
+
+Z=[x target];
+for col=1:min(size(Z))
+    Z(isnan(Z(:,col)),:)=[];
+end
+x=Z(:,1:end-1);
+y=Z(:,end);
+
+
+
+
+inputDelays = 1:delays;
+    feedbackDelays = 1:delays;
+    hiddenLayerSize = 10;
+    
+    net=patternnet(hiddenLayerSize);
+    net=train(net,x',target); %Look at confusion matrix. Not great.
+    
+    
+    net = narxnet(inputDelays,feedbackDelays,hiddenLayerSize);
+    net = removedelay(net);
+    [inputs,inputStates,layerStates,targets] = preparets(net,tonndata(x,false,false),{},tonndata(y,false,false));
+    
+    net.divideFcn = 'divideblock';
+    net.divideParam.trainRatio = 70/100;
+    net.divideParam.valRatio = 15/100;
+    net.divideParam.testRatio = 15/100;
+    
+
+    
+    [net,tr,Ys Es Xf Af] = train(net,inputs,targets,inputStates,layerStates);
+    
+    outputs = net(inputs,inputStates,layerStates);

### 2016-06-14 paper/paper.tex
Updated figures

@@
 \small
-\begin{tabular}{|c|cCc|}
- \hline 
-Days & Observed diff & \%  & p-val \\ \hline
--1 0 & -0.64 & 28.00\%\geq 0 & 0.23 \\ 
--1 1 & 0.99 & 22.40\%\leq 0 & 0.86 \\ 
- 1 0 & -1.63 & 12.40\%\geq 0 & 0.16 \\ 
-\hline
-\end{tabular}
+
+\input{../tables/DeltaBootstraps-case10.txt}
 \caption{Results of test on of means of $\rho_{eq}$ shown in the top panel of Figure~\ref{DailyAveragedDstEvents} between days of threshold crossing  near (day = 1 or -1) or on the day of a $D_{st}$ event (day = 0).}
@@
 	\centering
-	\includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedBz-case24-t020-tf25-GOES6.eps}
-	\includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedBz-case24-t025-tf30-GOES6.eps}
+	\includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedBzIMF-case24-t020-tf25-GOES6.eps}
+	\includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedBzIMF-case24-t025-tf30-GOES6.eps}
 	\caption{Binning \req\ events by $B_z$ value (a) at onset and four hours before, and (b) at onset and four hours after.}

### 2016-06-28 paper/paper.tex
Misc. edits

@@
 \begin{abstract}
-In this work we consider two types of events, determined by decreases in $D_{st}$ below a threshold value or increases in the $\rho_{eq}$ above a threshold value on 1-hour and 1-day time scales using the \cite{Denton2007} dataset.
-From the $D_{st}$ events, we find that there is no statistically significant relationship between either solar wind or geomagnetic activity under conditions of strong geomagnetic activity when hourly or daily averages of $\rho_{eq}$ are considered.
-Although very large geomagnetic storms have been observed to correspond to large increases in the plasma trough mass density, in general $\rho_{eq}$ following the onset of a geomagnetic storm does not depend on the storm intensity or the solar wind parameters $B_{z}$ and $P_{dyn}$.
+In this work we consider two types of events, determined by decreases in $D_{st}$ below a threshold value or increases in the the equatorial mass density at geosynchronous altitudes, $\rho_{eq}$, above a threshold value on 1-hour and 1-day time scales using the \cite{Takahashi2010} dataset.
+From the $D_{st}$ events, we find that there is no statistically significant.
+Although very large geomagnetic storms have been observed to correspond to large increases in the $\rho_{eq}$, in general $\rho_{eq}$ following the onset of a geomagnetic storm does not depend on the storm intensity or the solar wind parameters $B_{z}$ and $P_{dyn}$.
 From the $\rho_{eq}$ events, we find a weak dependence on $B_{z}$ after the onset of an event, with higher average $B_{z}$ six hours after the event onset corresponding to larger $\rho_{eq}$ events.
@@
 The dependence of the plasma trough density on geomagnetic and solar wind conditions has not been extensively studied until the past decade (\cite{Takahashi2006}; \cite{Takahashi2010}; \cite{Denton2016}).
-Earlier works that considered profiles of electron number density found a significant dependence on the plasmasphere boundary on geomagnetic activity (\cite{Chappell1970}; \cite{Anderson1993}), but there the relationship between geomagnetic activity and density in the plasma trough was not explicitly considered.
+Earlier works that considered profiles of hydrogen ion density found a significant dependence on the plasmasphere boundary on geomagnetic activity (\cite{Chappell1970}; \cite{Maynard1977}; \cite{Carpenter1992}), but there the relationship between geomagnetic activity and density in the plasma trough was not explicitly considered.
 
@@
 They found that the average ion mass, $M=\rho/n_e$, had some correlation with geomagnetic activity, with more negative hourly $D_{st}$ values corresponding to higher $M$ and 1.5- and 3-day averages of $K_p$ corresponding to higher $M$ (3-hour averages of $K_p$ had little visual correlation with $M$).
-The mass density estimates were obtained from CRRES observations in the MLT range of 12:00 and 18:00 with most observations having L between 5 and 7 $R_E$.
+The mass density estimates were obtained from CRRES observations in the MLT range of 12:00 and 18:00 with most observations having $L$ between 5 and 7 $R_E$.
 
-\cite{Denton2006} found a weak relationship between $D_{st}$ and and $K_p$ and the field line distribution of $\rho$ using observations of the first three toroidal Alfv\'en harmonic frequencies for $L$ in the range of 6-8$R_E$.
+\cite{Denton2006} found a weak relationship between $D_{st}$ and and $K_p$ and the field line distribution of $\rho$ using observations of the first three toroidal Alfv\'en harmonic frequencies for $L$ in the range of 6-8~$R_E$.
 A more pronounced peak in the distribution along a filed line near the equator was found for lower $D_{st}$ and larger $K_p$.
@@
 \cite{Takahashi2010} developed a mass density dataset using measurements from the Space Environment Monitor instruments on the Geostationary Operational Environmental Satellites (GOES) satellites from 1980 through 1992, with most measurements in the range of $L=6.8\pm0.2 R_E$.
-The mass density $\rho$ was estimated using the the Alfv\'en wave velocity relationship, $V_A=B/\sqrt{\mu_0\rho}$ a magnetic field model, and a numerical solution to a wave equation with an ionospheric boundary and the assumption of a zero resistance ionosphere.
+The mass density $\rho$ was estimated using the the Alfv\'en wave velocity relationship, $V_A=B/\sqrt{\mu_0\rho}$, a magnetic field model, and a numerical solution to a wave equation with an ionospheric boundary and the assumption of a zero resistance ionosphere.
 The equatorial mass density, $\rho_{eq}$, was derived from the estimated mass density using a power law dependence on the geocentric distance to the field line of the observation, $R$, $\rho=\rho_{eq}L/(R/R_E)$.
@@
 
-The parameters $\rho_{eq}$ and $F_{10.7}$ used in this work are from the dataset of \cite{Denton}, which was used in \cite{Takahashi2010}; data are available from 1980 through 1991 from GOES 2,3,5, 6 and 7.
+The parameters $\rho_{eq}$ and $F_{10.7}$ are from the dataset of \cite{Denton}, which was used in \cite{Takahashi2010}; data are available from 1980 through 1991 from GOES 2, 3, 5, 6 and 7.
 All other parameters used are from \cite{Kondrashov2014ReconstructionOfGaps} from 1972 through 2013, which are on a 1--hour time grid.
@@
 
-In this work, events are defined to occur when $D_{st}$ or $\rho_{eq}$ crosses a threshold value, as indicated by horizontal dashed lines in their respective panels of Figure~\ref{AllData}.
-
-Figure~\ref{ccplot} shows the long-term trends of $log(\rho_{eq})$ from GOES 6 and $F_{10.7}$ computed using the median values in 27-day non-overlapping windows.
+Figure~\ref{ccplot} shows the long-term trends of log$_{10}(\rho_{eq})$ from GOES 6 and $F_{10.7}$ computed using the median values in 27-day non-overlapping windows.
 A scatter plot of these two lines is shown in the lower panel of Figure~\ref{ccplot}.
@@
 Two types of events are considered.
-The first is a drop in the $D_{st}$ index \vinote{Cite Kyoto} below the threshold of -50~nT.
+The first is a drop in the $D_{st}$ index below the threshold of -50~nT.
 These types of events are considered in order to determine if there is a well-defined $\rho_{eq}$ dependence on geomagnetic activity/storms as indicated by $D_{st}$ index.
@@
 The second type of event is an increase in $\rho_{eq}$ above a threshold of 20~amu/cm$^3$.
-It is expected that these increases will typically occur after period of quiet geomagnetic activity.
+It is expected that these increases will typically occur after period of quiet geomagnetic activity but may also be the result of increases in geomagnetic activity.
 In this case, the plasmapause boundary may move outward past geosynchronous orbit and the increase will be due to measurements being made inside the plasmapause.
@@
 Our first analysis uses data only from the time interval 1989-1991, which corresponds with the interval used in the analysis in \cite{Takahashi2010}.
-In this interval, there were 329 $D_{st}$ events and 70 $\rho_{eq}$ events.
-For both types of events, the hour of the threshold crossing defines the zero epoch time, and for each event, $4\cdot24$ hours were considered before each event and $8\cdot24$ hours after each event.
+In this interval, there were 329 $D_{st}$ events.
+For both types of events, the hour of the threshold crossing defines the zero epoch time, and for each event, $4\cdot24$ hours were considered before and $8\cdot24$ hours after each event.
 To compute the epoch averages on a daily time scale, the median value of all available measurements for all events centered on a window of $\pm 12$ hours of the epoch zero hour was computed, and these averaging windows were shifted in increments of $24$~hours.
-Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians in 1-day bins and then compute the medians across events.
+Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians for each event in 1-day bins and then compute the medians across events.
 Error bars for each parameter are the standard deviation of the values used in computing the median divided by the square root of the number of values used.
 
-The stack plot in the upper panel of Figure \ref{DailyAveragedDstEvents} shows the epoch averages for these events.
+The stack plot in the upper panel of Figure \ref{DailyAveragedDstEvents} shows the epoch averages for the 329 events from 1989-1991.
 The minimum $D_{st}$ median is $-48$~nT.
-Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$, although the magnitude of increase observed here is $1.5$ amu/cm$^3$ (from 18 to 19.5~amu/cm$^3$) instead of the increase of $\sim 10$ amu/cm$^3$ found in Figure 11 of \cite{Takahashi2010}.
-The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute the medians and error bars.
+Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$ before and after the event, although the magnitude of increase observed here is $1.5$ amu/cm$^3$ (from 18 to 19.5~amu/cm$^3$) instead of the increase of $\sim 10$ amu/cm$^3$ found in Figure 11 of \cite{Takahashi2010}.
+The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute the medians and red error lines.
 For the non-\req\ medians, the number of measurements used in computing the medians is typically equal to the number of events, which is much larger than the number of \req\ values as we used all available measurements instead of restricting to only values where a non--fill $\rho_{eq}$ value existed.
@@
 To determine if the magnitude of the density medians in the top panel of \ref{DailyAveragedDstEvents} on days -1, 0, and 1 are statistically different from each other, we used a two-population bootstrap test.
-A bootstrap median was created by sampling the values used to compute the median on each day with replacement.
+A bootstrap sample of the medians for each day was created by sampling the actual values with replacement.
 The observed difference between the medians is shown in the table along with the fraction of observations in 1000 bootstrap differences with a different sign than that observed.
@@
 
-Because the dynamics of the magnetopshere take place on a time scale of less than one day, we have also considered hourly averages as shown in the top panel of Fig.~\ref{HourlyAveragedDstEvents}.
+We have also considered hourly averages as shown in the top panel of Fig.~\ref{HourlyAveragedDstEvents}.
 A total of 668 events were found in the interval of May 1983 through August 1991 with an average duration of 9 hours and a median duration of 3 hours.
 The error bars were computed in the same way as Fig.~\ref{DailyAveragedDstEvents}.
-In this plot, the overall trend is similar to that found in the bottom panel of Fig.~\ref{HourlyAveragedDstEvents} - $\rho_{eq}$ is slightly elevated at the time of the threshold crossing of $D_{st}$ with respect to the values one day before and after, but the elevation is small and in general not statistically significant.
+In this plot, the overall trend is similar to that found in the bottom panel of Fig.~\ref{HourlyAveragedDstEvents} - $\rho_{eq}$ is slightly elevated at the time of the threshold crossing of $D_{st}$ with respect to the values one day before and after, but the elevation is small relative to the error bars around the time of the event onset.
 At this timescale no obvious change in mass density at hourly timescale is visible.
-This points to an issue with only looking at long-timescale trends between density and $D_{st}$, and allows for the possibility that other factors are influencing the long term correlation because there is no obvious connection on a short timescale.
-One possibility is that, as suggested in \cite{Takahashi2010}, $F_{10.7}$ plays a significant role in driving long term density values which biases the long-term correlation of density and $D_{st}$.
 
@@
 In the time period of elevated mass density within 12 hours of the start of the event, there were an average of \inote{X} samples per hourly interval.
-This result is consistent with previous observations of large mass density spikes in the plasma trough region during large geomagnetic storms (\cite{Yao2008}; \cite{Takahashi2010} and the observation that solar wind parameters have very little correlation independent of $F_{10.7}$ (\cite{Denton2016}).
+This result is consistent with previous observations of large mass density spikes in the plasma trough region during large geomagnetic storms (\cite{Yao2008}; \cite{Takahashi2010}.
 To determine of this relationship can be observed in the events of the top panel of Fig.~\ref{HourlyAveragedDstEvents}, we sorted the events by the average $D_{st}$ values in the time interval of 0-12 hours, split the events in two and recomputed the epoch averages of $\rho_{eq}$.
-The result is that there is no statistically significant difference in the mass density epoch averages for large versus small storms.
-This indicates that to confirm the $\rho_{eq}$ dependence on large geomagnetic storms would require a dataset with a much larger number of strong geomagnetic storms.
+The result is that there is no statistically significant difference in the mass density epoch averages for large versus small events.
+This indicates that to confirm a statitical $\rho_{eq}$ dependence on large geomagnetic storms would require a dataset with a much larger number of strong geomagnetic storms.
 

### 2016-07-01 paper/paper.tex
Misc text additions and corrections

@@
-\documentclass[10pt,twocolumn]{article}
-\usepackage{graphicx}
+%\documentclass[11pt,twocolumn]{article}
+%\usepackage{graphicx}
+%\usepackage{fancyhdr}
+%\usepackage{amssymb,amsmath}
+%\usepackage[usenames,dvipsnames]{color}
+%\usepackage[colorlinks,citecolor=RedViolet,urlcolor=blue]{hyperref}
+%\usepackage{doi}
+%\usepackage{setspace}
+%\usepackage[paperwidth=8.5in, paperheight=11in,top=1in, bottom=1in, left=1in, r%ight=1in]{geometry}
+%\usepackage[compact]{titlesec}
+%\usepackage{abstract}
+%\usepackage[position=t,singlelinecheck=off,justification=raggedleft]{subcaption}
+%\usepackage[authoryear,square]{natbib}
+%\usepackage{aas_macros}
+%\usepackage{array}
+%\pagestyle{fancy}
+%\fancyhead[R]{Veibell \thepage}
+%\fancyhead[L]{}
+
+%\newcolumntype{L}{>{$}l<{$}} %To enable math mode in tables (for saying things like B_z)
+%\newcolumntype{C}{>{$}c<{$}}
+%\newcommand{\vinote}[1]{\textcolor{red}{\textbf{#1}}} %If you want \inote{#} instead of just \note #, for inline notes
+%\def\vnote#1\par{\textcolor{red}{\textbf{#1}}\\} %Make note bold and red, re-add newline
+%\newcommand{\req}{\ensuremath{\rho_{eq}}}
+%\newcommand{\inote}[1]{\textcolor{blue}{\textbf{#1}}} %Inline notes in blue
+%\def\note#1\par{\textcolor{blue}{\textbf{#1}}\\}
+
+\documentclass[12pt]{article}
+\bibliographystyle{./style/agufull}
+\usepackage[square,comma,authoryear]{natbib}
+\usepackage{epsfig}
+\usepackage{style/lineno}
+\usepackage{amsmath}
+%\usepackage{booktabs}
+\linenumbers*[1]
+\usepackage{subfig}
+
+\usepackage{setspace}  
 \usepackage{fancyhdr}
-\usepackage{amssymb,amsmath}
-\usepackage[usenames,dvipsnames]{color}
-\usepackage[colorlinks,citecolor=RedViolet,urlcolor=blue]{hyperref}
-\usepackage{doi}
-\usepackage{setspace}
-\usepackage[paperwidth=8.5in, paperheight=11in,top=1in, bottom=1in, left=1in, right=1in]{geometry}
-\usepackage[compact]{titlesec}
-\usepackage{abstract}
-\usepackage[position=t,singlelinecheck=off,justification=raggedleft]{subcaption}
-\usepackage[authoryear,square]{natbib}
-\usepackage{aas_macros}
-\usepackage{array}
+
+\newcommand{\citeay}[1]{%
+\citeauthor{#1}, \citeyear{#1}%
+}
+
 \pagestyle{fancy}
-\fancyhead[R]{Veibell \thepage}
-\fancyhead[L]{}
+\fancyhead{}
+\fancyfoot{}
+\fancyhead[R]{X - \thepage}
+\fancyhead[L]{VEIBELL: MASS DENSITY AT GEO}
+\fancyfoot[L]{D R A F T}
+\fancyfoot[C]{\today}
+\fancyfoot[R]{D R A F T}
+\renewcommand{\headrulewidth}{0.0pt}
+\renewcommand{\footrulewidth}{0.0pt}
 
-\newcolumntype{L}{>{$}l<{$}} %To enable math mode in tables (for saying things like B_z)
-\newcolumntype{C}{>{$}c<{$}}
-\newcommand{\vinote}[1]{\textcolor{red}{\textbf{#1}}} %If you want \inote{#} instead of just \note #, for inline notes
-\def\vnote#1\par{\textcolor{red}{\textbf{#1}}\\} %Make note bold and red, re-add newline
-\newcommand{\req}{\ensuremath{\rho_{eq}}}
-\newcommand{\inote}[1]{\textcolor{blue}{\textbf{#1}}} %Inline notes in blue
-\def\note#1\par{\textcolor{blue}{\textbf{#1}}\\}
+\oddsidemargin 0.0in
+\evensidemargin 1.0in
+\textwidth 6.5in
+\headheight 0.1in
+\topmargin -0.5in
+\textheight 9.0in
 
@@
 \title{Solar wind and geomagnetic activity influence on the equatorial plasma mass density at geosynchronous orbit}
-\author{
-Victoir Veibell\footnote{vveibell@gmu.edu}
-\and
-R.S. Weigel\footnote{rweigel@gmu.edu}}
+\author{V. Veibell and R.S. Weigel}
+\doublespacing
+\maketitle
 
-\setlength{\parskip}{3ex}
-\renewcommand{\labelitemi}{$-$}
-\titlespacing{\section}{0pc}{0.2pc}{-1pc}
-\titlespacing{\subsection}{0pc}{0.1pc}{-1pc}
-\titleformat*{\section}{\normalsize\bfseries}
-\titleformat*{\subsection}{\small\bfseries}
+%\author{
+%Victoir Veibell\footnote{vveibell@gmu.edu}
+%\and
+%R.S. Weigel\footnote{rweigel@gmu.edu}}
 
-\twocolumn[
-  \begin{@twocolumnfalse}
-\maketitle
-\hrule
+%\setlength{\parskip}{3ex}
+%\renewcommand{\labelitemi}{$-$}
+%\titlespacing{\section}{0pc}{0.2pc}{-1pc}
+%\titlespacing{\subsection}{0pc}{0.1pc}{-1pc}
+%\titleformat*{\section}{\normalsize\bfseries}
+%\titleformat*{\subsection}{\small\bfseries}
+
+%\twocolumn[
+%  \begin{@twocolumnfalse}
+%\maketitle
+%\hrule
 \begin{abstract}
-In this work we consider two types of events, determined by decreases in $D_{st}$ below a threshold value or increases in the the equatorial mass density at geosynchronous altitudes, $\rho_{eq}$, above a threshold value on 1-hour and 1-day time scales using the \cite{Takahashi2010} dataset.
-From the $D_{st}$ events, we find that there is no statistically significant.
-Although very large geomagnetic storms have been observed to correspond to large increases in the $\rho_{eq}$, in general $\rho_{eq}$ following the onset of a geomagnetic storm does not depend on the storm intensity or the solar wind parameters $B_{z}$ and $P_{dyn}$.
+We consider two types of events, identified by decreases in $D_{st}$ below a threshold value and increases in the the equatorial mass density at geosynchronous altitudes, $\rho_{eq}$, above a threshold value on 1-hour and 1-day time scales using the \cite{Takahashi2010} dataset.
+From the $D_{st}$ events, we find that there is a weak and small amplitude ($< 10$\%) difference between $\rho_{eq}$ on the day of the event and the days before and after on both daily and hourly timescales.
+Although very large geomagnetic storms have been observed to correspond to large increases in $\rho_{eq}$, on average, $\rho_{eq}$ following the onset of a geomagnetic storm does not depend on the storm intensity or north-south component of the interplanetary magnetic field, $B_z$.
 From the $\rho_{eq}$ events, we find a weak dependence on $B_{z}$ after the onset of an event, with higher average $B_{z}$ six hours after the event onset corresponding to larger $\rho_{eq}$ events.
+In contrast, the average of $B_z$ six hours prior to $\rho_{eq}$ events does not have a statistically significant impact on $\rho_{eq}$ after onset.
 \end{abstract}
-\vspace{2em}
-\hrule
-\vspace{2em}
- \end{@twocolumnfalse}
-  ]
+%\vspace{2em}
+%\hrule
+%\vspace{2em}
+% \end{@twocolumnfalse}
+%  ]
 
-\saythanks
+%\saythanks
 
@@
 
-The plasma trough is a transition region between the higher density and lower temperature plasmasphere and the lower density and higher energy magnetosphere \citep{Mayr1968ModelMagnetosphereTemperature}.
+%The plasma trough is a transition region between the higher density and lower temperature plasmasphere and the lower density and higher energy magnetosphere \citep{Mayr1968ModelMagnetosphereTemperature} and is .
 Inside of the plasmapause, the density is primarily due to ionospheric photoionization; outside of the plasmapause, the density has contributions from the co-rotating plasmasphere and Earthward convecting magnetosphere plasmas.
 
-The dependence of the plasmapause location on geomagnetic activity was observed as early as \cite{Carpenter1966}.
-There are well--validated models of the plasmapause boundary, as a function of $L$, $MLT$, and geomagnetic activity (\cite{LemaireEarthsPlasmasphere}, \cite{Moldwin2002ModelPlasmapause}, \cite{OBrien2003EmpiricalPlasmapause}).
-Models also exist for the plasmasphere density (\cite{Gallagher1988EmpiricalModelPlasmasphere}; \cite{LemaireEarthsPlasmasphere}).
+The dependence of the plasmapause location on geomagnetic activity was observed as early as \cite{Carpenter1966} and there are well--validated models of the plasmapause boundary, as a function of $L$, $MLT$, and geomagnetic activity (\cite{LemaireEarthsPlasmasphere}, \cite{Moldwin2002ModelPlasmapause}, \cite{OBrien2003EmpiricalPlasmapause}).
+Models also exist for the plasmasphere density (\cite{Gallagher1988EmpiricalModelPlasmasphere}; \cite{LemaireEarthsPlasmasphere}) with similar parameterization.
 
-The dependence of the plasma trough density on geomagnetic and solar wind conditions has not been extensively studied until the past decade (\cite{Takahashi2006}; \cite{Takahashi2010}; \cite{Denton2016}).
-Earlier works that considered profiles of hydrogen ion density found a significant dependence on the plasmasphere boundary on geomagnetic activity (\cite{Chappell1970}; \cite{Maynard1977}; \cite{Carpenter1992}), but there the relationship between geomagnetic activity and density in the plasma trough was not explicitly considered.
+The dependence of the plasma density outside of the nominal plasmapause location on geomagnetic and solar wind conditions has not been extensively studied until the past decade (\cite{Takahashi2006}; \cite{Takahashi2010}; \cite{Denton2016}).
+Earlier works that considered profiles of hydrogen ion density found a significant dependence of the plasmasphere and plasmapause on geomagnetic activity (\cite{Chappell1970}; \cite{Maynard1977}; \cite{Carpenter1992}), but the relationship between geomagnetic activity and density outside of the plasmapause was not explicitly considered.
 
-\cite{Takahashi2006} estimated magnetospheric mass density using measurements from the CRRES satellite during a 73-day period in 1991 (observations were made when CRRESS was in an elliptical, near equatorial orbit and primarily in the plasma trough region).
-They found that the average ion mass, $M=\rho/n_e$, had some correlation with geomagnetic activity, with more negative hourly $D_{st}$ values corresponding to higher $M$ and 1.5- and 3-day averages of $K_p$ corresponding to higher $M$ (3-hour averages of $K_p$ had little visual correlation with $M$).
-The mass density estimates were obtained from CRRES observations in the MLT range of 12:00 and 18:00 with most observations having $L$ between 5 and 7 $R_E$.
+\cite{Takahashi2006} estimated magnetospheric mass density using measurements from the CRRES satellite during a 73-day period in 1991 when CRRES was in an elliptical, near equatorial orbit and primarily beyond the plasmapause.
+They found that the local average ion mass, $M$, had some correlation with geomagnetic activity, with more negative hourly $D_{st}$ values corresponding to higher $M$ and 1.5- and 3-day averages of $K_p$ corresponding to higher $M$ (3-hour averages of $K_p$ had little visual correlation with $M$).
+The mass density estimates were obtained from CRRES observations in the MLT range of [12:00, 18:00] with most observations at $L$ between 5 and 7 $R_E$.
 
-\cite{Denton2006} found a weak relationship between $D_{st}$ and and $K_p$ and the field line distribution of $\rho$ using observations of the first three toroidal Alfv\'en harmonic frequencies for $L$ in the range of 6-8~$R_E$.
+\cite{Denton2006} found a weak relationship between $D_{st}$ and and $K_p$ and the field line distribution of mass density, $\rho$, using observations of the first three toroidal Alfv\'en harmonic frequencies for $L$ in the range of 6-8~$R_E$.
 A more pronounced peak in the distribution along a filed line near the equator was found for lower $D_{st}$ and larger $K_p$.
-The equatorial value of $\rho$ appeared identical for the bins of $D_{st}$ (-142 to -31 nT and -31 to 37 nT) and $K_p$ (1.5 to 3.4 and 3.4 to 5.9) considered .
+The equatorial value of $\rho$ appeared identical for $D_{st}$ bins of [-142, -31] and [-31, 37] nT and $K_p$ bins of [1.5,3.4] and [3.4, 5.9].
 
 \cite{Takahashi2010} developed a mass density dataset using measurements from the Space Environment Monitor instruments on the Geostationary Operational Environmental Satellites (GOES) satellites from 1980 through 1992, with most measurements in the range of $L=6.8\pm0.2 R_E$.
-The mass density $\rho$ was estimated using the the Alfv\'en wave velocity relationship, $V_A=B/\sqrt{\mu_0\rho}$, a magnetic field model, and a numerical solution to a wave equation with an ionospheric boundary and the assumption of a zero resistance ionosphere.
-The equatorial mass density, $\rho_{eq}$, was derived from the estimated mass density using a power law dependence on the geocentric distance to the field line of the observation, $R$, $\rho=\rho_{eq}L/(R/R_E)$.
-They found a high correlation ($\sim 0.93$) between 27-day averages of F10.7 and 27-day medians of $\rho_{eq}$.
+The mass density was estimated using the the Alfv\'en wave velocity relationship, $V_A=B/\sqrt{\mu_0\rho}$, a magnetic field model, and a numerical solution to a wave equation with an ionospheric boundary and the assumption of a zero resistance ionosphere.
+The equatorial mass density, $\rho_{eq}$, was derived from the estimated mass density using a power law dependence on the geocentric distance to the field line of the observation, $R$, $\rho=\rho_{eq}(LR_E/R)^{1/2}$.
+They found a high correlation ($\sim 0.94$) between 27-day averages of $F10.7$ and 27-day medians of $\rho_{eq}$.
 
@@
 For five storms, two had $\rho_{eq}$ spikes after the $D_{st}$ drop, two had $\rho_{eq}$ spikes before the drop, and one showed little change in $\rho_{eq}$.
-A key result was that when daily-averaged measurements were considered, an enhancement in $\rho_{eq}$ appeared on the same day as minimum $D_{st}$.
+A key result was that when daily-averaged measurements were considered, the epoch average of $D_st$ exhibited for storms with a minimum $D_{st} < -50$~nT, an enhancement in $\rho_{eq}$ the same day as minimum $D_{st}$ epoch averages.
 
 \cite{Yao2008} studied the relationship between $D_{st}$ and the number density of low-energy $O^+$ in different regions (ring current and plasma sheet) using the TEAMS and ESA instruments on the low-altitude and high-inclination orbiting FAST satellite and found that the average $N_{O^+}$ across the sampled L-shells (2-14) had a strong correlation (0.88) with the minimum $D_{st}$ of the storm.
-Although the correlation in the plasma trough was not calculated, the data presented for four events show that the variations in $N_{O^+}$ tended to appear near $D_{st}$ minimum ($\pm$ 2~hours).
+Although the correlation at geosynchronous distances was not calculated, the data presented for four events show that the variations in $N_{O^+}$ tended to appear near $D_{st}$ minimum ($\pm$ 2~hours).
 
-\cite{Denton2016} ...
-
-The results in the papers discussed indicate that (1) the mass density in the plasma trough region is best correlated with $F10.7$ and (2) there exists a much weaker relationship between mass density and the geomagnetic activity indices $K_p$ and $D_{st}$.
-In this work we consider the dependence of mass density estimates in the \cite{Takahashi2010} and attempt to identify and statistically characterize the relationship between geomagnetic activity with mass density in the plasma trough region.
+The above results in the papers discussed indicate that (1) the mass density in the at geosynchronous distances is best correlated with $F10.7$ and (2) there exists a much weaker statistical relationship between mass density and the geomagnetic activity indices $K_p$ and $D_{st}$.
+In this work we consider the dependence of mass density estimates in the \cite{Denton2006} data set and attempt to identify and statistically characterize the relationship between geomagnetic activity with mass density at geosynchronous distances.
 In addition, we attempt to identify solar wind processes that may drive changes in mass density.
 
-There are several issues that are addressed in detail: (1) the plasma density measurements are sparse, (2) The plasma trough density has a high correlation with F10.7, and geomagnetic and solar wind parameters also correlate with F10.7, (3) the dependence of mass density on the north/south component of the solar wind magnetic field is expected to be nonlinear.
+%There are several issues that are addressed in detail: (1) the plasma density measurements are sparse, (2) The plasma trough density has a high correlation with F10.7, and geomagnetic and solar wind parameters also correlate with F10.7, (3) the dependence of mass density on the north/south component of the solar wind magnetic field is expected to be nonlinear.
 For northward IMF, corresponding to low solar wind driving of the magnetosphere, the plasmasphere can expand past geosynchronous orbit where trough estimates of mass density are made resulting in an increase in observed density that are not due to solar wind driving; for southward IMF, events studies have shown an increase in mass density associated with strong southward IMF and enhanced magnetospheric activity (\cite{Takahashi2010}; \cite{Yao2008}).
 
-Issue (1) is addressed by considering in detail the number of observations that are used in epoch averages around the time of two types of events, decreases in $D_{st}$ below a threshold, and increases in $\rho_{eq}$ above a threshold.
+%Issue (1) is addressed by considering in detail the number of observations that are used in epoch averages around the time of two types of events, decreases in $D_{st}$ below a threshold, and increases in $\rho_{eq}$ above a threshold.
 Issue (2) is addressed using various methods to remove or isolate the F10.7 dependence.
@@
 
-In addition, we consider the influence of time averaging by comparing results using daily means and medians and hourly means and medians of solar wind and magnetospheric parameters.
+%In addition, we consider the influence of time averaging by comparing results using daily means and medians and hourly means and medians of solar wind and magnetospheric parameters.
 
@@
 
-The parameters $\rho_{eq}$ and $F_{10.7}$ are from the dataset of \cite{Denton}, which was used in \cite{Takahashi2010}; data are available from 1980 through 1991 from GOES 2, 3, 5, 6 and 7.
-All other parameters used are from \cite{Kondrashov2014ReconstructionOfGaps} from 1972 through 2013, which are on a 1--hour time grid.
+The parameters $\rho_{eq}$ and $F_{10.7}$ are from the dataset of \cite{Takahashi2010}; data are available from 1980 through 1991 from GOES 2, 3, 5, 6 and 7.
+All other parameters used are from \cite{Kondrashov2014ReconstructionOfGaps} which has coverage from 1972 through 2013, which are on a 1--hour time grid.
 $\rho_{eq}$ is the inferred equatorial mass density based on the 3rd harmonic torodial frequency of magnetic field measurements as described in \cite{Takahashi2010}.
@@
 To compute an hourly median over the same interval for which the solar wind parameters were averaged, the median of all $\rho_{eq}$ values in a given hour window was used.
-Fill (NaN) values were used for hours in which no measurements were available.
+GOES 6 had the longest span of available data and the primary results presented are for GOES 6 while measurements from other satellites were used for consistency checks.
+
+%Fill (NaN) values were used for hours in which no measurements were available.
 In cases where $\rho_{eq}$ was available from multiple GOES satellites at the same time, the value from GOES 6 was selected.
@@
 Figure~\ref{ccplot} shows the long-term trends of log$_{10}(\rho_{eq})$ from GOES 6 and $F_{10.7}$ computed using the median values in 27-day non-overlapping windows.
-A scatter plot of these two lines is shown in the lower panel of Figure~\ref{ccplot}.
+A scatter plot of these two lines is shown in the lower panel of Figure~\ref{ccplot} along with that for 1--day and 1--hour medians.
 The linear correlation for GOES 6 using all measurements is found to be $0.94$, which is the same value documented by \cite{Takahashi2010} who used measurements from all satellites in the time interval of 1980 through 1991 using the constraint $0600 \leq MLT \le 1200$, $K_{p3d}\ge1.0$ and $D_{st}\ge -50$~nT.
-Our 27-day correlations for GOES 2, 5, and 7 are 0.81, 0.78, and 0.87, and the time range of coverage of measurements from these satellites are 1980-01-01/1983-05-16, 1983-01-01/1987-02-28, and 1983-05-27/1991-08-29 respectively.
+Our 27-day correlations for GOES 2, 5, and 7 are 0.81, 0.78, and 0.87, and the time range of coverage of measurements from these satellites is 1980-01-01/1983-05-16, 1983-01-01/1987-02-28, and 1983-05-27/1991-08-29 respectively.
 
@@
 The first is a drop in the $D_{st}$ index below the threshold of -50~nT.
-These types of events are considered in order to determine if there is a well-defined $\rho_{eq}$ dependence on geomagnetic activity/storms as indicated by $D_{st}$ index.
+These types of events are considered in order to determine if there is a well-defined $\rho_{eq}$ dependence on geomagnetic activity/storms as indicated by the $D_{st}$ index.
 It is expected that the plasmasphere will exhibit two responses near these threshold crossings.
-First is the movement of the plasmasphere earthward (\cite{LemaireEarthsPlasmasphere}) and the second is a possible change in density due to magnetospheric processes.
+First is the movement of the plasmapause earthward (\cite{LemaireEarthsPlasmasphere}) and the second is a possible change in density due to magnetospheric processes.
 
@@
 
-Our first analysis uses data only from the time interval 1989-1991, which corresponds with the interval used in the analysis in \cite{Takahashi2010}.
+Our first analysis uses data only from the time interval 1989-1991, which corresponds with the interval used in \cite{Takahashi2010}.
 In this interval, there were 329 $D_{st}$ events.
@@
 Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians for each event in 1-day bins and then compute the medians across events.
-Error bars for each parameter are the standard deviation of the values used in computing the median divided by the square root of the number of values used.
 
@@
 The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute the medians and red error lines.
-For the non-\req\ medians, the number of measurements used in computing the medians is typically equal to the number of events, which is much larger than the number of \req\ values as we used all available measurements instead of restricting to only values where a non--fill $\rho_{eq}$ value existed.
+Error lines for each parameter are the standard deviation of the values used in computing the median divided by the square root of the number of values.
+For the non-$\rho_{eq}$\ medians, the number of measurements used in computing the medians is typically equal to the number of events, which is much larger than the number of $\rho_{eq}$\ values as all available measurements were used instead of restricting to only values where a $\rho_{eq}$ value also existed.
 
-In the lower panel of Figure \ref{DailyAveragedDstEvents} it is shown that the trends seen in the analysis of 1989-1991 also hold for the entire span of measurements from GOES 6, which spans 1983-1991 - a small elevation on the day of the event relative to the day before and day after, with median averages after the day of the event being slightly lower than that before.
-To determine if the magnitude of the density medians in the top panel of \ref{DailyAveragedDstEvents} on days -1, 0, and 1 are statistically different from each other, we used a two-population bootstrap test.
-A bootstrap sample of the medians for each day was created by sampling the actual values with replacement.
-The observed difference between the medians is shown in the table along with the fraction of observations in 1000 bootstrap differences with a different sign than that observed.
-The results are shown in the fourth column of Table~\ref{BootstrapDifferenceTable}.
-The fourth column shows the results of a 2-population t-test and the fifth column indicates ???.
+In the lower panel of Figure \ref{DailyAveragedDstEvents} it is shown that the trends seen in the analysis of 1989-1991 also hold for the entire span of measurements from GOES 6 - a small elevation on the day of the event relative to the day before and day after, with median averages after the day of the event being slightly lower than that before.
 
-If a statistically significant difference in the medians between two days existed, the fraction is expected to be much smaller ($<$ 5\%).
+To determine if the magnitude of the density medians in the top panel of Figure~\ref{DailyAveragedDstEvents} on epoch days -1, 0, and 1 are statistically different from each other, we used a two-population bootstrap test.
+A bootstrap sample of the medians for each epoch day was created by sampling the values used to compute the median on each epoch day with replacement.
+The observed difference between the medians is shown in Table~\ref{BootstrapDifferenceTable} along with the fraction of observations in 1000 bootstrap differences with a different sign than that observed.
+
+If a statistically significant difference in the medians between two days existed, the fraction of bootstrap samples with a different sign is expected to be much smaller ($<$ 5\%).
 In terms of a hypothesis test, we cannot reject the null hypothesis that the medians are the same with a confidence higher than 100 minus the \% value shown in the table; the highest confidence level of 87.6\% is in the difference between day 0 and day 1.
@@
 
-%\input{../tables/DeltaBootstraps.txt}
-
 \begin{table}
 \small
-
-\input{../tables/DeltaBootstraps-case10.txt}
+%\input{../tables/DeltaBootstraps-case10.txt}
 \caption{Results of test on of means of $\rho_{eq}$ shown in the top panel of Figure~\ref{DailyAveragedDstEvents} between days of threshold crossing  near (day = 1 or -1) or on the day of a $D_{st}$ event (day = 0).}
@@
 
-We have also considered hourly averages as shown in the top panel of Fig.~\ref{HourlyAveragedDstEvents}.
-A total of 668 events were found in the interval of May 1983 through August 1991 with an average duration of 9 hours and a median duration of 3 hours.
-The error bars were computed in the same way as Fig.~\ref{DailyAveragedDstEvents}.
-In this plot, the overall trend is similar to that found in the bottom panel of Fig.~\ref{HourlyAveragedDstEvents} - $\rho_{eq}$ is slightly elevated at the time of the threshold crossing of $D_{st}$ with respect to the values one day before and after, but the elevation is small relative to the error bars around the time of the event onset.
-At this timescale no obvious change in mass density at hourly timescale is visible.
+We have also considered hourly averages as shown in the top panel of Figure~\ref{HourlyAveragedDstEvents}.
+A total of 668 $D_{st}$ events were found in the interval of May 1983 through August 1991 with an average duration of 9 hours and a median duration of 3 hours.
+In this plot, the overall trend is similar to that found in the bottom panel of Figure~\ref{HourlyAveragedDstEvents} - $\rho_{eq}$ is slightly elevated at the time of the threshold crossing of $D_{st}$ with respect to the values one day before and after, but the elevation is small relative to the error bars around the time of the event onset.
 
-The bottom panel of Fig.~\ref{HourlyAveragedDstEvents} contains the events shown in the top panel under the constraint that $D_{st}$ remained below -50~nT for at least twelve hours after the event onset time.
-In the time period of elevated mass density within 12 hours of the start of the event, there were an average of \inote{X} samples per hourly interval.
-This result is consistent with previous observations of large mass density spikes in the plasma trough region during large geomagnetic storms (\cite{Yao2008}; \cite{Takahashi2010}.
-To determine of this relationship can be observed in the events of the top panel of Fig.~\ref{HourlyAveragedDstEvents}, we sorted the events by the average $D_{st}$ values in the time interval of 0-12 hours, split the events in two and recomputed the epoch averages of $\rho_{eq}$.
+The bottom panel of Figure~\ref{HourlyAveragedDstEvents} contains the events shown in the top panel under the constraint that $D_{st}$ remained below -50~nT for at least twelve hours after the event onset time.
+In the time period of elevated mass density within 12 hours of the start of the event, there are only $\sim$5 samples per hourly interval.
+This result is consistent with previous observations of large mass density spikes in the plasma trough region during large geomagnetic storms (\cite{Yao2008}; \cite{Takahashi2010}).
+
+To determine of this relationship can be also observed in the events of the top panel of Figure~\ref{HourlyAveragedDstEvents}, we sorted the events by the average $D_{st}$ values in the time interval of 0-12 hours, split the events in two and recomputed the epoch averages of $\rho_{eq}$.
 The result is that there is no statistically significant difference in the mass density epoch averages for large versus small events.
-This indicates that to confirm a statitical $\rho_{eq}$ dependence on large geomagnetic storms would require a dataset with a much larger number of strong geomagnetic storms.
+This indicates that to confirm a statistical $\rho_{eq}$ dependence on large geomagnetic storms would require a dataset with a much larger number of strong geomagnetic storms.
 
@@
 
-An alternative type of event can be defined that corresponds to large increases in $\rho\ $.
-Figure~\ref{HourlyAveragedRhoEvents} shows the epoch time series for events in which an increase of $\req\ $ above $20$~amu/cm$^2$ defines the start of the event.
-In finding $\rho_{eq}$ events, all fill values were replaced with linearly interpolated values.
-\vinote{Not including \req\ events?}
+An alternative type of event can be defined that corresponds to large increases in $\rho_{eq}$.
+Figure~\ref{HourlyAveragedRhoEvents} shows the epoch time series for events in which an increase of $\rho_{eq}$ above $20$~amu/cm$^2$ defines the start of the event.
+In finding $\rho_{eq}$ events, missing values were replaced with linearly interpolated values.
+These events are associated with positive $B_z$ and low values of $D_{st}$.
+Approximately 8 hours after onset, $\rho_{eq}$ peaks and then slowly decays after 40 hours to pre--onset levels.
 
-Here we see that such events tend to be associated with positive $B_z^{IMF}$ and low geomagnetic activity (\cite{Denton2016}).
+Figure~\ref{HourlyAveragedRhoEvents} can be compared with Figure~9 of \cite{Denton2016}, which shows daily averages of $\rho_{eq}$ from this dataset after the onset of quiet $K_p$ intervals.
+The growth shown here is approximately linear and lasts $\sim$ 12--18 hours whereas the 10 quiet $K_p$ events considered by \cite{Denton2016} showed growth that lasted for at least 48~hours.
 
-To determine if the sign of $B_z^{IMF}$ influences the $\rho\ $ epoch time series, we separated the events by the average of $B_z^{IMF}$ in a time window of $4$~hours.
+To determine if there is an IMF $B_{z}$ dependence, the epoch curve for $\rho_{eq}$ and $B_{z}$ was separated into two parts depending whether $B_z$ was above or below the average four hours before and including the onset hour and four hours after and including the hour of onset; the result is shown in Figure~\ref{fig:BzBinned}.
+Any statistically significant difference at a 95\% confidence level between the two parts is indicated by a green dot on the horizontal axis using the same bootstrap method described previously.
+(At this confidence level, false positives are expected to randomly occur 5\% of the time or 3.6 times for 72 values.) The largest separation occurs when the separation is performed by Figure~\ref{fig:BzBinned} after onset, with more positive $B_z$ leading to larger peak $\rho_{eq}$ than more negative $B_{z}$.
+The rate of change of $\rho_{eq}$ also appears to be insenstive to $B_z$ for approximately 12 hours prior to onset.
+We note that the equivalent epoch separation curves for $P_{dyn}$ had a statistically significant differences similar to that for $B_z$, with higher dynamic pressure playing a role similar to positive $B_z$.
 
-Figure~\label{fig:RhoBinned}(a) shows the epoch curves for $B_z^{IMF}\geq=0$ (257) events and $B_z^{IMF}\ge=0$ (139) have no statistically significant difference.
+Figure~\ref{fig:F107Binned} shows how the epoch average curve of $\rho_{eq}$ in Figure~\ref{fig:BzBinned} depends on $F10.7$.
+Statistically significant differences occur independent of if the separating factor the average of $F10.7$ before or after onset, as expected because the cadence of $F10.7$ is one day and its time scale of variation is longer than that of $\rho_{eq}$.
+Events with high $F10.7$ are associated with higher $\rho_{eq}$ before and after event onset but similar peak values.
+As was the case for $B_Z$, there is an approximately 12--hour time span of linear growth of $\rho_{eq}$ near the time of onset but because the initial starting $\rho_{eq}$ is higher for high $F10.7$, the associated growth rate is lower.
 
@@
 \newpage
-\footnotesize
-\bibliographystyle{plainnat}
+%\footnotesize
+%\bibliographystyle{plainnat}
 \bibliography{paper}
@@
 \clearpage
+
 \section{Figures}
@@
 The top four panels show parameters from \cite{Kondrashov2014ReconstructionOfGaps} and the bottom panel contains $\rho_{eq}$ based on GOES 6 measurements from \cite{Denton} after interpolation and averaging described in the text.
-Dashed horizontal lines in the $D_{st}$ and $\rho_{eq}$ panels indicate sample event cutoff thresholds of $D_{st} = -50$~nT and $\rho_{eq} = 20$~amu/cm$^3$} considered in Section~3.
+Dashed horizontal lines in the $D_{st}$ and $\rho_{eq}$ panels indicate sample event cutoff thresholds of $D_{st} = -50$~nT and $\rho_{eq} = 20$~amu/cm$^3$ considered in Section~3}.
 \label{AllData}
 \end{figure}
+
+\clearpage
 
@@
 \includegraphics[scale=0.40]{figures/ccplot-GOES6.eps}
-\caption{Top: 27-day non-overlapping medians of $F_{10.7}$ and $\log(\rho_{eq})$ from GOES 6.
-Bottom: Correlation between $\log(\rho_{eq})$ and $F_{10.7}$ using medians in non-overlapping hour, day, and 27-day windows.}
+\caption{Top: 27-day non-overlapping medians of $F_{10.7}$ and $log(\rho_{eq})$ from GOES 6.
+Bottom: Correlation between $log(\rho_{eq})$ and $F_{10.7}$ using medians in non-overlapping hour, day, and 27-day windows.}
 \label{ccplot}
@@
 
-\begin{figure}[tp!]
+\begin{figure}[h]
 \centering
 \includegraphics[scale=0.40]{figures/stormavs-dst-50-tak-GOES6.eps}
+\\
 \rule[1ex]{5cm}{1pt}
+\\
 \includegraphics[scale=0.40]{figures/stormavs-dst-day-GOES6.eps}
-\caption{$D_{st}$ events from GOES 6 using daily medians. Top: Events in the interval 1989-1991; compare to \cite{Takahashi2010} Fig.~11. Bottom: Events in the interval 1983-1991.}
+\caption{$D_{st}$ events from GOES 6 using daily medians. Top: Events in the interval 1989-1991; compare to \cite{Takahashi2010} Figure~11. Bottom: Events in the interval 1983-1991.}
 \label{DailyAveragedDstEvents}
 \end{figure}
+
+\clearpage
 
@@
 \includegraphics[scale=0.40]{figures/stormavs-dst.eps}
+\\
 \rule[1ex]{5cm}{1pt}
+\\
 \includegraphics[scale=0.40]{figures/stormavs-dd12-GOES6.eps}
 \caption{$D_{st}$ events from GOES 6 using hourly medians.
-Top: Events in the interval 1983-1991; compare to bottom panel Fig.~\ref{DailyAveragedDstEvents}.
+Top: Events in the interval 1983-1991; compare to bottom panel Figure~\ref{DailyAveragedDstEvents}.
 Bottom: Same as Top except for constraint that $D_{st}$ stayed below $-50$~nT for at least 12~hours after crossing below $-50$~nT.}
@@
 \includegraphics[scale=0.40]{figures/stormavs-mass-gt20-GOES6.eps}
-\caption{$\req\ > 20$~ amu/cm$^3$ events from GOES 6 using hourly medians.
-As described in the text, there is no statistically significant dependence of the \req\  plot on $B_z$ in the time interval of $\pm 2$~hours around the event.}
+\caption{$\rho_{eq} >$ 20~amu/cm$^3$ events from GOES 6 using hourly medians.
+As described in the text, there is no statistically significant dependence of the $\rho_{eq}$  plot on $B_z$ in the time interval of $pm 2$~hours around the event.}
 \label{HourlyAveragedRhoEvents}
+\end{figure}
+
+\clearpage
+\begin{figure}[tp!]
+  \centering
+  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedBzIMF-case24-t020-tf25-GOES6.eps}
+  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedBzIMF-case24-t025-tf30-GOES6.eps}
+  \caption{$\rho_{eq}$ events of Figure~\ref{HourlyAveragedRhoEvents} separated by the average $B_z$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
+  \label{fig:BzBinned}
 \end{figure}
@@
   \centering
-	\includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedBzIMF-case24-t020-tf25-GOES6.eps}
-	\includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedBzIMF-case24-t025-tf30-GOES6.eps}
-	\caption{Binning \req\ events by $B_z$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
-	\label{fig:RhoBinned}
+  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedF107-case24-t020-tf25-GOES6.eps}
+  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedF107-case24-t025-tf30-GOES6.eps}
+  \caption{$\rho_{eq}$ events of Figure~\ref{HourlyAveragedRhoEvents} separated by the average $F10.7$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
+  \label{fig:F107Binned}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[tp!]
+  \centering
+  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedPdyn-case24-t020-tf25-GOES6.eps}
+  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedPdyn-case24-t025-tf30-GOES6.eps}
+  \caption{Binning $\rho_{eq}$ events by $B_z$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
+  \label{fig:PdynBinned}
+\end{figure}
+
+\begin{figure}[tp!]
+  \centering
+  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedV_SW-case24-t020-tf25-GOES6.eps}
+  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedV_SW-case24-t025-tf30-GOES6.eps}
+  \caption{Binning $\rho_{eq}$ events by $B_z$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
+  \label{fig:V_SWBinned}
+\end{figure}
+
+\begin{figure}[tp!]
+  \centering
+  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedkp-case24-t020-tf25-GOES6.eps}
+  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedkp-case24-t025-tf30-GOES6.eps}
+  \caption{Binning $\rho_{eq}$ events by $B_z$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
+  \label{fig:KpBinned}
+\end{figure}
+
+\begin{figure}[tp!]
+  \centering
+  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinneddst-case24-t020-tf25-GOES6.eps}
+  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinneddst-case24-t025-tf30-GOES6.eps}
+  \caption{Binning $\rho_{eq}$ events by $B_z$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
+  \label{fig:DstBinned}
 \end{figure}

### 2016-07-01 paper/paper.tex
Adding conclusions

@@
 
-\subsection{Conclusions}
+\subsection{Summary and Conclusions}
+
+In recent years, various works have considered the influence of solar wind and geomagnetic control of plasma mass density at geosynchronous orbit, generally using event studies and linear correlations (\cite{Takahashi2006}; \cite{Denton2006}; \cite{Yao2008}; \cite{Takahashi2010}; \cite{Denton2016}).
+The event studies show a possible relationship between $\rho_{eq}$ and solar wind and geomagnetic activity indicators such as $K_p$ and $D_{st}$ while correlation studies have generally found a very weak relationship.
+
+This work presents a comprehensive analysis of two types of events intended to provide insight into the relationship between $\rho_{eq}$ and solar wind and geomagnetic parameters by considering both large geomagnetic events and large $\rho_{eq}$ events.
+The major difficulty with this identification is that enhancements in $\rho_{eq}$ can occur for two reasons: (1) extended period of positive $B_z$, which leads to low geomagnetic activity, plasmasphere refilling, and a possible expansion of the plasmasphere to geosynchronous altitudes and (2) strong negative $B_z$, which leads to the inward motion of the higher density plasmasphere and leaves geosynchronous altitudes in the lower density plasma trough just outside of the plasmapause but at the same time magnetospheric processes may be acting to enhance the mass density at geosynchronous altitudes.
+
+On average, around the time of large geomagnetic events, there is a very weak enhancement of $\rho_{eq}$ and this enhancement does not depend on either the interplanetary magnetic field $B_z$ or the intensity of the geomagnetic event.
+This indicates that there is an approximate balance between magnetospheric enhancement in $\rho_{eq}$ and any reduction due to the inward motion of the plasmasphere.
+$\rho_{eq}$ events are larger when $B_{z}$ is more positive after the onset of the event, which indicates that a substantial portion of the events may due to the apparent mass refilling mechanism described by \cite{Denton2016}.
+Without additional information about the location of the plasmapause, it may not be possible to separate out the conditions required for enhancement due to enhanced magnetospheric activity from this mechanism beyond the observation that over a time span of ~10 years, there were ~5 large geomagnetic events that corresponded to large increases in $\rho_{eq}$ at geosynchronous altitudes.
 

### 2016-07-01 paper/style/agu/aguplus/samplus.tex
Adding bib and style updates

%% Version of source file:
%% Date: 1998 Sep 14
%%  **************************************
%   *  SAMPLE INPUT FOR AGUTeX & AGU++   *
%%  **************************************
%  Various alternatives for the input are shown, commented out.
%  E.g., for the documentstyle options
%        for the authors' names,
%        for the bibliography
%  Feel free to play around with these variations, especially with
%    the style options ms and twocolumn and 11pt/12pt

 %%%% LATEX2E: SELECT ONE OF THE NEXT LINES
\documentclass[jgrga]{aguplus}                     % CAMERA-READY, JGR

%\documentclass[twoside,agupp]{aguplus}             % PREPRINT

%\documentclass[agums]{aguplus}                     % MANUSCRIPT
%                                                   % (ALWAYS 12PT)
%% <<<<<<<<<<<<<<<<<<<<<<<<<<<>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
%%   ADD THIS LINE IF POSTSCRIPT FONTS AVAILABLE
% \usepackage{times}                   % WITH TIMES ROMAN FONT
% ^^^^^^^^^^^^^^^^^^
%%   This is STRONGLY recommended for the camera-ready version!!
%% <<<<<<<<<<<<<<<<<<<<<<<<<<<>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>

 %%%% LATEX 2.09: SELECT ONE OF THE FOLLOWING
%\documentstyle[jgrga,aguplus]{article}         % CAMERA-READY FOR JGR

%\documentstyle[twoside,agupp,aguplus]{article} % PREPRINT, TWOSIDED

%\documentstyle[agums,aguplus]{article}         % MANUSCRIPT (12PT)

%% ADD THIS PACKAGE IF GRAPHICS ARE TO BE IMPORTED
% \usepackage{graphicx}

% SOME EXTRA FEATURES THAT MAY BE TURNED ON WITH APPROPRIATE COMMANDS
% THESE ARE ALL PART OF AGU++, NOT STANDARD AGUTeX
%
\printfigures              % PRINTS OUT FIGURES AT END OF MANUSCRIPT AND
                           %   CAMERA-READY COPY
\doublecaption{35pc}       % FIGURE CAPTIONS PRINTED OUT TWICE, IN REGULAR
                           %   WIDTH AND WIDTH 35 PICAS (STILL REQ'D BY JGR)
                           %   EFFECTIVE ONLY FOR CAMERA-READY COPY
\sectionnumbers            % TURNS ON SECTION NUMBERS, WHICH ARE TURNED
                           %   OFF BY DEFAULT (AGU DISCOURAGES THEM)
\extraabstract             % ADDS SUPPLEMENTAL ABSTRACT WITH PAPER NUMBER
                           %   AT END OF CAMERA-READY COPY (FOR JGR)
%\afour                    % SET PAPER SIZE FOR EUROPEAN A4 SPECIFICATION

%\figmarkoff % INCLUDE TO SUPPRESS AUTOMATIC MARGINAL MARKING OF FIGS, TABLES

%\tighten    % STANDARD AGUTeX: TURNS OFF DOUBLE SPACING IN MANUSCRIPT

% PREAMBLE INFOMATION ABOUT THE PAPER
\lefthead{Smith and Weston}
\righthead{Western Frontiers and Geophysics}
\received{April 1, 1989}
\revised{November 11, 1993}
\accepted{December 25, 1999}
\journalid{JGRA}{January 2000}
\articleid{1}{4}
\paperid{99JZ12345}
\ccc{0000-0000/00/99JZ-12345\$05.00}
   % \cpright{PD}{1999}
   % \cpright{Crown}{1999}
   % (Crown copyrights have no "\ccc{}" information.)
\cpright{AGU}{1999}

\authoraddr{J. G. Smith, Institute for Historical Geophysics, 26 Camrose
            Drive, Houston, Texas}

\authoraddr{H. K. Weston, School for Military Advances, 87 Blackborn Rd,
            London, United Kingdom}

\slugcomment{To appear in the Journal of Irreproducible Results,
             February 30, 1999}

\begin{document}
\title{How the Western Frontiers were Won with the Help of Geophysics}

%
% TWO METHODS FOR GIVING THE AUTHORS' NAMES
%
\author{J. G. Smith}
\affil{Institute for Historical Geophysics, Houston, Texas}

\author{H. K. Weston\altaffilmark{1}}
\affil{School for Military Advances, London, United Kingdom}

\altaffiltext{1}{Present address Playa del Ingeles, Gran Canaria.}

%\author{J. G. Weston\altaffilmark{1} and H. K. Smith\altaffilmark{2,3}}
%\altaffiltext{1}{Institute for Historical Geophysics, Houston, Texas.}
%\altaffiltext{2}{School for Military Advances, London, United Kingdom.}
%\altaffiltext{3}{Present address Playa del Ingeles, Gran Canaria.}

\begin{abstract}
To date, very little has been written about the very important role
played by the magnetosphere during the conquest of the Western Hemisphere.
This paper tries to fill this gap by drawing on historical documents from the
years 1492 to 1888, the most vital years for this development. Almost no
conclusions are drawn as the influence appears to approach absolute zero.
\end{abstract}

% FOR AGUTeX VERSION 4.0 AND LATER, TEXT MUST BE IN article ENVIRONMENT
% FOR EARLIER VERSIONS, THIS ENVIRONMENT IS NOT RECOGNIZED
\begin{article}

\section{Introduction}\label{sec:intro}

%% Citations: \citep for parenthetical (Columbus, 1492), or
%%            \citet for in text, shown by Columbus (1492)

With the discovery of America \citep{colu92} a new continent was opened up.
However its full exploitation by Europeans and their offspring was not fully
complete until many centuries later, as reported by \citet{jame76}. During this
interval, known as the Winning of the West \citep{smit54}, a major role in
the development of the continent was played by the lowly revolver
\citep[e.g.][]{gree00}.  Recently, \citet{phil99} suggested that the
magnetosphere could have played an even more significant role. In order to
pursue this conjecture, the authors of this work have carried out a historical
survey and have found start\-ling\-ly little evidence for such a claim.

\section{The Discovery}
\label{sec:dis}

America was discovered by \citet{colu92}, as illustrated in Figure~\ref{fig:dis}.
Without the use of the compass, this would never have been possible. In fact,
this could be considered the most important (and only) contribution of the
geomagnetism to the development of the American continent.  A painting of
Christopher Columbus' departure is shown in
Plate~\ref{pla:columbus}.

\begin{figure}
  \figbox{8cm}{4cm}{Paste map here}
  \caption[]{\label{fig:dis}
Columbus's voyages to the New World between 1492 and 1504.}
\end{figure}
\begin{plate*}
  \platewidth{35pc}
  \figbox*{}{}{\rule[-9cm]{0pt}{18cm}Paste painting here}
% If an eps graphics file is available, use this line instead:
% \figbox*{}{}{\includegraphics[width=35pc]{cc1492.eps}}
  \caption{\label{pla:columbus}
This lithograph shows famed explorer Christopher Columbus in 1492 departing
on his first voyage in search of a quicker route to Asia. Here, Columbus
takes leave of Ferdinand~V and Isabella, the king and queen of Castile, who
sponsored his first expedition.
(THE BETTMANN ARCHIVE)}
\end{plate*}

The subsequent taming of the West took place with considerable quantities of
lead, but since this non-mag\-ne\-tic, there are no geomagnetic variances
attributed to it.

\section{The Next Five Centuries}
\label{sec:next5}

In Section~\ref{sec:dis}, the discovery of America was described.
Here we will outline the subsequent history until the present. This is best
summarized in Table~\ref{tab:sum}.

\begin{planotable}{cll}
  \tablewidth{20pc}
\tablecaption
{\label{tab:sum}The History of America from Discovery to Present}
\tablehead{\colhead{Date} & \colhead{Event} & \colhead{Ref.}}
\startdata
1492 & Discovery & \citet{colu92}
  \nl
1776 & Independence & \citet{jame76}
  \nl
1954 & Nothing much & \citet{smit54}
  \nl
1999 & Present & \citet{phil99}
\end{planotable}

As can be seen from Table~\ref{tab:sum}, there is almost no mention of
geomagnetism or the magnetosphere at all. This sorry situation is discussed
further and explained away in Section~\ref{sec:end}.

\subsection{The Mathematics of Development}

The complete mathematical description is beyond the scope of this report, but
can be found in \citet{smit54}. The basic equation is
\begin{equation}
    z = \sqrt{x^2 + y^2} \label{eq:z} .
\end{equation}

In addition to Equation~\ref{eq:z}, we also have
\begin{eqnarray}
x & = & A \sin\theta \nonumber \\
y & = & A \cos\theta \nonumber \\
A & = & \int^\infty_0 dt\,f(t)  \label{eq:int}
.\end{eqnarray}
Equations~\ref{eq:z} and \ref{eq:int} together describe the entire time
development of the history of America. Again no geomagnetic term enters.

\subsubsection{Pseudo-mathematics.}
In addition to the true mathematics mentioned above, there are a number of
pseudo-mathematical theories, but these cannot be seriously considered by
reputable scientists.

\section{Conclusions}\label{sec:end}

Considering Figure~\ref{fig:dis} and Table~\ref{tab:sum} we see that the
influence of the geomagnetic and magnetospheric terms is negligible.
Furthermore, equations~\ref{eq:z} and \ref{eq:int} add no insight to the
problem. We must therefore conclude that \citet{phil99} incorrectly supposed
such a connection to exist.

In spite of this negative result, research will continue on this highly
interesting question. For if it were to prove correct, then the consequences
would be enormous to say the least.

\balance % USE THIS TO BALANCE THE LAST TWO COLUMNS IN TWOCOLUMN MODE

\appendix
%%
%% IF THERE IS ONLY ONE APPENDIX, USE \section*
%% FOR MORE THAN ONE, USE \section FOR EACH APPENDIX
%%
\section*{Mathematical Background}
Apart from the following equation
%%
%% HERE IS AN EXAMPLE OF AN EQUATION THAT IS TO BE BROKEN UP IN TWOCOLUMN
%% MODE, BUT LEFT IN ONE LINE IN ONECOLUMN
%%
\iftwocol{% HERE FOLLOWS THE TWOCOLUMN VERSION
\begin{eqnarray}
(1-x)^n & = & 1 - n x + \frac{n(n-1)}{2}\,x^2 \nonumber\\
 & & -{} \,\frac{n(n-1)(n-2)}{3\cdot2}\,x^3 + \cdots
\end{eqnarray}
}{%  NOW THE ONECOLUMN VERSION
\begin{equation}
(1-x)^n = 1 - n x + \frac{n(n-1)}{2!}\,x^2 - \frac{n(n-1)(n-2)}{3\cdot2}\,x^3 +
\cdots
\end{equation}} % END OF THE \iftwocol DEMONSTRATION
there is not very much to say about mathematical background to this topic.

% IF A LIST OF NOTATIONS IS TO BE INCLUDED, IT COMES AFTER ANY
% APPENDICES BUT BEFORE THE ACKNOWLEDGEMENTS. AGUPLUS PROVIDES
% AN ENVIRONMENT FOR THIS. THE ARGUMENT IS TO BE THE LONGEST
% SYMBOL PRINTED, SO THAT THE SIZE OF THE FIRST COLUMN
% IS PROPERLY SET

\begin{notation}{$V_{\mbox{\small max}}$}
  \item[$V$]  velocity in general
  \item[$V_{\mbox{\small p}}$]
              proton velocity
  \item[$V_{\mbox{\small max}}$]
              maximum velocity over the entire distribution of particles
\end{notation}

\acknowledgments % OR ALTERNATIVELY  \acknowledgements
The authors thank their colleagues for continuing support and discussion
around the coffee breaks. The editor thanks X. Y. Furore and another referee
for assisting in evaluating this paper.

%% TWO METHODS FOR INCLUDING THE BIBLIOGRAPHY (LIST OF REFERENCES)
%% EITHER TYPE IN THE ENTRIES YOURSELF AS SHOWN HERE IN
%% `thebibliography' ENVIRONMENT,
%%        OR
%% USE THE FOLLOWING TWO COMMANDS SO THAT BIBTEX WILL GENERATE
%% `thebibliography' TEXT FOR YOU AND READ IT IN.
%%
\bibliographystyle{agu}
%<-- LIST OF REFERENCES TO BE IN "AGU" STYLE
\bibliography{sample}
       %<-- REFERENCES ARE IN FILE "SAMPLE.BIB"

\end{article} % AGUTeX VERSION 4.0 AND LATER

\end{document}

### 2016-07-01 paper/style/agu/old/aguguide.tex
Adding bib and style updates

%%  AGUGUIDE.TEX  -- August 6, 1996 version
%
%%  User Guide for AGU's LaTeX Style Files.
%
%%  This document should be LaTeXed and 
%   printed, not viewed on screen.

\documentstyle[agupp]{article}
\setcounter{secnumdepth}{4}
\hyphenation{com-pu-scripts manu-script 
manu-scripts Springer-Ver-lag}

\begin{document}
\twocolumn

\title{\Large AGU's \LaTeX\ STYLE FILES Version 4.0}
\vspace{-2pc}

\begin{article}
\section{Introduction --- New Style Files}

\LaTeX\ style files have been created in order to 
ease the task of preparing AGU manuscripts for publication.
This guide contains instructions for using AGU's \LaTeX\ 
package, which consists of substyles to the standard \LaTeX\ 
{\tt article} style.

These instructions accompany version 4.0 of AGU's \LaTeX\ 
style files.  Version 4.0 contains many features and 
additions, such as automatic generation of the second 
set of figure captions and the potential to generate JGR 
supplemental abstracts.  Earlier formatting problems have 
been corrected as well.

Files created in previous versions of AGU's style files 
will run with this version, though you will need to include 
a \verb"\begin{article}" command in front of the body text 
and \verb"\end{article}" after the references (these 
control the single-column format).

Authors are expected to have at least a basic knowledge of 
\LaTeX.  Those who are unfamiliar with \LaTeX\ will need 
additional sources of information.  A number of publications 
are listed in the reference section of this guide.

AGU does not yet accept electronic submission of 
manuscripts.

\section{For Assistance}

For questions about AGU's \LaTeX\ style files, e-mail 
instruct@kosmos.agu.org (include your AGU paper number, 
if available) or call 202/462-6900, ext. 216.

To ask about the status of a manuscript, contact 
AGU's Author Information Line at 202/939-3200 
or e-mail cust\_ser@kosmos.agu.org (include your 
AGU paper number, if available).

\section{Creating Camera-Ready Manuscripts in \LaTeX}

Commands needed to create a camera-ready manuscript will 
be described in the same order they should appear in the 
input file.

The sample.tex file that accompanies this guide can be 
used as a sample document (simply \LaTeX\ and print it) 
or it can be used as a template (replace the sample text 
with the text of your manuscript and delete any extraneous
commands).

\subsection{Selecting a Document Style}

The first command in a \LaTeX\ manuscript must declare 
the overall style of the document.  AGU's \LaTeX\ 
style files provide several different formats.  There are 
five ``galley'' styles, a ``manuscript'' style, and a 
``preprint'' style.

The galley styles create camera-ready galley pages that 
authors may submit to AGU for publication.  Note that 
only one column is printed on a page; the single columns 
are placed into two-column format by AGU staff.
\vspace{10pt}

$\bullet$ The {\tt jgrga} substyle creates camera-ready 
          manuscripts for three journals:  {\it Journal of 
       Geophysical Research}, {\it Global Biogeochemical 
      Cycles}, and {\it Paleoceanography}.
\vspace{10pt}

$\bullet$ The {\tt grlga} substyle creates camera-ready 
       manuscripts for {\it Geophysical Research Letters}.
\vspace{10pt}

$\bullet$ The {\tt tecga} substyle creates camera-ready 
        manuscripts for {\it Tectonics}.
\vspace{10pt}

$\bullet$ The {\tt radga} substyle creates camera-ready 
   manuscripts for {\it Radio Science}.
\vspace{10pt}

$\bullet$ The {\tt rtjga} substyle creates camera-ready 
       manuscripts for the Russian translation journals.
\vspace{10pt}

$\bullet$ The {\tt agupp} substyle (preprint substyle) 
   creates a two-column format suitable for 
       distribution among colleagues.  This style can 
         be used as is, or \LaTeX\ style writers at your 
        institution may use this as a starting point for 
       creating their own preprint styles.  Do not submit 
     output from this style to AGU as camera-ready copy!
     Please note that the two-column format begins 
          at the point a \verb"\twocolumn" command appears 
       in the text.  If \verb"\twocolumn" is not 
      specified, the introductory material of the paper 
      will be set in one-column mode and the two-column 
      mode will engage with the first \verb"\section" 
        command.
\vspace{10pt}

$\bullet$ The {\tt agums} substyle (manuscript substyle)
   creates pages with large, double-spaced type with 
      wide margins for first-time submission to AGU 
          editors (i.e., for peer review and copyediting).
        This style uses a 12-point font.  If a font size 
       smaller than 12 is chosen, the {\tt agums} substyle 
    issues a warning message and will automatically 
        reset the size to 12 points; the file will still 
       be processed.
\vspace{10pt}

These style files are all substyles to the standard 
\LaTeX\ {\tt article} style and should be selected 
as substyle options, as shown:

\begin{center}
\begin{quote}
\verb"\documentstyle[jgrga]{article}" \\
\verb"\documentstyle[grlga]{article}" \\
\verb"\documentstyle[tecga]{article}" \\
\verb"\documentstyle[radga]{article}" \\
\verb"\documentstyle[rtjga]{article}" \\
\verb"\documentstyle[agupp]{article}" \\
\verb"\documentstyle[12pt,agums]{article}"
\end{quote}
\end{center}

\noindent The \verb"\documentstyle" command must appear 
first in any \LaTeX\ file.  Only one \verb"\documentstyle" 
may be chosen; other \verb"\documentstyle" commands must 
either be deleted or preceded by a comment symbol~({\tt \%}).

\subsection{Running Heads}

Authors must supply running head information.
There are two running head commands: \verb"\lefthead{}" 
and \verb"\righthead{}".

In the \verb"\lefthead{}" command, type only the last 
name(s) of the author(s) in all capital letters between 
the curly braces.  If your manuscript has three or 
more authors, type only the last name of the first author 
followed by ``ET AL.''

In the \verb"\righthead{}" command, type a short version of 
the article title (or include the entire title, if it fits) 
in all capital letters between the curly braces.

You may type a total of 60 characters (including letters, 
punctuation, and spaces) between the curly braces in 
either the \verb"\lefthead" or \verb"\righthead" commands 
(i.e., 10 characters in one command and 50 in the other 
is acceptable).  Please avoid nonstandard abbreviations.

\subsection{Received, Revised, and Accepted Dates}

\begin{quote}
\verb"\received{January 13, 1996}"\\
\verb"\revised{April 3, 1996}"\\
\verb"\accepted{August 6, 1996}"
\end{quote}

Received, revised, and accepted dates are supplied by 
your AGU editor.  The information typed in these commands 
will print at the end of the manuscript (after the 
references and author addresses).  Please type dates 
in the format shown above and in the sample.tex document.

The {\tt agums} style prints a blank line for the 
{\tt received} date if no text is included.

\subsection{Manuscript Information}

{\it Geophysical Research Letters} (GRL) manuscripts often 
have such quick turnaround times that authors do not 
receive manuscript information for their documents.
If you are submitting a camera-ready manuscript to GRL,
you may leave the \verb"\paperid", \verb"\cpright",
and \verb"\ccc" commands empty.

\subsubsection{Paper number}

Type your manuscript's AGU paper number between 
curly braces in the \verb"\paperid{}" command.  All 
manuscripts accepted by AGU are assigned a paper number, 
which is used to track and identify manuscripts.  AGU 
paper numbers contain two digits indicating the year a
manuscript was received at AGU, two letters indicating 
the journal, and five digits indicating in what order 
the manuscript was received at AGU headquarters.

\subsubsection{Copyright}

Type your copyright information between the first
set of curly braces in the \verb"\cpright{}{YEAR}" 
command (where {\tt YEAR} is the year the manuscript
is published).  There are three copyright options 
available.
\vspace{11pt}

1.~~If your paper is AGU copyright, choose 
the  ``AGU'' \verb"\cpright" command.
\vspace{11pt}

2.~~If your paper is in the public domain, 
choose the ``PD'' \verb"\cpright" command.
\vspace{11pt}

3.~~If your paper is Crown copyright, 
choose the ``Crown'' \verb"\cpright" command.
\vspace{11pt}

Copyright type is case-sensitive, so you must
type the command exactly as shown above.

If you are not sure which copyright to choose, 
please contact your production coordinator.
You must choose one of these copyright options 
(except for GRL manuscripts).

\subsubsection{Copyright Clearance Center Code}

Type your Copyright Clearance Center code between
curly braces in the \verb"\ccc" command.  (This
code is provided by your journal editor.)  Crown 
copyrights have no \verb"\ccc" information.  Do not 
forget to place a backslash in front of the dollar
sign or it will be interpreted as a math command.

\subsection{Author Addresses}

For author postal addresses, group authors by affiliation 
and list them in alphabetical order between curly braces 
in \verb"\authoraddress" commands.

Names include first initial only, optional middle initial, 
and last name.  If available, include e-mail addresses as 
shown in the sample.tex document.  E-mail addresses may be 
broken after a period or after the @ sign.  If your e-mail 
address includes an underscore, don't forget to place a 
backslash in front of it or it will be interpreted as a 
command.

Note that author addresses are different from author
affiliations.  Author addresses should include complete
postal address information, while author affiliations
include only department, institution, town, and state
(if state is not included in the name of the institution)
or country (if not the United States).

When {\LaTeX}ed, author addresses appear after the
references section.

\subsection{Slug Comments}

Authors may include short remarks on the title page 
of {\tt agums} and {\tt agupp} substyles (e.g.\ the 
name and date of the journal in which an article 
is scheduled to appear).

Type slug comments between the curly braces of a
\verb"\slugcomment{}" command.

In the {\tt agums} style, slug comments appear after 
the manuscript dates; in the {\tt agupp} style, they 
appear in the upper left corner of the title page.
Slug comments do not appear in the camera-ready styles.

\subsection{Numbering Your Sections}\label{numbring}

If you want \LaTeX\ to automatically number your sections, 
type \verb"\setcounter{secnumdepth}{4}" in the preamble 
of your input file (i.e., in front of your 
\verb"\begin{document}" command, as shown in the 
sample.tex document).  If you do not want section numbers,
type \verb"\setcounter{secnumdepth}{0}" in the \linebreak
preamble of your input file.

\subsection{``Begin Document'' and Front Matter \protect\\
Commands}

The main portion of the manuscript starts with a
\verb"\begin{document}" command, which is followed
by the front matter (title, author(s), affiliation(s),
and abstract).

\subsection{Title}

Type the title of your manuscript between the curly 
braces in the \verb"\title{}" command.  Capitalize 
only acronyms, first letter of the first word, first 
letter of proper nouns, first letter of the first word
after colons, and first letter of the first word of a 
subtitle.

If the title exceeds one line, break it so that the 
first line is longer than the second line; break the 
title before articles, prepositions, and conjunctions.
To break the title, type a double backslash where you 
want the break to occur, as shown in the sample.tex 
document.

\subsection{Authors and Affiliations}

\subsubsection{Authors}

Type author names between the curly braces in 
\verb"\author{}" command(s).  Author names consist 
of first name or initial, optional middle name or
initial, and last name.

If it is necessary to break author lines, make sure 
you break them between two author's names (using 
double backslash \verb"\\" commands).

\subsubsection{Affiliations}

Type affiliation information between the curly braces 
in an \verb"\affil{}" command immediately after each 
\verb"\author" command.  \linebreak Each \verb"\author" 
command must be followed by a corresponding \verb"\affil"
command.

\subsubsection{Alternate affiliations}

Authors often have affiliations in addition to their 
principal employer.  If your authors have such 
alternate affiliations, type an \verb"\altaffilmark{}" 
command after the author name, type a footnote number 
between the curly braces, then type the corresponding 
alternate affiliation information between curly braces 
in an \verb"\altaffiltext{}{}" command below the primary
author affiliation commands, as shown in the sample.tex 
document.  There must be a separate \verb"\altaffiltext"
command for each alternate affiliation.

This information will print as footnotes after the 
reference section in your {\LaTeX}ed manuscript and 
will appear on the bottom left-hand corner of the 
first page of your published manuscript.

\subsubsection{Footnoted affiliations}

If your manuscript contains more than three author 
and affiliation groupings, then all author names must 
be typed together in a single \verb"\author" command.
Then, type an \verb"\altaffilmark{}" command after each 
author name, and type each author affiliation between 
curly braces in \verb"\altaffiltext{}{}" commands.

Each affiliation should appear in a separate \linebreak
\verb"\altaffiltext{}{}" command, and the number 
in the \verb"\altaffilmark{#}" command should match 
the number in the appropriate \verb"altaffiltext{#}{}" 
command.  There is an example of this format in the 
sample.tex document.

\subsection{Abstract}

Type your abstract between \verb"\begin{abstract}"
and \verb"\end{abstract}" commands.

An abstract consists of a one-paragraph summary
of your paper, in 250 words or fewer.  Do not cite
references unless absolutely necessary.  If you
must cite, place the citation in square braces
using italic type (this abstract citation format
is new).  Do not include displayed material.

\subsection{Sections}

AGU's \LaTeX\ style files support four section~levels.

$\bullet$~Level 1 heads use \verb"\section{}" commands.

$\bullet$~Level 2 heads use \verb"\subsection{}" commands.

$\bullet$~Level 3 heads use \verb"\subsubsection{}" commands.

$\bullet$~Level 4 heads use \verb"\subsubsubsection{}" commands.

For level 1 and level 2 heads, capitalize the first 
letter of each word (except for prepositions, conjunctions, 
and articles that are 3 letters or shorter).  Do not 
hyphenate level 1 or level 2 heads.  To break lines, 
type \verb"\protect\\" where you want a break to occur.

For level 3 and level 4 heads, capitalize only acronyms, 
the first letter of the first word, first letter of proper 
nouns, and first letter of the first word after colons.
Hyphenation is permitted in level 3 and level 4 heads, 
if needed.  You must include at least two level 3 heads 
per level 2 head.  A level 4 head cannot directly follow 
a level 3 head; there must be a least one sentence between
the two heads.

Note that these commands delimit sections by marking the 
beginning of each section; there are no separate commands 
to identify the ends.

If you want to number your sections, see the information 
in section \ref{numbring}, above.

\subsection{Manuscript Text}

Type a \verb"\begin{article}" command, then begin 
the text of your manuscript.  Include section heads
wherever appropriate.  You may begin your text with 
an introductory section head, but this is not required.

The body of the manuscript text must start with the 
\verb"\begin{article}" command, and you must include 
an \verb"\end{article}" command after the references 
section (otherwise, your text will not print at the 
proper column width).

Do not underline text.  Italics should only be used 
for math variables and text citations.

See section \ref{formtext} for information on formatting
text in \LaTeX.

\subsection{Appendices}

If your manuscript contains appendices, type an
\verb"\appendix" command, then type your appendix
section headers within \verb"\section{}" commands,
with the appropriate appendix introduction, for example,
\verb"\section{Appendix A: Your Title}."

If you have several appendix sections, lettering in
appendix headers should match the above example.
If there is only one appendix, lettering does not
appear in the header: \verb"\section{Appendix: Your Title}."

The \verb"\appendix" command causes all following equations 
to use a lettered number (for instance, A1).  This is to 
distinguish appendix equations from equations that appear 
in the main body of the manuscript.

Appendix tables must be manually labeled.  If your manuscript 
contains tables that accompany an appendix section, you must 
use \verb"\tablenum{}" commands and label the table(s) accordingly.
(If there is one appendix section and one table, the table 
number will be \verb"\tablenum{A1}"; if there are two appendix 
sections, tables appearing in the second section will begin 
with \verb"\tablenum{B1}", etc.)  See the sample.tex document for
examples.

\subsection{Acknowledgments and Editor \protect\\
Acknowledgments}

Authors may include an acknowledgments section, if 
desired.  Acknowledgments appear after the last paragraph 
of manuscript text or after the appendices (if any).
Acknowledgments may be only one paragraph in length.

Type an \verb"\acknowledgments" command, then begin your 
acknowledgments text.  Be sure to spell ``acknowledgments'' 
exactly as it appears; otherwise, \LaTeX\ will not recognize 
the command.  There is no ``end acknowledgments'' command.

If your manuscript contains only one acknowledgment, use 
an \verb"\acknowledgment" command to produce a singular 
``Acknowledgment'' subhead.

If your manuscript contains Editor's acknowledgments (for
{\it JGR--Space Physics} only) set them in a new paragraph 
one empty line below the regular acknowledgments, as shown 
in the sample.tex document.

\subsection{References and Citations}

There are two methods for managing citations and 
references.  One method uses \verb"\begin{references}"
and \verb"\end{references}" commands.  The second \linebreak
method uses \verb"\begin{thebibliography}{}" and linebreak
\verb"\end{thebibliography}{}" commands.  See the 
sample.tex document for examples of each style.

\subsubsection{Method 1}
Authors may enter properly formatted citations directly 
in the manuscript text and enclose those citations in 
\verb"\markcite{}" commands.  This method uses a 
\verb"\begin{references}" and \verb"\end{references}" 
environment for your reference section.  Method 1 
marks all citations in your manuscript, but there 
is no interaction between the \verb"\markcite" 
commands and the reference section.

Type a \verb"\begin{references}" command
to start your reference section.  This command
automatically produces a correctly formatted 
``Reference'' head.  Next, type a \verb"\reference" 
command.  This command must appear in front of 
every reference in your reference section, or 
your references will not format properly.
Type reference information after the 
\verb"\reference" command.  It is the author's
responsibility to place bibliographic reference
information in the proper order with correct 
punctuation.  After the last reference in your
reference section, type an \verb"\end{references}"
command, then type an \verb"\end{article}" command.

To create in-text citations, enclose each citation
within a \verb"\markcite" command.  In-text
citation format italicizes all author names
and uses nonitalic type for publication years.
There are two ways to include in-text citations,
depending on the way you phrase your sentence.
You may either include an entire reference within
square braces \markcite{[{\it Merritt et al.,} 
1996]} or you may mention the author as part of 
your sentence and include only the year in braces, 
as in \markcite{{\it Ono} [1996]}.  Method 2 cannot 
create the second citation format, so if your 
manuscript ever contains this format, you should 
probably use method 1.

\subsubsection{Method Two}
Authors may create automated in-text citations 
with \verb"\cite" commands that correspond to tags 
in \LaTeX's \verb"\thebibliography{}" environment.
This method requires authors to create proper 
journal format within \verb"\bibitem" commands.

Type a \verb"\begin{thebibliography}{}" command to start
your reference section.  This command automatically 
produces a correctly formatted ``Reference'' head.

Next, type \verb"\bibitem[LABEL]{TAG} \reference"
where {\tt LABEL} is the correct AGU in-text
citation format (i.e.,
\verb"\bibitem[{\it Johnson,} 1996]{j96}" \linebreak
\verb"\reference").  {\tt TAG} text is chosen by the 
author and may follow any preferred format.  Type 
the full text of your reference after the 
\verb"\bibitem" command.  A \verb"\bibitem" 
command must appear in front of every reference 
in your reference section, or your references will 
not format properly.  It is the author's responsibility
to place bibliographic reference information in the 
proper order with correct punctuation.  After 
the last reference in your reference section, 
type an \verb"\end{thebibliography}" command, 
then type an \verb"\end{article}" command.

To create in-text citations, type \verb"\cite{TAG}", 
where the {\tt TAG} is identical to the {\tt TAG} 
used in the corresponding reference's 
\verb"\bibitem[]{TAG}" command.  (For example,
\verb"\cite{j96}".)

If you cite two references from two different years,
you must type only one \verb"\cite" in the input file 
and include the second year in square braces, as shown
in the sample.tex document, in order to output correct 
AGU reference style.

If you cite two references in the same year at
the same time, you must use an ``a, b'' format
after the publication year and code the 
\verb"\cite" command in the text as shown 
in the sample.tex document.

\subsubsection{AGU reference style}
Examples of a variety of publications referenced
in AGU bibliographic style are included in the
sample.tex document.  Contact AGU's Editorial
Services Department if you have a question about 
AGU reference style.

\subsubsubsection{In press}
AGU gives a full reference for works accepted for 
publication but not yet released by using the words 
``in press'' in place of the journal volume and 
page numbers and by using the year of acceptance as 
the date.  Manuscripts submitted for publication 
but not yet accepted are considered to be unpublished.

\subsubsubsection{Unpublished work}
AGU does not include personal communications, unpublished 
data, and manuscripts in preparation or submitted for 
publication in the reference list because AGU does not 
consider them to be part of public literature.  Refer to 
these works in text in parentheses by first initials and 
last name of source, type of material, and date.  For 
submitted papers include title and journal submitted to, 
if available.  If you wish, you may include the affiliation 
of the source, for example (J. Wilson, personal communication, 
1971) or (B. L. Smith, University of Massachusetts, unpublished 
data, 1979).

\subsubsubsection{Short journal commands}
Short commands have been created for some of the 
journals referenced most often.  Authors may use 
these commands in reference sections as shorthand 
rather than typing out the journal name.  Note 
that a comma is automatically included after each 
journal listing.

To avoid confusion, the following list shows full 
journal names, but the short commands will produce 
abbreviations appropriate for AGU bibliography 
style (thus ``\verb"\apj"'' produces ``\apj''):
\vspace{-10pt}
\begin{center}\begin{tabular}{ll}
\verb"\apj"    & {\it Astrophysical Journal}\\
\verb"\bams"   & {\it Bulletin of the American Meteorological}\\
               & \hspace{2em}{\it Society}\\
\verb"\bssa"   & {\it Bulletin of the Seismological Society of}\\
               & \hspace{2em}{\it America}\\
\verb"\dsr1"   & {\it Deep Sea Research Part I}\\
\verb"\dsr2"   & {\it Deep Sea Research Part II}\\
\verb"\eos"    & {\it Eos (Transactions of the American}\\
               & \hspace{2em}{\it Geophysical Union)}\\
\verb"\epsl"   & {\it Earth and Planetary Sciences Letters}\\
\verb"\gca"    & {\it Geochimica and Cosmochimica Acta}\\
\verb"\gji"    & {\it Geophysical Journal International}\\
\verb"\gjras"  & {\it Geophysical Journal of the Royal}\\
               & \hspace{2em}{\it Astronomical Society}\\
\verb"\grl"    & {\it Geophysical Research Letters}\\
\verb"\gsab"   & {\it Bulletin of the Geological Society of}\\
               & \hspace{2em}{\it America}\\
\verb"\jatp"   & {\it Journal of Atmospheric and Terrestrial}\\
               & \hspace{2em}{\it Physics}\\
\verb"\jgr"    & {\it Journal of Geophysical Research}\\
\verb"\jpo"    & {\it Journal of Physical Oceanography}\\
\verb"\mnras"  & {\it Monthly Notices of the Royal}\\
               & \hspace{2em}{\it Astronomical Society}\\
\verb"\mwr"    & {\it Monthly Weather Review}\\
\verb"\pag"    & {\it Pure and Applied Geophysics}\\
\verb"\pepi"   & {\it Physics of the Earth and Planetary}\\
               & \hspace{2em}{\it Interiors}\\
\verb"\pra"    & {\it Physical Review A: General Physics}\\
\verb"\prb"    & {\it Physical Review B: Solid State}\\
\verb"\prc"    & {\it Physical Review C: Nuclear Physics}\\
\verb"\prd"    & {\it Physical Review D: Particles and}\\
               & \hspace{2em}{\it Fields}\\
\verb"\prl"    & {\it Physical Review Letters}\\
\verb"\qjrms"  & {\it Quarterly Journal of the Royal}\\
               & \hspace{2em}{\it Meteorological Society}\\
\verb"\rg"     & {\it Reviews of Geophysics}\\
\verb"\rs"     & {\it Radio Science}\\
\verb"\usgsof" & {\it U.S. Geological Survey Open File}\\
               & \hspace{2em}{\it Report }\\
\verb"\usgspp" & {\it U.S. Geological Survey Professional}\\
               & \hspace{2em}{\it Papers}\\
\end{tabular}
\end{center}

\subsubsection{No reference section}
Both the \linebreak
\verb"\end{references}" and 
\verb"\end{thebibliography}{}" \linebreak
commands cause manuscript information to print.
If your manuscript contains no reference section, 
you must place a \verb"\forcesluginfo" command in the 
manuscript after the last paragraph of text (or 
after the acknowledgments, if any).

\subsection{Equations}

AGU journal style allows two types of equations: 
in-text equations and displayed equations.

In-text equations occur within a normal paragraph of
text.  These equations must not interfere with line
spacing.  If an in-text equation does affect line
spacing, it must be coded as a displayed equation.

Displayed equations are single-line or multiline
equations with extra space between the equation
and the preceding and following paragraphs of text.

\subsubsection{In-text equations}

To create math in normal text, type the 
equation within single dollar signs (\$), 
thus \verb"$\pi r^2$" yields $\pi r^2$.

\subsubsection{Displayed equations}

\LaTeX's dis-\linebreak played math environments 
allow displayed equations to be typeset in many 
ways.  The following three are probably used most.

\subsubsubsection{Unnumbered displayed equations}

To create unnumbered displayed equations, type your
equation between \verb"\begin{displaymath}" and  \linebreak
\verb"\end{displaymath}" commands (or use the 
shorter equivalent commands, \verb"\[" and \verb"\]").

\subsubsubsection{Numbered displayed equations}

To create numbered displayed equations, type your
equation between \verb"\begin{equation}" and \linebreak
\verb"\end{equation}" commands.

\subsubsubsection{Aligned and multiline displayed equations}

To create multiline equations or to vertically align
an equation (for example, a derivation where alignment 
is wanted on the equal sign), type \linebreak 
your equation between \verb"\begin{eqnarray}" and \linebreak
\verb"\end{eqnarray}" commands.

\subsubsection{Numbering equations}

By default, \LaTeX\ will number equations sequentially 
from the beginning to the end of a manuscript.  If you 
must specify equation numbers, use \verb"\eqnum{#}", 
where \# is the appropriate equation number, inside 
an {\tt equation} or {\tt eqnarray} environment.
\LaTeX's equation counter is not incremented when 
\verb"\eqnum" is used.

When unnumbered equations are desired, use either the 
{\tt displaymath} environment (for single-line displayed
equations) or use a \verb"\nonumber" command with an 
{\tt eqnarray} environment, (for multiline equations).
The \verb"\nonumber" command must be placed before the 
double backslash (\verb"\\").  \LaTeX's equation counter
is not incremented when \verb"\nonumber" is used.

If the use of \verb"\eqnum" or \verb"\nonumber" causes 
\LaTeX's equation counter to number equations in the wrong 
sequence, the counter may be reset with a \linebreak
\verb"\setcounter{equation}{#}" command, where \#
is the next desired equation number minus one (if
the next number is 7, \# should be 6).  This 
command must be used outside the equation environments.

\subsubsection{Lettering equations}

It may be necessary to group related equations together 
and identify them with letters appended to the same 
equation number (as opposed to each equation having a 
separate numeral).  Set such related equations in 
{\tt equation} or {\tt eqnarray} environments 
(whichever is appropriate may be used), and place 
this grouping within a {\tt mathletters} environment.
See the sample.tex document for examples.

\subsubsubsection{Keyboard math symbols}

You may create some math symbols simply by typing the 
appropriate keyboard command, but most of these commands 
must appear within a math or equation environment or they 
will not print correctly.\\
\verb" +  -  =  <  >  /  :  !  '  |  [  ]  (  )"

%\begin{displaymath}~~ + ~~ - ~~ = ~~ < ~~ > ~~ / ~~ : ~~ ! ~~ ' ~~ | ~~ [ ~~ ] ~~ ( ~~ ) ~~ \end{displaymath}

\subsubsubsection{Fractions in displayed equations}

AGU's \LaTeX\ style files contain an alternate command 
for fractions.  It may be unnecessary to use any command 
other than the standard \LaTeX\ \verb"\frac" command.
\LaTeX\ will set fractions in displayed math as built-up 
fractions.  However, it is sometimes desirable to use 
case fractions in displayed equations.  In such instances, 
authors may a \verb"\case" command rather than the 
\verb"\frac" command.  A shilled fraction is produced 
without any special markup, as shown:
\vspace{-4pt}
\begin{displaymath}
\renewcommand{\arraystretch}{1.4}
\begin{array}{llc}
\mbox{Built-up}    & 
\verb"\frac{1}{2}" & 
\displaystyle\frac{1}{2}\\[.5ex]
\mbox{Case}        & 
\verb"\case{1}{2}" & 
\case{1}{2} \\
\mbox{Shilled}     & 
\verb"1/2"         & 
1/2 \\
\end{array}
\end{displaymath}
\vspace{-10pt}

\subsection{Tables}

AGU's \LaTeX\ style files support two table mechanisms:
(1) A {\tt planotable} environment that facilitates the 
formatting of lengthy tables, and (2) \LaTeX's 
standard {\tt table} and {\tt tabular} environments.
Short tables (smaller than one manuscript page) may 
be created using either mechanism; tables longer than 
one page will require the use of {\tt planotable}.

It is possible to create fairly complex tables with 
arbitrary spacing, straddle heads, rules, etc. in \LaTeX.
Authors who need to create complicated tables should 
consult the \LaTeX\ manual [{\it Lamport}, 1985] for 
details.  Most of \LaTeX's {\tt tabular} capabilities 
are applicable to {\tt planotables} as well.

\subsubsection{Planotables}\label{tbl-sec}

Planotables automatically produce the table lines and
vertical table spacing required for correct AGU table style.
In addition, planotables have several capabilities that 
facilitate the formatting of tables.  For instance, 
it is possible to break long planotables across pages, 
and, where tabular tables print at an automatic width,
authors may choose a specific planotable width.

Type \verb"\begin{planotable}{COLS}", 
where {\tt COLS} \linebreak 
sets the justification for each column.
Choose one letter (``l,'' ``c,'' or ``r'') for each 
column, indicating left, center, or right justification.

To set a planotable to a specific width, type \linebreak
\verb"\tablewidth{}", with the desired table width between 
the curly braces, after the \verb"\begin{planotable}" 
command.  For instance, to create a single-column table 
for the {\it Journal of Geophysical Research,} type 
\verb"\tablewidth{20pc}", where ``20pc'' is 20 picas.
AGU journals permit a variety of table widths.  See the 
``Table Data'' information in your General Instruction 
booklet for the table widths needed for your journal.

Type planotable titles within the curly braces of
\verb"\tablecaption{}" commands.  Capitalize the first
letter of each word (except for prepositions, conjunctions,
and articles that are three letters or shorter).  Do not
allow table caption lines to hyphenate; use a
\verb"\protect\\" command to break lines where necessary.
The \verb"\tablecaption" command automatically generates
the ``{\bf Table \#.}'' information.  To change table
numbers, see ``numbering tables'' in section \ref{numtabl}.

Type a \verb"\startdata" command, and then type your table
data.  The startdata command formats column headings, 
engages the tabular formatting, and produces the table 
caption.  Data within a table row are separated by {\tt \&} 
(ampersand) characters.  The end of each row is indicated 
with a \verb"\nl" command.  Extra vertical space can be 
inserted between rows with a \verb"\vspace{}" command 
(type the desired amount of space between the curly
braces).

If a planotable is longer than one page, \LaTeX\ will 
automatically break it across pages.  To force a page 
break in a particular place, type a \verb"\tablebreak" 
command.  This command affects the following line of 
table data (not the line it appears with) as shown 
in the sample.tex document.

If a cell contains no data, type a \verb"\nodata" 
command to create a ``no data'' symbol.

\subsubsection{Tabular tables}

Tabular tables must begin with a \verb"\begin{table}" 
command and end with an \verb"\end{table}" command.
This {\tt table} environment must enclose the table 
caption, all tabular material, and any footnote or 
table note information associated with a particular table.

Type tabular table titles within the curly 
braces of \verb"\caption{}" commands.  Capitalize 
the first letter of each word (except for prepositions, 
conjunctions, and articles that are three letters or 
shorter).  Do not allow table caption lines to 
hyphenate; use a \verb"\protect\\" command to break 
lines where necessary.  The \verb"\caption" command 
will automatically generate the ``{\bf Table \#.}'' 
information.  To change table numbers, see 
``numbering tables'' in section \ref{numtabl}.

To begin table data, type \verb"\begin{tabular}{COLS}" 
where {\tt COLS} sets the justification for each column.
Choose one letter (``l'', ``c'', or ``r'') for each column,
indicating left, center, or right justification.  Consult the 
\LaTeX\ manual [{\it Lamport}, 1985] for details about using 
a {\tt tabular} environment to prepare tables.  Include only 
one {\tt tabular} environment within each {\tt table} environment.
Type \verb"\end{tabular}" after the table data (but before the 
\verb"\end{table}" command.

Authors must use \verb"\tableline" and spacing commands 
within tabular tables in order to create correct AGU 
table style.  The \verb"\tableline" command produces
a horizontal rule and must be included after the caption,
after the column headings, and after the table data (but
before any table footnotes or table comments).  Set at 
least 6 points of space between each rule and each line 
of text, including any table notes or footnotes.  AGU style
does not permit vertical rules.  Use either \verb"\vspace{}" 
or brace commands (such as \verb"\\[4ex]") to insert 
space.  Examples of both appear in the last table of the 
sample.tex document.

\subsubsubsection{Notation tables}

If your manuscript contains notation tables, use a level 
1 head for the word ``Notation'' and use a tabular 
environment without any rules for the notation information,
as shown in the sample.tex document.  If you numbered your 
sections, place a \verb"\setcounter{secnumdepth}{0}" in 
front of the Notation section head, so it will appear 
flush left and without numbers.  Set both notation
columns flush left.

\subsubsection{Table column headings}

Table column headings must be enclosed in a \verb"\tablehead" 
command.  The individual headings then appear within either 
\verb"\colhead" or \verb"\multicolumn" commands.  Each column 
of data must have a heading.  The double backslash command 
(\verb"\\") may be used to end table headings, and extra 
vertical spacing can be inserted with brace commands 
(\verb"\\[.5ex]").

It is possible for a complicated table heading to overflow
the vertical space allotted for the table heading.  The
fraction of the page allocated for the table heading may be
changed with \verb"\tableheadfrac".  The {\tt NUM} argument
to \verb"\tableheadfrac" should be the decimal fraction of
the page used for heading information.  The default value
is 0.1, meaning that 10\% of the page height is reserved
for the table heading.  It should rarely be necessary to
change this value.

\subsubsection{Table footnotes and table comments}

If your table contains material requiring footnotes, use a
\verb"\tablemark{TAG}" command to indicate the footnote,
then type the associated information (with a corresponding
{\tt TAG}) within a \verb"\tablenotetext{TAG}{}" command.

Short table comments can be created using a \linebreak 
\verb"\tablenotetext{\null}{TEXT}" command, with a \linebreak
\verb"\null" argument as the tag.  Longer comments may
be placed within a \verb"\tablecomment{TEXT}" command.
Lists of table references should use the following
format: \verb"\tablecomment{References:  Names of your
references.}"  Only one paragraph of material is permitted 
at the end of a table, (excluding superscripted footnotes),
so if both references and notes exist, they should
be run in together.  See the sample.tex document for 
examples of table footnotes and comments.

Both \verb"\tablenotetext" and \verb"\tablecomment" 
commands must appear after the column heading information
and before the table data; otherwise, they will affect
indentation of the last table cell.  These commands 
work with planotables and tabular tables.

\subsubsection{Numbering tables}\label{numtabl}

To choose a specific table number or to add a
letter before or after a table number, type a 
\verb"\tablenum{}" command on the line after a 
\verb"\begin{table}" or \verb"\begin{planotable}" 
command.  Type the desired table number between 
the curly braces in the \verb"\tablenum{}" command.
\linebreak \LaTeX's equation counter is affected 
when \verb"\tablenum" commands are used.

\subsubsection{Centered table heads}
AGU's \LaTeX\ style files allow centered, italic 
headings within planotables.  Type center head 
text within a \verb"\cutinhead{}" command.  At 
least two center heads per table are required 
if any are used.

\subsection{Figures and Plates}

Do not incorporate figure or plate captions
into the main text of your manuscript.  All captions 
should appear at the end of your submitted manuscript 
package.  Captions will be placed with the appropriate 
artwork when AGU staff prepares camera-ready pages.

Use a figure environment to create captions for 
gray scale or black-and-white line art; use a plate 
environment to create captions for any color artwork.

See the General Instruction booklet for information on
submitting artwork.

\subsubsection{Figures}

Type \verb"\begin{figure}", type your figure caption 
text between the curly braces in a \verb"\caption{}" 
command, then type \verb"\end{figure}".  Each separate 
figure caption must have at least three commands: a
\verb"\begin{figure}" command, a \verb"\caption" command, 
and an \verb"\end{figure}" command, as shown in the 
sample.tex document.

Several captions may be printed per page, as long 
as there is sufficient room to cut between the captions.

It may be necessary to use \verb"\clearpage" commands 
between a long series of captions, since too many 
captions can cause \LaTeX's memory buffer to overload 
and crash.  The \verb"\clearpage" command clears out 
the memory buffer and begins a new page.

AGU asks authors to submit two sets of captions; one 
set for single-column and one set for double-column 
figures.  You must type in the first set of captions, 
but AGU's \LaTeX\ style files automatically generate 
a second set of captions.  Captions print at the 
correct single- and double-column widths for your 
journal (these widths change depending on the 
document style you choose).

If you need to change the width of a figure caption
(for instance, to create broadside captions), type a 
\verb"\figurewidth{}" command, with the desired
figure width in the curly braces.  When used inside 
a figure environment, the \verb"\figurewidth" command sets 
the width of the first set of captions to the specified 
width.  When used in front of a series of figure captions,
the \verb"\figurewidth" command affects all following
caption widths.  Note that \verb"\figurewidth" commands 
do not affect the automated second set of captions.

Authors may type a \verb"\figurenum{}" command after
a \verb"\begin{figure}" command to explicitly number a
figure caption.  Letters or symbols may also be included.
This command does affect \LaTeX's figure counter.  Figure 
numbers of the second set of captions will always mirror 
the numbers of the first set of captions.  To reset 
\LaTeX's figure counter, type a \verb"\setcounter{figure}{#}" 
command in front of a \linebreak
\verb"\begin{figure}" command.  Set the \# to zero if 
the next desired figure number is one, or to three if the
next desired figure number is four, etc.  This command 
affects figure numbers of any following figures.

Figure caption lines may be broken by using a 
\verb"\protect\linebreak" command.

Be aware that figure width numbering commands may affect 
following plate captions and vice versa.

\subsubsection{Plates}

The plate environment and plate commands are 
similar to the figure environment and figure 
commands, with the word ``plate'' substituted for 
the word ``figure.''  Thus type plate captions in 
a \verb"\caption{}" command, which must appear within 
\verb"\begin{plate}" and %\linebreak 
\verb"\end{plate}" commands.  Use a \verb"\platenum{}" 
command to choose a specific plate number, and use a 
\verb"\platewidth{}" command if you need to choose a 
plate width.  Place a \verb"\setcounter{plate}{#}" 
command, where \# is the next desired equation number 
minus one, outside of a plate environment to reset 
the plate counter (this will affect plate numbers 
of all following plates).

The \verb"\plate" environment automatically generates
a second set of double-column width plate captions.

Be aware that plate width numbering commands may affect 
following figure captions and vice versa.

\subsection{Concluding the File}

The last thing in your input file is the \linebreak
\verb"\end{document}" command.  \LaTeX\ 
cannot process a file without this command.

\section{Callouts}

AGU asks authors to include callouts to indicate the first 
significant time a figure or table is mentioned (these show 
AGU where to place the graphics).  Callouts appear in the 
right margin of the original and any photocopies of your 
camera-ready manuscript.

Authors may either code callouts into the input file, 
or write them on the camera-ready pages using black ink 
(callouts will not be published).  Make sure all callouts 
appear in numerical sequence.

To create a callout, type \verb"\callout{}" around 
the text of a called-out item.  Any type within the 
curly braces will print both in the text of your 
manuscript and in a margin box to the right of your 
text.  You do not need to type called-out text twice.
See the sample.tex document for examples.

\section{Formatting Text in \LaTeX}\label{formtext}

Some text characters require special attention 
so that \LaTeX\ can properly format a file.

The following characters must be preceded by a 
backslash or \LaTeX\ will interpret them as commands:
\begin{quote}
~~~~~~~~~\$~~~\&~~~\%~~~\#~~~\_~~~\{~~~and~~~\}
\end{quote}
must be typed
\begin{center}
\begin{quote}
~~~~~~\verb"\$"~~~\verb"\&"~~~\verb"\%"~~~\verb"\#"
~~~\verb"\_"~~~\verb"\{"~~~and~~~\verb"\}".
\end{quote}
\end{center}

\LaTeX\ interprets all double quotes as closing quotes.
Therefore quotation marks must be typed as pairs of 
opening and closing single quotes, for example, 
{\tt ``quoted text.''}

Note that \LaTeX\ will not recognize greater than or
less than symbols unless they are typed within math
commands (\verb"$>$" or \verb"$<$").

\subsection{Line and Paragraph Spacing}

The ends of words and sentences are marked by white 
space.  It does not matter how many spaces are typed; 
one is as good as 100.  \LaTeX\ treats the end of a 
line in the input file as a space, not as a new line
or a new paragraph.

To create a new paragraph, leave one or more empty 
line(s) between the old paragraph and the new paragraph.

\subsubsection{Double spacing and single spacing}

Authors may wish to adjust vertical spacing within a 
preprint; for instance, double spacing text while 
single spacing tables.  To alternate between single 
and double spacing, use \verb"\singlespace" and 
\verb"\doublespace" commands.

\subsection{Line Breaks and Hyphenation}

If you need to break a line and maintain full justification,
use a \verb"\linebreak" command.  To break a line without
justification, use a double backslash command 
(\verb"\\").  Fragile arguments, such as section heads,
figure captions, or table captions, will not allow 
line breaks unless they are preceded by a {\tt \protect} 
command.  Thus, \verb"\protect\\" is appropriate for 
breaking level 1 and level 2 heads (since they are 
justified left, ragged right) and \verb"\protect\linebreak"
is appropriate for breaking level 3 and level 4 heads 
(since they have full justification).

\LaTeX\ takes care of most hyphenation automatically,
but some words are not included in the hyphenation table.
These words and other bad breaks caused by too much or
too little text on a line must be corrected by the author.
Use optional hyphens (\verb"\-") whenever possible.  When
\LaTeX\ requires a hyphen, the optional hyphen will appear
in the printout; otherwise, the word will appear unhyphenated.
(This is particularly useful when text is changed late in the
typesetting process.)

If a word requiring hyphenation occurs often in your 
manuscript, place a \hyphenation{} command in the 
preamble of your *.tex file; this will add the hyphenated 
words to {\LaTeX}'s hyphenation table.  For example, 
\verb"\hyphenation{geo-magnetism earth-quakes}".

Words that normally appear hyphenated, such as 
``author-prepared,'' may be hyphenated as usual 
(i.e., no special codes are required) but do 
not allow hyphenated words to break across lines in 
your input file, or \LaTeX\ will leave an extra space 
between the hyphen and the second half of the word.
Note that \LaTeX\ will not hyphenate a word that already 
contains a hyphen, so if ``author-prepared'' occurs 
near the end of a line you may have to provide an optional 
hyphen (\verb"author-pre\-pared") or the word ``prepared'' 
will print outside the margins.

\subsection{Bold and Italic Type}

To create boldface text, type an open curly brace,
a \verb"\bf" command, the text you want boldfaced, and
a close curly brace:  \verb"{\bf" {\bf This text is 
boldface} \verb"}".

To create italic text, type an open curly brace,
an \verb"\it" command, the text you want italicized, and
a close curly brace:  \verb"{\it" {\it This text is 
italicized} \verb"}".

\LaTeX\ automatically italicizes text within math or equation 
modes.  If you need normal (nonitalic) type within a math or
equation environment, use a \verb"\rm" command.  (For example, 
\verb"$J_{\rm Hf}t$" produces $J_{\rm Hf}(t)$).

To create boldface and italic type, use \LaTeX's 
\verb"\protect" and \verb"\boldmath" commands and place
the text inside math mode within curly braces: \linebreak 
\verb"{$\protect \boldmath" 
{$\protect \boldmath Bold\ Italic\ Text $} \verb"$}"

\section{Fonts}
AGU accepts manuscripts published in ``Computer Modern,'' 
\LaTeX's default typeface.  If authors have the ability
to select a different typeface, a ``Times Roman,'' ``Times
New Roman,'' or ``Times'' typeface is also acceptable.

Authors with Postscript printers may use AGU's \LaTeX\ 
style files to produce a Times Roman typeface.  Authors 
(or their system managers) must locate and install a dvips 
program.  Dvips is a freely redistributable PostScript 
driver for device independent files.  The program can 
be found on several different anonymous ftp sites
(including Comprehensive \TeX\ Archive Networks such as 
pip.shsu.edu or ftp.tex.ac.uk).  Once the program is 
correctly installed, authors should include the word 
``times'' in the optional argument to the document
style.
\begin{center}
\begin{quote}
\verb"\documentstyle[times,jgrga]{article}"
\end{quote}
\end{center}
Note that the {\tt times} option uses a great deal of 
memory, and that dvips is rather difficult to install.

\section{Cross-referencing}

Cross-referencing equations, tables, and figures in 
text uses ``tags,'' which are defined by the author.
Use a \verb"\label{TAG}" command to define an item 
and \verb"\ref{TAG}" command to refer to the labeled 
item.  Tags may be chosen by the author, but each 
\verb"\label" tag must match the corresponding 
\verb"\ref" tag.

Place \verb"\label" commands immediately after 
the item being labeled.  References to page numbers 
should not be made, since published page numbers 
are different from author's pages.

Table numbers are generated by the \verb"\caption" 
command, not by the \verb"\begin{}" command, so if 
you wish to \verb"\label" tables and figures, the 
\verb"\label" command should appear after the 
\verb"\caption".

See examples of \verb"label" and \verb"ref" commands in 
the sample.tex document.

\LaTeX\ keeps track of labeling commands, cross-reference
information, and counters (such as equation, table, or 
figure counters) by maintaining an auxiliary file in the 
same working directory as the source file.  The auxiliary
file will have an extension of {\tt .aux}.  This file 
should not be deleted, since subsequent \LaTeX\ processing 
uses the auxiliary file to number items and to create 
references.  This auxiliary file mechanism makes it 
necessary to run \LaTeX\ on your input file more than 
once.  This will resolve cross-reference information 
properly.  If changes are made that affect the number 
or the placement of equations, tables, or figure captions,
\LaTeX\ will issue a warning message that advises users 
to ``rerun to get cross-references right.'' If this occurs,
you should \LaTeX\ your file again.  If the error message
appears after two successive \LaTeX\ runs, it is likely
that a reference has been made to an undefined label.

Some older versions of \LaTeX\ do not have enough
memory to run AGU's \LaTeX\ style files without pausing
at undefined references the first time a file is
{\LaTeX}ed.  Either press [Enter] each time this occurs
in the first \LaTeX\ run, or type \verb"\input{update.tex}"
in front of the \verb"\begin{document}" command.  The
``update.tex'' file is part of AGU's \LaTeX\ style file
package and is available on the kosmos.agu.org ftp site.

\section{Abstract Supplement (for \protect\\
\protect\boldmath $JGR$--\protect\boldmath 
$Space~Physics$ only)}

{\it JGR--Space Physics} requires authors to submit 
an abstract supplement with each camera-ready manuscript.
Abstract supplements appear in the {\it JGR--Space Physics}
subsets.  Text of abstract supplements must be 
identical to the text of the abstract published 
with your camera-ready {\it JGR--Space Physics} article.

To generate an abstract supplement, type \linebreak
\verb"\printabstract" in front of the 
\verb"\end{document}" command.  \LaTeX\ will then 
automatically copy any text within the 
\verb"\begin{abstract}" and \verb"\end{abstract}" 
environment, format it in Abstract Supplement style, 
and print it at the end of your \LaTeX\ document.

The \verb"\printabstract" command works only with 
{\tt jgrga.sty}; it will cause all other substyles 
to crash.

\section{Additional Documentation}

The \verb"sample.tex" document is a comprehensive 
example requiring nearly all the capabilities of AGU's
\LaTeX\ style file package (in terms of commands as well
as formatting).  It also contains comments that describe
the purpose of the markup.

This user guide ({\tt\jobname.tex}) was also created 
using commands from AGU's \LaTeX\ style files, although 
it is not the best example of a scientific paper.

A number of commands described in the preceding sections
are standard \LaTeX\ commands, and the reader who is 
unfamiliar with them may refer to the \LaTeX\ manual
[{\it Lamport}, 1985] for details.  A cribsheet listing
all the \LaTeX\ commands (and some pertinent plain \TeX\
commands) with short descriptions of each is published
by the \TeX\ Users Group [{\it Botway and Biemesderfer},
1989].

Authors interested in \TeX\ (rather than \LaTeX) should 
read the {\it\TeX book} [{\it Knuth}, 1984], probably more 
than once.  There is a good deal of general information 
about typography in this source.  Also, many details of 
mathematical typography are discussed in a book by 
{\it Swanson} [1971].

\clearpage
\appendix
\section{\hspace{9pt} Appendix: Special Symbols}

AGU's \LaTeX\ style files contain an assortment
of commands for creating special symbols.  Some
are native to \LaTeX\ and others are a function
of AGU's \LaTeX\ style files.

\subsection{\LaTeX\ Symbols}
\LaTeX\ has a wide variety of special symbols for 
which markup commands have already been defined.
These range from diacritics to exotic mathematical 
operators.  Tables A1--A12 list these commands
by grouping symbols together more or less according 
to function.  Some of these symbols are primarily 
for use in text; most of them are mathematical 
symbols and can only be used in \LaTeX's 
math mode.  These tables are excerpted from the 
{\it \LaTeX\ Command Summary} [{\it Botway and 
Biemesderfer,} 1989].

\subsection{Additional Symbols}

Some of the additional symbol definitions come from the
{\it Astronomy and Astrophysics\/} package \linebreak
{[{\it Springer-Verlag}, 1989]}; some are contributions 
from individuals.  We have tried to select a tractable 
number that were useful and also somewhat difficult to 
get right:

\begin{center}
\begin{tabular}{ll@{\hspace*{3em}}ll}
\verb"\deg"    & \deg    & \verb"\sq"        & \sq \\
\verb"\sun"    & \sun    & \verb"\earth"     & \earth \\
\verb"\arcmin" & \arcmin & \verb"\arcsec"    & \arcsec \\
\verb"\fd"     & \fd     & \verb"\fh"        & \fh \\
\verb"\fm"     & \fm     & \verb"\fs"        & \fs \\
\verb"\fdg"    & \fdg    & \verb"\farcm"     & \farcm \\
\verb"\farcs"  & \farcs  & \verb"\fp"        & \fp \\
\verb"\micron" & \micron & \verb"$\lesssim$" & $\lesssim$ \\
\end{tabular}
\end{center}

Most of these commands can be used in running text as 
well as when setting mathematical expressions.  The 
\verb"\lesssim" and \verb"\gtrsim" commands can only 
be used in math mode, which is logical since they are 
relations.

When discussing atomic species, ionization levels 
can be indicated with the following command:
\begin{quote}
\verb"\ion{ELEMENT}{LEVEL}"
\end{quote}
The ionization state is specified as the second 
argument, and should be given as a numeral.
For example, \ion{Ca}{3} is specified by typing 
\verb"\ion{Ca}{3}".

\begin{references}
\reference 
   Botway, L., and C. Biemesderfer, 
   {\it \LaTeX\ Command Summary},
   \TeX\ Users Group, Providence, R. I., 1989.

\reference 
   Knuth, D., {\it The \TeX book}, 
   Addison-Wesley, Reading, Mass., 1984.

\reference 
   Lamport, L., 
   {\it \LaTeX: A Document Preparation System\/},
   Addison-Wesley, Reading, Mass., 1985.

\reference 
   Springer-Verlag, 
   {\it Springer-Verlag \TeX\ AA Macro Package}, 
   Springer-Verlag, New York, 1989.

\reference 
   Springer-Verlag, 
   {\it Springer-Verlag \LaTeX\ AA Macro Package}, 
   Springer-Verlag, New York, 1990.

\reference 
   Swanson, E., \, 
   {\it Mathematics \, Into \, Type}, \,
   Am. Math. Soc., Providence, R. I., 1979.
\end{references}
\end{article}

\clearpage
\setcounter{table}{0}

\begin{table}
\tablenum{A1}
\caption{Text-Mode Accents}
\tablenotetext{\null}{Note that repeated 
  column heads do not follow AGU style.} 
\begin{tabular}{cccccc}
& & & & & \\[-15pt]
\tableline
& & & & & \\[-5pt]
\multicolumn{1}{c}{Symbol} & 
\multicolumn{1}{c}{Command} & 
\multicolumn{1}{c}{Symbol} & 
\multicolumn{1}{c}{Command} & 
\multicolumn{1}{c}{Symbol} & 
\multicolumn{1}{c}{Command} \\[4pt]
\tableline
& & & & & \\[-6pt]
\`{o}         & \verb"\`{o}"        & \={o}         & 
\verb"\={o}"  & \t{oo}              & \verb"\t{oo}" \\
\'{o}         & \verb"\'{o}"        & \.{o}         & 
\verb"\.{o}"  & \c{o}               & \verb"\c{o}"  \\
\^{o}         & \verb"\^{o}"        & \u{o}         &
\verb"\u{o}"  & \d{o}               & \verb"\d{o}"  \\
\"{o}         & \verb"\""\verb"{o}" & \v{o}         & 
\verb"\v{o}"  & \b{o}               & \verb"\b{o}"  \\
\~{o}         & \verb"\~{o}"        & \H{o}         &
\verb"\H{o}"  &                     &               \\[4pt]
\tableline
& & & \\[-3pt]
\end{tabular}
\end{table}

\vspace{3pc}

\begin{table}
\caption{National Symbols}
\begin{tabular}{ccclcl}
& & & & & \\[-15pt]
\tableline
& & & & & \\[-5pt]
\multicolumn{1}{c}{Symbol}  & 
\multicolumn{1}{c}{Command} & 
\multicolumn{1}{c}{Symbol}  & 
\multicolumn{1}{l}{Command} & 
\multicolumn{1}{c}{Symbol}  & 
\multicolumn{1}{l}{Command} \\[4pt]
\tableline
& & & & & \\[-6pt]
\oe            & \verb"\oe" & \aa           & 
\verb"   \aa"  & \l         & \verb"   \l"  \\
\OE            & \verb"\OE" & \AA           & 
\verb"   \AA"  & \L         & \verb"   \L"  \\
\ae            & \verb"\ae" & \o            & 
\verb"   \o"   & \ss        & \verb"   \ss" \\
\AE            & \verb"\AE" & \O            & 
\verb"   \O"   &            &               \\[4pt]
\tableline
& & & \\[-6pt]
\end{tabular}
\end{table}

\vspace{3pc}

\begin{table}
\caption{Miscellaneous Symbols}
\begin{tabular}{clcccl}
& & & & & \\[-15pt]
\tableline
& & & & & \\[-5pt]
\multicolumn{1}{c}{Symbol} & 
\multicolumn{1}{l}{Command} & 
\multicolumn{1}{c}{Symbol} & 
\multicolumn{1}{c}{Command} & 
\multicolumn{1}{c}{Symbol} & 
\multicolumn{1}{l}{Command} \\[4pt]
\tableline
& & & & & \\[-6pt]
\dag        & \verb"\dag"  & \S                & 
\verb"\S"   & \copyright   & \verb"\copyright" \\
\ddag       & \verb"\ddag" & \P                & 
\verb"\P"   & \pounds      & \verb"\pounds"    \\
\#          & \verb"\#"    & \$                & 
\verb"\$"   & \%           & \verb"\%"         \\
\&          & \verb"\&"    & \_                & 
\verb"\_"   &              &                   \\
\{          & \verb"\{"    & \}                & 
\verb"\}"   &              &                   \\[4pt]
\tableline
& & & & & \\[-6pt]
\end{tabular}
\end{table}

\vspace{3pc}

\begin{table}
\caption{Math-Mode Accents}
\begin{tabular}{cl@{\hspace{4em}}cl}
& & & \\[-15pt]
\tableline
& & & \\[-5pt]
\multicolumn{1}{c}{Symbol} & 
\multicolumn{1}{l}{Command} & 
\multicolumn{1}{c}{Symbol} & 
\multicolumn{1}{l}{Command} \\[4pt]
\tableline
& & & \\[-6pt]
$\hat{a}$   & \verb"\hat{a}"   & 
$\dot{a}$   & \verb"\dot{a}"   \\
$\check{a}$ & \verb"\check{a}" & 
$\ddot{a}$  & \verb"\ddot{a}"  \\
$\tilde{a}$ & \verb"\tilde{a}" & 
$\breve{a}$ & \verb"\breve{a}" \\
$\acute{a}$ & \verb"\acute{a}" & 
$\bar{a}$   & \verb"\bar{a}"   \\
$\grave{a}$ & \verb"\grave{a}" & 
$\vec{a}$   & \verb"\vec{a}"   \\[4pt]
\tableline
& & & \\[-6pt]
\end{tabular}
\end{table}

\clearpage

\begin{table}
\caption{Greek Letters (Math Mode)}
\begin{tabular}{cl@{\hspace{3em}}cl}
& & & \\[-15pt]
\tableline
& & & \\[-5pt]
\multicolumn{1}{c}{Symbol} & 
\multicolumn{1}{l}{Command} & 
\multicolumn{1}{c}{Symbol} & 
\multicolumn{1}{l}{Command} \\[4pt]
\tableline
& & & \\[-6pt]
$\alpha$      & \verb"\alpha"      & 
$\nu$         & \verb"\nu"         \\
$\beta$       & \verb"\beta"       & 
$\xi$         & \verb"\xi"         \\
$\gamma$      & \verb"\gamma"      & 
$o$           & \verb"o"           \\
$\delta$      & \verb"\delta"      & 
$\pi$         & \verb"\pi"         \\
$\epsilon$    & \verb"\epsilon"    & 
$\rho$        & \verb"\rho"        \\
$\zeta$       & \verb"\zeta"       & 
$\sigma$      & \verb"\sigma"      \\
$\eta$        & \verb"\eta"        & 
$\tau$        & \verb"\tau"        \\
$\theta$      & \verb"\theta"      & 
$\upsilon$    & \verb"\upsilon"    \\
$\iota$       & \verb"\iota"       & 
$\phi$        & \verb"\phi"        \\
$\kappa$      & \verb"\kappa"      & 
$\chi$        & \verb"\chi"        \\
$\lambda$     & \verb"\lambda"     & 
$\psi$        & \verb"\psi"        \\
$\mu$         & \verb"\mu"         & 
$\omega$      & \verb"\omega"      \vspace{1em}\\
$\varepsilon$ & \verb"\varepsilon" & 
$\varsigma$   & \verb"\varsigma"   \\
$\vartheta$   & \verb"\vartheta"   & 
$\varphi$     & \verb"\varphi"     \\
$\varrho$     & \verb"\varrho"     & 
              & \vspace{1em}       \\
$\Gamma$      & \verb"\Gamma"      & 
$\Sigma$      & \verb"\Sigma"      \\
$\Delta$      & \verb"\Delta"      & 
$\Upsilon$    & \verb"\Upsilon"    \\
$\Theta$      & \verb"\Theta"      & 
$\Phi$        & \verb"\Phi"        \\
$\Lambda$     & \verb"\Lambda"     &
$\Psi$        & \verb"\Psi"        \\
$\Xi$         & \verb"\Xi"         & 
$\Omega$      & \verb"\Omega"      \\
$\Pi$         & \verb"\Pi"         & 
              &                    \\[4pt]
\tableline
& & & \\[-6pt]
\end{tabular}
\end{table}

\vspace{3pc}

\begin{table}
\caption{Binary Operations (Math Mode)}
\begin{tabular}{cl@{\hspace{3em}}cl}
& & & \\[-15pt]
\tableline
& & & \\[-5pt]
\multicolumn{1}{c}{Symbol} & 
\multicolumn{1}{l}{Command} & 
\multicolumn{1}{c}{Symbol} & 
\multicolumn{1}{l}{Command} \\[4pt]
\tableline
& & & \\[-6pt]
$\pm$              & \verb"\pm"              & 
$\cap$             & \verb"\cap"             \\
$\mp$              & \verb"\mp"              & 
$\cup$             & \verb"\cup"             \\
$\setminus$        & \verb"\setminus"        & 
$\uplus$           & \verb"\uplus"           \\
$\cdot$            & \verb"\cdot"            & 
$\sqcap$           & \verb"\sqcap"           \\
$\times$           & \verb"\times"           & 
$\sqcup$           & \verb"\sqcup"           \\
$\ast$             & \verb"\ast"             & 
$\triangleleft$    & \verb"\triangleleft"    \\
$\star$            & \verb"\star"            & 
$\triangleright$   & \verb"\triangleright"   \\
$\diamond$         & \verb"\diamond"         & 
$\wr$              & \verb"\wr"              \\
$\circ$            & \verb"\circ"            & 
$\bigcirc$         & \verb"\bigcirc"         \\
$\bullet$          & \verb"\bullet"          & 
$\bigtriangleup$   & \verb"\bigtriangleup"   \\
$\div$             & \verb"\div"             & 
$\bigtriangledown$ & \verb"\bigtriangledown" \\
$\lhd$             & \verb"\lhd"             & 
$\rhd$             & \verb"\rhd"             \\
$\vee$             & \verb"\vee"             & 
$\odot$            & \verb"\odot"            \\
$\wedge$           & \verb"\wedge"           & 
$\dagger$          & \verb"\dagger"          \\
$\oplus$           & \verb"\oplus"           & 
$\ddagger$         & \verb"\ddagger"         \\
$\ominus$          & \verb"\ominus"          & 
$\amalg$           & \verb"\amalg"           \\
$\otimes$          & \verb"\otimes"          & 
$\unlhd$           & \verb"\unlhd"           \\
$\oslash$          & \verb"\oslash"          & 
$\unrhd$           & \verb"\unrhd"           \\[4pt]
\tableline
& & & \\[-6pt]
\end{tabular}
\end{table}

\vspace{3pc}

\begin{table}
\caption{Relations (Math Mode)}
\begin{tabular}{cl@{\hspace{4em}}cl}
& & & \\[-15pt]
\tableline
& & & \\[-5pt]
\multicolumn{1}{c}{Symbol} & 
\multicolumn{1}{l}{Command} & 
\multicolumn{1}{c}{Symbol} & 
\multicolumn{1}{l}{Command} \\[4pt]
\tableline
& & & \\[-6pt]
$\leq$        & \verb"\leq"        & 
$\geq$        & \verb"\geq"        \\
$\prec$       & \verb"\prec"       & 
$\succ$       & \verb"\succ"       \\
$\preceq$     & \verb"\preceq"     & 
$\succeq$     & \verb"\succeq"     \\
$\ll$         & \verb"\ll"         & 
$\gg$         & \verb"\gg"         \\
$\subset$     & \verb"\subset"     & 
$\supset$     & \verb"\supset"     \\
$\subseteq$   & \verb"\subseteq"   & 
$\supseteq$   & \verb"\supseteq"   \\
$\sqsubset$   & \verb"\sqsubset"   & 
$\sqsupset$   & \verb"\sqsupset"   \\
$\sqsubseteq$ & \verb"\sqsubseteq" & 
$\sqsupseteq$ & \verb"\sqsupseteq" \\
$\in$         & \verb"\in"         & 
$\ni$         & \verb"\ni"         \\
$\vdash$      & \verb"\vdash"      & 
$\dashv$      & \verb"\dashv"      \\
$\smile$      & \verb"\smile"      & 
$\mid$        & \verb"\mid"        \\
$\frown$      & \verb"\frown"      & 
$\parallel$   & \verb"\parallel"   \\
$\neq$        & \verb"\neq"        & 
$\perp$       & \verb"\perp"       \\
$\equiv$      & \verb"\equiv"      & 
$\cong$       & \verb"\cong"       \\
$\sim$        & \verb"\sim"        & 
$\bowtie$     & \verb"\bowtie"     \\
$\simeq$      & \verb"\simeq"      & 
$\propto$     & \verb"\propto"     \\
$\asymp$      & \verb"\asymp"      & 
$\models$     & \verb"\models"     \\
$\approx$     & \verb"\approx"     & 
$\doteq$      & \verb"\doteq"      \\
              &                    & 
$\Join$       & \verb"\Join"       \\[4pt]
\tableline
& & & \\[-6pt]
\end{tabular}
\end{table}

\vspace{3pc}

\begin{table}
\caption{Variable-Sized Symbols (Math Mode)}
\begin{tabular}{ccl@{\hspace{2em}}ccl}
& & & \\[-15pt]
\tableline
& & & \\[-5pt]
\multicolumn{1}{c}{Symbol} & 
\multicolumn{1}{c}{Display Style} & 
\multicolumn{1}{l}{Command} & 
\multicolumn{1}{c}{Symbol} & 
\multicolumn{1}{c}{Display Style} &
\multicolumn{1}{l}{Command}  \\[4pt]
\tableline
& & & \\[-6pt]
$\sum$                     & $\displaystyle \sum$       &
$\hbox{\verb"\sum"}$       & $\bigcap$                  &
$\displaystyle \bigcap$    & $\hbox{\verb"\bigcap"}$
\vspace{4pt}\\ 
$\prod$                    & $\displaystyle \prod$      &
$\hbox{\verb"\prod"}$      & $\bigcup$                  &
$\displaystyle \bigcup$    & $\hbox{\verb"\bigcup"}$
\vspace{4pt}\\ 
$\coprod$                  & $\displaystyle \coprod$    &
$\hbox{\verb"\coprod"}$    & $\bigsqcup$                &
$\displaystyle \bigsqcup$  & $\hbox{\verb"\bigsqcup"}$
\vspace{4pt}\\ 
$\int$                     & $\displaystyle \int$       &
$\hbox{\verb"\int"}$       & $\bigvee$                  &
$\displaystyle \bigvee$    & $\hbox{\verb"\bigvee"}$
\vspace{4pt}\\ 
$\oint$                    & $\displaystyle \oint$      &
$\hbox{\verb"\oint"}$      & $\bigwedge$                &
$\displaystyle \bigwedge$  & $\hbox{\verb"\bigwedge"}$
\vspace{4pt}\\ 
$\bigodot$                 & $\displaystyle \bigodot$   &
$\hbox{\verb"\bigodot"}$   & $\bigotimes$               &
$\displaystyle \bigotimes$ & $\hbox{\verb"\bigotimes"}$ 
\vspace{4pt}\\ 
$\bigoplus$                & $\displaystyle \bigoplus$  &
$\hbox{\verb"\bigoplus"}$  & $\biguplus$                &
$\displaystyle \biguplus$  & $\hbox{\verb"\biguplus"}$  \\[4pt]
\tableline
& & & \\[-6pt]
\end{tabular}
\end{table}

\vspace{3pc}

\begin{table}
\caption{Delimiters (Math Mode)}
\begin{tabular}{cl@{\hspace{2em}}cl}
& & & \\[-15pt]
\tableline
& & & \\[-5pt]
\multicolumn{1}{l}{Symbol} & 
\multicolumn{1}{l}{Command} & 
\multicolumn{1}{l}{Symbol} & 
\multicolumn{1}{l}{Command} \\[4pt]
\tableline
& & & \\[-6pt]
$($            & \verb"("            & 
$)$            & \verb")"            \\
$[$            & \verb"["            & 
$]$            & \verb"]"            \\
$\{$           & \verb"\{"           & 
$\}$           & \verb"\}"           \\
$\lfloor$      & \verb"\lfloor"      & 
$\rfloor$      & \verb"\rfloor"      \\
$\lceil$       & \verb"\lceil"       &
$\rceil$       & \verb"\rceil"       \\
$\langle$      & \verb"\langle"      & 
$\rangle$      & \verb"\rangle"      \\
$/$            & \verb"/"            & 
$\backslash$   & \verb"\backslash"   \\
$\vert$        & \verb"\vert"        & 
$\Vert$        & \verb"\Vert"        \\
$\uparrow$     & \verb"\uparrow"     & 
$\Uparrow$     & \verb"\Uparrow"     \\
$\downarrow$   & \verb"\downarrow"   & 
$\Downarrow$   & \verb"\Downarrow"   \\
$\updownarrow$ & \verb"\updownarrow" & 
$\Updownarrow$ & \verb"\Updownarrow" \\[4pt]
\tableline
& & & \\[-6pt]
\end{tabular}
\end{table}

\vspace{3pc}

\begin{table}
\caption{Function Names (Math Mode)}
\begin{tabular}{l@{\hspace{2pc}}l@{\hspace{2pc}}
                l@{\hspace{2pc}}l@{\hspace{2pc}}}
& & & \\[-15pt]
\tableline
& & & \\[-6pt]
\verb"\arccos" &   \verb"\csc" &
\verb"\ker"    &  \verb"\min"  \\
\verb"\arcsin" &   \verb"\deg" &
\verb"\lg"     &  \verb"\Pr"   \\
\verb"\arctan" &   \verb"\det" &
\verb"\lim"    &  \verb"\sec"  \\
\verb"\arg"    &   \verb"\dim" &
\verb"\liminf" &  \verb"\sin"  \\
\verb"\cos"    &   \verb"\exp" &
\verb"\limsup" &  \verb"\sinh" \\
\verb"\cosh"   &   \verb"\gcd" &
\verb"\ln"     &  \verb"\sup"  \\
\verb"\cot"    &   \verb"\hom" &
\verb"\log"    &  \verb"\tan"  \\
\verb"\coth"   &   \verb"\inf" &
\verb"\max"    &  \verb"\tanh" \\[4pt]
\tableline
& & & \\[-6pt]
\end{tabular}
\end{table}

\vspace{6pc}

\begin{table}
\caption{Arrows (Math Mode)}
\begin{tabular}{clcl}
& & & \\[-15pt]
\tableline
& & & \\[-5pt]
\multicolumn{1}{c}{Symbol} &
\multicolumn{1}{l}{Command} & 
\multicolumn{1}{c}{Symbol} & 
\multicolumn{1}{l}{Command} \\[4pt]
\tableline
& & & \\[-6pt]
$\leftarrow$          & \verb"\leftarrow"          & 
$\longleftarrow$      & \verb"\longleftarrow"      \\
$\Leftarrow$          & \verb"\Leftarrow"          & 
$\Longleftarrow$      & \verb"\Longleftarrow"      \\
$\rightarrow$         & \verb"\rightarrow"         & 
$\longrightarrow$     & \verb"\longrightarrow"     \\
$\Rightarrow$         & \verb"\Rightarrow"         & 
$\Longrightarrow$     & \verb"\Longrightarrow"     \\
$\leftrightarrow$     & \verb"\leftrightarrow"     & 
$\longleftrightarrow$ & \verb"\longleftrightarrow" \\
$\Leftrightarrow$     & \verb"\Leftrightarrow"     & 
$\Longleftrightarrow$ & \verb"\Longleftrightarrow" \\
$\mapsto$             & \verb"\mapsto"             & 
$\longmapsto$         & \verb"\longmapsto"         \\ 
$\hookleftarrow$      & \verb"\hookleftarrow"      & 
$\hookrightarrow$     & \verb"\hookrightarrow"     \\
$\leftharpoonup$      & \verb"\leftharpoonup"      & 
$\rightharpoonup$     & \verb"\rightharpoonup"     \\
$\leftharpoondown$    & \verb"\leftharpoondown"    & 
$\rightharpoondown$   & \verb"\rightharpoondown"   \\
$\rightleftharpoons$  & \verb"\rightleftharpoons"  & 
$\leadsto$            & \verb"\leadsto"            \\
$\uparrow$            & \verb"\uparrow"            & 
$\Updownarrow$        & \verb"\Updownarrow"        \\
$\Uparrow$            & \verb"\Uparrow"            & 
$\nearrow$            & \verb"\nearrow"            \\
$\downarrow$          & \verb"\downarrow"          & 
$\searrow$            & \verb"\searrow"            \\
$\Downarrow$          & \verb"\Downarrow"          &
$\swarrow$            & \verb"\swarrow"            \\
$\updownarrow$        & \verb"\updownarrow"        & 
$\nwarrow$            & \verb"\nwarrow"            \\[4pt]
\tableline
& & & \\[-6pt]
\end{tabular}
\end{table}

\vspace{3pc}

\begin{table}
\caption{Miscellaneous Symbols (Math Mode)}
\begin{tabular}{cl@{\hspace{3em}}cl}
& & & \\[-15pt]
\tableline
& & & \\[-5pt]
\multicolumn{1}{c}{Symbol} & 
\multicolumn{1}{l}{Command} & 
\multicolumn{1}{c}{Symbol} & 
\multicolumn{1}{l}{Command} \\[4pt]
\tableline
& & & \\[-6pt]
$\aleph$       & \verb"\aleph"       & 
$\prime$       & \verb"\prime"       \\
$\hbar$        & \verb"\hbar"        & 
$\emptyset$    & \verb"\emptyset"    \\
$\imath$       & \verb"\imath"       & 
$\nabla$       & \verb"\nabla"       \\
$\jmath$       & \verb"\jmath"       & 
$\surd$        & \verb"\surd"        \\
$\ell$         & \verb"\ell"         & 
$\top$         & \verb"\top"         \\
$\wp$          & \verb"\wp"          & 
$\bot$         & \verb"\bot"         \\
$\Re$          & \verb"\Re"          & 
$\|$           & \verb"\|"           \\
$\Im$          & \verb"\Im"          & 
$\angle$       & \verb"\angle"       \\
$\partial$     & \verb"\partial"     & 
$\triangle$    & \verb"\triangle"    \\
$\infty$       & \verb"\infty"       & 
$\backslash$   & \verb"\backslash"   \\
$\Box$         & \verb"\Box"         & 
$\Diamond$     & \verb"\Diamond"    \\
$\forall$      & \verb"\forall"      & 
$\sharp$       & \verb"\sharp"       \\
$\exists$      & \verb"\exists"      & 
$\clubsuit$    & \verb"\clubsuit"    \\
$\neg$         & \verb"\neg"         & 
$\diamondsuit$ & \verb"\diamondsuit" \\
$\flat$        & \verb"\flat"        & 
$\heartsuit$   & \verb"\heartsuit"   \\
$\natural$     & \verb"\natural"     & 
$\spadesuit$   & \verb"\spadesuit"   \\
$\mho$         & \verb"\mho"         & 
               &                     \\[4pt]
\tableline
& & & \\[-6pt]
\end{tabular}
\end{table}

\end{document}

### 2016-07-01 paper/paper.tex

@@
 \usepackage[square,comma,authoryear]{natbib}
+\usepackage{aas_macros}
 \usepackage{epsfig}
+\usepackage{amsmath}
 \usepackage{style/lineno}
-\usepackage{amsmath}
 %\usepackage{booktabs}
@@
 \small
-%\input{../tables/DeltaBootstraps-case10.txt}
+\input{../tables/DeltaBootstraps-case10.txt}
 \caption{Results of test on of means of $\rho_{eq}$ shown in the top panel of Figure~\ref{DailyAveragedDstEvents} between days of threshold crossing  near (day = 1 or -1) or on the day of a $D_{st}$ event (day = 0).}
@@
 \centering
-\includegraphics[scale=0.40]{figures/stormavs-dst.eps}
+\includegraphics[scale=0.40]{figures/stormavs-dst-GOES6.eps}
 \\
@@
   \centering
-  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedBzIMF-case24-t020-tf25-GOES6.eps}
-  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedBzIMF-case24-t025-tf30-GOES6.eps}
+  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedB_z-case24-t020-tf25-GOES6.eps}
+  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedB_z-case24-t025-tf30-GOES6.eps}
   \caption{$\rho_{eq}$ events of Figure~\ref{HourlyAveragedRhoEvents} separated by the average $B_z$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
@@
   \centering
-  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedkp-case24-t020-tf25-GOES6.eps}
-  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedkp-case24-t025-tf30-GOES6.eps}
+  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedKp-case24-t020-tf25-GOES6.eps}
+  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedKp-case24-t025-tf30-GOES6.eps}
   \caption{Binning $\rho_{eq}$ events by $B_z$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
@@
   \centering
-  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinneddst-case24-t020-tf25-GOES6.eps}
-  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinneddst-case24-t025-tf30-GOES6.eps}
+  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedDst-case24-t020-tf25-GOES6.eps}
+  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedDst-case24-t025-tf30-GOES6.eps}
   \caption{Binning $\rho_{eq}$ events by $B_z$ value (a) at onset and four hours before, and (b) at onset and four hours after.}

### 2016-07-05 BasicPlots.m
Updated figures to look better

@@ -329,12 +329,12 @@ if(MakePaperPlots && stormcase==28 && sy==1989 && ey==1989) %For a short time pe
     
     plot(FILLEDTime,xnew,'r','LineWidth',1.5);
     text(0.01,0.1,'D_{st} (nT)','Units','normalized','FontSize',14);
-    legend('Actual',sprintf('IR Model - CC %2.2f',corr),sprintf('Persistence Model - %2.2f',corr2),'Location','SouthEast')
-    
+    h_legend=legend('Measured',sprintf('IR Model - CC %2.2f',corr),sprintf('Persistence Model - %2.2f',corr2),'Location','SouthEast');
+    set(h_legend,'FontSize',14)
     h(2)=subplot('position',subplotstack(2,2)); 
     
     plot(FILLEDTime,VBS,'k','LineWidth',1.5);
-    text(0.01,0.92,'V_{B_S}','Units','normalized','FontSize',14);
+    text(0.01,0.92,'vB_S (\mu{}V/m)','Units','normalized','FontSize',14);
     set(findobj('type','axes'),'xticklabel',{[]});
 set(findobj('type','axes'),'xgrid','on','ygrid','on','box','on')
 axis tight;
@@ -342,7 +342,7 @@ datetick('x','keeplimits')
 set(findobj('type','axes'),'xtick',get(h(end),'xtick'))
 linkaxes(h,'x')
 axis tight;
-    xlabel('Date')
+    xlabel('Date of 1989')
     
     print('-depsc2', '-r200', sprintf('figures/BasicModelExample-GOES%d.eps',satnum));
     print('-dpng', '-r200', sprintf('figures/PNGs/BasicModelExample-GOES%d.png',satnum));

### 2016-07-05 paperfigures.m

@@ -5,3 +5,9 @@ Density(24,6) %RhoBinned case24, mass-gt20
 Density(10,6) %dst-50-tak, and significance table
 Density(5,6) %dd12
 Density(13,6) %dst-day
+
+%Dissertation plots
+Density(28,6,[datenum('Mar-10-1989') datenum('Mar-18-1989')])
+Density(28,6,[datenum('Oct-01-1985') datenum('Oct-11-1985')])
+Density(28,6,[datenum('Oct-22-1988') datenum('Nov-03-1988')])
+Density(28,6,[datenum('Jun-05-1989') datenum('Jun-26-1989')])

### 2016-07-05 stackplot.m

@@ -30,7 +30,8 @@ Time(Time>datelimits(2))=[];
 for i=1:numvars
     h(i)=subplot('position',subplotstack(numvars,i));
     if(i<numvars)
-        plot(Time,Data(:,i),'-','MarkerSize',10);
+        plot(Time,Data(:,i),'-','LineWidth',1.5);
+     
     else
         plot(Time,Data(:,i),'r.','MarkerSize',10); %Plot last subplot in red
     end
@@ -53,16 +54,24 @@ datetick('x','keeplimits')
 set(findobj('type','axes'),'xtick',get(h(end),'xtick'))
 linkaxes(h,'x')
 axis tight;
-xlabel(sprintf('Date from %s through %s',datestr(Time(1),1),datestr(Time(end),1)),'FontSize',14);
 
 sy=year(Time(1));
 ey=year(Time(end));
+
+if(sy~=ey)
+    xlabel(sprintf('Date from %s through %s',datestr(Time(1),1),datestr(Time(end),1)),'FontSize',14);
+else
+    xlabel(sprintf('Date of %d',sy),'FontSize',14);
+end
+
+
 
 if(sy ~= ey)
 %print('-depsc2',sprintf('paperfigures/alldata-GOES%d-%d-%d.eps',satnum,sy,ey));
 print('-depsc2','-r300',sprintf('paper/figures/alldata-GOES%d-%d-%d.eps',satnum,sy,ey));
 print('-dpng','-r200',sprintf('paper/figures/PNGs/alldata-GOES%d-%d-%d.png',satnum,sy,ey));
 else
+    
     sy=datestr(Time(1),'ddmmmyyyy');
     ey=datestr(Time(end),'ddmmmyyyy');
     print('-depsc2','-r300',sprintf('paper/figures/alldata-GOES%d-%s-%s.eps',satnum,sy,ey));

### 2016-07-05 paper/paper.tex

--- 2016-07-01 paper/paper.tex
@@
 From the $D_{st}$ events, we find that there is a weak and small amplitude ($< 10$\%) difference between $\rho_{eq}$ on the day of the event and the days before and after on both daily and hourly timescales.
-Although very large geomagnetic storms have been observed to correspond to large increases in $\rho_{eq}$, on average, $\rho_{eq}$ following the onset of a geomagnetic storm does not depend on the storm intensity or north-south component of the interplanetary magnetic field, $B_z$.
+Although very large geomagnetic storms have been observed to correspond to large increases in $\rho_{eq}$, on average, $\rho_{eq}$ following the onset of a geomagnetic storm does not depend on the storm intensity or the north-south component of the interplanetary magnetic field, $B_z$.
 From the $\rho_{eq}$ events, we find a weak dependence on $B_{z}$ after the onset of an event, with higher average $B_{z}$ six hours after the event onset corresponding to larger $\rho_{eq}$ events.
@@
 
-The dependence of the plasmapause location on geomagnetic activity was observed as early as \cite{Carpenter1966} and there are well--validated models of the plasmapause boundary, as a function of $L$, $MLT$, and geomagnetic activity (\cite{LemaireEarthsPlasmasphere}, \cite{Moldwin2002ModelPlasmapause}, \cite{OBrien2003EmpiricalPlasmapause}).
+The dependence of the plasmapause location on geomagnetic activity was observed as early as \cite{Carpenter1966} and there are well--validated models of the plasmapause boundary as a function of $L$, $MLT$, and geomagnetic activity (\cite{LemaireEarthsPlasmasphere}, \cite{Moldwin2002ModelPlasmapause}, \cite{OBrien2003EmpiricalPlasmapause}).
 Models also exist for the plasmasphere density (\cite{Gallagher1988EmpiricalModelPlasmasphere}; \cite{LemaireEarthsPlasmasphere}) with similar parameterization.
@@
 The dependence of the plasma density outside of the nominal plasmapause location on geomagnetic and solar wind conditions has not been extensively studied until the past decade (\cite{Takahashi2006}; \cite{Takahashi2010}; \cite{Denton2016}).
-Earlier works that considered profiles of hydrogen ion density found a significant dependence of the plasmasphere and plasmapause on geomagnetic activity (\cite{Chappell1970}; \cite{Maynard1977}; \cite{Carpenter1992}), but the relationship between geomagnetic activity and density outside of the plasmapause was not explicitly considered.
+Earlier works that considered profiles of hydrogen ion density found a significant dependence plasmapause location on geomagnetic activity (\cite{Chappell1970}; \cite{Maynard1977}; \cite{Carpenter1992}), but the relationship between geomagnetic activity and density outside of the plasmapause was not explicitly considered.
 
@@
 \cite{Denton2006} found a weak relationship between $D_{st}$ and and $K_p$ and the field line distribution of mass density, $\rho$, using observations of the first three toroidal Alfv\'en harmonic frequencies for $L$ in the range of 6-8~$R_E$.
-A more pronounced peak in the distribution along a filed line near the equator was found for lower $D_{st}$ and larger $K_p$.
-The equatorial value of $\rho$ appeared identical for $D_{st}$ bins of [-142, -31] and [-31, 37] nT and $K_p$ bins of [1.5,3.4] and [3.4, 5.9].
+A more pronounced peak in the distribution along a field line near the equator was found for lower $D_{st}$ and larger $K_p$.
+The equatorial value of $\rho$ were found to be similar for $D_{st}$ bins of [-142, -31] and [-31, 37] nT and $K_p$ bins of [1.5,3.4] and [3.4, 5.9].
 
@@
 \cite{Takahashi2010} noted that downward spikes in the $D_{st}$ index coincided with with significant changes in $\rho_{eq}$ for $L$ near 6.8~$R_E$.
-For five storms, two had $\rho_{eq}$ spikes after the $D_{st}$ drop, two had $\rho_{eq}$ spikes before the drop, and one showed little change in $\rho_{eq}$.
-A key result was that when daily-averaged measurements were considered, the epoch average of $D_st$ exhibited for storms with a minimum $D_{st} < -50$~nT, an enhancement in $\rho_{eq}$ the same day as minimum $D_{st}$ epoch averages.
+For five storms, two had $\rho_{eq}$ spikes after $D_{st}$ minimum, two had $\rho_{eq}$ spikes before the drop, and one showed little change in $\rho_{eq}$.
+A key result was that when daily-averaged measurements were considered, the epoch average of $D_{st}$ exhibited for storms with a minimum $D_{st} < -50$~nT showed an enhancement in $\rho_{eq}$ the same day as minimum $D_{st}$ in the epoch averages.
 
 \cite{Yao2008} studied the relationship between $D_{st}$ and the number density of low-energy $O^+$ in different regions (ring current and plasma sheet) using the TEAMS and ESA instruments on the low-altitude and high-inclination orbiting FAST satellite and found that the average $N_{O^+}$ across the sampled L-shells (2-14) had a strong correlation (0.88) with the minimum $D_{st}$ of the storm.
-Although the correlation at geosynchronous distances was not calculated, the data presented for four events show that the variations in $N_{O^+}$ tended to appear near $D_{st}$ minimum ($\pm$ 2~hours).
+Although the correlation at geosynchronous distances was not calculated, the data presented for four events show that the enhancements in $N_{O^+}$ tended to appear near $D_{st}$ minimum ($\pm$ 2~hours).
 
-The above results in the papers discussed indicate that (1) the mass density in the at geosynchronous distances is best correlated with $F10.7$ and (2) there exists a much weaker statistical relationship between mass density and the geomagnetic activity indices $K_p$ and $D_{st}$.
-In this work we consider the dependence of mass density estimates in the \cite{Denton2006} data set and attempt to identify and statistically characterize the relationship between geomagnetic activity with mass density at geosynchronous distances.
+The above results indicate that (1) the mass density in the at geosynchronous distances is best correlated with $F10.7$ and (2) there exists a much weaker statistical relationship between mass density and the geomagnetic activity indices $K_p$ and $D_{st}$.
+In this work we consider the dependence of mass density estimates in the \cite{Takahashi2010} data set and attempt to identify and statistically characterize the relationship between geomagnetic activity with mass density at geosynchronous distances.
 In addition, we attempt to identify solar wind processes that may drive changes in mass density.
@@
 A scatter plot of these two lines is shown in the lower panel of Figure~\ref{ccplot} along with that for 1--day and 1--hour medians.
-The linear correlation for GOES 6 using all measurements is found to be $0.94$, which is the same value documented by \cite{Takahashi2010} who used measurements from all satellites in the time interval of 1980 through 1991 using the constraint $0600 \leq MLT \le 1200$, $K_{p3d}\ge1.0$ and $D_{st}\ge -50$~nT.
-Our 27-day correlations for GOES 2, 5, and 7 are 0.81, 0.78, and 0.87, and the time range of coverage of measurements from these satellites is 1980-01-01/1983-05-16, 1983-01-01/1987-02-28, and 1983-05-27/1991-08-29 respectively.
+The linear correlation for GOES 6 using all measurements is found to be $0.94$, which is the same value documented by \cite{Takahashi2010} who used combined measurements from all satellites in the time interval of 1980 through 1991 using the constraint $0600 \leq MLT \le 1200$, $K_{p3d}\ge1.0$ and $D_{st}\ge -50$~nT.
+Our 27-day correlations for GOES 2, 5, and 7 are 0.81, 0.78, and 0.87, and the time range of coverage of measurements from these satellites is 1980-01-01/1983-05-16, 1983-01-01/1987-02-28, and 1983-05-27/1991-08-29, respectively.
 
-\section{Epoch Average Results}
+\section{Results}
 
@@
 
-Our first analysis uses data only from the time interval 1989-1991, which corresponds with the interval used in \cite{Takahashi2010}.
+Our first analysis uses GOES-6 data only from the time interval 1989-1991, which corresponds with the interval used in \cite{Takahashi2010}.
 In this interval, there were 329 $D_{st}$ events.
-For both types of events, the hour of the threshold crossing defines the zero epoch time, and for each event, $4\cdot24$ hours were considered before and $8\cdot24$ hours after each event.
+For both types of events, the hour of the threshold crossing defines the zero epoch time, and for each event, $4\cdot24$ hours were considered before and $8\cdot24$ hours after event onset.
 To compute the epoch averages on a daily time scale, the median value of all available measurements for all events centered on a window of $\pm 12$ hours of the epoch zero hour was computed, and these averaging windows were shifted in increments of $24$~hours.
-Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians for each event in 1-day bins and then compute the medians across events.
+Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians for each event in 1-day bins and then compute the medians across events in each epoch day.
 
@@
 Error lines for each parameter are the standard deviation of the values used in computing the median divided by the square root of the number of values.
-For the non-$\rho_{eq}$\ medians, the number of measurements used in computing the medians is typically equal to the number of events, which is much larger than the number of $\rho_{eq}$\ values as all available measurements were used instead of restricting to only values where a $\rho_{eq}$ value also existed.
+For the non-$\rho_{eq}$\ parameters, the number of measurements used in computing the medians is typically equal to the number of events, which is much larger than the number of $\rho_{eq}$\ values as all available measurements were used instead of restricting to only values where a $\rho_{eq}$ value also existed.
 
-In the lower panel of Figure \ref{DailyAveragedDstEvents} it is shown that the trends seen in the analysis of 1989-1991 also hold for the entire span of measurements from GOES 6 - a small elevation on the day of the event relative to the day before and day after, with median averages after the day of the event being slightly lower than that before.
+In the lower panel of Figure \ref{DailyAveragedDstEvents}, it is shown that the trends seen in the analysis of 1989-1991 also hold for the entire span of measurements from GOES 6 - a small elevation on the day of the event relative to the day before and day after, with median averages after the day of the event being slightly lower than that before.
 
@@
 
-These tests indicate that there is not a statistically significant change in medians of $\rho_{eq}$ on the day before and day after a threshold crossing in $D_{st}$.
-In addition, the observed differences are on the order of only 10\% of the $\rho_{eq}$, which is small compared to the variance in the observations.
+These tests indicate that there is not a statistically significant difference in medians of $\rho_{eq}$ on the day before and day after a threshold crossing in $D_{st}$.
+In addition, the observed differences are on the order of only 10\% of the local average of $\rho_{eq}$, which is small compared to the variance in the observations.
 
@@
 \small
-%\input{../tables/DeltaBootstraps-case10.txt}
+\centering
+\input{../tables/DeltaBootstraps-case10.txt}
 \caption{Results of test on of means of $\rho_{eq}$ shown in the top panel of Figure~\ref{DailyAveragedDstEvents} between days of threshold crossing  near (day = 1 or -1) or on the day of a $D_{st}$ event (day = 0).}
@@
 The bottom panel of Figure~\ref{HourlyAveragedDstEvents} contains the events shown in the top panel under the constraint that $D_{st}$ remained below -50~nT for at least twelve hours after the event onset time.
-In the time period of elevated mass density within 12 hours of the start of the event, there are only $\sim$5 samples per hourly interval.
+In the time period of elevated mass density within 12 hours of the start of the event, there are only $\sim$4 samples per hourly interval.
 This result is consistent with previous observations of large mass density spikes in the plasma trough region during large geomagnetic storms (\cite{Yao2008}; \cite{Takahashi2010}).
@@
 
-\subsection{Conclusions}
+\subsection{Summary and Conclusions}
+
+In recent years, various works have considered the influence of solar wind control and the geomagnetic activity relationship to the equatorial plasma mass density at geosynchronous orbit, generally using event studies and linear correlations (\cite{Takahashi2006}; \cite{Denton2006}; \cite{Yao2008}; \cite{Takahashi2010}; \cite{Denton2016}).
+The event studies show a possible relationship between $\rho_{eq}$ and solar wind and geomagnetic activity indicators such as $K_p$ and $D_{st}$ while correlation studies have generally found a very weak relationship.
+
+This work presents an analysis of two types of events intended to provide insight into the relationship between $\rho_{eq}$ and solar wind and geomagnetic parameters by considering both large geomagnetic events and large $\rho_{eq}$ events.
+The analysis attempts to address a major difficulty with the identification of the cause in $\rho_{eq}$ enhancements, which can occur for two reasons: (1) an extended period of positive $B_z$, which leads to low geomagnetic activity, plasmasphere refilling, and a possible expansion of the plasmasphere to geosynchronous altitudes and (2) strong negative $B_z$, which (a) leads to the inward motion of the higher density plasmasphere and leaves geosynchronous altitudes in the lower density plasma trough just outside of the plasmapause and (b) causes possible magnetospheric processes to enhance the mass density at geosynchronous altitudes.
+
+On average, around the time of large geomagnetic events, there is a very weak enhancement of $\rho_{eq}$ and this enhancement does not depend on either the interplanetary magnetic field $B_z$ or the intensity of the geomagnetic event.
+This indicates that there is an approximate balance between magnetospheric enhancement in $\rho_{eq}$ and any reduction due to the inward motion of the plasmasphere.
+
+$\rho_{eq}$ events are larger when $B_{z}$ is more positive after the onset of the event, which indicates that a substantial portion of the events may due to the apparent mass refilling mechanism described by \cite{Denton2016}.
+Without additional information about the location of the plasmapause, it may not be possible to separate out the conditions required for enhancement due to enhanced magnetospheric activity from this mechanism.
 
@@
 
-\clearpage
-
-\begin{figure}[tp!]
-  \centering
-  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedPdyn-case24-t020-tf25-GOES6.eps}
-  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedPdyn-case24-t025-tf30-GOES6.eps}
-  \caption{Binning $\rho_{eq}$ events by $B_z$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
-  \label{fig:PdynBinned}
-\end{figure}
-
-\begin{figure}[tp!]
-  \centering
-  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedV_SW-case24-t020-tf25-GOES6.eps}
-  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedV_SW-case24-t025-tf30-GOES6.eps}
-  \caption{Binning $\rho_{eq}$ events by $B_z$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
-  \label{fig:V_SWBinned}
-\end{figure}
-
-\begin{figure}[tp!]
-  \centering
-  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedkp-case24-t020-tf25-GOES6.eps}
-  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedkp-case24-t025-tf30-GOES6.eps}
-  \caption{Binning $\rho_{eq}$ events by $B_z$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
-  \label{fig:KpBinned}
-\end{figure}
-
-\begin{figure}[tp!]
-  \centering
-  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinneddst-case24-t020-tf25-GOES6.eps}
-  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinneddst-case24-t025-tf30-GOES6.eps}
-  \caption{Binning $\rho_{eq}$ events by $B_z$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
-  \label{fig:DstBinned}
-\end{figure}
-
 \end{document}

### 2016-07-07 paper/paper.tex
Adding text for new figures

@@
 \begin{document}
-\title{Solar wind and geomagnetic activity influence on the equatorial plasma mass density at geosynchronous orbit}
+\title{Average solar wind and geomagnetic activity influence on the equatorial plasma mass density at geosynchronous orbit}
 \author{V. Veibell and R.S. Weigel}
@@
 %\setlength{\parskip}{3ex}
-%\renewcommand{\labelitemi}{$-$}
+
 %\titlespacing{\section}{0pc}{0.2pc}{-1pc}
@@
 From the $D_{st}$ events, we find that there is a weak and small amplitude ($< 10$\%) difference between $\rho_{eq}$ on the day of the event and the days before and after on both daily and hourly timescales.
-Although very large geomagnetic storms have been observed to correspond to large increases in $\rho_{eq}$, on average, $\rho_{eq}$ following the onset of a geomagnetic storm does not depend on the storm intensity or the north-south component of the interplanetary magnetic field, $B_z$.
-From the $\rho_{eq}$ events, we find a weak dependence on $B_{z}$ after the onset of an event, with higher average $B_{z}$ six hours after the event onset corresponding to larger $\rho_{eq}$ events.
-In contrast, the average of $B_z$ six hours prior to $\rho_{eq}$ events does not have a statistically significant impact on $\rho_{eq}$ after onset.
+Although very large geomagnetic storms have been observed to correspond to large increases in $\rho_{eq}$, on average, $\rho_{eq}$ following the onset of a geomagnetic storm does not depend on the north-south component of the interplanetary magnetic field, $B_z$ near onset time.
+From the $\rho_{eq}$ events, we find a weak dependence on $B_{z}$ after the onset of an event, with higher average $B_{z}$ four hours after the event onset corresponding to larger $\rho_{eq}$ events.
+In contrast, the average of $B_z$ four hours prior to $\rho_{eq}$ events does not have a statistically significant impact on $\rho_{eq}$ after onset.
 \end{abstract}
@@
 
-The dependence of the plasmapause location on geomagnetic activity was observed as early as \cite{Carpenter1966} and there are well--validated models of the plasmapause boundary as a function of $L$, $MLT$, and geomagnetic activity (\cite{LemaireEarthsPlasmasphere}, \cite{Moldwin2002ModelPlasmapause}, \cite{OBrien2003EmpiricalPlasmapause}).
+The dependence of the plasmapause location on geomagnetic activity was observed as early as \cite{Carpenter1966} and there are well--validated models of the plasmapause location as a function of $L$, $MLT$, and geomagnetic activity (\cite{LemaireEarthsPlasmasphere}, \cite{Moldwin2002ModelPlasmapause}, \cite{OBrien2003EmpiricalPlasmapause}).
 Models also exist for the plasmasphere density (\cite{Gallagher1988EmpiricalModelPlasmasphere}; \cite{LemaireEarthsPlasmasphere}) with similar parameterization.
@@
 The dependence of the plasma density outside of the nominal plasmapause location on geomagnetic and solar wind conditions has not been extensively studied until the past decade (\cite{Takahashi2006}; \cite{Takahashi2010}; \cite{Denton2016}).
-Earlier works that considered profiles of hydrogen ion density found a significant dependence plasmapause location on geomagnetic activity (\cite{Chappell1970}; \cite{Maynard1977}; \cite{Carpenter1992}), but the relationship between geomagnetic activity and density outside of the plasmapause was not explicitly considered.
+Earlier works that considered profiles of ion density found a significant dependence of the plasmapause location on geomagnetic activity (\cite{Chappell1970}; \cite{Maynard1977}; \cite{Carpenter1992}), but the relationship between geomagnetic activity and density outside of the plasmapause was not explicitly considered.
 
-\cite{Takahashi2006} estimated magnetospheric mass density using measurements from the CRRES satellite during a 73-day period in 1991 when CRRES was in an elliptical, near equatorial orbit and primarily beyond the plasmapause.
+\cite{Takahashi2006} estimated magnetospheric mass density using measurements from the CRRES satellite during a 73-day period in 1991 when CRRES was in an elliptical, near equatorial orbit and primarily beyond the nominal plasmapause.
 They found that the local average ion mass, $M$, had some correlation with geomagnetic activity, with more negative hourly $D_{st}$ values corresponding to higher $M$ and 1.5- and 3-day averages of $K_p$ corresponding to higher $M$ (3-hour averages of $K_p$ had little visual correlation with $M$).
@@
 
-\cite{Denton2006} found a weak relationship between $D_{st}$ and and $K_p$ and the field line distribution of mass density, $\rho$, using observations of the first three toroidal Alfv\'en harmonic frequencies for $L$ in the range of 6-8~$R_E$.
-A more pronounced peak in the distribution along a field line near the equator was found for lower $D_{st}$ and larger $K_p$.
-The equatorial value of $\rho$ were found to be similar for $D_{st}$ bins of [-142, -31] and [-31, 37] nT and $K_p$ bins of [1.5,3.4] and [3.4, 5.9].
+\cite{Denton2006} found a weak relationship between $D_{st}$ and and $K_p$ and the field line distribution of plasma mass density, $\rho$, using observations of the first three toroidal Alfv\'en harmonic frequencies for $L$ in the range of 6-8~$R_E$.
+A more pronounced peak in the distribution along a field line near the equator was found for lower $D_{st}$ and larger $K_p$, but the equatorial value of $\rho$ was found to be similar for $D_{st}$ bins of [-142, -31] and [-31, 37] nT and $K_p$ bins of [1.5,3.4] and [3.4, 5.9].
 
@@
 
-\cite{Takahashi2010} noted that downward spikes in the $D_{st}$ index coincided with with significant changes in $\rho_{eq}$ for $L$ near 6.8~$R_E$.
+\cite{Takahashi2010} noted that downward drops in the $D_{st}$ index coincided with significant changes in $\rho_{eq}$ for $L$ near 6.8~$R_E$.
 For five storms, two had $\rho_{eq}$ spikes after $D_{st}$ minimum, two had $\rho_{eq}$ spikes before the drop, and one showed little change in $\rho_{eq}$.
@@
 In this work we consider the dependence of mass density estimates in the \cite{Takahashi2010} data set and attempt to identify and statistically characterize the relationship between geomagnetic activity with mass density at geosynchronous distances.
-In addition, we attempt to identify solar wind processes that may drive changes in mass density.
+In addition, we attempt to identify solar wind processes that may drive the changes.
 
@@
 The parameters $\rho_{eq}$ and $F_{10.7}$ are from the dataset of \cite{Takahashi2010}; data are available from 1980 through 1991 from GOES 2, 3, 5, 6 and 7.
-All other parameters used are from \cite{Kondrashov2014ReconstructionOfGaps} which has coverage from 1972 through 2013, which are on a 1--hour time grid.
+All other parameters used are from \cite{Kondrashov2014ReconstructionOfGaps}, which has coverage from 1972 through 2013 and are on a 1--hour time grid.
 $\rho_{eq}$ is the inferred equatorial mass density based on the 3rd harmonic torodial frequency of magnetic field measurements as described in \cite{Takahashi2010}.
@@
 
-Figure~\ref{ccplot} shows the long-term trends of log$_{10}(\rho_{eq})$ from GOES 6 and $F_{10.7}$ computed using the median values in 27-day non-overlapping windows.
+The top panel of Figure~\ref{ccplot} shows the long-term trends of log$_{10}(\rho_{eq})$ from GOES 6 and $F_{10.7}$ computed using the median values in 27-day non-overlapping windows.
 A scatter plot of these two lines is shown in the lower panel of Figure~\ref{ccplot} along with that for 1--day and 1--hour medians.
@@
 The second type of event is an increase in $\rho_{eq}$ above a threshold of 20~amu/cm$^3$.
-It is expected that these increases will typically occur after period of quiet geomagnetic activity but may also be the result of increases in geomagnetic activity.
+It is expected that these increases will typically occur after period of quiet geomagnetic activity but may also be the result of increases in solar wind driven geomagnetic activity.
 In this case, the plasmapause boundary may move outward past geosynchronous orbit and the increase will be due to measurements being made inside the plasmapause.
@@
 
-Our first analysis uses GOES-6 data only from the time interval 1989-1991, which corresponds with the interval used in \cite{Takahashi2010}.
+Our first analysis uses GOES-6 data only from the time interval 1989-1991, which corresponds with the interval used in the epoch analysis of \cite{Takahashi2010}.
 In this interval, there were 329 $D_{st}$ events.
@@
 To compute the epoch averages on a daily time scale, the median value of all available measurements for all events centered on a window of $\pm 12$ hours of the epoch zero hour was computed, and these averaging windows were shifted in increments of $24$~hours.
-Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians for each event in 1-day bins and then compute the medians across events in each epoch day.
+Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians for each event in 1-day bins and then compute the medians across events on each epoch day.
 
@@
 These tests indicate that there is not a statistically significant difference in medians of $\rho_{eq}$ on the day before and day after a threshold crossing in $D_{st}$.
-In addition, the observed differences are on the order of only 10\% of the local average of $\rho_{eq}$, which is small compared to the variance in the observations.
+In addition, the observed differences are on the order of only 10\% of the value of $\rho_{eq}$ on the onset day, which is similar to the variation in the observations over the displayed epoch time interval.
 
@@
 In the time period of elevated mass density within 12 hours of the start of the event, there are only $\sim$4 samples per hourly interval.
-This result is consistent with previous observations of large mass density spikes in the plasma trough region during large geomagnetic storms (\cite{Yao2008}; \cite{Takahashi2010}).
+This result is consistent with previous observations of large mass density increases in the plasma trough region during large geomagnetic storms (\cite{Yao2008}; \cite{Takahashi2010}).
 
-To determine of this relationship can be also observed in the events of the top panel of Figure~\ref{HourlyAveragedDstEvents}, we sorted the events by the average $D_{st}$ values in the time interval of 0-12 hours, split the events in two and recomputed the epoch averages of $\rho_{eq}$.
-The result is that there is no statistically significant difference in the mass density epoch averages for large versus small events.
-This indicates that to confirm a statistical $\rho_{eq}$ dependence on large geomagnetic storms would require a dataset with a much larger number of strong geomagnetic storms.
+The top panel of Figure~\ref{HourlyAveragedDstEvents} shows that, on average, near the onset of $D_{st}$ events there is not a significant reponse in $\rho_{eq}$ while the bottom panel shows that for rare and large $D_{st}$ events elevated $\rho_{eq}$ can be observed.
+To determine if there is an IMF $B_{z}$ dependence, the epoch curves in the top panel of Figure~\ref{HourlyAveragedDstEvents} for $\rho_{eq}$ and $B_{z}$ were separated into two parts depending whether $B_z$ was above or below its average four hours before and including the onset hour and four hours after and including the hour of onset; the result is shown in Figure~\ref{fig:BzBinnedDstEvents}.
+Any statistically significant difference at a 95\% confidence level between the two parts is indicated by a green dot on the horizontal axis using the same bootstrap method described previously.
+(At this confidence level, false positives are expected to randomly occur 5\% of the time, or 3.6 times for 72 values.)  These two curves indicate that there is not a statistically significant dependence on IMF $B_{z}$ around the time of the onset of a $D_{st}$ event.
+
+The process for creating Figure~\ref{fig:BzBinnedDstEvents} was repeated except using the sort variable $F10.7$ instead of $B_z$, as shown in Figure~\ref{fig:F107BinnedDstEvents}.
+As expected, difference between the epoch curves is statistically significant at all times, as expected, but elevated $F10.7$ is associated with a peak in the $\rho_{eq}$ curve approximately 5 hours after onset.
 
@@
 
-To determine if there is an IMF $B_{z}$ dependence, the epoch curve for $\rho_{eq}$ and $B_{z}$ was separated into two parts depending whether $B_z$ was above or below the average four hours before and including the onset hour and four hours after and including the hour of onset; the result is shown in Figure~\ref{fig:BzBinned}.
-Any statistically significant difference at a 95\% confidence level between the two parts is indicated by a green dot on the horizontal axis using the same bootstrap method described previously.
-(At this confidence level, false positives are expected to randomly occur 5\% of the time or 3.6 times for 72 values.) The largest separation occurs when the separation is performed by Figure~\ref{fig:BzBinned} after onset, with more positive $B_z$ leading to larger peak $\rho_{eq}$ than more negative $B_{z}$.
+The largest difference occurs when the separation is performed after onset, with more positive $B_z$ leading to larger peak $\rho_{eq}$ than more negative $B_{z}$.
 The rate of change of $\rho_{eq}$ also appears to be insenstive to $B_z$ for approximately 12 hours prior to onset.
-We note that the equivalent epoch separation curves for $P_{dyn}$ had a statistically significant differences similar to that for $B_z$, with higher dynamic pressure playing a role similar to positive $B_z$.
+The equivalent epoch separation curves for $P_{dyn}$ had a statistically significant differences similar to that for $B_z$, with higher dynamic pressure playing a role similar to positive $B_z$.
 
@@
 The top four panels show parameters from \cite{Kondrashov2014ReconstructionOfGaps} and the bottom panel contains $\rho_{eq}$ based on GOES 6 measurements from \cite{Denton} after interpolation and averaging described in the text.
-Dashed horizontal lines in the $D_{st}$ and $\rho_{eq}$ panels indicate sample event cutoff thresholds of $D_{st} = -50$~nT and $\rho_{eq} = 20$~amu/cm$^3$ considered in Section~3}.
+Dashed horizontal lines in the $D_{st}$ and $\rho_{eq}$ panels indicate sample event cutoff thresholds of $D_{st} = -50$~nT and $\rho_{eq} = 20$~amu/cm$^3$ considered in Section~3.}
 \label{AllData}
@@
 \caption{$D_{st}$ events from GOES 6 using hourly medians.
-Top: Events in the interval 1983-1991; compare to bottom panel Figure~\ref{DailyAveragedDstEvents}.
+Top: Events in the interval 1983-1991.
 Bottom: Same as Top except for constraint that $D_{st}$ stayed below $-50$~nT for at least 12~hours after crossing below $-50$~nT.}
 \label{HourlyAveragedDstEvents}
+\end{figure}
+
+\clearpage
+\begin{figure}[tp!]
+  \centering
+  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedB_z-case1-t020-tf25-GOES6.eps}
+  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedB_z-case1-t025-tf30-GOES6.eps}
+  \caption{$D_{st}$ events of Figure~\ref{HourlyAveragedDstEvents} separated by the average $D_{st}$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
+  \label{fig:BzBinnedDstEvents}
+\end{figure}
+
+\begin{figure}[tp!]
+  \centering
+  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedF107-case1-t020-tf25-GOES6.eps}
+  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedF107-case1-t025-tf30-GOES6.eps}
+  \caption{$D_{st}$ events of Figure~\ref{HourlyAveragedDstEvents} separated by the average $F10.7$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
+  \label{fig:F107BinnedDstEvents}
 \end{figure}
@@
 \includegraphics[scale=0.40]{figures/stormavs-mass-gt20-GOES6.eps}
-\caption{$\rho_{eq} >$ 20~amu/cm$^3$ events from GOES 6 using hourly medians.
-As described in the text, there is no statistically significant dependence of the $\rho_{eq}$  plot on $B_z$ in the time interval of $pm 2$~hours around the event.}
+\caption{$\rho_{eq} >$ 20~amu/cm$^3$ events from GOES 6 using hourly medians.}
 \label{HourlyAveragedRhoEvents}

### 2016-07-26 paper/paper.tex
Paper closer to reproducing Takahashi 2010

@@
   \centering
-  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedF107-case1-t020-tf25-GOES6.eps}
-  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedF107-case1-t025-tf30-GOES6.eps}
+  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedF_{10.7}-case1-t020-tf25-GOES6.eps}
+  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedF_{10.7}-case1-t025-tf30-GOES6.eps}
   \caption{$D_{st}$ events of Figure~\ref{HourlyAveragedDstEvents} separated by the average $F10.7$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
@@
   \centering
-  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedF107-case24-t020-tf25-GOES6.eps}
-  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedF107-case24-t025-tf30-GOES6.eps}
+  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedF_{10.7}-case24-t020-tf25-GOES6.eps}
+  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedF_{10.7}-case24-t025-tf30-GOES6.eps}
   \caption{$\rho_{eq}$ events of Figure~\ref{HourlyAveragedRhoEvents} separated by the average $F10.7$ value (a) at onset and four hours before, and (b) at onset and four hours after.}

### 2016-07-26 ComplexPlots.m

@@ -30,7 +30,7 @@ end
 
 
 if(MakePaperPlots && (stormcase==2 || stormcase==24 || stormcase==1)) 
-    tws=[12:17; 20:25; 25:30];
+    tws=[20:25; 25:30];
     for varnum=[5 6 8 13 15 30]
     %varnum=30; %5 is Bz, 15 is dst, 8 is p, 6 is Vsw, 13 is kp, 30 is f10.7
     varname=headers{varnum};
@@ -391,7 +391,7 @@ if(MakePaperPlots)
 end
 
 if(MakePaperPlots && MDCut>0) %Add a stack plot for Pressure for mass events
-    xa=(-timewidth:LongTimeScale:timewidth*2)./LongTimeScale;
+    xa=(-timewidth:LongTimeScale:timewidth*2-1)./LongTimeScale;
     h=figure('Visible',visible);
     orient tall;
     

### 2016-07-26 Density.m

@@ -142,8 +142,11 @@ switch stormcase
         storms=diff([0 (FILLED(:,15)<-50)' 0]);
         DSTCut=-50;
         LongTimeScale=24;
+        cutoffduration=12;
+        cutconditions=1;
         figurename=strcat(figurename,'dst-day',sprintf('-GOES%d.eps',satnum));
-        yr=1;
+        yr=5;
+        yranges(5,:,:)=[-2 2; 400 600; -80 0; 150 230; 5 25];
     case 14
         storms=diff([0 (MassDensityNanSpline>40)' 0]); 
         MDCut=40;

### 2016-07-28 paper/paper.tex
Clarifying paper

@@
 Our first analysis uses GOES-6 data only from the time interval 1989-1991, which corresponds with the interval used in the epoch analysis of \cite{Takahashi2010}.
-In this interval, there were 329 $D_{st}$ events.
-For both types of events, the hour of the threshold crossing defines the zero epoch time, and for each event, $4\cdot24$ hours were considered before and $8\cdot24$ hours after event onset.
+In this interval, there were 75 $D_{st}$ events where $D_{st}$ remained below the $-50$~nT threshold for at least 12 hours.
+For both types of events, the first hour of a local minimum $D_{st}$ following a threshold crossing defines the zero epoch time, and for each event, $4\cdot24$ hours were considered before and $8\cdot24$ hours after event onset.
 To compute the epoch averages on a daily time scale, the median value of all available measurements for all events centered on a window of $\pm 12$ hours of the epoch zero hour was computed, and these averaging windows were shifted in increments of $24$~hours.
@@
 
-The stack plot in the upper panel of Figure \ref{DailyAveragedDstEvents} shows the epoch averages for the 329 events from 1989-1991.
-The minimum $D_{st}$ median is $-48$~nT.
-Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$ before and after the event, although the magnitude of increase observed here is $1.5$ amu/cm$^3$ (from 18 to 19.5~amu/cm$^3$) instead of the increase of $\sim 10$ amu/cm$^3$ found in Figure 11 of \cite{Takahashi2010}.
+The stack plot in the upper panel of Figure \ref{DailyAveragedDstEvents} shows the epoch averages for the 75 events from 1989-1991.
+The minimum $D_{st}$ median is $-75$~nT.
+Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$ before and after the event, although the magnitude of increase observed here is $7$ amu/cm$^3$ (from 18 to 25~amu/cm$^3$) instead of the increase of $\sim 10$ amu/cm$^3$ found in Figure 11 of \cite{Takahashi2010}.
 The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute the medians and red error lines.
@@
 If a statistically significant difference in the medians between two days existed, the fraction of bootstrap samples with a different sign is expected to be much smaller ($<$ 5\%).
-In terms of a hypothesis test, we cannot reject the null hypothesis that the medians are the same with a confidence higher than 100 minus the \% value shown in the table; the highest confidence level of 87.6\% is in the difference between day 0 and day 1.
+In terms of a hypothesis test, we cannot reject the null hypothesis that the medians are the same with a confidence higher than 100 minus the \% value shown in the table; the highest confidence level of 87.8\% is in the difference between day 0 and day -1.
 
 These tests indicate that there is not a statistically significant difference in medians of $\rho_{eq}$ on the day before and day after a threshold crossing in $D_{st}$.
-In addition, the observed differences are on the order of only 10\% of the value of $\rho_{eq}$ on the onset day, which is similar to the variation in the observations over the displayed epoch time interval.
+In addition, the observed differences are on the order of only 25\% of the value of $\rho_{eq}$ on the onset day, which is similar to the variation in the observations over the displayed epoch time interval.
 
@@
 As expected, difference between the epoch curves is statistically significant at all times, as expected, but elevated $F10.7$ is associated with a peak in the $\rho_{eq}$ curve approximately 5 hours after onset.
+The values contributing to the peak were compared to a baseline of all values 16-48 hours after onset via a Wilcoxon rank-sum test and found to have significantly different medians at the 99\% significance level.
 

### 2016-07-28 ComplexPlots.m

@@ -73,6 +73,13 @@ if(MakePaperPlots && (stormcase==2 || stormcase==24 || stormcase==1))
            print('-dpng',sprintf('paper/figures/RhoBinned/PNGs/RhoBinned%s-case%d-t0%d-tf%d-GOES%d-histogram.png',varname,stormcase,tw(1),tw(end),satnum));
         end
         
+        if(varnum==30 && i==2)
+            baseline=AVMDMat(nanmedian(AVMat(:,tw,varnum),2)>=topcut,40:end);
+            spike=AVMDMat(nanmedian(AVMat(:,tw,varnum),2)>=topcut,29);
+            [p,h]=ranksum(spike,baseline(:));
+            fprintf('Probability spike events come from same median distribution as baseline: %2.2f\n',p);
+        end
+        
         
         h=figure('Visible',visible);
         hold on;

### 2016-07-28 paper/paper.tex
Making sure figures still valid. Adding ability to make presentation figures

@@
 For both types of events, the first hour of a local minimum $D_{st}$ following a threshold crossing defines the zero epoch time, and for each event, $4\cdot24$ hours were considered before and $8\cdot24$ hours after event onset.
+For multiple detected threshold crossings within 24 hours of each other, the first crossing was selected as the event since visual inspection showed the following crossings to typically be from brief deviations during the recovery period.
 To compute the epoch averages on a daily time scale, the median value of all available measurements for all events centered on a window of $\pm 12$ hours of the epoch zero hour was computed, and these averaging windows were shifted in increments of $24$~hours.
@@
 The minimum $D_{st}$ median is $-75$~nT.
-Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$ before and after the event, although the magnitude of increase observed here is $7$ amu/cm$^3$ (from 18 to 25~amu/cm$^3$) instead of the increase of $\sim 10$ amu/cm$^3$ found in Figure 11 of \cite{Takahashi2010}.
+Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$ before and after the event, although the magnitude of increase observed here is, on average, $4.5$ amu/cm$^3$ (from $\sim$19 to ${\sim}$24~amu/cm$^3$) instead of the increase of ${\sim} 10$ amu/cm$^3$ found in Figure 11 of \cite{Takahashi2010}.
 The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute the medians and red error lines.
@@
 If a statistically significant difference in the medians between two days existed, the fraction of bootstrap samples with a different sign is expected to be much smaller ($<$ 5\%).
-In terms of a hypothesis test, we cannot reject the null hypothesis that the medians are the same with a confidence higher than 100 minus the \% value shown in the table; the highest confidence level of 87.8\% is in the difference between day 0 and day -1.
+In terms of a hypothesis test, we cannot reject the null hypothesis that the medians are the same with a confidence higher than 100 minus the \% value shown in the table; the highest confidence level of 89\% is in the difference between day 0 and day -1.
 
 These tests indicate that there is not a statistically significant difference in medians of $\rho_{eq}$ on the day before and day after a threshold crossing in $D_{st}$.
-In addition, the observed differences are on the order of only 25\% of the value of $\rho_{eq}$ on the onset day, which is similar to the variation in the observations over the displayed epoch time interval.
+In addition, the observed differences are on the order of only 20\% of the value of $\rho_{eq}$ on the onset day, which is similar to the variation in the observations over the displayed epoch time interval.
 
@@
 We have also considered hourly averages as shown in the top panel of Figure~\ref{HourlyAveragedDstEvents}.
-A total of 668 $D_{st}$ events were found in the interval of May 1983 through August 1991 with an average duration of 9 hours and a median duration of 3 hours.
+A total of 333 $D_{st}$ events were found in the interval of May 1983 through August 1991 with an average duration of 10 hours and a median duration of 3 hours.
 In this plot, the overall trend is similar to that found in the bottom panel of Figure~\ref{HourlyAveragedDstEvents} - $\rho_{eq}$ is slightly elevated at the time of the threshold crossing of $D_{st}$ with respect to the values one day before and after, but the elevation is small relative to the error bars around the time of the event onset.

### 2016-07-31 Density.m
Adding MLT cutoff to Fig 4

@@ -67,6 +67,7 @@ switch stormcase
         DSTCut=-50;
         figurename=strcat(figurename,'dst',sprintf('-GOES%d.eps',satnum));
         yr=2;
+        cutconditions=1;
         MakeBinPlots=1;
     case 2
         storms=diff([0 (MassDensityNanSpline>40)' 0]); %Mass Density Storm, started at 40
@@ -90,6 +91,7 @@ switch stormcase
         cutoffduration=12; %12 hour DST storm
         figurename=strcat(figurename,'dd12',sprintf('-GOES%d.eps',satnum));
         yr=5;
+        cutconditions=1;
         yranges(5,:,:)=[-10 5; 400 700; -100 0; 150 200; 0 70];
     case 6
         storms=diff([0 (MassDensityNanSpline>40)' 0]);

### 2016-08-04 paper/paper.tex
Adding MLT cutoff to Fig 4
Fixing the issues the git merge caused
Updated abstract and results

@@
 We consider two types of events, identified by decreases in $D_{st}$ below a threshold value and increases in the the equatorial mass density at geosynchronous altitudes, $\rho_{eq}$, above a threshold value on 1-hour and 1-day time scales using the \cite{Takahashi2010} dataset.
-From the $D_{st}$ events, we find that there is a weak and small amplitude ($< 10$\%) difference between $\rho_{eq}$ on the day of the event and the days before and after on both daily and hourly timescales.
-Although very large geomagnetic storms have been observed to correspond to large increases in $\rho_{eq}$, on average, $\rho_{eq}$ following the onset of a geomagnetic storm does not depend on the north-south component of the interplanetary magnetic field, $B_z$ near onset time.
-From the $\rho_{eq}$ events, we find a weak dependence on $B_{z}$ after the onset of an event, with higher average $B_{z}$ four hours after the event onset corresponding to larger $\rho_{eq}$ events.
+From the $D_{st}$ events, we find that there is a statistically weak and small amplitude difference between $\rho_{eq}$ on the day of the event and the days before and after on daily timescales.
+On hourly timescales, it is observed that for 6 hours after onset, very few measurements of  $\rho_{eq}$ are found and that most of the contribution to the daily averages is from 6-24 hours after onset.
+On hourly timescales, $\rho_{eq}$ following the onset of a $D_{st}$ event does not depend on the north-south component of the interplanetary magnetic field, $B_z$ near onset time.
+The primary factor that determines if a post-$D_{st}$ event onset peak in $\rho_{eq}$ will occur is elevated $F10.7$.
+From the $\rho_{eq}$ events, we find a weak dependence on $B_{z}$ after the onset of an event, with higher average $B_{z}$ four hours after the event onset corresponding to larger $\rho_{eq}$ values 24-36 hours after onset.
 In contrast, the average of $B_z$ four hours prior to $\rho_{eq}$ events does not have a statistically significant impact on $\rho_{eq}$ after onset.
@@
 In this interval, there were 75 $D_{st}$ events where $D_{st}$ remained below the $-50$~nT threshold for at least 12 hours.
-For both types of events, the first hour of a local minimum $D_{st}$ following a threshold crossing defines the zero epoch time, and for each event, $4\cdot24$ hours were considered before and $8\cdot24$ hours after event onset.
-For multiple detected threshold crossings within 24 hours of each other, the first crossing was selected as the event since visual inspection showed the following crossings to typically be from brief deviations during the recovery period.
+Only events with an onset time between 06 and noon MLT were considered.
+For both types of events, the first hour of a local minimum in $D_{st}$ following a threshold crossing defines the zero epoch time, and for each event, $4\cdot24$ hours were considered before and $8\cdot24$ hours after event onset.
+For multiple detected threshold crossings within 24 hours of each other, the first crossing was selected as the event since visual inspection showed the following crossings to typically be from brief deviations during the recovery period of a geomagnetic storm.
 To compute the epoch averages on a daily time scale, the median value of all available measurements for all events centered on a window of $\pm 12$ hours of the epoch zero hour was computed, and these averaging windows were shifted in increments of $24$~hours.
@@
 If a statistically significant difference in the medians between two days existed, the fraction of bootstrap samples with a different sign is expected to be much smaller ($<$ 5\%).
-In terms of a hypothesis test, we cannot reject the null hypothesis that the medians are the same with a confidence higher than 100 minus the \% value shown in the table; the highest confidence level of 89\% is in the difference between day 0 and day -1.
+In terms of a hypothesis test, we cannot reject the null hypothesis that the medians are the same with a confidence higher than 100 minus the \% value shown in the table; the highest confidence level of 86\% is in the difference between day 0 and day -1.
 
-These tests indicate that there is not a statistically significant difference in medians of $\rho_{eq}$ on the day before and day after a threshold crossing in $D_{st}$.
+A similar hypothesis test run for the bottom panel of Figure~\ref{DailyAveragedDstEvents} yields a maximum confidence level of $\sim$85\%.
+
+These tests indicate that there is not a statistically significant difference in medians of daily averaged $\rho_{eq}$ on the day before and day after a threshold crossing in $D_{st}$.
 In addition, the observed differences are on the order of only 20\% of the value of $\rho_{eq}$ on the onset day, which is similar to the variation in the observations over the displayed epoch time interval.
@@
 
-We have also considered hourly averages as shown in the top panel of Figure~\ref{HourlyAveragedDstEvents}.
-A total of 333 $D_{st}$ events were found in the interval of May 1983 through August 1991 with an average duration of 10 hours and a median duration of 3 hours.
+We have also considered the hourly averages from the events shown in the bottom panel of Figure~\ref{HourlyAveragedDstEvents}, which shown in the top panel of Figure~\ref{HourlyAveragedDstEvents}.
+In the time period of elevated mass density within 6 hours of the start of the event, there are only $\sim$4 samples per hourly interval.
+The peak value of $\sim$70 amu/cm$^3$ is associated with a single observation.
+
+To increase the number events, we have remove the constraint that the events must occur in the MLT range from 06-12 and the constraint that $D_{st}$ remained below the threshold value for 12 hours or longer.
+The result is shown in the bottom panel of Figure~\ref{HourlyAveragedDstEvents}.
+
+%This result is consistent with previous observations of large mass density increases in the plasma trough region during large geomagnetic storms (\cite{Yao2008}; \cite{Takahashi2010}).
+
+%A total of 333 $D_{st}$ events were found in the interval of May 1983 through August 1991 with an average duration of 10 hours and a median duration of 3 hours.
 In this plot, the overall trend is similar to that found in the bottom panel of Figure~\ref{HourlyAveragedDstEvents} - $\rho_{eq}$ is slightly elevated at the time of the threshold crossing of $D_{st}$ with respect to the values one day before and after, but the elevation is small relative to the error bars around the time of the event onset.
 
-The bottom panel of Figure~\ref{HourlyAveragedDstEvents} contains the events shown in the top panel under the constraint that $D_{st}$ remained below -50~nT for at least twelve hours after the event onset time.
-In the time period of elevated mass density within 12 hours of the start of the event, there are only $\sim$4 samples per hourly interval.
-This result is consistent with previous observations of large mass density increases in the plasma trough region during large geomagnetic storms (\cite{Yao2008}; \cite{Takahashi2010}).
+%The top panel of Figure~\ref{HourlyAveragedDstEvents} shows that, on average, near the onset of $D_{st}$ events there is not a significant reponse in $\rho_{eq}$ while the bottom panel shows that for rare and large $D_{st}$ events elevated $\rho_{eq}$ can be observed.
 
-The top panel of Figure~\ref{HourlyAveragedDstEvents} shows that, on average, near the onset of $D_{st}$ events there is not a significant reponse in $\rho_{eq}$ while the bottom panel shows that for rare and large $D_{st}$ events elevated $\rho_{eq}$ can be observed.
 To determine if there is an IMF $B_{z}$ dependence, the epoch curves in the top panel of Figure~\ref{HourlyAveragedDstEvents} for $\rho_{eq}$ and $B_{z}$ were separated into two parts depending whether $B_z$ was above or below its average four hours before and including the onset hour and four hours after and including the hour of onset; the result is shown in Figure~\ref{fig:BzBinnedDstEvents}.
@@
 \centering
-\includegraphics[scale=0.40]{figures/stormavs-dst-GOES6.eps}
+\includegraphics[scale=0.40]{figures/stormavs-dd12-GOES6.eps}
 \\
@@
 \\
-\includegraphics[scale=0.40]{figures/stormavs-dd12-GOES6.eps}
+\includegraphics[scale=0.40]{figures/stormavs-dst-GOES6.eps}
 \caption{$D_{st}$ events from GOES 6 using hourly medians.
-Top: Events in the interval 1983-1991.
-Bottom: Same as Top except for constraint that $D_{st}$ stayed below $-50$~nT for at least 12~hours after crossing below $-50$~nT.}
+Top: Events with the constraint that $D_{st}$ stayed below $-50$~nT for at least 12~hours after crossing below $-50$~nT.
+Bottom: Same as Top except without constraint.}
 \label{HourlyAveragedDstEvents}

### 2016-08-04 paper/paper.tex
Adding significance test for two peaks

@@
 
-We have also considered the hourly averages from the events shown in the bottom panel of Figure~\ref{HourlyAveragedDstEvents}, which shown in the top panel of Figure~\ref{HourlyAveragedDstEvents}.
+We have also considered the hourly averages from the events shown in the bottom panel of Figure~\ref{DailyAveragedDstEvents}, which shown in the top panel of Figure~\ref{HourlyAveragedDstEvents}.
 In the time period of elevated mass density within 6 hours of the start of the event, there are only $\sim$4 samples per hourly interval.
@@
 
-To increase the number events, we have remove the constraint that the events must occur in the MLT range from 06-12 and the constraint that $D_{st}$ remained below the threshold value for 12 hours or longer.
+To increase the number of events, we have removed the constraint that the events must occur in the MLT range from 06-12 and the constraint that $D_{st}$ remained below the threshold value for 12 hours or longer.
 The result is shown in the bottom panel of Figure~\ref{HourlyAveragedDstEvents}.
+The two spikes (one updwards after onset, one downwards before onset) were tested for significant deviation from two baselines, one 24-12 hours before onset, one 16-48 hours after onset.
+The probability of the left spike coming from the same distribution as the left baseline is 1.06\%, and 8.2\% from the right baseline, whereas the probability of the right spike coming from the left baseline is 1.89\% and 0.17\% from the right baseline.
 

### 2016-08-09 paper/paper.tex
Misc edits

@@
 \begin{document}
-\title{Average solar wind and geomagnetic activity influence on the equatorial plasma mass density at geosynchronous orbit}
+\title{Solar wind and geomagnetic activity influence on the equatorial plasma mass density at geosynchronous orbit}
 \author{V. Veibell and R.S. Weigel}
@@
 \begin{abstract}
-We consider two types of events, identified by decreases in $D_{st}$ below a threshold value and increases in the the equatorial mass density at geosynchronous altitudes, $\rho_{eq}$, above a threshold value on 1-hour and 1-day time scales using the \cite{Takahashi2010} dataset.
-From the $D_{st}$ events, we find that there is a statistically weak and small amplitude difference between $\rho_{eq}$ on the day of the event and the days before and after on daily timescales.
-On hourly timescales, it is observed that for 6 hours after onset, very few measurements of  $\rho_{eq}$ are found and that most of the contribution to the daily averages is from 6-24 hours after onset.
-On hourly timescales, $\rho_{eq}$ following the onset of a $D_{st}$ event does not depend on the north-south component of the interplanetary magnetic field, $B_z$ near onset time.
-The primary factor that determines if a post-$D_{st}$ event onset peak in $\rho_{eq}$ will occur is elevated $F10.7$.
+We consider two types of events, identified by decreases in $D_{st}$ below a threshold value and increases in the the equatorial mass density at geosynchronous altitudes, $\rho_{eq}$, above a threshold value using the \cite{Takahashi2010} dataset.
+From the $D_{st}$ events and 1-day averages, we find that there is a statistically weak and small amplitude difference between $\rho_{eq}$ on the day of the event and the days before and after.
+For hourly averages, it is found that for 6 hours after onset, very few measurements of $\rho_{eq}$ exist and that most of the contribution to the daily averages is from 6-24 hours after onset.
+For hourly averages, $\rho_{eq}$ following the onset of a $D_{st}$ event does not depend on the north-south component of the interplanetary magnetic field, $B_z$ near onset time.
+The primary factor that determines if a post-$D_{st}$ event onset peak in $\rho_{eq}$ will occur in the hourly averages is elevated $F10.7$.
 From the $\rho_{eq}$ events, we find a weak dependence on $B_{z}$ after the onset of an event, with higher average $B_{z}$ four hours after the event onset corresponding to larger $\rho_{eq}$ values 24-36 hours after onset.
@@
 In this interval, there were 75 $D_{st}$ events where $D_{st}$ remained below the $-50$~nT threshold for at least 12 hours.
-Only events with an onset time between 06 and noon MLT were considered.
-For both types of events, the first hour of a local minimum in $D_{st}$ following a threshold crossing defines the zero epoch time, and for each event, $4\cdot24$ hours were considered before and $8\cdot24$ hours after event onset.
-For multiple detected threshold crossings within 24 hours of each other, the first crossing was selected as the event since visual inspection showed the following crossings to typically be from brief deviations during the recovery period of a geomagnetic storm.
+Only events with an onset time between 06:00 and 12:00 MLT were considered.
+The first hour of a local minimum in $D_{st}$ following a threshold crossing defines the zero epoch time, and for each event, $4\cdot24$ hours were considered before and $8\cdot24$ hours after event onset.
+For multiple detected threshold crossings within 24 hours of each other, the first crossing was selected as the event because visual inspection showed the following crossings to typically be from brief downward deviations during the recovery period of a geomagnetic storm.
 To compute the epoch averages on a daily time scale, the median value of all available measurements for all events centered on a window of $\pm 12$ hours of the epoch zero hour was computed, and these averaging windows were shifted in increments of $24$~hours.
@@
 The minimum $D_{st}$ median is $-75$~nT.
-Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$ before and after the event, although the magnitude of increase observed here is, on average, $4.5$ amu/cm$^3$ (from $\sim$19 to ${\sim}$24~amu/cm$^3$) instead of the increase of ${\sim} 10$ amu/cm$^3$ found in Figure 11 of \cite{Takahashi2010}.
+Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$ before and after the event, although the magnitude of increase observed here is $4.5$ amu/cm$^3$ instead of the increase of ${\sim} 10$ amu/cm$^3$ found in Figure 11 of \cite{Takahashi2010}.
 The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute the medians and red error lines.
@@
 If a statistically significant difference in the medians between two days existed, the fraction of bootstrap samples with a different sign is expected to be much smaller ($<$ 5\%).
-In terms of a hypothesis test, we cannot reject the null hypothesis that the medians are the same with a confidence higher than 100 minus the \% value shown in the table; the highest confidence level of 86\% is in the difference between day 0 and day -1.
+In terms of a hypothesis test, we cannot reject the null hypothesis that the medians are the same with a confidence higher than 100 minus the percentage value shown in the table; the highest confidence level of 86\% is in the difference between day 0 and day -1.
 
@@
 
-These tests indicate that there is not a statistically significant difference in medians of daily averaged $\rho_{eq}$ on the day before and day after a threshold crossing in $D_{st}$.
+These tests indicate that there is not a statistically significant difference in medians of daily-averaged $\rho_{eq}$ on the day before and day after a threshold crossing in $D_{st}$.
 In addition, the observed differences are on the order of only 20\% of the value of $\rho_{eq}$ on the onset day, which is similar to the variation in the observations over the displayed epoch time interval.
@@
 We have also considered the hourly averages from the events shown in the bottom panel of Figure~\ref{DailyAveragedDstEvents}, which shown in the top panel of Figure~\ref{HourlyAveragedDstEvents}.
-In the time period of elevated mass density within 6 hours of the start of the event, there are only $\sim$4 samples per hourly interval.
-The peak value of $\sim$70 amu/cm$^3$ is associated with a single observation.
+In the time period of elevated mass density within 6 hours of the start of the event, there are only $\sim$4 samples per hourly interval and the peak value of $\sim$70 amu/cm$^3$ is associated with a single observation.
 
-To increase the number of events, we have removed the constraint that the events must occur in the MLT range from 06-12 and the constraint that $D_{st}$ remained below the threshold value for 12 hours or longer.
+To increase the number of events, we have removed the constraint that the events must occur in the MLT range from 06:00-12:00 and the constraint that $D_{st}$ remained below the threshold value for 12 hours or longer.
 The result is shown in the bottom panel of Figure~\ref{HourlyAveragedDstEvents}.
-The two spikes (one updwards after onset, one downwards before onset) were tested for significant deviation from two baselines, one 24-12 hours before onset, one 16-48 hours after onset.
+The two spikes (one upwards after onset, one downwards before onset) were tested for significant deviation from two baselines, one 24-12 hours before onset, one 16-48 hours after onset.
 The probability of the left spike coming from the same distribution as the left baseline is 1.06\%, and 8.2\% from the right baseline, whereas the probability of the right spike coming from the left baseline is 1.89\% and 0.17\% from the right baseline.
-
-%This result is consistent with previous observations of large mass density increases in the plasma trough region during large geomagnetic storms (\cite{Yao2008}; \cite{Takahashi2010}).
+This indicates that there is a statistically significant peak in $\rho_{eq}$ within 6 hours of onset when hourly averages are considered.
+This result is consistent with previous observations of large mass density increases in the plasma trough region during large geomagnetic storms (\cite{Yao2008}; \cite{Takahashi2010}).
 
@@
 
-To determine if there is an IMF $B_{z}$ dependence, the epoch curves in the top panel of Figure~\ref{HourlyAveragedDstEvents} for $\rho_{eq}$ and $B_{z}$ were separated into two parts depending whether $B_z$ was above or below its average four hours before and including the onset hour and four hours after and including the hour of onset; the result is shown in Figure~\ref{fig:BzBinnedDstEvents}.
+To determine if there is an IMF $B_{z}$ dependence, the epoch curves in the bottom panel of Figure~\ref{HourlyAveragedDstEvents} for $\rho_{eq}$ and $B_{z}$ were separated into two parts depending whether $B_z$ was above or below its average four hours before and including the onset hour and four hours after and including the hour of onset; the result is shown in Figure~\ref{fig:BzBinnedDstEvents}.
 Any statistically significant difference at a 95\% confidence level between the two parts is indicated by a green dot on the horizontal axis using the same bootstrap method described previously.
-(At this confidence level, false positives are expected to randomly occur 5\% of the time, or 3.6 times for 72 values.)  These two curves indicate that there is not a statistically significant dependence on IMF $B_{z}$ around the time of the onset of a $D_{st}$ event.
+(At this confidence level, false positives are expected to randomly occur 5\% of the time, or 3.6 times for 72 values.)  These two plots indicate that there is not a statistically significant dependence on IMF $B_{z}$ around the time of the onset of a $D_{st}$ event.
 
-The process for creating Figure~\ref{fig:BzBinnedDstEvents} was repeated except using the sort variable $F10.7$ instead of $B_z$, as shown in Figure~\ref{fig:F107BinnedDstEvents}.
-As expected, difference between the epoch curves is statistically significant at all times, as expected, but elevated $F10.7$ is associated with a peak in the $\rho_{eq}$ curve approximately 5 hours after onset.
-The values contributing to the peak were compared to a baseline of all values 16-48 hours after onset via a Wilcoxon rank-sum test and found to have significantly different medians at the 99\% significance level.
+The process for creating Figure~\ref{fig:BzBinnedDstEvents} was repeated except using the sort variable $F10.7$ instead of $B_z$, and the result is shown in Figure~\ref{fig:F107BinnedDstEvents}.
+The difference between the epoch curves is statistically significant at all times, as expected due to the high correlation between $\rho_{eq}$ and $F10.7$, but elevated $F10.7$ is associated with a peak in the $\rho_{eq}$ curve approximately 5 hours after onset.
+The values contributing to the peak were compared to a baseline of all values 16-48 hours after onset via a Wilcoxon rank-sum test and were found to have significantly different medians at the 99\% significance level.
+This indicates the possibility that there must be a high base-line level of $\rho_{eq}$ in order for an increase in $\rho_{eq}$ to be observed for a $D_{st}$ event.
 
@@
 These events are associated with positive $B_z$ and low values of $D_{st}$.
-Approximately 8 hours after onset, $\rho_{eq}$ peaks and then slowly decays after 40 hours to pre--onset levels.
+Approximately 12 hours after onset, $\rho_{eq}$ slowly decays over 40 hours to near pre--onset levels.
 
@@
 
-The largest difference occurs when the separation is performed after onset, with more positive $B_z$ leading to larger peak $\rho_{eq}$ than more negative $B_{z}$.
+Figure~\ref{BzBinned} shows the the events of Figure~\ref{HourlyAveragedRhoEvents} when separated by $B_z$ in the same manner as Figure~\ref{fig:BzBinnedDstEvents}.
+The largest difference occurs when the separation is performed after onset, with more positive $B_z$ leading to a larger peak in $\rho_{eq}$ than more negative $B_{z}$.
 The rate of change of $\rho_{eq}$ also appears to be insenstive to $B_z$ for approximately 12 hours prior to onset.
-The equivalent epoch separation curves for $P_{dyn}$ had a statistically significant differences similar to that for $B_z$, with higher dynamic pressure playing a role similar to positive $B_z$.
+
+%The equivalent epoch separation curves for $P_{dyn}$ had a statistically significant differences similar to that for $B_z$, with higher dynamic pressure playing a role similar to positive $B_z$.
 
@@
 
-On average, around the time of large geomagnetic events, there is a very weak enhancement of $\rho_{eq}$ and this enhancement does not depend on either the interplanetary magnetic field $B_z$ or the intensity of the geomagnetic event.
-This indicates that there is an approximate balance between magnetospheric enhancement in $\rho_{eq}$ and any reduction due to the inward motion of the plasmasphere.
+On average, around the time of large geomagnetic events, there is a statistically weak enhancement of daily-averaged $\rho_{eq}$, but consideration of hourly average $\rho_{eq}$ shows enhancements over a 6-hour window that contains few events.
+For the hourly-averaged measurements, the average of $B_{z}$ around onset time did not have a significant impact on $\rho_{eq}$ after onset.
 
-$\rho_{eq}$ events are larger when $B_{z}$ is more positive after the onset of the event, which indicates that a substantial portion of the events may due to the apparent mass refilling mechanism described by \cite{Denton2016}.
+It was shown that a key factor in determining if large $\rho_{eq}$ enhancements will be observed is elevated $F10.7$.
+When geomagnetic events were separated according to if they occured when $F10.7$ was low or high, significant enhancements in $\rho_{eq}$ were only observed under high $F10.7$ conditions.
+
+For $\rho_{eq}$, more postive $B_{z}$ after onset lead to higher values of subsequent $\rho_{eq}$, which indicates that a substantial portion of the events may due to the apparent mass refilling mechanism described by \cite{Denton2016}.
 Without additional information about the location of the plasmapause, it may not be possible to separate out the conditions required for enhancement due to enhanced magnetospheric activity from this mechanism.

### 2016-08-11 paper/paper.tex
Double checking paper results with other satellites

@@
 
-The top panel of Figure~\ref{ccplot} shows the long-term trends of log$_{10}(\rho_{eq})$ from GOES 6 and $F_{10.7}$ computed using the median values in 27-day non-overlapping windows.
-A scatter plot of these two lines is shown in the lower panel of Figure~\ref{ccplot} along with that for 1--day and 1--hour medians.
+The top panel of Figure~\ref{fig:ccplot} shows the long-term trends of log$_{10}(\rho_{eq})$ from GOES 6 and $F_{10.7}$ computed using the median values in 27-day non-overlapping windows.
+A scatter plot of these two lines is shown in the lower panel of Figure~\ref{fig:ccplot} along with that for 1--day and 1--hour medians.
 The linear correlation for GOES 6 using all measurements is found to be $0.94$, which is the same value documented by \cite{Takahashi2010} who used combined measurements from all satellites in the time interval of 1980 through 1991 using the constraint $0600 \leq MLT \le 1200$, $K_{p3d}\ge1.0$ and $D_{st}\ge -50$~nT.
@@
 
-The stack plot in the upper panel of Figure \ref{DailyAveragedDstEvents} shows the epoch averages for the 75 events from 1989-1991.
+The stack plot in the upper panel of Figure \ref{fig:DailyAveragedDstEvents} shows the epoch averages for the 75 events from 1989-1991.
 The minimum $D_{st}$ median is $-75$~nT.
@@
 
-In the lower panel of Figure \ref{DailyAveragedDstEvents}, it is shown that the trends seen in the analysis of 1989-1991 also hold for the entire span of measurements from GOES 6 - a small elevation on the day of the event relative to the day before and day after, with median averages after the day of the event being slightly lower than that before.
+In the lower panel of Figure \ref{fig:DailyAveragedDstEvents}, it is shown that the trends seen in the analysis of 1989-1991 also hold for the entire span of measurements from GOES 6 (1983-1991) - a small elevation on the day of the event relative to the day before and day after, with median averages after the day of the event being slightly lower than that before.
+This trend is also seen for GOES 7 (1987-1991), is much less significant for GOES 5 (1983-1987), and much more significant for GOES 2 (1981-1983), correlating with the average value of $F_{10.7}$ during each respective coverage period.
 
-To determine if the magnitude of the density medians in the top panel of Figure~\ref{DailyAveragedDstEvents} on epoch days -1, 0, and 1 are statistically different from each other, we used a two-population bootstrap test.
+To determine if the magnitude of the density medians in the top panel of Figure~\ref{fig:DailyAveragedDstEvents} on epoch days -1, 0, and 1 are statistically different from each other, we used a two-population bootstrap test.
 A bootstrap sample of the medians for each epoch day was created by sampling the values used to compute the median on each epoch day with replacement.
-The observed difference between the medians is shown in Table~\ref{BootstrapDifferenceTable} along with the fraction of observations in 1000 bootstrap differences with a different sign than that observed.
+The observed difference between the medians is shown in Table~\ref{fig:BootstrapDifferenceTable} along with the fraction of observations in 1000 bootstrap differences with a different sign than that observed.
 
@@
 
-A similar hypothesis test run for the bottom panel of Figure~\ref{DailyAveragedDstEvents} yields a maximum confidence level of $\sim$85\%.
+A similar hypothesis test run for the bottom panel of Figure~\ref{fig:DailyAveragedDstEvents} yields a maximum confidence level of $\sim$85\%.
 
@@
 \input{../tables/DeltaBootstraps-case10.txt}
-\caption{Results of test on of means of $\rho_{eq}$ shown in the top panel of Figure~\ref{DailyAveragedDstEvents} between days of threshold crossing  near (day = 1 or -1) or on the day of a $D_{st}$ event (day = 0).}
+\caption{Results of test on of means of $\rho_{eq}$ shown in the top panel of Figure~\ref{fig:DailyAveragedDstEvents} between days of threshold crossing  near (day = 1 or -1) or on the day of a $D_{st}$ event (day = 0).}
 \label{BootstrapDifferenceTable}
@@
 
-We have also considered the hourly averages from the events shown in the bottom panel of Figure~\ref{DailyAveragedDstEvents}, which shown in the top panel of Figure~\ref{HourlyAveragedDstEvents}.
+We have also considered the hourly averages from the events shown in the bottom panel of Figure~\ref{fig:DailyAveragedDstEvents}, which shown in the top panel of Figure~\ref{fig:HourlyAveragedDstEvents}.
 In the time period of elevated mass density within 6 hours of the start of the event, there are only $\sim$4 samples per hourly interval and the peak value of $\sim$70 amu/cm$^3$ is associated with a single observation.
@@
 To increase the number of events, we have removed the constraint that the events must occur in the MLT range from 06:00-12:00 and the constraint that $D_{st}$ remained below the threshold value for 12 hours or longer.
-The result is shown in the bottom panel of Figure~\ref{HourlyAveragedDstEvents}.
+The result is shown in the bottom panel of Figure~\ref{fig:HourlyAveragedDstEvents}.
 The two spikes (one upwards after onset, one downwards before onset) were tested for significant deviation from two baselines, one 24-12 hours before onset, one 16-48 hours after onset.
 The probability of the left spike coming from the same distribution as the left baseline is 1.06\%, and 8.2\% from the right baseline, whereas the probability of the right spike coming from the left baseline is 1.89\% and 0.17\% from the right baseline.
+This significant result is also maintained for GOES 2, 5, and 7.
 This indicates that there is a statistically significant peak in $\rho_{eq}$ within 6 hours of onset when hourly averages are considered.
@@
 
-To determine if there is an IMF $B_{z}$ dependence, the epoch curves in the bottom panel of Figure~\ref{HourlyAveragedDstEvents} for $\rho_{eq}$ and $B_{z}$ were separated into two parts depending whether $B_z$ was above or below its average four hours before and including the onset hour and four hours after and including the hour of onset; the result is shown in Figure~\ref{fig:BzBinnedDstEvents}.
+To determine if there is an IMF $B_{z}$ dependence, the epoch curves in the bottom panel of Figure~\ref{fig:HourlyAveragedDstEvents} for $\rho_{eq}$ and $B_{z}$ were separated into two parts depending whether $B_z$ was above or below its average four hours before and including the onset hour and four hours after and including the hour of onset; the result is shown in Figure~\ref{fig:BzBinnedDstEvents}.
 Any statistically significant difference at a 95\% confidence level between the two parts is indicated by a green dot on the horizontal axis using the same bootstrap method described previously.
@@
 An alternative type of event can be defined that corresponds to large increases in $\rho_{eq}$.
-Figure~\ref{HourlyAveragedRhoEvents} shows the epoch time series for events in which an increase of $\rho_{eq}$ above $20$~amu/cm$^2$ defines the start of the event.
+Figure~\ref{fig:HourlyAveragedRhoEvents} shows the epoch time series for events in which an increase of $\rho_{eq}$ above $20$~amu/cm$^2$ defines the start of the event.
 In finding $\rho_{eq}$ events, missing values were replaced with linearly interpolated values.
@@
 
-Figure~\ref{HourlyAveragedRhoEvents} can be compared with Figure~9 of \cite{Denton2016}, which shows daily averages of $\rho_{eq}$ from this dataset after the onset of quiet $K_p$ intervals.
+Figure~\ref{fig:HourlyAveragedRhoEvents} can be compared with Figure~9 of \cite{Denton2016}, which shows daily averages of $\rho_{eq}$ from this dataset after the onset of quiet $K_p$ intervals.
 The growth shown here is approximately linear and lasts $\sim$ 12--18 hours whereas the 10 quiet $K_p$ events considered by \cite{Denton2016} showed growth that lasted for at least 48~hours.
 
-Figure~\ref{BzBinned} shows the the events of Figure~\ref{HourlyAveragedRhoEvents} when separated by $B_z$ in the same manner as Figure~\ref{fig:BzBinnedDstEvents}.
+Figure~\ref{fig:BzBinned} shows the the events of Figure~\ref{fig:HourlyAveragedRhoEvents} when separated by $B_z$ in the same manner as Figure~\ref{fig:BzBinnedDstEvents}.
 The largest difference occurs when the separation is performed after onset, with more positive $B_z$ leading to a larger peak in $\rho_{eq}$ than more negative $B_{z}$.
@@
 Dashed horizontal lines in the $D_{st}$ and $\rho_{eq}$ panels indicate sample event cutoff thresholds of $D_{st} = -50$~nT and $\rho_{eq} = 20$~amu/cm$^3$ considered in Section~3.}
-\label{AllData}
+\label{fig:AllData}
 \end{figure}
@@
 Bottom: Correlation between $log(\rho_{eq})$ and $F_{10.7}$ using medians in non-overlapping hour, day, and 27-day windows.}
-\label{ccplot}
+\label{fig:ccplot}
 \end{figure}
@@
 \caption{$D_{st}$ events from GOES 6 using daily medians. Top: Events in the interval 1989-1991; compare to \cite{Takahashi2010} Figure~11. Bottom: Events in the interval 1983-1991.}
-\label{DailyAveragedDstEvents}
+\label{fig:DailyAveragedDstEvents}
 \end{figure}
@@
 Bottom: Same as Top except without constraint.}
-\label{HourlyAveragedDstEvents}
+\label{fig:HourlyAveragedDstEvents}
 \end{figure}
@@
 \caption{$\rho_{eq} >$ 20~amu/cm$^3$ events from GOES 6 using hourly medians.}
-\label{HourlyAveragedRhoEvents}
+\label{fig:HourlyAveragedRhoEvents}
 \end{figure}

### 2016-08-11 ComplexPlots.m

@@ -391,11 +391,12 @@ if(MakePaperPlots)
     hold on; plot(xa,AVMDMatBars(:,:),'r-.'); %ylim(AX(1),yranges(yr,5,:))
     if(MDCut>0), plot([xa(1) xa(end)],[MDCut MDCut],'k-.','LineWidth',2); end
     TryTick=0.5;
-    Tryi=4;
-    while(TryTick~=round(TryTick)) %Find a number of ticks that divide evenly
+    Tryi=3;
+    while(sum(TryTick~=round(TryTick))>0) %Find a number of ticks that divide evenly
         TryTick=linspace(yranges(yr,5,1),yranges(yr,5,2),Tryi);
         if(Tryi==8)
             TryTick=linspace(yranges(yr,5,1),yranges(yr,5,2),4);
+            break
         end
         Tryi=Tryi+1;
     end

### 2016-08-11 Density.m

@@ -66,7 +66,7 @@ DentonData
 
 yranges=zeros(5,5,2);
 yranges(1,:,:)=[-2 2; 350 550; -60 0; 150 230; 8 16];
-yranges(2,:,:)=[-8 3; 400 600; -80 0; 140 180; 8 18];
+yranges(2,:,:)=[-8 3; 400 600; -80 0; 140 180; 8 36];
 yranges(3,:,:)=[-8 3; 350 580; -90 0; 170 200; 12 22];
 yranges(4,:,:)=[-3 2; 400 550; -30 -10; 80 120; 12 22];
 yranges(5,:,:)=[-10 10; 0 1000; -100 0; 00 200; 12 22]; %Made for overwriting with specific cases

### 2016-08-11 paper/paper.tex
More verification figures

@@
   \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedB_z-case1-t025-tf30-GOES6.eps}
-  \caption{$D_{st}$ events of Figure~\ref{HourlyAveragedDstEvents} separated by the average $D_{st}$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
+  \caption{$D_{st}$ events of Figure~\ref{fig:HourlyAveragedDstEvents} separated by the average $D_{st}$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
   \label{fig:BzBinnedDstEvents}
@@
   \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedF_{10.7}-case1-t025-tf30-GOES6.eps}
-  \caption{$D_{st}$ events of Figure~\ref{HourlyAveragedDstEvents} separated by the average $F10.7$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
+  \caption{$D_{st}$ events of Figure~\ref{fig:HourlyAveragedDstEvents} separated by the average $F10.7$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
   \label{fig:F107BinnedDstEvents}
@@
   \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedB_z-case24-t025-tf30-GOES6.eps}
-  \caption{$\rho_{eq}$ events of Figure~\ref{HourlyAveragedRhoEvents} separated by the average $B_z$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
+  \caption{$\rho_{eq}$ events of Figure~\ref{fig:HourlyAveragedRhoEvents} separated by the average $B_z$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
   \label{fig:BzBinned}
@@
   \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedF_{10.7}-case24-t025-tf30-GOES6.eps}
-  \caption{$\rho_{eq}$ events of Figure~\ref{HourlyAveragedRhoEvents} separated by the average $F10.7$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
+  \caption{$\rho_{eq}$ events of Figure~\ref{fig:HourlyAveragedRhoEvents} separated by the average $F10.7$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
   \label{fig:F107Binned}

### 2016-08-11 ComplexPlots.m

@@ -60,7 +60,11 @@ if(MakePaperPlots && (stormcase==2 || stormcase==24 || stormcase==1))
         bottombar=nanstd(AVMDMat(nanmedian(AVMat(:,tw,varnum),2)<bottomcut,:))./sqrt(sum(~isnan(AVMDMat(nanmedian(AVMat(:,tw,varnum),2)<bottomcut,:))));
         tvals=ones(1,length(top));
         for j=1:length(top)
+            try
             [p,tvals(j)]=ranksum(AVMDMat(nanmedian(AVMat(:,tw,varnum),2)>=topcut,j),AVMDMat(nanmedian(AVMat(:,tw,varnum),2)<topcut,j));
+            catch
+                tvals(j)=0;
+            end
         end
         %tvals=ttest2(AVMDMat(nanmedian(AVMat(:,tw,varnum),2)>=topcut,:),AVMDMat(nanmedian(AVMat(:,tw,varnum),2)<bottomcut,:));
         tvals(tvals==0)=NaN;

### 2016-08-11 FindStorms.m

@@ -35,6 +35,8 @@ duration(tooclose)=[];
 
 %Cut down found storms to only include pre-noon conditions
 if(cutconditions) 
+    
+    
    endi(MLTFit(starti)>12 | MLTFit(starti)<6)=[];
    duration(MLTFit(starti)>12 | MLTFit(starti)<6)=[];
    starti(MLTFit(starti)>12 | MLTFit(starti)<6)=[];

### 2016-08-17 paper/paper.tex
Near final edits

@@
 In this work we consider the dependence of mass density estimates in the \cite{Takahashi2010} data set and attempt to identify and statistically characterize the relationship between geomagnetic activity with mass density at geosynchronous distances.
-In addition, we attempt to identify solar wind processes that may drive the changes.
+In addition, we attempt to identify solar wind variables that may drive the changes.
 
@@
 A scatter plot of these two lines is shown in the lower panel of Figure~\ref{fig:ccplot} along with that for 1--day and 1--hour medians.
-The linear correlation for GOES 6 using all measurements is found to be $0.94$, which is the same value documented by \cite{Takahashi2010} who used combined measurements from all satellites in the time interval of 1980 through 1991 using the constraint $0600 \leq MLT \le 1200$, $K_{p3d}\ge1.0$ and $D_{st}\ge -50$~nT.
+The linear correlation for GOES 6 using all measurements is found to be $0.94$, which is the same value documented by \cite{Takahashi2010} who used combined measurements from all satellites in the time interval of 1980 through 1991 using the constraint $06\mbox{:}00 \leq MLT \le 12\mbox{:}00$, $K_{p3d}\ge1.0$ and $D_{st}\ge -50$~nT.
 Our 27-day correlations for GOES 2, 5, and 7 are 0.81, 0.78, and 0.87, and the time range of coverage of measurements from these satellites is 1980-01-01/1983-05-16, 1983-01-01/1987-02-28, and 1983-05-27/1991-08-29, respectively.
@@
 Two types of events are considered.
-The first is a drop in the $D_{st}$ index below the threshold of -50~nT.
+The first is a drop in the $D_{st}$ index below the threshold value of -50~nT.
 These types of events are considered in order to determine if there is a well-defined $\rho_{eq}$ dependence on geomagnetic activity/storms as indicated by the $D_{st}$ index.
@@
 The second type of event is an increase in $\rho_{eq}$ above a threshold of 20~amu/cm$^3$.
-It is expected that these increases will typically occur after period of quiet geomagnetic activity but may also be the result of increases in solar wind driven geomagnetic activity.
+It is expected that some of these increases will typically occur after period of quiet geomagnetic activity.
 In this case, the plasmapause boundary may move outward past geosynchronous orbit and the increase will be due to measurements being made inside the plasmapause.
-A second possible reason for the increase could be due to magnetospheric processes.
+A second possible reason for the increase could be due to the same mechanism associated with increases that occur during enhanced geomagnetic activity.
 
@@
 Only events with an onset time between 06:00 and 12:00 MLT were considered.
-The first hour of a local minimum in $D_{st}$ following a threshold crossing defines the zero epoch time, and for each event, $4\cdot24$ hours were considered before and $8\cdot24$ hours after event onset.
-For multiple detected threshold crossings within 24 hours of each other, the first crossing was selected as the event because visual inspection showed the following crossings to typically be from brief downward deviations during the recovery period of a geomagnetic storm.
+The first hour of a local minimum in $D_{st}$ following a threshold crossing defines the zero epoch time, and for each event, $4\cdot24$ hours were considered before and $8\cdot24$ hours after onset.
+For multiple detected threshold crossings within 24 hours of each other, the first crossing was selected as the event onset because visual inspection showed the subsequent crossings to typically be from brief downward deviations during the recovery period of a geomagnetic storm.
 To compute the epoch averages on a daily time scale, the median value of all available measurements for all events centered on a window of $\pm 12$ hours of the epoch zero hour was computed, and these averaging windows were shifted in increments of $24$~hours.
-Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians for each event in 1-day bins and then compute the medians across events on each epoch day.
+Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians for each event in 1-day bins and then compute the medians across the averaged event time series on each epoch day.
 
@@
 In the lower panel of Figure \ref{fig:DailyAveragedDstEvents}, it is shown that the trends seen in the analysis of 1989-1991 also hold for the entire span of measurements from GOES 6 (1983-1991) - a small elevation on the day of the event relative to the day before and day after, with median averages after the day of the event being slightly lower than that before.
-This trend is also seen for GOES 7 (1987-1991), is much less significant for GOES 5 (1983-1987), and much more significant for GOES 2 (1981-1983), correlating with the average value of $F_{10.7}$ during each respective coverage period.
+This trend is also seen for GOES 7 (1987-1991), is much less significant for GOES 5 (1983-1987), and much more significant for GOES 2 (1981-1983).
+We note here that this trend has a relationship with the average value of F10.7 during each respective coverage period, with the most significance found during the 1981-1983 time interval when F10.7 was consistently elevated.
 
@@
 A bootstrap sample of the medians for each epoch day was created by sampling the values used to compute the median on each epoch day with replacement.
-The observed difference between the medians is shown in Table~\ref{fig:BootstrapDifferenceTable} along with the fraction of observations in 1000 bootstrap differences with a different sign than that observed.
+The observed difference between the medians is shown in Table~\ref{BootstrapDifferenceTable} along with the fraction of observations in 1000 bootstrap differences with a different sign than that observed.
 
 If a statistically significant difference in the medians between two days existed, the fraction of bootstrap samples with a different sign is expected to be much smaller ($<$ 5\%).
-In terms of a hypothesis test, we cannot reject the null hypothesis that the medians are the same with a confidence higher than 100 minus the percentage value shown in the table; the highest confidence level of 86\% is in the difference between day 0 and day -1.
+In terms of a hypothesis test, we cannot reject the null hypothesis that the medians are the same with a confidence higher than 100 minus the percentage value shown in the table; the highest confidence level of 86\% is in the difference between days -1 and 0.
 
@@
 \input{../tables/DeltaBootstraps-case10.txt}
-\caption{Results of test on of means of $\rho_{eq}$ shown in the top panel of Figure~\ref{fig:DailyAveragedDstEvents} between days of threshold crossing  near (day = 1 or -1) or on the day of a $D_{st}$ event (day = 0).}
+\caption{Results of test on of medians of $\rho_{eq}$ shown in the top panel of Figure~\ref{fig:DailyAveragedDstEvents} between days of threshold crossing  near (day = 1 or -1) or on the day of a $D_{st}$ event (day = 0).}
 \label{BootstrapDifferenceTable}
@@
 
-To increase the number of events, we have removed the constraint that the events must occur in the MLT range from 06:00-12:00 and the constraint that $D_{st}$ remained below the threshold value for 12 hours or longer.
+To increase the number of events, we have removed the constraint that the events must occur in the MLT range of 06:00-12:00 and the constraint that $D_{st}$ remained below the threshold value for 12 hours or longer.
 The result is shown in the bottom panel of Figure~\ref{fig:HourlyAveragedDstEvents}.
-The two spikes (one upwards after onset, one downwards before onset) were tested for significant deviation from two baselines, one 24-12 hours before onset, one 16-48 hours after onset.
-The probability of the left spike coming from the same distribution as the left baseline is 1.06\%, and 8.2\% from the right baseline, whereas the probability of the right spike coming from the left baseline is 1.89\% and 0.17\% from the right baseline.
+The two variations from a baseline (one downwards before onset and one upwards after onset) were tested for significant deviation from two baselines, one 24-12 hours before onset, one 16-48 hours after onset.
+The probability of the downward variation coming from the same distribution as the data from the left baseline is 1.06\%, whereas the probability of the right upward variation coming from the same distribution of the data for the right baseline is 0.17\%.
 This significant result is also maintained for GOES 2, 5, and 7.
-This indicates that there is a statistically significant peak in $\rho_{eq}$ within 6 hours of onset when hourly averages are considered.
-This result is consistent with previous observations of large mass density increases in the plasma trough region during large geomagnetic storms (\cite{Yao2008}; \cite{Takahashi2010}).
+This indicates that there are statistically significant local variation in $\rho_{eq}$ within 6 hours of onset when hourly averages are considered.
+The signficance of the upward variation result is consistent with previous observations of large mass density increases in the plasma trough region during large geomagnetic storms (\cite{Yao2008}; \cite{Takahashi2010}).
 
@@
 The difference between the epoch curves is statistically significant at all times, as expected due to the high correlation between $\rho_{eq}$ and $F10.7$, but elevated $F10.7$ is associated with a peak in the $\rho_{eq}$ curve approximately 5 hours after onset.
-The values contributing to the peak were compared to a baseline of all values 16-48 hours after onset via a Wilcoxon rank-sum test and were found to have significantly different medians at the 99\% significance level.
-This indicates the possibility that there must be a high base-line level of $\rho_{eq}$ in order for an increase in $\rho_{eq}$ to be observed for a $D_{st}$ event.
+The values contributing to the peak were compared to a baseline of all values 16-48 hours after onset via a Wilcoxon rank-sum test and were found to have significantly different medians at the 99\% confidence level.
+This indicates the possibility that there must be a high pre-existing baseline level of $\rho_{eq}$ in order for an increase in $\rho_{eq}$ to be observed for a $D_{st}$ event.
+This result is also consistent with the the analysis of Figure~3 when repeated using measurements from GOES satellites taken during different parts of the solar cycle; the significance of the differences between the days around onset were largest when the measurements were take during time intervals when F10.7 was consistently elevated.
 
@@
 In finding $\rho_{eq}$ events, missing values were replaced with linearly interpolated values.
-These events are associated with positive $B_z$ and low values of $D_{st}$.
-Approximately 12 hours after onset, $\rho_{eq}$ slowly decays over 40 hours to near pre--onset levels.
+These events are associated with on-average positive $B_z$ and small values of $D_{st}$ with little variability.
+Approximately 12 hours after onset, $\rho_{eq}$ slowly decays over 36 hours to near pre--onset levels.
 
@@
 The largest difference occurs when the separation is performed after onset, with more positive $B_z$ leading to a larger peak in $\rho_{eq}$ than more negative $B_{z}$.
-The rate of change of $\rho_{eq}$ also appears to be insenstive to $B_z$ for approximately 12 hours prior to onset.
+The rate of change of $\rho_{eq}$ also appears to be insensitive to $B_z$ for in the time windows used to determine the separation.
 
@@
 
-Figure~\ref{fig:F107Binned} shows how the epoch average curve of $\rho_{eq}$ in Figure~\ref{fig:BzBinned} depends on $F10.7$.
+Figure~\ref{fig:F107Binned} shows how the epoch average curve of $\rho_{eq}$ in Figure~\ref{fig:HourlyAveragedRhoEvents} depends on $F10.7$.
 Statistically significant differences occur independent of if the separating factor the average of $F10.7$ before or after onset, as expected because the cadence of $F10.7$ is one day and its time scale of variation is longer than that of $\rho_{eq}$.
 Events with high $F10.7$ are associated with higher $\rho_{eq}$ before and after event onset but similar peak values.
-As was the case for $B_Z$, there is an approximately 12--hour time span of linear growth of $\rho_{eq}$ near the time of onset but because the initial starting $\rho_{eq}$ is higher for high $F10.7$, the associated growth rate is lower.
+As was the case for $B_z$, there is an approximately 12--hour time span of linear growth of $\rho_{eq}$ near the time of onset but because the initial starting $\rho_{eq}$ is higher for high $F10.7$, the associated growth rate is lower.
 
@@
 
-On average, around the time of large geomagnetic events, there is a statistically weak enhancement of daily-averaged $\rho_{eq}$, but consideration of hourly average $\rho_{eq}$ shows enhancements over a 6-hour window that contains few events.
+On average, around the time of large geomagnetic events, there is a statistically weak enhancement of daily-averaged $\rho_{eq}$.
+For hourly averages $\rho_{eq}$ shows enhancements over a 6-hour window that contains too few events for a statistical analysis.
+When the constraint of extended geomagnetic events (greater than 12 hours below a threshold value) and the MLT of the observation of $\rho{eq}$ (06:00-12:00) is removed to allow for more events, statistically significant variations are found, with a peak occurring approximately six hours after the event onset.
 For the hourly-averaged measurements, the average of $B_{z}$ around onset time did not have a significant impact on $\rho_{eq}$ after onset.
@@
 It was shown that a key factor in determining if large $\rho_{eq}$ enhancements will be observed is elevated $F10.7$.
-When geomagnetic events were separated according to if they occured when $F10.7$ was low or high, significant enhancements in $\rho_{eq}$ were only observed under high $F10.7$ conditions.
+When geomagnetic events were separated according to if they occurred when $F10.7$ was low or high, significant enhancements in $\rho_{eq}$ above a baseline value were only observed under high $F10.7$ conditions.
 
-For $\rho_{eq}$, more postive $B_{z}$ after onset lead to higher values of subsequent $\rho_{eq}$, which indicates that a substantial portion of the events may due to the apparent mass refilling mechanism described by \cite{Denton2016}.
+For $\rho_{eq}$, more positive $B_{z}$ after onset lead to higher values of subsequent $\rho_{eq}$, which indicates that a substantial portion of the events may due to the apparent mass refilling mechanism described by \cite{Denton2016}.
 Without additional information about the location of the plasmapause, it may not be possible to separate out the conditions required for enhancement due to enhanced magnetospheric activity from this mechanism.
@@
 \includegraphics[scale=0.40]{figures/ccplot-GOES6.eps}
-\caption{Top: 27-day non-overlapping medians of $F_{10.7}$ and $log(\rho_{eq})$ from GOES 6.
-Bottom: Correlation between $log(\rho_{eq})$ and $F_{10.7}$ using medians in non-overlapping hour, day, and 27-day windows.}
+\caption{Top: 27-day non-overlapping medians of $F_{10.7}$ and $\log_{10}(\rho_{eq})$ from GOES 6.
+Bottom: Correlation between $\log_{10}(\rho_{eq})$ and $F_{10.7}$ using medians in non-overlapping hour, day, and 27-day windows.}
 \label{fig:ccplot}
@@
   \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedB_z-case1-t025-tf30-GOES6.eps}
-  \caption{$D_{st}$ events of Figure~\ref{fig:HourlyAveragedDstEvents} separated by the average $D_{st}$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
+  \caption{$D_{st}$ events of the bottom panel of Figure~\ref{fig:HourlyAveragedDstEvents} separated by the average $D_{st}$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
   \label{fig:BzBinnedDstEvents}
@@
   \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedF_{10.7}-case1-t025-tf30-GOES6.eps}
-  \caption{$D_{st}$ events of Figure~\ref{fig:HourlyAveragedDstEvents} separated by the average $F10.7$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
+  \caption{$D_{st}$ events of the bottom panel of Figure~\ref{fig:HourlyAveragedDstEvents} separated by the average $F10.7$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
   \label{fig:F107BinnedDstEvents}

### 2016-08-17 paper/paper.tex
Fixing figures

@@
 To compute an hourly median over the same interval for which the solar wind parameters were averaged, the median of all $\rho_{eq}$ values in a given hour window was used.
-GOES 6 had the longest span of available data and the primary results presented are for GOES 6 while measurements from other satellites were used for consistency checks.
+GOES 6 had the longest span of available (May 1983 to August 1991) data and the primary results presented are for GOES 6 while measurements from other satellites were used for consistency checks.
 

### 2016-08-17 paper/paper.tex
Abstract update

--- 2016-08-17 paper/paper.tex
@@
 We consider two types of events, identified by decreases in $D_{st}$ below a threshold value and increases in the the equatorial mass density at geosynchronous altitudes, $\rho_{eq}$, above a threshold value using the \cite{Takahashi2010} dataset.
-From the $D_{st}$ events and 1-day averages, we find that there is a statistically weak and small amplitude difference between $\rho_{eq}$ on the day of the event and the days before and after.
-For hourly averages, it is found that for 6 hours after onset, very few measurements of $\rho_{eq}$ exist and that most of the contribution to the daily averages is from 6-24 hours after onset.
+From the $D_{st}$ events and 1-day averages, we find that there is a statistically weak and small-amplitude difference between $\rho_{eq}$ on the day of the event and the days before and after.
+
 For hourly averages, $\rho_{eq}$ following the onset of a $D_{st}$ event does not depend on the north-south component of the interplanetary magnetic field, $B_z$ near onset time.
-The primary factor that determines if a post-$D_{st}$ event onset peak in $\rho_{eq}$ will occur in the hourly averages is elevated $F10.7$.
+The primary factor that determines the post-$D_{st}$ event onset peak amplitude in $\rho_{eq}$ in the hourly averages is elevated $F10.7$.
 From the $\rho_{eq}$ events, we find a weak dependence on $B_{z}$ after the onset of an event, with higher average $B_{z}$ four hours after the event onset corresponding to larger $\rho_{eq}$ values 24-36 hours after onset.

### 2016-08-17 FindStorms.m
Making mass density figure with interpolated MLT cutoff

@@ -40,6 +40,8 @@ if(cutconditions)
    endi(MLTFit(starti)>12 | MLTFit(starti)<6)=[];
    duration(MLTFit(starti)>12 | MLTFit(starti)<6)=[];
    starti(MLTFit(starti)>12 | MLTFit(starti)<6)=[];
+end
+if(cutconditions && DstCut<0)
    
    drop=[];
    for i=1:length(starti)

### 2016-08-17 paper/paper.tex
Misc edits

@@
 \begin{document}
-\title{Solar wind and geomagnetic activity influence on the equatorial plasma mass density at geosynchronous orbit}
+\title{Solar wind, F10.7, and geomagnetic activity relationship to the equatorial plasma mass density at geosynchronous orbit}
 \author{V. Veibell and R.S. Weigel}
@@
 %\hrule
+
+% Hourly averages are required to show a statistically significant mass density response during high geomagnetic activity
+% The response of mass density for high geomagnetic activity intervals is strongest when F10.7 is elevated
+% There is no solar wind variation signature associated with large mass density events
+
 \begin{abstract}
@@
 From the $D_{st}$ events and 1-day averages, we find that there is a statistically weak and small-amplitude difference between $\rho_{eq}$ on the day of the event and the days before and after.
-
-For hourly averages, $\rho_{eq}$ following the onset of a $D_{st}$ event does not depend on the north-south component of the interplanetary magnetic field, $B_z$ near onset time.
-The primary factor that determines the post-$D_{st}$ event onset peak amplitude in $\rho_{eq}$ in the hourly averages is elevated $F10.7$.
+When hourly averages are considered, a signficant peak is found to occur six hours after event onset and the primary factor that determines the post-onset peak amplitude in $\rho_{eq}$ in the hourly averages is elevated $F10.7$.
+In addition, for hourly averages, $\rho_{eq}$ following the onset of a $D_{st}$ event does not depend on the north-south component of the interplanetary magnetic field, $B_z$ near the time of onset.
 From the $\rho_{eq}$ events, we find a weak dependence on $B_{z}$ after the onset of an event, with higher average $B_{z}$ four hours after the event onset corresponding to larger $\rho_{eq}$ values 24-36 hours after onset.
@@
 This work presents an analysis of two types of events intended to provide insight into the relationship between $\rho_{eq}$ and solar wind and geomagnetic parameters by considering both large geomagnetic events and large $\rho_{eq}$ events.
-The analysis attempts to address a major difficulty with the identification of the cause in $\rho_{eq}$ enhancements, which can occur for two reasons: (1) an extended period of positive $B_z$, which leads to low geomagnetic activity, plasmasphere refilling, and a possible expansion of the plasmasphere to geosynchronous altitudes and (2) strong negative $B_z$, which (a) leads to the inward motion of the higher density plasmasphere and leaves geosynchronous altitudes in the lower density plasma trough just outside of the plasmapause and (b) causes possible magnetospheric processes to enhance the mass density at geosynchronous altitudes.
+The two types of events were considered in order to account for a difficulty with the identification of the cause in $\rho_{eq}$ enhancements, which can occur for two reasons: (1) an extended period of positive $B_z$, which leads to low geomagnetic activity, plasmasphere refilling, and a possible expansion of the plasmasphere to geosynchronous altitudes and (2) strong negative $B_z$, which (a) leads to the inward motion of the higher density plasmasphere and leaves geosynchronous altitudes in the lower density plasma trough just outside of the plasmapause and (b) causes possible magnetospheric processes to enhance the mass density at geosynchronous altitudes.
 
-On average, around the time of large geomagnetic events, there is a statistically weak enhancement of daily-averaged $\rho_{eq}$.
-For hourly averages $\rho_{eq}$ shows enhancements over a 6-hour window that contains too few events for a statistical analysis.
-When the constraint of extended geomagnetic events (greater than 12 hours below a threshold value) and the MLT of the observation of $\rho{eq}$ (06:00-12:00) is removed to allow for more events, statistically significant variations are found, with a peak occurring approximately six hours after the event onset.
+On average, around the time of large geomagnetic events, there is a statistically weak enhancement of daily-averaged $\rho_{eq}$ measurements.
+For hourly averages, $\rho_{eq}$ shows enhancements over a 6-hour post-onset window that contains too few events for a statistical analysis.
+When the constraint of extended geomagnetic events (greater than 12 hours below a threshold value) and the MLT of the observation of $\rho_{eq}$ (06:00-12:00) is removed to allow for more events, statistically significant variations are found, with a peak occurring approximately six hours after the event onset.
 For the hourly-averaged measurements, the average of $B_{z}$ around onset time did not have a significant impact on $\rho_{eq}$ after onset.
@@
 
-For $\rho_{eq}$, more positive $B_{z}$ after onset lead to higher values of subsequent $\rho_{eq}$, which indicates that a substantial portion of the events may due to the apparent mass refilling mechanism described by \cite{Denton2016}.
-Without additional information about the location of the plasmapause, it may not be possible to separate out the conditions required for enhancement due to enhanced magnetospheric activity from this mechanism.
+For $\rho_{eq}$, more positive $B_{z}$ after onset corresponded to higher values of subsequent $\rho_{eq}$, which indicates that a substantial portion of the events may due to the apparent mass refilling mechanism described by \cite{Denton2016}.
+In order to separate this mechanism from an enhancement due to magnetospheric activity, additional information about the location of the plasmapause may be required.
 

### 2016-08-18 paper/paper.tex
Finalizing paper

@@
 To determine if there is an IMF $B_{z}$ dependence, the epoch curves in the bottom panel of Figure~\ref{fig:HourlyAveragedDstEvents} for $\rho_{eq}$ and $B_{z}$ were separated into two parts depending whether $B_z$ was above or below its average four hours before and including the onset hour and four hours after and including the hour of onset; the result is shown in Figure~\ref{fig:BzBinnedDstEvents}.
-Any statistically significant difference at a 95\% confidence level between the two parts is indicated by a green dot on the horizontal axis using the same bootstrap method described previously.
+Any statistically significant difference at a 95\% confidence level between the two parts is indicated by a green dot on the horizontal axis using a Wilcoxon rank-sum test.
+For verification, the significance values were also tested with the same bootstrap method described previously and found to be similar.
 (At this confidence level, false positives are expected to randomly occur 5\% of the time, or 3.6 times for 72 values.)  These two plots indicate that there is not a statistically significant dependence on IMF $B_{z}$ around the time of the onset of a $D_{st}$ event.

### 2016-08-18 Density.m

@@ -66,7 +66,7 @@ DentonData
 
 yranges=zeros(5,5,2);
 yranges(1,:,:)=[-2 2; 350 550; -60 0; 150 230; 8 16];
-yranges(2,:,:)=[-8 3; 400 600; -80 0; 140 180; 8 36];
+yranges(2,:,:)=[-8 3; 400 600; -80 0; 140 180; 4 22];
 yranges(3,:,:)=[-8 3; 350 580; -90 0; 170 200; 12 22];
 yranges(4,:,:)=[-3 2; 400 550; -30 -10; 80 120; 12 22];
 yranges(5,:,:)=[-10 10; 0 1000; -100 0; 00 200; 12 22]; %Made for overwriting with specific cases
@@ -351,11 +351,11 @@ if(cutoffduration>1)
     durationcaveat=sprintf('longer than %d hours',cutoffduration);
 end
 
-
+%{
 while(sum(isnan(MLTFit))>0)
    MLTFit(isnan(MLTFit))=mod(MLTFit(find(isnan(MLTFit))-1)+1,24);
 end
-
+%}
 
 %%%%%%
 %Find storm indices and apply conditions to prune storms based on duration

### 2016-08-18 paper/paper.tex
Misc edit

--- 2016-08-17 paper/paper.tex
@@
 
+% Key points
 % Hourly averages are required to show a statistically significant mass density response during high geomagnetic activity
@@
 
+% Reviewers
+% Takahashi
+% O'Brien
+% Denton
+% Galager
+% Singer
+
 \begin{abstract}
@@
 From the $D_{st}$ events and 1-day averages, we find that there is a statistically weak and small-amplitude difference between $\rho_{eq}$ on the day of the event and the days before and after.
-When hourly averages are considered, a signficant peak is found to occur six hours after event onset and the primary factor that determines the post-onset peak amplitude in $\rho_{eq}$ in the hourly averages is elevated $F10.7$.
+When hourly averages are considered, a signficant peak is found to occur six hours after event onset, and the primary factor that determines the post-onset peak amplitude in $\rho_{eq}$ is elevated $F10.7$.
 In addition, for hourly averages, $\rho_{eq}$ following the onset of a $D_{st}$ event does not depend on the north-south component of the interplanetary magnetic field, $B_z$ near the time of onset.

### 2016-09-02 paper/paper.tex
Updated paper figures, added denton notes

@@
 From the $D_{st}$ events and 1-day averages, we find that there is a statistically weak and small-amplitude difference between $\rho_{eq}$ on the day of the event and the days before and after.
-When hourly averages are considered, a signficant peak is found to occur six hours after event onset, and the primary factor that determines the post-onset peak amplitude in $\rho_{eq}$ is elevated $F10.7$.
-In addition, for hourly averages, $\rho_{eq}$ following the onset of a $D_{st}$ event does not depend on the north-south component of the interplanetary magnetic field, $B_z$ near the time of onset.
+When hourly averages are considered, a significant peak is found to occur six hours after event onset, and the primary factor that determines the post-onset peak amplitude in $\rho_{eq}$ is elevated $F10.7$.
+In addition, for hourly averages, $\rho_{eq}$ following the onset of a $D_{st}$ event depends on the north-south component of the interplanetary magnetic field, $B_z$ after the time of onset, with higher average $B_{z}$ four hours after the event onset corresponding to larger $\rho_{eq}$ value 7-11 hours after onset.
 From the $\rho_{eq}$ events, we find a weak dependence on $B_{z}$ after the onset of an event, with higher average $B_{z}$ four hours after the event onset corresponding to larger $\rho_{eq}$ values 24-36 hours after onset.
-In contrast, the average of $B_z$ four hours prior to $\rho_{eq}$ events does not have a statistically significant impact on $\rho_{eq}$ after onset.
 \end{abstract}
@@
 \cite{Takahashi2006} estimated magnetospheric mass density using measurements from the CRRES satellite during a 73-day period in 1991 when CRRES was in an elliptical, near equatorial orbit and primarily beyond the nominal plasmapause.
-They found that the local average ion mass, $M$, had some correlation with geomagnetic activity, with more negative hourly $D_{st}$ values corresponding to higher $M$ and 1.5- and 3-day averages of $K_p$ corresponding to higher $M$ (3-hour averages of $K_p$ had little visual correlation with $M$).
+They found that the local average ion mass, $M$, had some correlation with geomagnetic activity, with more negative hourly $D_{st}$ values corresponding to higher $M$ and larger 1.5- and 3-day averages of $K_p$ corresponding to higher $M$ (3-hour averages of $K_p$ had little visual correlation with $M$).
 The mass density estimates were obtained from CRRES observations in the MLT range of [12:00, 18:00] with most observations at $L$ between 5 and 7 $R_E$.
 
-\cite{Denton2006} found a weak relationship between $D_{st}$ and and $K_p$ and the field line distribution of plasma mass density, $\rho$, using observations of the first three toroidal Alfv\'en harmonic frequencies for $L$ in the range of 6-8~$R_E$.
+\cite{Denton2006} found a weak relationship between $D_{st}$ and $K_p$ and the field line distribution of plasma mass density, $\rho$, using observations of the first three toroidal Alfv\'en harmonic frequencies for $L$ in the range of 6-8~$R_E$.
 A more pronounced peak in the distribution along a field line near the equator was found for lower $D_{st}$ and larger $K_p$, but the equatorial value of $\rho$ was found to be similar for $D_{st}$ bins of [-142, -31] and [-31, 37] nT and $K_p$ bins of [1.5,3.4] and [3.4, 5.9].
@@
 \cite{Takahashi2010} noted that downward drops in the $D_{st}$ index coincided with significant changes in $\rho_{eq}$ for $L$ near 6.8~$R_E$.
-For five storms, two had $\rho_{eq}$ spikes after $D_{st}$ minimum, two had $\rho_{eq}$ spikes before the drop, and one showed little change in $\rho_{eq}$.
-A key result was that when daily-averaged measurements were considered, the epoch average of $D_{st}$ exhibited for storms with a minimum $D_{st} < -50$~nT showed an enhancement in $\rho_{eq}$ the same day as minimum $D_{st}$ in the epoch averages.
+For five storms, two had $\rho_{eq}$ increases after $D_{st}$ minimum, two had $\rho_{eq}$ spikes before the minimum, and one showed little change in $\rho_{eq}$.
+A key result was that when daily-averaged measurements were considered, the epoch average of $D_{st}$ for storms with a minimum $D_{st} < -50$~nT showed an enhancement in $\rho_{eq}$ the same day as minimum $D_{st}$ in the epoch averages.
 
@@
 
-The above results indicate that (1) the mass density in the at geosynchronous distances is best correlated with $F10.7$ and (2) there exists a much weaker statistical relationship between mass density and the geomagnetic activity indices $K_p$ and $D_{st}$.
+The above results indicate that (1) the mass density at geosynchronous distances is best correlated with $F10.7$ and (2) there exists a much weaker statistical relationship between mass density and the geomagnetic activity indices $K_p$ and $D_{st}$.
 In this work we consider the dependence of mass density estimates in the \cite{Takahashi2010} data set and attempt to identify and statistically characterize the relationship between geomagnetic activity with mass density at geosynchronous distances.
-In addition, we attempt to identify solar wind variables that may drive the changes.
+In addition, we attempt to identify solar wind variables that may drive or be associated with the changes.
 
@@
 
-The parameters $\rho_{eq}$ and $F_{10.7}$ are from the dataset of \cite{Takahashi2010}; data are available from 1980 through 1991 from GOES 2, 3, 5, 6 and 7.
+The parameters $\rho_{eq}$ and $F_{10.7}$ are from the dataset of \cite{Takahashi2010} data are available from 1980 through 1991 from GOES 2, 3, 5, 6 and 7.
 All other parameters used are from \cite{Kondrashov2014ReconstructionOfGaps}, which has coverage from 1972 through 2013 and are on a 1--hour time grid.
@@
 The first is a drop in the $D_{st}$ index below the threshold value of -50~nT.
-These types of events are considered in order to determine if there is a well-defined $\rho_{eq}$ dependence on geomagnetic activity/storms as indicated by the $D_{st}$ index.
-It is expected that the plasmasphere will exhibit two responses near these threshold crossings.
+These types of events are considered in order to determine if there is a well-defined $\rho_{eq}$ dependence on geomagnetic activity as indicated by the $D_{st}$ index.
+It is expected that the plasmasphere will exhibit two responses near the time of these threshold crossings.
 First is the movement of the plasmapause earthward (\cite{LemaireEarthsPlasmasphere}) and the second is a possible change in density due to magnetospheric processes.
@@
 The second type of event is an increase in $\rho_{eq}$ above a threshold of 20~amu/cm$^3$.
-It is expected that some of these increases will typically occur after period of quiet geomagnetic activity.
+It is expected that some of these increases will typically occur after a period of quiet geomagnetic activity.
 In this case, the plasmapause boundary may move outward past geosynchronous orbit and the increase will be due to measurements being made inside the plasmapause.
@@
 
-Our first analysis uses GOES-6 data only from the time interval 1989-1991, which corresponds with the interval used in the epoch analysis of \cite{Takahashi2010}.
+Our first analysis uses GOES-6 data only from the time interval 1989-1991, which corresponds to the interval used in the epoch analysis of \cite{Takahashi2010}.
 In this interval, there were 75 $D_{st}$ events where $D_{st}$ remained below the $-50$~nT threshold for at least 12 hours.
@@
 
-The stack plot in the upper panel of Figure \ref{fig:DailyAveragedDstEvents} shows the epoch averages for the 75 events from 1989-1991.
+The stack plot in the upper panel of Figure \ref{fig:DailyAveragedDstEvents} shows the epoch averages for the 75 events from 1989-1991 using data from GOES 6.
 The minimum $D_{st}$ median is $-75$~nT.
@@
 The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute the medians and red error lines.
-Error lines for each parameter are the standard deviation of the values used in computing the median divided by the square root of the number of values.
+Error lines for each parameter have a width that is twice the standard deviation of the values used in computing the median divided by the square root of the number of values.
 For the non-$\rho_{eq}$\ parameters, the number of measurements used in computing the medians is typically equal to the number of events, which is much larger than the number of $\rho_{eq}$\ values as all available measurements were used instead of restricting to only values where a $\rho_{eq}$ value also existed.
 
-In the lower panel of Figure \ref{fig:DailyAveragedDstEvents}, it is shown that the trends seen in the analysis of 1989-1991 also hold for the entire span of measurements from GOES 6 (1983-1991) - a small elevation on the day of the event relative to the day before and day after, with median averages after the day of the event being slightly lower than that before.
-This trend is also seen for GOES 7 (1987-1991), is much less significant for GOES 5 (1983-1987), and much more significant for GOES 2 (1981-1983).
-We note here that this trend has a relationship with the average value of F10.7 during each respective coverage period, with the most significance found during the 1981-1983 time interval when F10.7 was consistently elevated.
+In the lower panel of Figure \ref{fig:DailyAveragedDstEvents}, it is shown that the trends seen in the analysis of 1989-1991 also hold for the entire span of measurements from GOES 6 (with coverage years of 1983-1991) - a small elevation on the day of the event relative to the day before and day after, with median averages after the day of the event being slightly lower than that before.
+A similar result is obtained for GOES 7 (1987-1991); the result is much less significant for GOES 5 (1983-1987) and is much more significant for GOES 2 (1981-1983).
+This trend has a relationship with the average value of F10.7 during each respective coverage period, with the most significance found during the 1981-1983 time interval when F10.7 was consistently elevated.
 
@@
 A similar hypothesis test run for the bottom panel of Figure~\ref{fig:DailyAveragedDstEvents} yields a maximum confidence level of $\sim$85\%.
+For verification, the significance values were also tested using a Wilcoxon rank-sum test and were found to be similar.
 
 These tests indicate that there is not a statistically significant difference in medians of daily-averaged $\rho_{eq}$ on the day before and day after a threshold crossing in $D_{st}$.
-In addition, the observed differences are on the order of only 20\% of the value of $\rho_{eq}$ on the onset day, which is similar to the variation in the observations over the displayed epoch time interval.
+In addition, the observed differences are on the order of only 20\% of the value of $\rho_{eq}$ on the onset day, which is similar to the magnitude of variation in the observations over the displayed epoch time interval.
 
@@
 
-We have also considered the hourly averages from the events shown in the bottom panel of Figure~\ref{fig:DailyAveragedDstEvents}, which shown in the top panel of Figure~\ref{fig:HourlyAveragedDstEvents}.
+We have also considered hourly averages of data for the events shown in the bottom panel of Figure~\ref{fig:DailyAveragedDstEvents}, which are shown in the top panel of Figure~\ref{fig:HourlyAveragedDstEvents}.
 In the time period of elevated mass density within 6 hours of the start of the event, there are only $\sim$4 samples per hourly interval and the peak value of $\sim$70 amu/cm$^3$ is associated with a single observation.
@@
 This significant result is also maintained for GOES 2, 5, and 7.
-This indicates that there are statistically significant local variation in $\rho_{eq}$ within 6 hours of onset when hourly averages are considered.
+This indicates that there are statistically significant variations in $\rho_{eq}$ within 6 hours of onset when hourly averages are considered.
 The signficance of the upward variation result is consistent with previous observations of large mass density increases in the plasma trough region during large geomagnetic storms (\cite{Yao2008}; \cite{Takahashi2010}).
@@
 Any statistically significant difference at a 95\% confidence level between the two parts is indicated by a green dot on the horizontal axis using a Wilcoxon rank-sum test.
-For verification, the significance values were also tested with the same bootstrap method described previously and found to be similar.
-(At this confidence level, false positives are expected to randomly occur 5\% of the time, or 3.6 times for 72 values.)  These two plots indicate that there is not a statistically significant dependence on IMF $B_{z}$ around the time of the onset of a $D_{st}$ event.
+For the case where the separation is made according to the value of $B_{z}$ after onset, there is a visible and significant separation between the curves from 7-11 hours after onset, with more negative $B_z$ values corresponding to lower values of $\rho_{eq}$.
+
+% (At this confidence level, false positives are expected to randomly occur 5\% of the time, or 3.6 times for 72 values.)
 
@@
 This indicates the possibility that there must be a high pre-existing baseline level of $\rho_{eq}$ in order for an increase in $\rho_{eq}$ to be observed for a $D_{st}$ event.
-This result is also consistent with the the analysis of Figure~3 when repeated using measurements from GOES satellites taken during different parts of the solar cycle; the significance of the differences between the days around onset were largest when the measurements were take during time intervals when F10.7 was consistently elevated.
+This result is also consistent with the the analysis of Figure~3 when repeated using measurements from GOES satellites taken during different parts of the solar cycle; the significance of the differences between the days around onset were largest when the measurements were taken during time intervals when F10.7 was consistently elevated.
 
@@
 The largest difference occurs when the separation is performed after onset, with more positive $B_z$ leading to a larger peak in $\rho_{eq}$ than more negative $B_{z}$.
-The rate of change of $\rho_{eq}$ also appears to be insensitive to $B_z$ for in the time windows used to determine the separation.
+The rate of change of $\rho_{eq}$ also appears to be insensitive to $B_z$ for the time windows used to determine the separation.
 
@@
 Figure~\ref{fig:F107Binned} shows how the epoch average curve of $\rho_{eq}$ in Figure~\ref{fig:HourlyAveragedRhoEvents} depends on $F10.7$.
-Statistically significant differences occur independent of if the separating factor the average of $F10.7$ before or after onset, as expected because the cadence of $F10.7$ is one day and its time scale of variation is longer than that of $\rho_{eq}$.
+Statistically significant differences occur independent of whether the separating factor is the average of $F10.7$ before or after onset, as expected because the cadence of $F10.7$ is one day and its time scale of variation is longer than that of $\rho_{eq}$.
 Events with high $F10.7$ are associated with higher $\rho_{eq}$ before and after event onset but similar peak values.
@@
 When the constraint of extended geomagnetic events (greater than 12 hours below a threshold value) and the MLT of the observation of $\rho_{eq}$ (06:00-12:00) is removed to allow for more events, statistically significant variations are found, with a peak occurring approximately six hours after the event onset.
-For the hourly-averaged measurements, the average of $B_{z}$ around onset time did not have a significant impact on $\rho_{eq}$ after onset.
+For the hourly-averaged measurements, $\rho_{eq}$ averages within 7-11 hours after the onset time was lower when the average of $B_{z}$ four hours after the onset time was more positive.
+This result highlights the complexity of the response of $\rho_{eq}$ to solar wind driving.
+Negative values of $B_{z}$ are generally needed for a large geomagnetic event to occur and we have shown an association between large geomagnetic events and increases in $\rho_{eq}$ within six hours of the event onset, but after the onset of the event, more positive values of $B_z$ are associated with larger $\rho_{eq}$ values.
 
 It was shown that a key factor in determining if large $\rho_{eq}$ enhancements will be observed is elevated $F10.7$.
-When geomagnetic events were separated according to if they occurred when $F10.7$ was low or high, significant enhancements in $\rho_{eq}$ above a baseline value were only observed under high $F10.7$ conditions.
+When geomagnetic events were separated according to if they occurred when $F10.7$ was low or high, larger enhancements in $\rho_{eq}$ above a baseline value were only observed under high $F10.7$ conditions.
 
-For $\rho_{eq}$, more positive $B_{z}$ after onset corresponded to higher values of subsequent $\rho_{eq}$, which indicates that a substantial portion of the events may due to the apparent mass refilling mechanism described by \cite{Denton2016}.
-In order to separate this mechanism from an enhancement due to magnetospheric activity, additional information about the location of the plasmapause may be required.
+For $\rho_{eq}$ events, more positive $B_{z}$ after onset corresponded to higher values of subsequent $\rho_{eq}$, which indicates that a substantial portion of the events may be due to the apparent mass refilling mechanism described by \cite{Denton2016}.
+In order to separate this mechanism from an enhancement due to magnetospheric activity using this type of analysis, additional information about the location of the plasmapause may be required.
 
@@
 \caption{Top: 27-day non-overlapping medians of $F_{10.7}$ and $\log_{10}(\rho_{eq})$ from GOES 6.
-Bottom: Correlation between $\log_{10}(\rho_{eq})$ and $F_{10.7}$ using medians in non-overlapping hour, day, and 27-day windows.}
+Bottom: Scatter plot of $\log_{10}(\rho_{eq})$ and $F_{10.7}$ using medians in non-overlapping hour, day, and 27-day windows.}
 \label{fig:ccplot}

### 2016-09-02 BasicPlots.m

@@ -346,17 +346,17 @@ if(MakePaperPlots && stormcase==28 && sy==1989 && ey==1989) %For a short time pe
     [~,~, ~,xnew,corr2] = IR(FILLED(:,15),VBS,1,0,0,0); %persistence 
     
     plot(FILLEDTime,xnew,'r','LineWidth',1.5);
-    text(0.01,0.1,'D_{st} (nT)','Units','normalized','FontSize',14);
+    text(0.01,0.1,'D_{st} (nT)','Units','normalized','FontSize',max(get(0,'DefaultAxesFontSize'),14));
     h_legend=legend('Measured',sprintf('IR Model - CC %2.2f',corr),sprintf('Persistence Model - %2.2f',corr2),'Location','SouthEast');
-    set(h_legend,'FontSize',14)
+    set(h_legend,'FontSize',max(get(0,'DefaultAxesFontSize'),14))
     h(2)=subplot('position',subplotstack(2,2)); 
     
     plot(FILLEDTime,VBS,'k','LineWidth',1.5);
-    text(0.01,0.92,'vB_S (V/Km)','Units','normalized','FontSize',14);
+    text(0.01,0.92,'vB_S (V/km)','Units','normalized','FontSize',max(get(0,'DefaultAxesFontSize'),14));
     set(findobj('type','axes'),'xticklabel',{[]});
 set(findobj('type','axes'),'xgrid','on','ygrid','on','box','on')
 axis tight;
-datetick('x','keeplimits')
+datetick('x','keeplimits','keepticks')
 set(findobj('type','axes'),'xtick',get(h(end),'xtick'))
 linkaxes(h,'x')
 axis tight;

### 2016-09-02 ComplexPlots.m

@@ -131,6 +131,9 @@ if(MakePaperPlots && (stormcase==2 || stormcase==24 || stormcase==1))
         plot(xa,bottom,'k','LineWidth',2)%'Color',[0.3 0.8 0.3])
         plot(xa,[top+topbar; top-topbar],'b-.')
         plot(xa,[bottom+bottombar; bottom-bottombar],'k-.')%,'Color',[0.3 0.8 0.3])
+        if(stormcase==24 && figuretype==2 && varnum==30)
+            ylim([0 40])
+        end
         ylims=get(gca,'YLim');
         plot(xa,tvals+ylims(1)-1,'.','MarkerSize',15,'Color',[0.3 0.8 0.3])
         rect=rectangle('Position',[tw(1)-timewidth-1 ylims(1) tw(end)-tw(1) ylims(2)-ylims(1)]) ;
@@ -386,14 +389,14 @@ if(MakePaperPlots)
     h=figure('Visible',visible);
     orient tall;
     
-    h1=subplot('position',subplotstack(5,1));plot(xa,AVs(:,5),'+-','LineWidth',2); text(0.01,0.85,'B_z (nT)','Units','normalized','FontSize',14); %ylabel('B_z (nT)'); %Bz
+    h1=subplot('position',subplotstack(5,1));plot(xa,AVs(:,5),'+-','LineWidth',2); text(0.01,0.85,'B_z (nT)','Units','normalized','FontSize',max(get(0,'DefaultAxesFontSize'),14)); %ylabel('B_z (nT)'); %Bz
     hold on; plot(xa,AVMatBars(:,:,5),'r-.'); ylim(yranges(yr,1,:))
-    h2=subplot('position',subplotstack(5,2));plot(xa,AVs(:,6),'+-','LineWidth',2); text(0.01,0.85,'V_{SW} (km/s)','Units','normalized','FontSize',14); %ylabel('V_{SW} (km/s)');%V_sw
+    h2=subplot('position',subplotstack(5,2));plot(xa,AVs(:,6),'+-','LineWidth',2); text(0.01,0.85,'V_{SW} (km/s)','Units','normalized','FontSize',max(get(0,'DefaultAxesFontSize'),14)); %ylabel('V_{SW} (km/s)');%V_sw
     hold on; plot(xa,AVMatBars(:,:,6),'r-.'); ylim(yranges(yr,2,:))
[…]

### 2016-09-02 Density.m

@@ -47,6 +47,9 @@ if(figuretype==2)
      set(0,'DefaultAxesFontSize',18) %set(groot for R2014b and newer, though seems to work here too?
      set(0,'DefaultTextFontSize',18)
      %set(0,'DefaultLineLinewidth',1.5)
+elseif(figuretype==1)
+     set(0,'DefaultAxesFontSize',16) %set(groot for R2014b and newer, though seems to work here too?
+     set(0,'DefaultTextFontSize',16)
 else
      set(0,'DefaultAxesFontSize',12) %The usual defaults. Set just in case you run the code multiple times (it doesn't reset) 
      set(0,'DefaultTextFontSize',12)

### 2016-09-02 stackplot.m

@@ -38,7 +38,7 @@ for i=1:numvars
     if(sum(ThreshLines(:,1)==i)>0)
         hold on; plot(Time,ones(1,length(Time)).*(ThreshLines(ThreshLines(:,1)==i,2)),'k-.','LineWidth',2)
     end
-    text(0.01,0.85,labels{i},'Units','normalized','FontSize',14);
+    text(0.01,0.85,labels{i},'Units','normalized','FontSize',max(get(0,'DefaultAxesFontSize'),14));
     if(ylims~=0)
         ylim(ylims(1,i,:));
     end
@@ -50,7 +50,7 @@ end
 set(findobj('type','axes'),'xticklabel',{[]});
 set(findobj('type','axes'),'xgrid','on','ygrid','on','box','on')
 axis tight;
-datetick('x','keeplimits')
+datetick('x','keeplimits','keepticks')
 set(findobj('type','axes'),'xtick',get(h(end),'xtick'))
 linkaxes(h,'x')
 axis tight;
@@ -61,7 +61,7 @@ ey=year(Time(end));
 if(sy~=ey)
     xlabel(sprintf('Date from %s through %s',datestr(Time(1),1),datestr(Time(end),1)),'FontSize',14);
 else
-    xlabel(sprintf('Date of %d',sy),'FontSize',14);
+    xlabel(sprintf('Date of %d',sy),'FontSize',max(get(0,'DefaultAxesFontSize'),14));
 end
 
 

### 2016-09-02 paper/paper.tex
Following meeting with Victoir

@@
 The minimum $D_{st}$ median is $-75$~nT.
-Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$ before and after the event, although the magnitude of increase observed here is $4.5$ amu/cm$^3$ instead of the increase of ${\sim} 10$ amu/cm$^3$ found in Figure 11 of \cite{Takahashi2010}.
+Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$ on the day of the event relative to the day before and after, although the magnitude of increase observed here is $4.5$ amu/cm$^3$ instead of the increase of ${\sim} 10$ amu/cm$^3$ found in Figure 11 of \cite{Takahashi2010}.
 The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute the medians and red error lines.
-Error lines for each parameter have a width that is twice the standard deviation of the values used in computing the median divided by the square root of the number of values.
+The uncertainty is shown with error lines for each parameter that have a width that is twice the standard deviation of the values used in computing the median divided by the square root of the number of values.
 For the non-$\rho_{eq}$\ parameters, the number of measurements used in computing the medians is typically equal to the number of events, which is much larger than the number of $\rho_{eq}$\ values as all available measurements were used instead of restricting to only values where a $\rho_{eq}$ value also existed.
@@
 To determine if the magnitude of the density medians in the top panel of Figure~\ref{fig:DailyAveragedDstEvents} on epoch days -1, 0, and 1 are statistically different from each other, we used a two-population bootstrap test.
-A bootstrap sample of the medians for each epoch day was created by sampling the values used to compute the median on each epoch day with replacement.
+A bootstrap sample of the medians for each epoch day was created by sampling all values (with replacement) used to compute the median on each epoch day.
 The observed difference between the medians is shown in Table~\ref{BootstrapDifferenceTable} along with the fraction of observations in 1000 bootstrap differences with a different sign than that observed.
@@
 
-To determine if there is an IMF $B_{z}$ dependence, the epoch curves in the bottom panel of Figure~\ref{fig:HourlyAveragedDstEvents} for $\rho_{eq}$ and $B_{z}$ were separated into two parts depending whether $B_z$ was above or below its average four hours before and including the onset hour and four hours after and including the hour of onset; the result is shown in Figure~\ref{fig:BzBinnedDstEvents}.
+To determine if there is an IMF $B_{z}$ dependence, the epoch curves in the bottom panel of Figure~\ref{fig:HourlyAveragedDstEvents} for $\rho_{eq}$ and $B_{z}$ were separated into two parts based on the median value of $B_z$ within a window.
+One window covered the four hours before onset and onset and the other covered onset and the following four hours; the result is shown in Figure~\ref{fig:BzBinnedDstEvents}.
 Any statistically significant difference at a 95\% confidence level between the two parts is indicated by a green dot on the horizontal axis using a Wilcoxon rank-sum test.
@@
 Figure~\ref{fig:HourlyAveragedRhoEvents} can be compared with Figure~9 of \cite{Denton2016}, which shows daily averages of $\rho_{eq}$ from this dataset after the onset of quiet $K_p$ intervals.
-The growth shown here is approximately linear and lasts $\sim$ 12--18 hours whereas the 10 quiet $K_p$ events considered by \cite{Denton2016} showed growth that lasted for at least 48~hours.
+The growth shown here (using the $\rho_m$ threshold criteria with no constraint on $K_p$) is approximately linear and lasts $\sim$ 12--18 hours whereas the 10 $K_p$ events (elevated $K_p$ followed by 2 days with $K_p \le 1^+$) considered by \cite{Denton2016} showed growth that lasted for at least 48~hours.
 
@@
 Events with high $F10.7$ are associated with higher $\rho_{eq}$ before and after event onset but similar peak values.
-As was the case for $B_z$, there is an approximately 12--hour time span of linear growth of $\rho_{eq}$ near the time of onset but because the initial starting $\rho_{eq}$ is higher for high $F10.7$, the associated growth rate is lower.
+As was the case for $B_z$, there is an approximately 12--hour time span of linear growth of $\rho_{eq}$ near the time of onset but because the initial starting $\rho_{eq}$ is higher for high $F10.7$, the associated growth rate is lower, consistent with \cite{Denton2016}.
 

### 2016-09-02 paper/paper.tex
Add author and acknowledgements
Other mods

@@
 \title{Solar wind, F10.7, and geomagnetic activity relationship to the equatorial plasma mass density at geosynchronous orbit}
-\author{V. Veibell and R.S. Weigel}
+\author{V. Veibell, R.S. Weigel, and R.E. Denton}
 \doublespacing
@@
 The largest difference occurs when the separation is performed after onset, with more positive $B_z$ leading to a larger peak in $\rho_{eq}$ than more negative $B_{z}$.
-The rate of change of $\rho_{eq}$ also appears to be insensitive to $B_z$ for the time windows used to determine the separation.
+The rate of change of $\rho_{eq}$ also appears to be insensitive to the time windows used to determine the separation (before or after onset).
 
@@
 
-In recent years, various works have considered the influence of solar wind control and the geomagnetic activity relationship to the equatorial plasma mass density at geosynchronous orbit, generally using event studies and linear correlations (\cite{Takahashi2006}; \cite{Denton2006}; \cite{Yao2008}; \cite{Takahashi2010}; \cite{Denton2016}).
+In recent years, various works have considered the influence of solar wind control and the geomagnetic activity relationship to the equatorial plasma mass density at geosynchronous orbit, generally using event studies and linear correlations (\cite{Takahashi2006}; \cite{Denton2006}; \cite{Yao2008}; \cite{Takahashi2010}; \cite{Denton2011}; \cite{Denton2016}).
 The event studies show a possible relationship between $\rho_{eq}$ and solar wind and geomagnetic activity indicators such as $K_p$ and $D_{st}$ while correlation studies have generally found a very weak relationship.
@@
 
+%Based on a weak linear relationship between $\rho_{eq}$ and $B_z$, \cite{Denton2016} speculated that this may be a result of a closed magnetosphere being more conducive to plasmasphere refilling.
+
 It was shown that a key factor in determining if large $\rho_{eq}$ enhancements will be observed is elevated $F10.7$.
@@
 In order to separate this mechanism from an enhancement due to magnetospheric activity using this type of analysis, additional information about the location of the plasmapause may be required.
+
+\section{Acknowledgements}
+
+Work at Dartmouth College was supported by NSF grant AGS-1105790
 

### 2016-10-13 paper/paper.tex
Edits based on review

@@
 \usepackage{style/lineno}
+\usepackage[hidelinks]{hyperref}
+%\usepackage{url}
+
 %\usepackage{booktabs}
@@
 \renewcommand{\footrulewidth}{0.0pt}
-
 \oddsidemargin 0.0in
@@
 \begin{abstract}
-We consider two types of events, identified by decreases in $D_{st}$ below a threshold value and increases in the the equatorial mass density at geosynchronous altitudes, $\rho_{eq}$, above a threshold value using the \cite{Takahashi2010} dataset.
+We consider two types of events, identified by decreases in $D_{st}$ below a threshold value and increases in the equatorial mass density at geosynchronous altitudes, $\rho_{eq}$, above a threshold value using the \cite{Takahashi2010} dataset.
 From the $D_{st}$ events and 1-day averages, we find that there is a statistically weak and small-amplitude difference between $\rho_{eq}$ on the day of the event and the days before and after.
@@
 \cite{Takahashi2010} developed a mass density dataset using measurements from the Space Environment Monitor instruments on the Geostationary Operational Environmental Satellites (GOES) satellites from 1980 through 1992, with most measurements in the range of $L=6.8\pm0.2 R_E$.
-The mass density was estimated using the the Alfv\'en wave velocity relationship, $V_A=B/\sqrt{\mu_0\rho}$, a magnetic field model, and a numerical solution to a wave equation with an ionospheric boundary and the assumption of a zero resistance ionosphere.
+The mass density was estimated using the Alfv\'en wave velocity relationship, $V_A=B/\sqrt{\mu_0\rho}$, a magnetic field model, and a numerical solution to a wave equation with an ionospheric boundary and the assumption of a zero resistance ionosphere.
 The equatorial mass density, $\rho_{eq}$, was derived from the estimated mass density using a power law dependence on the geocentric distance to the field line of the observation, $R$, $\rho=\rho_{eq}(LR_E/R)^{1/2}$.
@@
 In this interval, there were 75 $D_{st}$ events where $D_{st}$ remained below the $-50$~nT threshold for at least 12 hours.
-Only events with an onset time between 06:00 and 12:00 MLT were considered.
+Only events with an onset time when the spacecraft was located between 06:00 and 12:00 MLT were considered.
 The first hour of a local minimum in $D_{st}$ following a threshold crossing defines the zero epoch time, and for each event, $4\cdot24$ hours were considered before and $8\cdot24$ hours after onset.
@@
 This indicates the possibility that there must be a high pre-existing baseline level of $\rho_{eq}$ in order for an increase in $\rho_{eq}$ to be observed for a $D_{st}$ event.
-This result is also consistent with the the analysis of Figure~3 when repeated using measurements from GOES satellites taken during different parts of the solar cycle; the significance of the differences between the days around onset were largest when the measurements were taken during time intervals when F10.7 was consistently elevated.
+This result is also consistent with the analysis of Figure~3 when repeated using measurements from GOES satellites taken during different parts of the solar cycle; the significance of the differences between the days around onset were largest when the measurements were taken during time intervals when F10.7 was consistently elevated.
 
@@
 
-Figure~\ref{fig:BzBinned} shows the the events of Figure~\ref{fig:HourlyAveragedRhoEvents} when separated by $B_z$ in the same manner as Figure~\ref{fig:BzBinnedDstEvents}.
+Figure~\ref{fig:BzBinned} shows the events of Figure~\ref{fig:HourlyAveragedRhoEvents} when separated by $B_z$ in the same manner as Figure~\ref{fig:BzBinnedDstEvents}.
 The largest difference occurs when the separation is performed after onset, with more positive $B_z$ leading to a larger peak in $\rho_{eq}$ than more negative $B_{z}$.
@@
 For hourly averages, $\rho_{eq}$ shows enhancements over a 6-hour post-onset window that contains too few events for a statistical analysis.
-When the constraint of extended geomagnetic events (greater than 12 hours below a threshold value) and the MLT of the observation of $\rho_{eq}$ (06:00-12:00) is removed to allow for more events, statistically significant variations are found, with a peak occurring approximately six hours after the event onset.
+When the constraint of extended geomagnetic events (greater than 12 hours below a threshold value) and the spacecraft MLT for observation of $\rho_{eq}$ (06:00-12:00) is removed to allow for more events, statistically significant variations are found, with a peak occurring approximately six hours after the event onset.
 For the hourly-averaged measurements, $\rho_{eq}$ averages within 7-11 hours after the onset time was lower when the average of $B_{z}$ four hours after the onset time was more positive.
@@
 
-Work at Dartmouth College was supported by NSF grant AGS-1105790
+Work at Dartmouth College was supported by NSF grant AGS-1105790.
+
+The mass density data used for this work can be obtained from \url{http://www.dartmouth.edu/~rdenton} and the gap-filled solar wind data is available at \url{http://virbo.org/ftp/users/kondrashov/}.
 

### 2016-10-17 paper/paper.tex
First pass of paper revisions

@@
 \begin{abstract}
-We consider two types of events, identified by decreases in $D_{st}$ below a threshold value and increases in the equatorial mass density at geosynchronous altitudes, $\rho_{eq}$, above a threshold value using the \cite{Takahashi2010} dataset.
+We consider two types of events, identified by decreases in $D_{st}$ below a threshold value and increases in the equatorial mass density at geosynchronous altitudes, $\rho_{eq}$, above a threshold value using the \citet{Takahashi2010} dataset.
 From the $D_{st}$ events and 1-day averages, we find that there is a statistically weak and small-amplitude difference between $\rho_{eq}$ on the day of the event and the days before and after.
@@
 
-The dependence of the plasmapause location on geomagnetic activity was observed as early as \cite{Carpenter1966} and there are well--validated models of the plasmapause location as a function of $L$, $MLT$, and geomagnetic activity (\cite{LemaireEarthsPlasmasphere}, \cite{Moldwin2002ModelPlasmapause}, \cite{OBrien2003EmpiricalPlasmapause}).
-Models also exist for the plasmasphere density (\cite{Gallagher1988EmpiricalModelPlasmasphere}; \cite{LemaireEarthsPlasmasphere}) with similar parameterization.
+The dependence of the plasmapause location on geomagnetic activity was observed as early as \citet{Carpenter1966} and there are well--validated models of the plasmapause location as a function of $L$, $MLT$, and geomagnetic activity (\citet{LemaireEarthsPlasmasphere}, \citet{Moldwin2002ModelPlasmapause}, \citet{OBrien2003EmpiricalPlasmapause}).
+Models also exist for the plasmasphere density (\citet{Gallagher1988EmpiricalModelPlasmasphere}; \citet{LemaireEarthsPlasmasphere}) with similar parameterization.
 
-The dependence of the plasma density outside of the nominal plasmapause location on geomagnetic and solar wind conditions has not been extensively studied until the past decade (\cite{Takahashi2006}; \cite{Takahashi2010}; \cite{Denton2016}).
-Earlier works that considered profiles of ion density found a significant dependence of the plasmapause location on geomagnetic activity (\cite{Chappell1970}; \cite{Maynard1977}; \cite{Carpenter1992}), but the relationship between geomagnetic activity and density outside of the plasmapause was not explicitly considered.
+The dependence of the plasma density outside of the nominal plasmapause location on geomagnetic and solar wind conditions has not been extensively studied until the past decade (\citet{Takahashi2006}; \citet{Takahashi2010}; \citet{Denton2016}).
+Earlier works that considered profiles of ion density found a significant dependence of the plasmapause location on geomagnetic activity (\citet{Chappell1970}; \citet{Maynard1977}; \citet{Carpenter1992}), but the relationship between geomagnetic activity and density outside of the plasmapause was not explicitly considered.
 
-\cite{Takahashi2006} estimated magnetospheric mass density using measurements from the CRRES satellite during a 73-day period in 1991 when CRRES was in an elliptical, near equatorial orbit and primarily beyond the nominal plasmapause.
+\citet{Takahashi2006} estimated magnetospheric mass density using measurements from the CRRES satellite during a 73-day period in 1991 when CRRES was in an elliptical, near equatorial orbit and primarily beyond the nominal plasmapause.
 They found that the local average ion mass, $M$, had some correlation with geomagnetic activity, with more negative hourly $D_{st}$ values corresponding to higher $M$ and larger 1.5- and 3-day averages of $K_p$ corresponding to higher $M$ (3-hour averages of $K_p$ had little visual correlation with $M$).
@@
 
-\cite{Denton2006} found a weak relationship between $D_{st}$ and $K_p$ and the field line distribution of plasma mass density, $\rho$, using observations of the first three toroidal Alfv\'en harmonic frequencies for $L$ in the range of 6-8~$R_E$.
+\citet{Denton2006} found a weak relationship between $D_{st}$ and $K_p$ and the field line distribution of plasma mass density, $\rho$, using observations of the first three toroidal Alfv\'en harmonic frequencies for $L$ in the range of 6-8~$R_E$.
 A more pronounced peak in the distribution along a field line near the equator was found for lower $D_{st}$ and larger $K_p$, but the equatorial value of $\rho$ was found to be similar for $D_{st}$ bins of [-142, -31] and [-31, 37] nT and $K_p$ bins of [1.5,3.4] and [3.4, 5.9].
 
-\cite{Takahashi2010} developed a mass density dataset using measurements from the Space Environment Monitor instruments on the Geostationary Operational Environmental Satellites (GOES) satellites from 1980 through 1992, with most measurements in the range of $L=6.8\pm0.2 R_E$.
+\citet{Takahashi2010} developed a mass density dataset using measurements from the Space Environment Monitor instruments on the Geostationary Operational Environmental Satellites (GOES) satellites from 1980 through 1992, with most measurements in the range of $L=6.8\pm0.2 R_E$.
 The mass density was estimated using the Alfv\'en wave velocity relationship, $V_A=B/\sqrt{\mu_0\rho}$, a magnetic field model, and a numerical solution to a wave equation with an ionospheric boundary and the assumption of a zero resistance ionosphere.
@@
 
-\cite{Takahashi2010} noted that downward drops in the $D_{st}$ index coincided with significant changes in $\rho_{eq}$ for $L$ near 6.8~$R_E$.
+\citet{Takahashi2010} noted that downward drops in the $D_{st}$ index coincided with significant changes in $\rho_{eq}$ for $L$ near 6.8~$R_E$.
 For five storms, two had $\rho_{eq}$ increases after $D_{st}$ minimum, two had $\rho_{eq}$ spikes before the minimum, and one showed little change in $\rho_{eq}$.
@@
 
-\cite{Yao2008} studied the relationship between $D_{st}$ and the number density of low-energy $O^+$ in different regions (ring current and plasma sheet) using the TEAMS and ESA instruments on the low-altitude and high-inclination orbiting FAST satellite and found that the average $N_{O^+}$ across the sampled L-shells (2-14) had a strong correlation (0.88) with the minimum $D_{st}$ of the storm.
+\citet{Yao2008} studied the relationship between $D_{st}$ and the number density of low-energy $O^+$ in different regions (ring current and plasma sheet) using the TEAMS and ESA instruments on the low-altitude and high-inclination orbiting FAST satellite and found that the average $N_{O^+}$ across the sampled L-shells (2-14) had a strong correlation (0.88) with the minimum $D_{st}$ of the storm.
 Although the correlation at geosynchronous distances was not calculated, the data presented for four events show that the enhancements in $N_{O^+}$ tended to appear near $D_{st}$ minimum ($\pm$ 2~hours).
@@
 The above results indicate that (1) the mass density at geosynchronous distances is best correlated with $F10.7$ and (2) there exists a much weaker statistical relationship between mass density and the geomagnetic activity indices $K_p$ and $D_{st}$.
-In this work we consider the dependence of mass density estimates in the \cite{Takahashi2010} data set and attempt to identify and statistically characterize the relationship between geomagnetic activity with mass density at geosynchronous distances.
+In this work we consider the dependence of mass density estimates in the \citet{Takahashi2010} data set and attempt to identify and statistically characterize the relationship between geomagnetic activity with mass density at geosynchronous distances.
 In addition, we attempt to identify solar wind variables that may drive or be associated with the changes.
@@
 %There are several issues that are addressed in detail: (1) the plasma density measurements are sparse, (2) The plasma trough density has a high correlation with F10.7, and geomagnetic and solar wind parameters also correlate with F10.7, (3) the dependence of mass density on the north/south component of the solar wind magnetic field is expected to be nonlinear.
-For northward IMF, corresponding to low solar wind driving of the magnetosphere, the plasmasphere can expand past geosynchronous orbit where trough estimates of mass density are made resulting in an increase in observed density that are not due to solar wind driving; for southward IMF, events studies have shown an increase in mass density associated with strong southward IMF and enhanced magnetospheric activity (\cite{Takahashi2010}; \cite{Yao2008}).
+For northward IMF, corresponding to low solar wind driving of the magnetosphere, the plasmasphere can expand past geosynchronous orbit where trough estimates of mass density are made resulting in an increase in observed density that are not due to solar wind driving; for southward IMF, events studies have shown an increase in mass density associated with strong southward IMF and enhanced magnetospheric activity (\citet{Takahashi2010}; \citet{Yao2008}).
 
@@
 
-The parameters $\rho_{eq}$ and $F_{10.7}$ are from the dataset of \cite{Takahashi2010} data are available from 1980 through 1991 from GOES 2, 3, 5, 6 and 7.
-All other parameters used are from \cite{Kondrashov2014ReconstructionOfGaps}, which has coverage from 1972 through 2013 and are on a 1--hour time grid.
-$\rho_{eq}$ is the inferred equatorial mass density based on the 3rd harmonic torodial frequency of magnetic field measurements as described in \cite{Takahashi2010}.
+The parameters $\rho_{eq}$ and $F_{10.7}$ are from the dataset of \citet{Takahashi2010} data are available from 1980 through 1991 from GOES 2, 3, 5, 6 and 7.
+All other parameters used are from \citet{Kondrashov2014ReconstructionOfGaps}, which has coverage from 1972 through 2013 and are on a 1--hour time grid.
+$\rho_{eq}$ is the inferred equatorial mass density based on the 3rd harmonic torodial frequency of magnetic field measurements as described in \citet{Takahashi2010}.
 The smallest cadence for $\rho_{eq}$ values is 10 minutes.
@@
 A scatter plot of these two lines is shown in the lower panel of Figure~\ref{fig:ccplot} along with that for 1--day and 1--hour medians.
-The linear correlation for GOES 6 using all measurements is found to be $0.94$, which is the same value documented by \cite{Takahashi2010} who used combined measurements from all satellites in the time interval of 1980 through 1991 using the constraint $06\mbox{:}00 \leq MLT \le 12\mbox{:}00$, $K_{p3d}\ge1.0$ and $D_{st}\ge -50$~nT.
+The linear correlation for GOES 6 using all measurements is found to be $0.94$, which is the same value documented by \citet{Takahashi2010} who used combined measurements from all satellites in the time interval of 1980 through 1991 using the constraint $06\mbox{:}00 \leq MLT \le 12\mbox{:}00$, $K_{p3d}\ge1.0$ and $D_{st}\ge -50$~nT.
 Our 27-day correlations for GOES 2, 5, and 7 are 0.81, 0.78, and 0.87, and the time range of coverage of measurements from these satellites is 1980-01-01/1983-05-16, 1983-01-01/1987-02-28, and 1983-05-27/1991-08-29, respectively.
@@
 It is expected that the plasmasphere will exhibit two responses near the time of these threshold crossings.
-First is the movement of the plasmapause earthward (\cite{LemaireEarthsPlasmasphere}) and the second is a possible change in density due to magnetospheric processes.
+First is the movement of the plasmapause earthward (\citet{LemaireEarthsPlasmasphere}) and the second is a possible change in density due to magnetospheric processes.
 
@@
 
-Our first analysis uses GOES-6 data only from the time interval 1989-1991, which corresponds to the interval used in the epoch analysis of \cite{Takahashi2010}.
+Our first analysis uses GOES-6 data only from the time interval 1989-1991, which corresponds to the interval used in the epoch analysis of \citet{Takahashi2010}.
 In this interval, there were 75 $D_{st}$ events where $D_{st}$ remained below the $-50$~nT threshold for at least 12 hours.
@@
 The minimum $D_{st}$ median is $-75$~nT.
-Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$ on the day of the event relative to the day before and after, although the magnitude of increase observed here is $4.5$ amu/cm$^3$ instead of the increase of ${\sim} 10$ amu/cm$^3$ found in Figure 11 of \cite{Takahashi2010}.
+Consistent with \citet{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$ on the day of the event relative to the day before and after, although the magnitude of increase observed here is $4.5$ amu/cm$^3$ instead of the increase of ${\sim} 10$ amu/cm$^3$ found in Figure 11 of \citet{Takahashi2010}.
 The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute the medians and red error lines.
@@
 This indicates that there are statistically significant variations in $\rho_{eq}$ within 6 hours of onset when hourly averages are considered.
-The signficance of the upward variation result is consistent with previous observations of large mass density increases in the plasma trough region during large geomagnetic storms (\cite{Yao2008}; \cite{Takahashi2010}).
+The signficance of the upward variation result is consistent with previous observations of large mass density increases in the plasma trough region during large geomagnetic storms (\citet{Yao2008}; \citet{Takahashi2010}).
 
@@
 
-Figure~\ref{fig:HourlyAveragedRhoEvents} can be compared with Figure~9 of \cite{Denton2016}, which shows daily averages of $\rho_{eq}$ from this dataset after the onset of quiet $K_p$ intervals.
-The growth shown here (using the $\rho_m$ threshold criteria with no constraint on $K_p$) is approximately linear and lasts $\sim$ 12--18 hours whereas the 10 $K_p$ events (elevated $K_p$ followed by 2 days with $K_p \le 1^+$) considered by \cite{Denton2016} showed growth that lasted for at least 48~hours.
+Figure~\ref{fig:HourlyAveragedRhoEvents} can be compared with Figure~9 of \citet{Denton2016}, which shows daily averages of $\rho_{eq}$ from this dataset after the onset of quiet $K_p$ intervals.
+The growth shown here (using the $\rho_m$ threshold criteria with no constraint on $K_p$) is approximately linear and lasts $\sim$ 12--18 hours whereas the 10 $K_p$ events (elevated $K_p$ followed by 2 days with $K_p \le 1^+$) considered by \citet{Denton2016} showed growth that lasted for at least 48~hours.
 
@@
 Events with high $F10.7$ are associated with higher $\rho_{eq}$ before and after event onset but similar peak values.
-As was the case for $B_z$, there is an approximately 12--hour time span of linear growth of $\rho_{eq}$ near the time of onset but because the initial starting $\rho_{eq}$ is higher for high $F10.7$, the associated growth rate is lower, consistent with \cite{Denton2016}.
+As was the case for $B_z$, there is an approximately 12--hour time span of linear growth of $\rho_{eq}$ near the time of onset but because the initial starting $\rho_{eq}$ is higher for high $F10.7$, the associated growth rate is lower, consistent with \citet{Denton2016}.
 
@@
 
-In recent years, various works have considered the influence of solar wind control and the geomagnetic activity relationship to the equatorial plasma mass density at geosynchronous orbit, generally using event studies and linear correlations (\cite{Takahashi2006}; \cite{Denton2006}; \cite{Yao2008}; \cite{Takahashi2010}; \cite{Denton2011}; \cite{Denton2016}).
+In recent years, various works have considered the influence of solar wind control and the geomagnetic activity relationship to the equatorial plasma mass density at geosynchronous orbit, generally using event studies and linear correlations (\citet{Takahashi2006}; \citet{Denton2006}; \citet{Yao2008}; \citet{Takahashi2010}; \citet{Denton2011}; \citet{Denton2016}).
 The event studies show a possible relationship between $\rho_{eq}$ and solar wind and geomagnetic activity indicators such as $K_p$ and $D_{st}$ while correlation studies have generally found a very weak relationship.
@@
 
-%Based on a weak linear relationship between $\rho_{eq}$ and $B_z$, \cite{Denton2016} speculated that this may be a result of a closed magnetosphere being more conducive to plasmasphere refilling.
+%Based on a weak linear relationship between $\rho_{eq}$ and $B_z$, \citet{Denton2016} speculated that this may be a result of a closed magnetosphere being more conducive to plasmasphere refilling.
 
@@
 
-For $\rho_{eq}$ events, more positive $B_{z}$ after onset corresponded to higher values of subsequent $\rho_{eq}$, which indicates that a substantial portion of the events may be due to the apparent mass refilling mechanism described by \cite{Denton2016}.
+For $\rho_{eq}$ events, more positive $B_{z}$ after onset corresponded to higher values of subsequent $\rho_{eq}$, which indicates that a substantial portion of the events may be due to the apparent mass refilling mechanism described by \citet{Denton2016}.
 In order to separate this mechanism from an enhancement due to magnetospheric activity using this type of analysis, additional information about the location of the plasmapause may be required.
@@
 %\bibliographystyle{plainnat}
-\bibliography{paper}
+%\bibliography{paper}
+
+\begin{thebibliography}{16}
+	\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+	\bibitem[{{\it Carpenter\/}(1966)}]{Carpenter1966}
+	Carpenter, D.~L., Whistler studies of the plasmapause in the magnetosphere: 1.
+	{T}emporal variations in the position of the knee and some evidence on plasma
+	motions near the knee, {\it J. Geophys. Res.\/}, {\it 71\/}, 693--709, 1966.
+
+	\bibitem[{{\it Carpenter and Anderson\/}(1992)}]{Carpenter1992}
+	Carpenter, D.~L., and R.~R. Anderson, An {ISEE}/whistler model of equatorial
+	electron density in the magnetosphere, {\it J. Geophys. Res.\/}, {\it 97\/},
+	1097--1108, 1992.
+
+	\bibitem[{{\it Chappell et~al.\/}(1970)}]{Chappell1970}
+	Chappell, C.~R., K.~K. Harris, and G.~W. Sharp, A study of the influence of
+	magnetic activity on the location of the plasmapause as measured by {OGO} 5,
+	{\it J. Geophys. Res.\/}, {\it 75\/}, 50--56, 1970.
+
+	\bibitem[{{\it {Denton}\/}(2007)}]{Denton}
+	{Denton}, R., {Database of Input Parameters for Tsyganenko Magnetic Field
+		Models}, 2007.
+
+	\bibitem[{{\it {Denton} et~al.\/}(2006)}]{Denton2006}
+	{Denton}, R.~E., K.~{Takahashi}, I.~A. {Galkin}, P.~A. {Nsumei}, X.~{Huang},
+	B.~W. {Reinisch}, R.~R. {Anderson}, M.~K. {Sleeper}, and W.~J. {Hughes},
+	{Distribution of density along magnetospheric field lines}, {\it J. of
+		Geophys. Res.\/}, {\it 111\/}, 4213, 2006.
+
+	\bibitem[{{\it Denton et~al.\/}(2011)}]{Denton2011}
+	Denton, R.~E., M.~F. Thomsen, K.~Takahashi, R.~R. Anderson, and H.~J. Singer,
+	Solar cycle dependence of bulk ion composition at geosynchronous orbit, {\it
+		J. Geophys. Res.\/}, {\it 116\/}, n/a--n/a, 2011.
+
+	\bibitem[{{\it Denton et~al.\/}(2016)}]{Denton2016}
+	Denton, R.~E., K.~Takahashi, J.~Amoh, and H.~J. Singer, Mass density at
+	geostationary orbit and apparent mass refilling, {\it J. Geophys. Res.\/},
+	{\it 121\/}, 2962--2975, 2016.
+
+	\bibitem[{{\it {Gallagher} et~al.\/}(1988)}]{Gallagher1988EmpiricalModelPlasmasphere}
+	{Gallagher}, D.~L., P.~D. {Craven}, and R.~H. {Comfort}, {An empirical model of
+		the earth's plasmasphere}, {\it Advances in Space Research\/}, {\it 8\/},
+	15--21, 1988.
+
+	\bibitem[{{\it {Kondrashov} et~al.\/}(2014)}]{Kondrashov2014ReconstructionOfGaps}
+	{Kondrashov}, D., R.~{Denton}, Y.~Y. {Shprits}, and H.~J. {Singer},
+	{Reconstruction of gaps in the past history of solar wind parameters}, {\it
+		Geophys. Res. Lett.\/}, {\it 41\/}, 2702--2707, 2014.
+
+	\bibitem[{{\it Lemaire\/}(1998)}]{LemaireEarthsPlasmasphere}
+	Lemaire, J., {\it The Earth's Plasmasphere\/}, Cambridge University Press,
+	1998.
+
+	\bibitem[{{\it Maynard and Grebowsky\/}(1977)}]{Maynard1977}
+	Maynard, N.~C., and J.~M. Grebowsky, The plasmapause revisited, {\it J.
+		Geophys. Res.\/}, {\it 82\/}, 1591--1600, 1977.
+
+	\bibitem[{{\it {Moldwin} et~al.\/}(2002)}]{Moldwin2002ModelPlasmapause}
+	{Moldwin}, M.~B., L.~{Downward}, H.~K. {Rassoul}, R.~{Amin}, and R.~R.
+	{Anderson}, {A new model of the location of the plasmapause: CRRES results},
+	{\it J. of Geophys. Res.\/}, {\it 107\/}, 1339, 2002.
+
+	\bibitem[{{\it {O'Brien} and
+			{Moldwin}\/}(2003)}]{OBrien2003EmpiricalPlasmapause}
+	{O'Brien}, T.~P., and M.~B. {Moldwin}, {Empirical plasmapause models from
+		magnetic indices}, {\it Geophys. Res. Lett.\/}, {\it 30\/}, 1--1, 2003.
+
+	\bibitem[{{\it {Takahashi} et~al.\/}(2006)}]{Takahashi2006}
+	{Takahashi}, K., R.~E. {Denton}, R.~R. {Anderson}, and W.~J. {Hughes}, {Mass
+		density inferred from toroidal wave frequencies and its comparison to
+		electron density}, {\it J. of Geophys. Res.\/}, {\it 111\/}, 1201, 2006.
+
+	\bibitem[{{\it {Takahashi} et~al.\/}(2010)}]{Takahashi2010}
+	{Takahashi}, K., R.~E. {Denton}, and H.~J. {Singer}, {Solar cycle variation of
+		geosynchronous plasma mass density derived from the frequency of standing
+		Alfv{\'e}n waves}, {\it J. of Geophys. Res.\/}, {\it 115\/}, 7207, 2010.
+
+	\bibitem[{{\it {Yao} et~al.\/}(2008)}]{Yao2008}
+	{Yao}, Y., K.~{Seki}, Y.~{Miyoshi}, J.~P. {McFadden}, E.~J. {Lund}, and C.~W.
+	{Carlson}, {Effect of solar wind variation on low-energy O$^+$ populations in
+		the magnetosphere during geomagnetic storms: FAST observations}, {\it J. of
+		Geophys. Res.\/}, {\it 113\/}, 2008.
+
+\end{thebibliography}
 
@@
 \centering
-\includegraphics[scale=0.45]{figures/alldata-GOES6-1983-1991.eps}
+\includegraphics[scale=0.45]{UsedFigures/2016SW001507R-p01.eps}
 \caption{Overview of data used in this article.
-The top four panels show parameters from \cite{Kondrashov2014ReconstructionOfGaps} and the bottom panel contains $\rho_{eq}$ based on GOES 6 measurements from \cite{Denton} after interpolation and averaging described in the text.
+The top four panels show parameters from \citet{Kondrashov2014ReconstructionOfGaps} and the bottom panel contains $\rho_{eq}$ based on GOES 6 measurements from \citet{Denton} after interpolation and averaging described in the text.
 Dashed horizontal lines in the $D_{st}$ and $\rho_{eq}$ panels indicate sample event cutoff thresholds of $D_{st} = -50$~nT and $\rho_{eq} = 20$~amu/cm$^3$ considered in Section~3.}
@@
 \centering
-\includegraphics[scale=0.40]{figures/F107MD27d-GOES6.eps}
-\includegraphics[scale=0.40]{figures/ccplot-GOES6.eps}
+\includegraphics[scale=0.40]{UsedFigures/2016SW001507R-p02a.eps}
+\includegraphics[scale=0.40]{UsedFigures/2016SW001507R-p02b.eps}
 \caption{Top: 27-day non-overlapping medians of $F_{10.7}$ and $\log_{10}(\rho_{eq})$ from GOES 6.
@@
 \centering
-\includegraphics[scale=0.40]{figures/stormavs-dst-50-tak-GOES6.eps}
+\includegraphics[scale=0.40]{UsedFigures/2016SW001507R-p03a.eps}
 \\
@@
 \\
-\includegraphics[scale=0.40]{figures/stormavs-dst-day-GOES6.eps}
-\caption{$D_{st}$ events from GOES 6 using daily medians. Top: Events in the interval 1989-1991; compare to \cite{Takahashi2010} Figure~11. Bottom: Events in the interval 1983-1991.}
+\includegraphics[scale=0.40]{UsedFigures/2016SW001507R-p03b.eps}
+\caption{$D_{st}$ events from GOES 6 using daily medians. Top: Events in the interval 1989-1991; compare to \citet{Takahashi2010} Figure~11. Bottom: Events in the interval 1983-1991.}
 \label{fig:DailyAveragedDstEvents}
@@
 \centering
-\includegraphics[scale=0.40]{figures/stormavs-dd12-GOES6.eps}
+\includegraphics[scale=0.40]{UsedFigures/2016SW001507R-p04a.eps}
 \\
@@
 \\
-\includegraphics[scale=0.40]{figures/stormavs-dst-GOES6.eps}
+\includegraphics[scale=0.40]{UsedFigures/2016SW001507R-p04b.eps}
 \caption{$D_{st}$ events from GOES 6 using hourly medians.
@@
   \centering
-  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedB_z-case1-t020-tf25-GOES6.eps}
-  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedB_z-case1-t025-tf30-GOES6.eps}
+  \includegraphics[scale=0.40]{UsedFigures/2016SW001507R-p05a.eps}
+  \includegraphics[scale=0.40]{UsedFigures/2016SW001507R-p05b.eps}
   \caption{$D_{st}$ events of the bottom panel of Figure~\ref{fig:HourlyAveragedDstEvents} separated by the average $D_{st}$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
@@
   \centering
-  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedF_{10.7}-case1-t020-tf25-GOES6.eps}
-  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedF_{10.7}-case1-t025-tf30-GOES6.eps}
+  \includegraphics[scale=0.40]{UsedFigures/2016SW001507R-p06a.eps}
+  \includegraphics[scale=0.40]{UsedFigures/2016SW001507R-p06b.eps}
   \caption{$D_{st}$ events of the bottom panel of Figure~\ref{fig:HourlyAveragedDstEvents} separated by the average $F10.7$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
@@
 \centering
-\includegraphics[scale=0.40]{figures/stormavs-mass-gt20-GOES6.eps}
+\includegraphics[scale=0.40]{UsedFigures/2016SW001507R-p07.eps}
 \caption{$\rho_{eq} >$ 20~amu/cm$^3$ events from GOES 6 using hourly medians.}
@@
   \centering
-  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedB_z-case24-t020-tf25-GOES6.eps}
-  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedB_z-case24-t025-tf30-GOES6.eps}
+  \includegraphics[scale=0.40]{UsedFigures/2016SW001507R-p08a.eps}
+  \includegraphics[scale=0.40]{UsedFigures/2016SW001507R-p08b.eps}
   \caption{$\rho_{eq}$ events of Figure~\ref{fig:HourlyAveragedRhoEvents} separated by the average $B_z$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
@@
   \centering
-  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedF_{10.7}-case24-t020-tf25-GOES6.eps}
-  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedF_{10.7}-case24-t025-tf30-GOES6.eps}
+  \includegraphics[scale=0.40]{UsedFigures/2016SW001507R-p09a.eps}
+  \includegraphics[scale=0.40]{UsedFigures/2016SW001507R-p09b.eps}
   \caption{$\rho_{eq}$ events of Figure~\ref{fig:HourlyAveragedRhoEvents} separated by the average $F10.7$ value (a) at onset and four hours before, and (b) at onset and four hours after.}

### 2016-10-18 paper/paper.tex
Add conclusion sentence

--- 2016-10-13 paper/paper.tex
@@
 \cite{Takahashi2010} developed a mass density dataset using measurements from the Space Environment Monitor instruments on the Geostationary Operational Environmental Satellites (GOES) satellites from 1980 through 1992, with most measurements in the range of $L=6.8\pm0.2 R_E$.
-The mass density was estimated using the Alfv\'en wave velocity relationship, $V_A=B/\sqrt{\mu_0\rho}$, a magnetic field model, and a numerical solution to a wave equation with an ionospheric boundary and the assumption of a zero resistance ionosphere.
+The mass density was estimated using the Alfv\'en wave velocity relationship, $V_A=B/\sqrt{\mu_0\rho}$, a storm-time magnetic field model, and a numerical solution to a wave equation with an ionospheric boundary and the assumption of a zero resistance ionosphere.
 The equatorial mass density, $\rho_{eq}$, was derived from the estimated mass density using a power law dependence on the geocentric distance to the field line of the observation, $R$, $\rho=\rho_{eq}(LR_E/R)^{1/2}$.
@@
 When geomagnetic events were separated according to if they occurred when $F10.7$ was low or high, larger enhancements in $\rho_{eq}$ above a baseline value were only observed under high $F10.7$ conditions.
+\cite{Denton2016} showed that the ratio of O$^+$/H$^+$ changes greatly with solar cycle, with larger amounts of O$^+$ occurring during solar maximum (when $F10.7$ is elevated).
+The dependence of the mass density response on $F10.7$ suggests that the process responsible for enhancing $\rho_{eq}$ during geomagnetic storms may have a strong sensitivity to the O$^+$/H$^+$ ratio.
 

### 2016-10-18 paper/paper.production.tex
Paper diff in new file, figures split into pdfs

--- 2016-10-17 paper/paper.tex
@@
 \citet{Takahashi2010} developed a mass density dataset using measurements from the Space Environment Monitor instruments on the Geostationary Operational Environmental Satellites (GOES) satellites from 1980 through 1992, with most measurements in the range of $L=6.8\pm0.2 R_E$.
-The mass density was estimated using the Alfv\'en wave velocity relationship, $V_A=B/\sqrt{\mu_0\rho}$, a magnetic field model, and a numerical solution to a wave equation with an ionospheric boundary and the assumption of a zero resistance ionosphere.
+The mass density was estimated using the Alfv\'en wave velocity relationship, $V_A=B/\sqrt{\mu_0\rho}$, a storm-time magnetic field model, and a numerical solution to a wave equation with an ionospheric boundary and the assumption of a zero resistance ionosphere.
 The equatorial mass density, $\rho_{eq}$, was derived from the estimated mass density using a power law dependence on the geocentric distance to the field line of the observation, $R$, $\rho=\rho_{eq}(LR_E/R)^{1/2}$.

### 2016-10-18 paper/paper.tex
Paper diff in new file, figures split into pdfs

@@
 \centering
-\includegraphics[scale=0.45]{figures/alldata-GOES6-1983-1991.eps}
+\includegraphics[scale=0.45]{UsedFigures/2016SW001507R-p01.eps}
 \caption{Overview of data used in this article.
@@
 \\
-\includegraphics[scale=0.40]{figures/stormavs-dst-day-GOES6.eps}
+\includegraphics[scale=0.40]{UsedFigures/2016SW001507R-p03b.eps}
 \caption{$D_{st}$ events from GOES 6 using daily medians. Top: Events in the interval 1989-1991; compare to \cite{Takahashi2010} Figure~11. Bottom: Events in the interval 1983-1991.}

### 2016-10-19 paper/paper.template.tex
Filling out AGU template

--- 2016-10-18 paper/paper.production.tex
@@
-%\documentclass[11pt,twocolumn]{article}
-%\usepackage{graphicx}
-%\usepackage{fancyhdr}
-%\usepackage{amssymb,amsmath}
-%\usepackage[usenames,dvipsnames]{color}
-%\usepackage[colorlinks,citecolor=RedViolet,urlcolor=blue]{hyperref}
-%\usepackage{doi}
-%\usepackage{setspace}
-%\usepackage[paperwidth=8.5in, paperheight=11in,top=1in, bottom=1in, left=1in, r%ight=1in]{geometry}
-%\usepackage[compact]{titlesec}
-%\usepackage{abstract}
-%\usepackage[position=t,singlelinecheck=off,justification=raggedleft]{subcaption}
-%\usepackage[authoryear,square]{natbib}
-%\usepackage{aas_macros}
-%\usepackage{array}
-%\pagestyle{fancy}
-%\fancyhead[R]{Veibell \thepage}
-%\fancyhead[L]{}
+%% 11/23/2015
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% AGUJournalTemplate.tex: this template file is for articles formatted with LaTeX
+%
+% This file includes commands and instructions
+% given in the order necessary to produce a final output that will
+% satisfy AGU requirements. 
+%
+% You may copy this file and give it your
+% article name, and enter your text.
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% PLEASE DO NOT USE YOUR OWN MACROS
+% DO NOT USE \newcommand, \renewcommand, or \def, etc.
+%
+% FOR FIGURES, DO NOT USE \psfrag or \subfigure.
+% DO NOT USE \psfrag or \subfigure commands.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% All questions should be e-mailed to latex@agu.org.
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% Step 1: Set the \documentclass
+%
+% There are two options for article format:
+%
+% 1) PLEASE USE THE DRAFT OPTION TO SUBMIT YOUR PAPERS.
+% The draft option produces double spaced output.
+% 
+% 2) numberline will give you line numbers.
 
-%\newcolumntype{L}{>{$}l<{$}} %To enable math mode in tables (for saying things like B_z)
-%\newcolumntype{C}{>{$}c<{$}}
-%\newcommand{\vinote}[1]{\textcolor{red}{\textbf{#1}}} %If you want \inote{#} instead of just \note #, for inline notes
-%\def\vnote#1\par{\textcolor{red}{\textbf{#1}}\\} %Make note bold and red, re-add newline
-%\newcommand{\req}{\ensuremath{\rho_{eq}}}
-%\newcommand{\inote}[1]{\textcolor{blue}{\textbf{#1}}} %Inline notes in blue
-%\def\note#1\par{\textcolor{blue}{\textbf{#1}}\\}
+%% To submit your paper:
+\documentclass[draft,linenumbers]{agujournal}
+\draftfalse
 
-\documentclass[12pt]{article}
-\bibliographystyle{./style/agufull}
-\usepackage[square,comma,authoryear]{natbib}
-\usepackage{aas_macros}
-\usepackage{epsfig}
-\usepackage{amsmath}
-\usepackage{style/lineno}
-\usepackage[hidelinks]{hyperref}
-%\usepackage{url}
+%% For final version.
+% \documentclass{agujournal}
 
-%\usepackage{booktabs}
-\linenumbers*[1]
-\usepackage{subfig}
+% Now, type in the journal name: \journalname{<Journal Name>}
 
-\usepackage{setspace}  
-\usepackage{fancyhdr}
+% ie, \journalname{Journal of Geophysical Research}
+%% Choose from this list of Journals:
+%
+% JGR-Atmospheres
+% JGR-Biogeosciences
+% JGR-Earth Surface
+% JGR-Oceans
+% JGR-Planets
+% JGR-Solid Earth
+% JGR-Space Physics
+% Global Biochemical Cycles
+% Geophysical Research Letters
+% Paleoceanography
+% Radio Science
+% Reviews of Geophysics
+% Tectonics
+% Space Weather
+% Water Resource Research
+% Geochemistry, Geophysics, Geosystems
+% Journal of Advances in Modeling Earth Systems (JAMES)
+% Earth's Future
+% Earth and Space Science
+%
+%
 
-\newcommand{\citeay}[1]{%
-\citeauthor{#1}, \citeyear{#1}%
-}
-
-\pagestyle{fancy}
-\fancyhead{}
-\fancyfoot{}
-\fancyhead[R]{X - \thepage}
-\fancyhead[L]{VEIBELL: MASS DENSITY AT GEO}
-\fancyfoot[L]{D R A F T}
-\fancyfoot[C]{\today}
-\fancyfoot[R]{D R A F T}
-\renewcommand{\headrulewidth}{0.0pt}
-\renewcommand{\footrulewidth}{0.0pt}
-\oddsidemargin 0.0in
-\evensidemargin 1.0in
-\textwidth 6.5in
-\headheight 0.1in
-\topmargin -0.5in
-\textheight 9.0in
+\journalname{Space Weather}
 
 \begin{document}
+
+%% ------------------------------------------------------------------------ %%
+%  Title
+% 
+% (A title should be specific, informative, and brief. Use
+% abbreviations only if they are defined in the abstract. Titles that
+% start with general keywords then specific terms are optimized in
+% searches)
+%
+%% ------------------------------------------------------------------------ %%
+
+% Example: \title{This is a test title}
+
 \title{Solar wind, F10.7, and geomagnetic activity relationship to the equatorial plasma mass density at geosynchronous orbit}
-\author{V. Veibell, R.S. Weigel, and R.E. Denton}
-\doublespacing
-\maketitle
 
-%\author{
-%Victoir Veibell\footnote{vveibell@gmu.edu}
-%\and
-%R.S. Weigel\footnote{rweigel@gmu.edu}}
+%% ------------------------------------------------------------------------ %%
+%
+%  AUTHORS AND AFFILIATIONS
+%
+%% ------------------------------------------------------------------------ %%
 
-%\setlength{\parskip}{3ex}
+% Authors are individuals who have significantly contributed to the
+% research and preparation of the article. Group authors are allowed, if
+% each author in the group is separately identified in an appendix.)
 
-%\titlespacing{\section}{0pc}{0.2pc}{-1pc}
-%\titlespacing{\subsection}{0pc}{0.1pc}{-1pc}
-%\titleformat*{\section}{\normalsize\bfseries}
-%\titleformat*{\subsection}{\small\bfseries}
+% List authors by first name or initial followed by last name and
+% separated by commas. Use \affil{} to number affiliations, and
+% \thanks{} for author notes.  
+% Additional author notes should be indicated with \thanks{} (for
+% example, for current addresses).
 
-%\twocolumn[
-%  \begin{@twocolumnfalse}
-%\maketitle
-%\hrule
+% Example: \authors{A. B. Author\affil{1}\thanks{Current address, Antartica}, B. C. Author\affil{2,3}, and D. E.
+% Author\affil{3,4}\thanks{Also funded by Monsanto.}}
 
-% Key points
-% Hourly averages are required to show a statistically significant mass density response during high geomagnetic activity
-% The response of mass density for high geomagnetic activity intervals is strongest when F10.7 is elevated
-% There is no solar wind variation signature associated with large mass density events
+\authors{V. Veibell\affil{1}, R.S. Weigel\affil{1}, and R.E. Denton\affil{2}}
 
-% Reviewers
-% Takahashi
-% O'Brien
-% Denton
-% Galager
-% Singer
+% \affiliation{1}{First Affiliation}
+% \affiliation{2}{Second Affiliation}
+% \affiliation{3}{Third Affiliation}
+% \affiliation{4}{Fourth Affiliation}
+
+\affiliation{1}{George Mason University}
+\affiliation{2}{Dartmouth University}
+%(repeat as many times as is necessary)
+
+%% Corresponding Author:
+% Corresponding author mailing address and e-mail address:
+
+% (include name and email addresses of the corresponding author.  More
+% than one corresponding author is allowed in this LaTeX file and for
+% publication; but only one corresponding author is allowed in our
+% editorial system.)
+
+% Example: \correspondingauthor{First and Last Name}{email@address.edu}
+
+%\correspondingauthor{=name=}{=email address=}
+
+%% Keypoints, final entry on title page.
+
+% Example: 
+% \begin{keypoints}
+% \item	List up to three key points (at least one is required)
+% \item	Key Points summarize the main points and conclusions of the article
+% \item	Each must be 100 characters or less with no special characters or punctuation 
+% \end{keypoints}
+
+%  List up to three key points (at least one is required)
+%  Key Points summarize the main points and conclusions of the article
+%  Each must be 100 characters or less with no special characters or punctuation
+
+\begin{keypoints}
+\item = enter point 1 here = 
+\item = enter point 2 here = 
+\item = enter point 3 here = 
+\end{keypoints}
+
+%% ------------------------------------------------------------------------ %%
+%
+%  ABSTRACT
+%
+% A good abstract will begin with a short description of the problem
+% being addressed, briefly describe the new data or analyses, then
+% briefly states the main conclusion(s) and how they are supported and
+% uncertainties. 
+%% ------------------------------------------------------------------------ %%
+
+%% \begin{abstract} starts the second page
 
@@
 \end{abstract}
-%\vspace{2em}
-%\hrule
-%\vspace{2em}
-% \end{@twocolumnfalse}
-%  ]
-
-%\saythanks
 
@@
 
-\section{Acknowledgements}
-
+\acknowledgments
 Work at Dartmouth College was supported by NSF grant AGS-1105790.
 
-The mass density data used for this work can be obtained from \url{http://www.dartmouth.edu/~rdenton} and the gap-filled solar wind data is available at \url{http://virbo.org/ftp/users/kondrashov/}.
+The mass density data used for this work can be obtained from http://www.dartmouth.edu/~rdenton and the gap-filled solar wind data is available at http://virbo.org/ftp/users/kondrashov/.
 
-\newpage
-%\footnotesize
-%\bibliographystyle{plainnat}
-%\bibliography{paper}
+%% ------------------------------------------------------------------------ %%
+%% Citations
+
+% Please use ONLY \citet and \citep for reference citations.
+% DO NOT use other cite commands (e.g., \cite, \citeyear, \nocite, \citealp, etc.).
+
+%% Example \citet and \citep:
+%  ...as shown by \citet{Boug10}, \citet{Buiz07}, \citet{Fra10},
+%  \citet{Ghel00}, and \citet{Leit74}.
+
+%  ...as shown by \citep{Boug10}, \citep{Buiz07}, \citep{Fra10},
+%  \citep{Ghel00, Leit74}.
+
+%  ...has been shown \citep [e.g.,][]{Boug10,Buiz07,Fra10}.
+
+%%  REFERENCE LIST AND TEXT CITATIONS
+%
+% Either type in your references using
+%
+% \begin{thebibliography}{}
+% \bibitem[{\textit{Kobayashi et~al.}}(2003)]{R2013} Kobayashi, T.,
+% Tran, A.~H., Nishijo, H., Ono, T., and Matsumoto, G.  (2003).
+% Contribution of hippocampal place cell activity to learning and
+% formation of goal-directed navigation in rats. \textit{Neuroscience}
+% 117, 1025--1035.
+%
+% \bibitem{}
+% Text
+% \end{thebibliography}
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Or, to use BibTeX:
+%
+% Follow these steps
+%
+% 1. Type in \bibliography{<name of your .bib file>} 
+%    Run LaTeX on your LaTeX file.
+%
+% 2. Run BiBTeX on your LaTeX file.
+%
+% 3. Open the new .bbl file containing the reference list and
+%   copy all the contents into your LaTeX file here.
+%
+% 4. Run LaTeX on your new file which will produce the citations.
+%
+% AGU does not want a .bib or a .bbl file. Please copy in the contents of your .bbl file here.
+
+%% After you run BibTeX, Copy in the contents of the .bbl file here:
 
@@
 \end{thebibliography}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Track Changes:
+% To add words, \added{<word added>}
+% To delete words, \deleted{<word deleted>}
+% To replace words, \replace{<word to be replaced>}{<replacement word>}
+% To explain why change was made: \explain{<explanation>} This will put
+% a comment into the right margin.
 
-\clearpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% At the end of the document, use \listofchanges, which will list the
+% changes and the page and line number where the change was made.
+
+% When final version, \listofchanges will not produce anything,
+% \added{<word or words>} word will be printed, \deleted{<word or words} will take away the word,
+% \replaced{<delete this word>}{<replace with this word>} will print only the replacement word.
+%  In the final version, \explain will not print anything.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%
+%\listofchanges
+%%%
 

### 2016-10-19 paper/paper.template.tex
Now with table included

@@
 \begin{keypoints}
-\item = enter point 1 here = 
-\item = enter point 2 here = 
-\item = enter point 3 here = 
+\item Hourly averages are required to show a statistically significant mass density response during high geomagnetic activity
+
+\item The response of mass density for high geomagnetic activity intervals is strongest when F10.7 is elevated
+
+\item There is no solar wind variation signature associated with large mass density events 
 \end{keypoints}
@@
 	\centering
-	\input{../tables/DeltaBootstraps-case10.txt}
+	\begin{tabular}{|c|cc|}
+		\hline 
+		Days & Difference (amu/cm$^3$) & \%  \\ \hline
+		-1 0 & -4.48 & $10.90\%\geq 0$  \\ 
+		-1 1 & -1.46 & $34.30\%\geq 0$  \\ 
+		1 0 & -3.02 & $21.50\%\geq 0$  \\ 
+		\hline
+	\end{tabular}
 	\caption{Results of test on of medians of $\rho_{eq}$ shown in the top panel of Figure~\ref{fig:DailyAveragedDstEvents} between days of threshold crossing  near (day = 1 or -1) or on the day of a $D_{st}$ event (day = 0).}
